\section{Abigail\textsuperscript{4} (Simonds) Rogan}

\ref{per:Abigail4Simonds}.\ \MainPerson{Abigail\textsuperscript{4} Simonds} (\Lineage{3}{Margaret}, \Lineage{2}{Abigail}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts, on 23 January 1867.\cite{Abigail4SimondsBirth} She died in Dedham, Norfolk County, Massachusetts, on 8 May 1958.\cite{Abigail4SimondsDeath} She married, in Boston on 13 April 1890, \MainPerson{John H.\ Rogan}. He was born in Massachusetts from 1866-1867 to William and Mary (\_\_\_\_\_) Rogan.\cite{Census1880JohnRogan} He died sometime before 1958.\cite{Abigail4SimondsDeath}

In 1900, Abigail and John were living with their three children at 21 Murdock St.\ in Somerville, Middlesex County, Massachusetts. John's occupation is listed as ``printer.''\cite{Census1900AbigailSimonds} The 1910 census shows the family had returned to Boston.\cite{Census1910AbigailSimonds} By 1930, John was not living in Abigail's household. Abigail was on Holmes St.\ in Boston with her daughters Abigail, Mary, and Anna, all three of them working for the telephone company.\cite{Census1930AbigailSimonds} It's possible that Abigail's husband John was the newspaper printer boarding at 95 Waltham St.\ in Boston.\cite{Census1930JohnRogan}

\begin{KidsIntro}
	Children of John H.\ Rogan and Abigail\textsuperscript{4} (Simonds) Rogan:
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{William H.\textsuperscript{5} Rogan}, b.\ Chelsea, Suffolk Co., Mass., 22 Jan.\ 1891;\cite{William5RoganBirth} d.\ Broward Co., Fla., 1 Jan.\ 1963;\cite{William5RoganDeath,William5RoganHeadstone} m.\ Manhattan, Kings Co., N.Y., 18 Aug.\ 1918, \KidName{Irene Hickey}.\cite{William5RoganMarriage} William served in the U.S.\ Navy during WWI.\cite{William5RoganHeadstone}
	
	\KidNum{}{ii.}\KidName{Marguerite E.\ Rogan}, b. Chelsea, 28 Apr.\ 1893;\cite{Marguerite5RoganBirth} m.\ \KidName{John J.\ Shea}.\cite{Census1940Marguerite5Rogan}
	
	\KidNum{}{iii.}\KidName{Abigail Josephine ``Abbie'' Rogan}, b.\ Chelsea, 26 Jan.\ 1898;\cite{Abigail5RoganBirth} d.\ Dedham, 9 March 1960; unm.\cite{Abigail5RoganDeath}
	
	\KidNum{}{iv.}\KidName{Mary Alice Rogan}, b.\ Boston, 13 June 1904;\cite{Mary5RoganBirth} d.\ Dedham, 8 Sept.\ 1971; unm.\cite{Mary5RoganDeath}
	
	\KidNum{}{v.}\KidName{Anne Irene Rogan}, b.\ Boston, 2 Nov.\ 1907;\cite{Anne5RoganBirth} d.\ Louisville, Jefferson Co., Ky., 10 Dec.\ 2001;\cite{Anne5RoganDeath} m.\ \KidName{John P.\ Doran}.\cite{Census1940Anne5Rogan}
\end{Kids}