\section{Albert Francis Wickens}\label{per:Albert4Wickens}

\MainPerson{Albert Francis\textsuperscript{4} Wickens}\index{Wickens!Albert Francis\textsuperscript{4}|bb} (\Lineage{3}{Frances}, \Lineage{2}{Michael}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 7 May 1898.\cite{Albert4WickensBirth} He died in Plainfield, Union County, New Jersey,\index{New Jersey!Plainfield} on 17 September 1977.\cite{Albert4WickensDeath,Albert4WickensDeath2} He married, in New Jersey\index{New Jersey} on 13 June 1922, \MainPerson{Mary Helen Schaller}.\index{Schaller!Mary Helen}\index{Wickens!Mary Helen (Schaller)}\cite{Albert4WickensMarriage} She was born in New York\index{New York} on 24 October 1892\cite{MarySchallerDeath,Census1900MarySchaller} to Frank Xavier Schaller\index{Schaller!Frank Xavier} and Anna (Schauer) Schaller.\index{Schaller!Anna (Schauer)}\index{Schauer!Anna}\cite{Census1900MarySchaller,MarySchallerParents} She died in Rahway, Union County, New Jersey,\index{New Jersey!Rahway} on 8 April 1984.\cite{MarySchallerDeath,MarySchallerDeath2}

In the 1930 census, Albert\index{Wickens!Albert Francis\textsuperscript{4}|bb} and family were living in Newark, Essex County, New Jersey,\index{New Jersey!Newark} where Albert was working as a shipping clerk\index{shipping clerk} at an automobile factory.\index{automobile manufacturing}\cite{Census1930AlbertWickens} In 1940 the family was still in Newark and Albert was working as a deputy tax collector\index{tax collector} at city hall.\cite{Census1940AlbertWickens}

\begin{KidsIntro}
	Children of Albert Francis\textsuperscript{4} Wickens\index{Wickens!Albert Francis\textsuperscript{4}|bb} and Mary Helen (Schaller) Wickens:\index{Schaller!Mary Helen}\index{Wickens!Mary Helen (Schaller)}
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{Mary E.\textsuperscript{5} Wickens}\index{Wickens!Mary E.\textsuperscript{5}}
	
	\KidNum{}{ii.}\KidName{Barbara Wickens}\index{Wickens!Barbara\textsuperscript{5}}
	
	\KidNum{}{iii.}\KidName{Albert Wickens}\index{Wickens!Albert\textsuperscript{5}}
	
	\KidNum{}{iv.}\KidName{Paul Wickens}\index{Wickens!Paul\textsuperscript{5}}
	
	\KidNum{}{v.}\KidName{Jean Wickens}\index{Wickens!Jean\textsuperscript{5}}
	
	\KidNum{}{vi.}\KidName{Joseph Wickens}\index{Wickens!Joseph\textsuperscript{5}}
	
	\KidNum{}{vii.}\KidName{John Wickens}\index{Wickens!John\textsuperscript{5}}
	
	\KidNum{}{viii.}\KidName{James Wickens}\index{Wickens!James\textsuperscript{5}}
\end{Kids}

