\section{Beatrice Field (O'Brien) Brady}\label{per:Beatrice4OBrien}

\MainPerson{Beatrice Field\textsuperscript{4} O'Brien}\index{O'Brien!Beatrice Field\textsuperscript{4}|bb}\index{Brady!Beatrice Field\textsuperscript{4} (O'Brien)} (\Lineage{3}{Edward}, \Lineage{2}{Michael}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 11 August 1919.\cite{Beatrice4OBrienBirth} She died in Needham, Norfolk County, Massachusetts,\index{Massachusetts!Needham} on 29 June 1976.\cite{Beatrice4OBrienDeath} She married, in Boston in 1941, \MainPerson{John Francis Brady}.\index{Brady!John Francis}\cite{Beatrice4OBrienMarriage} He was born in Boston on 1 June 1914 to Patrick Brady\index{Brady!Patrick} and Delia (Burke) Brady.\index{Brady!Delia (Burke)}\index{Burke!Delia}\cite{JohnBradyDraft,Census1920JohnBrady,PatrickBradyMarriage} He died in Milton, Norfolk County, Massachusetts,\index{Massachusetts!Milton} on 14 March 1983.\cite{JohnBradyDeath}

In 1951, Beatrice and John were living in West Roxbury. John was working as a maintenance electrician for the MTA (the Boston transit system now known as the MBTA).\cite{JohnBrady1951,HistoryoftheT} In 1965, the family was still living in West Roxbury, and John was working as an electrician for the Boston Housing Authority.\cite{JohnBrady1965} The family likely relocated to Milton, then Norwell and Green Harbor.\cite{Beatrice4OBrienObit}

\begin{KidsIntro}
	Children of John F.\ Brady\index{Brady!John Francis} and Beatrice F.\textsuperscript{4} (O'Brien) Brady:\index{O'Brien!Beatrice Field\textsuperscript{4}}\index{Brady!Beatrice Field\textsuperscript{4} (O'Brien)}
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{$\bullet$}\KidName{Joan\textsuperscript{5} Brady}\index{Brady!Joan\textsuperscript{5}}
	
	\KidNum{}{$\bullet$}\KidName{Walter Brady}\index{Brady!Walter\textsuperscript{5}}
	
	\KidNum{}{$\bullet$}\KidName{Paul Brady}\index{Brady!Paul\textsuperscript{5}}
	
	\KidNum{}{$\bullet$}\KidName{Beatrice Brady}\index{Brady!Beatrice\textsuperscript{5}}
\end{Kids}

