\section{Caroline Emma (Fernald) McGurin}

\MainPerson{Caroline\textsuperscript{4} Fernald}\index{Fernald!Caroline Emma\textsuperscript{4}|bb}\index{McGurin!Caroline Emma\textsuperscript{4} (Fernald)|bb} (\Lineage{3}{Margaret}, \Lineage{2}{Abigail}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 16 March 1876.\cite{Caroline4FernaldBirth} She died in Everett, Middlesex County, Massachusetts,\index{Massachusetts!Everett} on 28 August 1927.\cite{Caroline4FernaldDeath} She married, in Everett on 19 October 1893, \MainPerson{John Joseph McGurin}.\index{McGurin!John Joseph} He was born, in Boston on 22 January 1875, to William P.\ McGurin\index{McGurin!William P.} and Harriet F.\ (Saunders) McGurin.\index{McGurin!Harriet F.\ (Saunders)}\index{Saunders!Harriet F.}\cite{JohnMcGurinBirth,WilliamMcGurinMarriage} He died in Marshfield,\index{Massachusetts!Marshfield} Plymouth County, Massachusetts, on 10 January 1968.\cite{JohnMcGurinDeath}

\begin{KidsIntro}
	Children of William P.\ McGurin\index{McGurin!William P.} and Caroline\textsuperscript{4} (Fernald) McGurin:\index{Fernald!Caroline Emma\textsuperscript{4}|bb}\index{McGurin!Caroline Emma\textsuperscript{4} (Fernald)|bb}
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{Robert Alexander\textsuperscript{5} McGurin},\index{McGurin!Robert Alexandar\textsuperscript{5}} b.\ Everett,\index{Massachusetts!Everett} 13 April 1894;\cite{Robert5McGurinBirth} d.\ Everett, 1955;\cite{Robert5McGurinDeath} m.\ Boston,\index{Massachusetts!Boston} 7 July 1913, \KidName{Alta M.\ Saunders}.\index{Saunders!Alta M.}\index{McGurin!Alta M.\ (Saunders)}\cite{Robert5McGurinMarriage}
	
	\KidNum{}{ii.}\KidName{Walter Edward McGurin},\index{McGurin!Walter Edward\textsuperscript{5}} b.\ Boston,\index{Massachusetts!Boston} 2 May 1896;\cite{Walter5McGurinBirth} d.\ Stoneham,\index{Massachusetts!Stoneham} Middlesex Co., Mass., 29 March 1974;\cite{Walter5McGurinDeath} m.\ \KidName{Bernice L.\ Wood}.\index{Wood!Bernice L.}\index{McGurin!Bernice L.\ (Wood)}\cite{Walter5McGurinDeath}
	
	\KidNum{}{iii.}\KidName{Alfred John McGurin},\index{McGurin!Alfred John\textsuperscript{5}} b.\ Boston,\index{Massachusetts!Boston} 5 April 1898;\cite{Alfred5McGurinBirth} d.\ Montfaucon,\index{France!Montfaucon} France, 22 Oct.\ 1918.\cite{Alfred5McGurinDeath} Alfred was killed in action while serving with the 55th Artillery at the Battle of Verdun.\cite{Alfred5McGurinDeath2}\index{France!Verdun}\index{World War I}\index{Verdun (battle)}
	
	\KidNum{}{iv.}\KidName{Margaret A.\ McGurin},\index{McGurin!Margaret A.\textsuperscript{5}}\index{Phillips!Margaret A.\textsuperscript{5} (McGurin)} b.\ Boston,\index{Massachusetts!Boston} 27 Dec.\ 1899;\cite{Margaret5McGurinBirth} d.\ Everett,\index{Massachusetts!Everett} 17 Nov.\ 1992;\cite{Margaret5McGurinDeath} m.\ \KidName{Henry J.\ Phillips Sr.}\index{Phillips!Henry J. Sr.}\cite{Margaret5McGurinDeath}
	
	\KidNum{}{v.}\KidName{Sarah H.\ ``Sadie'' McGurin},\index{McGurin!Sarah/Sadie H.\textsuperscript{5}}\index{Murphy!Sarah/Sadie H.\textsuperscript{5}} b.\ Boston,\index{Massachusetts!Boston} 8 July 1901;\cite{Sarah5McGurinBirth} d.\ Saugus,\index{Massachusetts!Saugus} Essex Co., Mass., 6 Jan.\ 1999;\cite{Sarah5McGurinDeath} m.\ \KidName{James P.\ Murphy}.\index{Murphy!James P.}\cite{Sarah5McGurinDeath}
	
	\KidNum{}{vi.}\KidName{Edward Joseph McGurin},\index{McGurin!Edward Joseph\textsuperscript{5}} b.\ Boston,\index{Massachusetts!Boston} 18 Dec.\ 1902;\cite{Edward5McGurinBirth} d.\ Ft.\ Lauderdale,\index{Florida!Ft.\ Lauderdale} Broward Co., Fla.;\cite{Edward5McGurinDeath} m.\ Boston, 8 Oct.\ 1922, \KidName{Helen Duffy}.\index{Duffy!Helen}\index{McGurin!Helen (Duffy)}\cite{Edward5McGurinMarriage}
	
	\KidNum{}{vii.}\KidName{Caroline Josephine McGurin},\index{McGurin!Caroline Josephine\textsuperscript{5}} b.\ Boston,\index{Massachusetts!Boston} 2 July 1904;\cite{Caroline5McGurinBirth} d.\ Boston, 2 April 1921; unm.\cite{Caroline5McGurinDeath}
	
	\KidNum{}{viii.}\KidName{Catherine McGurin},\index{McGurin!Catherine\textsuperscript{5}} b. Boston, 9 Sept.\ 1906;\cite{Catherine5McGurinBirth} d.\ Everett, 17 Dec.\ 1999;\cite{Catherine5McGurinDeath} m.\ \KidName{Francis Kelleher}.\cite{Catherine5McGurinDeath}
	
	\KidNum{}{ix.}\KidName{Josephine McGurin},\index{McGurin!Josephine\textsuperscript{5}} b.\ Boston,\index{Massachusetts!Boston} 30 Dec.\ 1908;\cite{Josephine5McGurinBirth} d.\ Boston, 18 May 1926; unm.\cite{Josephine5McGurinDeath}
	
	\KidNum{}{x.}\KidName{John Francis McGurin},\index{McGurin!John Francis\textsuperscript{5}} b.\ Boston,\index{Massachusetts!Boston} 2 April 1914;\cite{John5McGurinBirth} d.\ South Dennis,\index{Massachusetts!South Dennis} Barnstable Co., Mass., 3 Dec.\ 2005;\cite{John5McGurinDeath} m.\ \KidName{Beatrice M.\ Tassinari}.\index{Tassarini!Beatrice M.}\index{McGurin!Beatrice M.\ (Tassarini)}\cite{John5McGurinDeath}
	
	\KidNum{}{xi.}\KidName{Charles Alford McGurin},\index{McGurin!Charles Alford\textsuperscript{5}} b.\ Boston,\index{Massachusetts!Boston} 17 Aug.\ 1916;\cite{Charles5McGurinBirth} d.\ Peabody,\index{Massachusetts!Peabody} Essex Co., Mass., 18 Dec 2004;\cite{Charles5McGurinDeath} m.\ \KidName{Cecelia Mullen}.\index{Mullen!Cecelia}\index{McGurin!Cecelia (Mullen)}\cite{Charles5McGurinDeath}
\end{Kids}