\section{Catherine Mary (O'Brien) MacDonald}\label{per:Catherine4OBrien}

\MainPerson{Catherine Mary\textsuperscript{4} O'Brien}\index{O'Brien!Catherine Mary\textsuperscript{4}|bb}\index{MacDonald!Catherine Mary\textsuperscript{4} (O'Brien)} (\Lineage{3}{Edward}, \Lineage{2}{Michael}, \Lineage{1}{William}) was born in Hartford, Hartford County, Connecticut,\index{Connecticut!Hartford} in 1910.\cite{Census1910Edward3OBrien:2,Census1920Edward3OBrien,Catherine4OBrienMarriage} She died in Milton, Norfolk County, Massachusetts,\index{Massachusetts!Milton} on 27 April 1964.\cite{Catherine4OBrienDeath:1} She married, in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 2 October 1937, \MainPerson{Frederick Augustus MacDonald Jr.}\index{MacDonald!Frederick Augustus (1908--1983)}\cite{Catherine4OBrienMarriage,Catherine4OBrienMarriage2:1} They were married by Catherine's uncle, Walter H.\ Gill,\index{Gill!Walter H.} a priest in Brockton, Plymouth County, Massachusetts.\index{Massachusetts!Brockton}\cite{Catherine4OBrienMarriage2:2,Catherine4OBrienDeath:2} Frederick was born in Hyde Park, Norfolk County, Massachusetts\index{Massachusetts!Hyde Park}\index{Massachusetts!Boston!Hyde Park} (now part of the City of Boston\cite{HydePark}) on 22 October 1908 to Frederick MacDonald\index{MacDonald!Frederick Augustus (1877--1943)} and Jane A.\ (Kelley) MacDonald.\index{MacDonald!Jane A.\ (Kelley)}\index{Kelley!Jane A.}\cite{FrederickMacDonaldBirth,FrederickMacDonaldDraft} He died in Weymouth, Norfolk County, Massachusetts,\index{Massachusetts!Weymouth} on 11 November 1983.\cite{FrederickMacDonaldDeath:1}

Catherine\index{O'Brien!Catherine Mary\textsuperscript{4}}\index{MacDonald!Catherine Mary\textsuperscript{4} (O'Brien)} was a teacher\index{teacher} when she married in 1937.\cite{Catherine4OBrienMarriage2:3} Frederick\index{MacDonald!Frederick Augustus (1908--1983)} graduated from the Massachusetts Institute of Technology\index{Massachusetts Institute of Technology} and was an architect\index{architect} for the First National Bank of Boston.\index{First National Bank of Boston}\cite{FrederickMacDonaldDeath:2}

\begin{KidsIntro}
	Children of Frederick A.\ MacDonald\index{MacDonald!Frederick Augustus (1908--1983)} and Catherine M.\textsuperscript{4} (O'Brien) MacDonald:\index{O'Brien!Catherine Mary\textsuperscript{4}}\index{MacDonald!Catherine Mary\textsuperscript{4} (O'Brien)}
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{Jane Marie\textsuperscript{5} MacDonald}\index{MacDonald!Jane Marie\textsuperscript{5}}
	
	\KidNum{}{ii.}\KidName{Frederick Augustus\ MacDonald Jr.}\index{MacDonald!Frederick Augustus\textsuperscript{5}}
\end{Kids}