\section{Catharine (Simonds) McCarthy}

\MainPerson{Catharine\textsuperscript{4} Simonds}\index{Simonds!Catharine\textsuperscript{4}|bb}\index{McCarthy!Catharine\textsuperscript{4} (Simonds)|bb} (\Lineage{3}{Margaret}, \Lineage{2}{Abigail}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 10 December 1860.\cite{Catharine4SimondsBirth} She died in Boston on 24 February 1890.\cite{Catharine4SimondsDeath} She married, in Boston on 7 April 1879, \MainPerson{John F.\ McCarthy}.\index{McCarthy!John F. (husband of Catharine (Simonds))}\cite{JohnMcCarthyMarriage} He was born in Ireland\index{Ireland} about 1858 to John McCarthy\index{McCarthy!John (father of John F.)} and Ellen (\_\_\_\_\_) McCarthy.\index{McCarthy!Ellen (\_\_\_\_\_)}\index{_@Unknown surnames!Ellen (mother of John F.\ McCarthy)}\cite{JohnMcCarthyMarriage} The time and location of his death are unknown.

Catharine\index{Simonds!Catharine\textsuperscript{4}|bb}\index{McCarthy!Catharine\textsuperscript{4} (Simonds)|bb} was baptized at St. Stephen Church\index{St. Stephen's (church)} in Boston\index{Massachusetts!Boston} on 22 December 1860.\cite{Catharine4SimondsBaptism} After her marriage, Catharine and John\index{McCarthy!John F. (husband of Catharine (Simonds))} were living at 146 Marginal St.\ in East Boston.\index{Massachusetts!Boston!Marginal St.}\index{Massachusetts!Boston!East Boston} Next door at 148 Marginal St.\ were Catharine's mother, Margaret (Dooley) Fernald,\index{Dooley!Margaret\textsuperscript{3}}\index{Simonds!Margaret\textsuperscript{3} (Dooley)}\index{Fernald!Margaret\textsuperscript{3} (Dooley) (Simonds)} and her grandmother, Abigail (O'Brien) Dooley.\index{O'Brien!Abigail\textsuperscript{2}}\index{Dooley!Abigail\textsuperscript{2} (O'Brien)} Catharine's husband John's occupation is listed as ``painter.''\index{painter}\cite{Census1880Catharine4Simonds}

\begin{KidsIntro}
	Child of John F.\ McCarthy\index{McCarthy!John F. (husband of Catharine (Simonds))} and Catharine\textsuperscript{4} (Simonds) McCarthy:\index{Simonds!Catharine\textsuperscript{4}|bb}\index{McCarthy!Catharine\textsuperscript{4} (Simonds)|bb}
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{Helen\textsuperscript{5} McCarthy},\index{McCarthy!Helen\textsuperscript{5}}\index{Westlake!Helen\textsuperscript{5} (McCarthy)} b.\ Boston, 23 June 1879;\cite{Helen5McCarthyBirth} d.\ Medford,\index{Massachusetts!Medford} Middlesex Co., Mass., 17 April 1966;\cite{Helen5McCarthyDeath} m.\ Boston, 9 Aug.\ 1899, \KidName{William H.\ Westlake}.\index{Westlake!William H.}\cite{Helen5McCarthyMarriage}

\begin{GrandkidsIntro}
	Child of William H.\ Westlake and Helen\textsuperscript{5} (McCarthy) Westlake:
\end{GrandkidsIntro}

\begin{Grandkids}		
	\GrandkidNum{1.}\GrandkidName{William Atwell Westlake},\index{Westlake!William Atwell\textsuperscript{6}} b.\ Boston, 17 July 1900,\cite{William5WestlakeBirth} d.\ Medford,\index{Massachusetts!Medford} Middlesex Co., Mass., 1 Jan.\ 1926; unm.\cite{William5WestlakeDeath} William was a clerk in the shopping card department at Filene's\index{Filene's department store} department store. He drowned in upper Mystic Lake\index{Mystic Lake} while ice skating on the morning of New Year's Day.\cite{William5WestlakeDeath}
\end{Grandkids}

\end{Kids}


