\section{Edith A.\ (Wickens) Giguere}\label{per:Edith4Wickens}

\MainPerson{Edith A.\textsuperscript{4} Wickens}\index{Wickens!Edith A.\textsuperscript{4}|bb}\index{Giguere!Edith A.\textsuperscript{4} (Wickens)|bb} (\Lineage{3}{Frances}, \Lineage{2}{Michael}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 22 July 1894.\cite{Edith4WickensBirth} She died in Detroit, Wayne County, Michigan,\index{Michigan!Detroit} on 9 February 1957.\cite{Edith4WickensDeath} She married, in Boston on 12 October 1913, \MainPerson{George Hector Giguere}.\index{Giguere!George Hector|bb}\cite{Edith4WickensMarriage} He was born in Holyoke, Hampden County, Massachusetts,\index{Massachusetts!Holyoke} on 25 February 1893 to John B.\ Giguere\index{Giguere!John B.} and Corinne (Lecours) Giguere.\index{Giguere!Corinne (Lecours)}\index{Lecours!Corinne}\cite{GeorgeGiguereBirth} He died in Detroit, Wayne County, Michigan,\index{Michigan!Detroit} on 19 July 1974.\cite{GeorgeGiguereDeath}

By 1930 the family had moved from Boston to Detroit. George was working as a consulting engineer.\index{engineer} The family owned their home, worth \$11,000, at 13002 Greiner Ave.\cite{Census1930GeorgeGiguere}

\begin{KidsIntro}
	Children of George H.\ Giguere and Edith A.\ (Wickens) Giguere:
\end{KidsIntro}

\begin{Kids}
	
	\KidNum{}{i.}\KidName{George Elmer\textsuperscript{5} Giguere},\index{Giguere, George Elmer\textsuperscript{5}}\index{Giguere, Elmer\textsuperscript{5}} b.\ Boston, 17 Jul 1914;\cite{ElmerGiguereBirth} d.\ Boston, 7 May 1916.\cite{ElmerGiguereDeath}
	
	\KidNum{}{ii.}\KidName{Robert E.\ Giguere},\index{Giguere!Robert E.\textsuperscript{5}} b.\ Boston,\index{Massachusetts!Boston} 17 Dec.\ 1915;\cite{Robert5GiguereDeath:1} d.\ Boston, 26 Sept.\ 1916.\cite{Robert5GiguereDeath:2}
	
	\KidNum{}{iii.}\KidName{Dorris Marjorie Giguere},\index{Giguere!Dorris Marjorie\textsuperscript{5}}\index{May!Dorris Marjorie\textsuperscript{5} (Giguere)}\index{Meyers!Dorris Marjorie\textsuperscript{5} (Giguere) (May)}\index{Leonard!Dorris Marjorie\textsuperscript{5} (Giguere) (May) (Meyers)} b.\ Boston\index{Massachusetts!Boston} 23 March 1917;\cite{JohnMeyersMarriage:1} d.\ Bruce, Macomb Co., Mich.,\index{Michigan!Bruce} 10 July 1981;\cite{Dorris5GiguereMichiganDeath} m.\ (1) Detroit,\index{Michigan!Detroit} 17 July 1943, \KidName{Robert C.\ May};\index{May!Robert C.}\cite{RobertMayMarriage} m.\ (2) Steuben Co., Ind.,\index{Indiana!Steuben County} 6 July 1950, \KidName{John E.\ Meyers}\index{Meyers!John E.};\cite{JohnMeyersMarriage:2} m.\ (3) \KidName{Joseph Leonard}.\index{Leonard!Joseph}\cite{Dorris5GiguereObit}
\end{Kids}