\section{Ethel Mary (Wickens) Heuman}\label{per:Ethel4Wickens}

\MainPerson{Ethel Mary\textsuperscript{4} Wickens}\index{Wickens!Ethel Mary\textsuperscript{4}|bb}\index{Heuman!Ethel Mary\textsuperscript{4} (Wickens)} (\Lineage{3}{Frances}, \Lineage{2}{Michael}, \Lineage{1}{William}) was born on 17 June 1902 in Boston, Suffolk County, Massachusetts.\index{Massachusetts!Boston}\cite{Ethel4WickensBirth} She died on 27 July 1967 in Macomb, Macomb County, Michigan.\index{Michigan!Macomb}\cite{Ethel4WickensDeath} She married, on 20 September 1923 in Wayne County, Michigan,\index{Michigan!Wayne County} \MainPerson{Harold Edward Heuman}.\index{Heuman!Harold Edward}\cite{Ethel4WickensMarriage} He was born on 12 May 1902 in Chicago, Cook County, Illinois\index{Illinois!Chicago}\cite{HaroldHeumanDeath:1,HaroldHeumanDraft} to John Heuman\index{Heuman!John} and Augusta (Martin) Heuman.\index{Heuman!Augusta (Martin)}\index{Martin!Augusta}\cite{Census1910HaroldHeuman,GraceHeumanBirth} He died in Clinton, Macomb County, Michigan,\index{Michigan!Clinton} on 10 May 1993.\cite{HaroldHeumanDeath:2}

In the 1940 census, the family was living in Mount Clemens, Macomb County, Michigan,\index{Michigan!Mount Clemens} where Harold was working as a plant policeman\index{policeman} at an automobile manufacturing company.\index{automobile manufacturing}\cite{Census1940HaroldHeuman}

\begin{KidsIntro}
	Children of Harold E.\ Heuman\index{Heuman!Harold Edward} and Ethel Mary\textsuperscript{4} (Wickens) Heuman:\index{Wickens!Ethel Mary\textsuperscript{4}}\index{Heuman!Ethel Mary\textsuperscript{4} (Wickens)}
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{Virginia\textsuperscript{5} Heuman}\index{Heuman!Virginia\textsuperscript{5}}
	
	\KidNum{}{ii.}\KidName{Edward Heuman}\index{Heuman!Edward\textsuperscript{5}}
	
	\KidNum{}{iii.}\KidName{Harold Heuman Jr.}\index{Heuman!Harold\textsuperscript{5}, Jr.}
\end{Kids}