\section{Francis Joseph O'Brien}

\ref{per:Francis4OBrien}.\ \MainPerson{Francis Joseph\textsuperscript{4} ``Frank'' O'Brien} (\Lineage{2-3}{John}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts, on 2 April 1892.\cite{Francis4OBrienBirth} He died in Malden, Middlesex County, Massachusetts, on 4 February 1958.\cite{Francis4OBrienDeath} He married, in Malden on 12 September 1921, \MainPerson{Mary Helena Flynn} (aka Helena Catherine Flynn).\cite{Francis4OBrienMarriageCert} She was born in Charlottetown, Queens County, Prince Edward Island, Canada, on 27 April 1892 to Thomas Flynn and Mary Ann Greenan.\cite{MaryFlynnBirth} She died in Malden on 19 April 1981.\cite{MaryFlynnDeath}

Frank worked for the Boston and Maine (B\&M) Railroad, first in the Accounting Department\cite{Francis4OBrienAccounting} and later as Inspector of Transportation.\cite{Francis4OBrienInspector} A member of the Brotherhood of Railway Clerks, North Union Lodge, he was known as the ``lodge poet.'' Frank would write poems for each lodge member at the annual banquet.\cite{Francis4OBrienPoet} He was also a member of the B.\ P.\ O.\ E.\ (Elks), Medford Lodge \#915.\cite{Francis4OBrienBPOE}

\begin{KidsIntro}
	Children of Francis Joseph\textsuperscript{4} O'Brien and Mary Helena (Flynn) O'Brien:
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{Francis Joseph\textsuperscript{5} ``Frank'' O'Brien Jr.}
	%, b.\ Melrose, Middlesex Co., Mass., 8 Dec.\ 1922;\cite{Francis5OBrienBirth} d.\ Tampa, Hillsborough Co., Fla., 19 Oct.\ 2015;\cite{Francis5OBrienDeath} m.\ Andover, Essex Co., Mass., 10 June 1950, \KidName{Marie Eastwood}.\cite{Francis5OBrienMarriage} Frank graduated from Brown University and Tufts University School of Dental Medicine, practicing dentistry in Whitman, Mass., for 37 years.\cite{Francis5OBrienDeath}
	
	\KidNum{}{ii.}\KidName{Pauline M.\ O'Brien}
	
	\KidNum{}{iii.}\KidName{Mildred O'Brien}
	
	\KidNum{}{iv.}\KidName{Helena O'Brien}
	
	\KidNum{}{v.}\KidName{Therese Celine O'Brien}
\end{Kids}