\begin{thebibliography}{999}
	
% Generation 4

%% Catharine Simonds

\bibitem{Catharine4SimondsBirth}
Boston, Massachusetts Vital Records, Birth Records, 1860, no.\ 3592, Catharine Simons; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 28 Apr 2020), Boston > Births, Marriages and Death > image 54601.

\bibitem{Catharine4SimondsDeath}
Massachusetts Vital Records, Death Records, 1890, no.\ 1930, Catharine McCarthy m.n.\ Simonds; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 28 Apr 2020), \_Pre 1903 > 1890 > image 1087.

\bibitem{JohnMcCarthyMarriage:1}
Massachusetts Vital Records, Marriage Records, 1879, no.\ 560, John McCarthy and Catharine Simons; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 28 Apr 2020), \_Up Through 1910 > 1879 > image 757.

\bibitem{JohnMcCarthyMarriage:2}
Massachusetts Vital Records, Marriage Records, 1879, no.\ 560, John McCarthy and Catharine Simons.

\bibitem{Catharine4SimondsBaptism}
St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 380, Catharine Simonds; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/380/1423783048} : viewed on 28 Apr 2020).

\bibitem{Census1880Catharine4Simonds}
1880 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 587, Boston, page no.\ 3, dwelling no.\ 15, family no.\ 23, Katie McCarthy in John F.\ McCarthy household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 28 Apr 2020), Massachusetts > Suffolk > Boston > 587 > image 3.

%% Abigail Simonds

\bibitem{Abigail4SimondsBirth}
Massachusetts Vital Records, Birth Records, 1867, no.\ 22, Abby Simonds; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 1 May 2020), \_up through 1910 > 1867 > image 762.

\bibitem{Abigail4SimondsDeath:1}
Abigail J. (Simonds) Rogan obituary, \textit{The Boston Globe}, 9 May 1958, p.\ 26; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50035569/the-boston-globe/?xid=637} : viewed on 1 May 2020).

\bibitem{Census1880JohnRogan}
1880 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 790, Chelsea, page no.\ 42, dwelling no.\ 337, family no.\ 472, John Rogan in William Rogan household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 1 May 2020), Massachusetts > Suffolk > Chelsea > 790 > image 42.

\bibitem{Abigail4SimondsDeath:2}
Abigail J. (Simonds) Rogan obituary, \textit{The Boston Globe}, 9 May 1958, p.\ 26.

\bibitem{Census1900AbigailSimonds}
1900 U.S.\ census, Middlesex County, Massachusetts, population schedule, Enumeration District (ED) 947, Somerville, sheet no.\ 3B, dwelling no.\ 51, family no.\ 58, John H.\ Rogan household; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 1 May 2020), Massachusetts > Middlesex > Somerville Ward 05 > District 0947.

\bibitem{Census1910AbigailSimonds}
1910 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 1269, Boston City, sheet no.\ 13B, dwelling no.\ 104, family no.\ 232, John H.\ Rogan household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 1 May 2020), Massachusetts > Suffolk > Boston Ward 2 > District 1269 > image 26.

\bibitem{Census1930AbigailSimonds}
1930 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 13-5, sheet no.\ 17A, dwelling no.\ 349, family no.\ 349, Abbigail J.\ Rogan household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 1 May 2020), Massachusetts > Suffolk > Boston (Districts 1-250) > District 0005 > image 33.

\bibitem{Census1930JohnRogan}
1930 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 13-117, sheet no.\ 17B, dwelling no.\ 216, family no.\ 249, John H.\ Rogan in Mabel F.\ Patton household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 1 May 2020), Massachusetts > Suffolk > Boston (Districts 1-250) > District 0117 > image 34.

%% Caroline Fernald

\bibitem{Caroline4FernaldBirth}
Massachusetts Vital Records, Birth Records, 1876, no.\ 4804, Caroline Fernald; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1876 > image 979.

\bibitem{Caroline4FernaldDeath}
``EAST BOSTON DISTRICT,'' \textit{The Boston Globe}, 31 Aug 1927, p.\ 5; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/24119074/the-boston-globe/?xid=637} : viewed on 2 May 2020).

\bibitem{JohnMcGurinBirth}
Massachusetts Vital Records, Birth Records, 1875, no.\ 2301, John McGurin; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1875 > image 965.

Boston, Massachusetts Vital Records, Marriage Records, 1873, no.\ 2252, William P McGurin and Harriet F Saunders; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495} : viewed on 16 Jul 2020), Boston > Boston Marriages, 1873 > image 134.

\bibitem{JohnMcGurinDeath}
John J.\ McGurin obituary, \textit{The Boston Globe}, 12 Jan 1968, p.\ 33; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50073830/obituary-for-john-j-mcgurin/?xid=637} : viewed on 2 May 2020).

%% Sarah Fernald

\bibitem{Sarah4FernaldBirth}
Massachusetts Vital Records, Birth Records, 1879, no.\ 2887, Sarah Fernald; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 6 May 2020), \_up through 1910 > 1879 > image 936.

\bibitem{Sarah4FernaldDeath}
Sarah H.\ Leonard obituary, \textit{The Boston Globe}, 26 Mar 1943, p.\ 21; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50391545/obituary-for-sarah-h-fernald-leonard/?xid=637} : viewed on 6 May 2020).

\bibitem{Sarah4FernaldMarriage:1}
Massachusetts Vital Records, Marriage Records, 1902, no.\ 4372, Christopher T Leonard and Sarah H Fernald; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 6 May 2020), \_up through 1910 > 1902 > image 1742.

\bibitem{ChristopherLeonardBirth}
Boston, Massachusetts Vital Records, Birth Records, 1872, no.\ 6431, Christopher Leonard; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 6 May 2020), Boston > Additions and Corrections to Births, 1870-1881 > image 57. Aug 24 crossed out and written Jul 29; typed: ``Bapt Rec''

\bibitem{Sarah4FernaldMarriage:2}
Massachusetts Vital Records, Marriage Records, 1902, no.\ 4372, Christopher T Leonard and Sarah H Fernald.

\bibitem{ChristopherLeonardDeath}
Christopher T. Leonard obituary, \textit{The Boston Globe}, 11 Sep 1945, p.\ 32; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50392156/obituary-for-christopher-t-leonard-in/?xid=637} : viewed on 6 May 2020).

%% Robert Fernald

\bibitem{Robert4FernaldBirth}
Massachusetts Vital Records, Birth Records, 1882, p.\ 123, no.\ 5520, Robert Atwell Fernald; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 10 May 2020), \_up through 1910 > 1882 > image 1104.

\bibitem{Robert4FernaldDeath:1}
Robert A.\ Fernald obituary, \textit{The Boston Globe}, 28 May 1965, p.\ 31; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50690743/obituary-for-robert-a-fernald-aged-82/?xid=637} : viewed on 10 May 2020).

\bibitem{Robert4FernaldMarriage:1}
Massachusetts Vital Records, Marriage Records, 1911, p.\ 160, no.\ 3670, Robert A Fernald and Agnes M Leonard; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 10 May 2020), 1911 > Boston > image 160.

\bibitem{AgnesLeonardBirth}
Boston, Massachusetts Vital Records, Birth Records, 1881, no.\ 3971, Agnes Leonard; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 10 May 2020), Boston > Births, Marriages and Death > image 58657.

\bibitem{Robert4FernaldMarriage:2}
Massachusetts Vital Records, Marriage Records, 1911, p.\ 160, no.\ 3670, Robert A Fernald and Agnes M Leonard.

\bibitem{AgnesLeonardDeath}
U.S.\ Social Security Administration, \textit{Death Master File} database, Agnes Fernald, Oct 1975; accessed at ``United States Social Security Death Index,'' database, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:J1Y2-Q2R} : viewed on 10 May 2020).

\bibitem{Robert4FernaldDeath:2}
Robert A.\ Fernald obituary, \textit{The Boston Globe}, 28 May 1965, p.\ 31.

%% Francis O'Brien

\bibitem{Francis4OBrienBirth}
Massachusetts Vital Records, Birth Records, 1892, no.\ 9515, Francis Joseph O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 10 May 2020), \_up through 1910 > 1892 > image 1606.

\bibitem{Francis4OBrienDeath}
Malden, Middlesex County, Massachusetts, City Vital Records, Standard Certificate of Death for Frank J. O'Brien, 1958, no.\ 72.

\bibitem{Francis4OBrienMarriageCert}
Massachusetts Vital Records, Copy of Certificate of Marriage, 1921, p.\ 307, no.\ 383, Francis Joseph O'Brien and Helena Catherine Flynn.

\bibitem{MaryFlynnBirth}
Government of Prince Edward Island, \textit{PARO Collections} database (\url{http://www.gov.pe.ca/parosearch/} : viewed on 10 May 2020), baptismal record of Mary Helena Flynn, citing St. Dunstan's Basilica, record book no.\ 5, p.\ 9.

\bibitem{MaryFlynnDeath}
Helena C.\ (Flynn) O'Brien obituary, \textit{The Boston Globe}, 21 Apr 1981, p.\ 22; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50697200/obituary-for-helena-c-obrien/?xid=637} : viewed on 10 May 2020).

\bibitem{Census1910Francis4OBrien}
1910 U.S. census, Middlesex County, Massachusetts, population schedule, town of Medford, enumeration district 928, sheet 7A, dwelling no.\ 117, family no.\ 140, Francis J.\ O'Brien in John J.\ O'Brien household; accessed at  ``1910 United States Federal Census,'' Ancestry.com (\url{https://www.ancestry.com/search/collections/7884} : viewed on 27 Mar 2021), Massachusetts > Middlesex > Medford Ward 2 > District 0928 > image 13; also, recollection of Pauline (O'Brien) Spencer, as told to Gavin O'Brien by phone call, 26 Mar 2021.

\bibitem{Francis4OBrienAccounting}
\textit{Boston and Maine Railroad Employees Magazine}, vol.\ 17, no.\ 5, May 1949, p.\ 30, accounting department photo showing Frank O'Brien; Boston \& Maine Railroad Historical Society, Lowell, Mass.

\bibitem{Francis4OBrienInspector}
\textit{Boston and Maine Railroad Employees Magazine}, vol.\ 19, no.\ 11, Nov 1951, p.\ 31, photo showing Frank O'Brien; Boston \& Maine Railroad Historical Society, Lowell, Mass.

\bibitem{Francis4OBrienPoet}
``B.\ of R.\ C.\ Installation,'' \textit{Boston and Maine Railroad Employees Magazine}, vol.\ 4, no.\ 11, Feb 1928, p.\ 28; Boston \& Maine Railroad Historical Society, Lowell, Mass.

\bibitem{Francis4OBrienBPOE}
Deaths, ``MEDFORD LODGE \#915, B.\ P.\ O.\ E.,'' \textit{The Boston Globe}, 6 Feb 1958, p.\ 25; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50699087/the-boston-globe/?xid=637} : viewed on 10 May 2020).

%% Pauline O'Brien

\bibitem{Pauline4OBrienBirth}
Massachusetts Vital Records, Birth Records, 1894, p.\ 155 (stamped), no.\ 7033, Pauline O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 17 May 2020), \_up through 1910 > 1894 > image 1809.

\bibitem{Pauline4OBrienBaptism}
St. Peter (Dorchester) Baptisms, 1887-1895, p.\ 89, Paulina O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/57120/89/1426642661} : viewed on 17 May 2020).

\bibitem{Pauline4OBrienDeath}
U.S.\ Social Security Administration, \textit{Death Master File}, Pauline Baine, 1967; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 17 May 2020).


\bibitem{CharlesBaineMarriage:1}
Massachusetts vital records, certificate of marriage, Charles Lucius Baine and Pauline Mary O'Brien, 1930, vol.\ 45, no.\ 323.

\bibitem{CharlesBainePassport}
U.S.\ Department of State, ``Passport Applications, 1914-1925,'' Special Series: New York, vol.\ 4, application numbers 1 to 249, no.\ 51, application for Charles L.\ Baine; aaccessed at ``U.S. Passport Applications, 1795-1925,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/1174/} : viewed on 17 May 2020), Passport Applications: Chicago, New York City, New Orleans, San Francisco and Seattle, 1914-1925 > 1918-1919 > Volume 04: Special Series - New York > image 264.

\bibitem{Census1880CharlesBaine}
1880 U.S. census, Monroe County, New York, population schedule, Enumeration District (ED) 93, Rochester, p. 11, dwelling no.\ 105, family no.\ 113, William Baine household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 17 May 2020), New York > Monroe > Rochester > 093 > image 11.

Chicago, Illinois, Catholic Diocese, ``Old St. Stephen Chicago Baptism 1869-1915 N.I.,'' 1895, p.\ 131, Charles L. Baine on 15 Jul 1895; accessed at ``Illinois, Chicago, Catholic Church Records, 1833-1925,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:QVMJ-3Q37} : viewed on 17 Jul 2020), St Stephen Parish (Chicago: Old, Ohio St) > Baptisms, marriages 1869-1915 > image 137.

Massachusetts vital records, certificate of marriage, Charles Lucius Baine and Pauline Mary O'Brien, 1930, vol.\ 45, no.\ 323.

\bibitem{CharlesBaineDeath:1}
Charles L.\ Baine obituary, \textit{The Boston Globe}, 2 Mar 1962, p.\ 24; accessed at \textit{Newspapers.com} (\url{https://www.newspapers.com/clip/22565355/charles-l-baine-obituary/?xid=865} : viewed on 17 May 2020).

\bibitem{Gompers}
Samuel Gompers, edited by Peter J. Albert and Grace Palladino, \textit{The Samuel Gompers Papers: Progress and Reaction in the Age of Reform, 1909-1913} (Urbana and Chicago: University of Illinois Press, 2000), pp.\ 415--416; accessed at \textit{Google Books} (\url{https://books.google.com/books?id=5IYsQ\_8fSIoC\&lpg=PA416\&ots=oQa308V0UG\&dq=samuel\%20gompers\%20charles\%20baine\&pg=PA416\#v=onepage\&q=samuel\%20gompers\%20charles\%20baine\&f=false} : viewed on 17 May 2020).

\bibitem{Pauline4OBrienDeath2}
Pauline M.\ Baine obituary, \textit{The Boston Globe}, 3 Feb 1967, p.\ 30; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/46653093/obituary-for-pauline-m-baine/?xid=637} : viewed on 17 May 2020).

\bibitem{CharlesBaineDeath:2}
Charles L.\ Baine obituary, \textit{The Boston Globe}, 2 Mar 1962, p.\ 24.

%% Mildred O'Brien

\bibitem{Mildred4OBrien2Birth}
Massachusetts Vital Records, Birth Records, 1896, p.\ 169, no.\ 7598, Mildred O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 17 May 2020), \_up through 1910 > 1896 > image 2036.

\bibitem{Mildred4OBrien2Death}
Boston, Suffolk County, Massachusetts, ``Standard Certificate of Death'' for Mildred French, 1927, no.\ 1911.

\bibitem{Mildred4OBrienMarriage}
``YOUNG COUPLES WHO SELECTED FEBRUARY AS WEDDING MONTH,'' \textit{The Boston Globe}, 28 Feb 1925, p.\ 9; accessed at \textit{Newspapers.com}, database with images (\url{https://bostonglobe.newspapers.com/clip/48666373/the-boston-globe/?xid=637} : viewed on 13 Apr 2020). Marriage performed in rectory of St. Francis of Assisi Church in Medford.

\bibitem{AlbertFrenchBirth}
Massachusetts Vital Records, Birth Records, 1900, p.\ 537 (stamped), no.\ 218, Albert Joseph French; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 17 May 2020), \_up through 1910 > 1900 > image 1475.

\bibitem{AlbertFrenchDeath}
U.S.\ Social Security Administration, \textit{Death Master File}, Albert French, 1980; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 17 May 2020).

U.S.\ Department of Veterans Affairs, ``Beneficiary Identification Records Locator Subsystem (BIRLS) Death File,'' Albert French, death date 30 Dec 1980; accessed at ``U.S., Department of Veterans Affairs BIRLS Death File, 1850-2010,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2441/} : viewed on 17 May 2020).

%% Mary (Duggan) (Johnson) MacLean

\bibitem{Mary4DugganBirth}
Massachusetts Vital Records, birth records, Boston, 1895, p.\ 179 (stamped), entry no.\ 2035, Mary Frances Duggan; accessed at ``Massachusetts, U.S., Birth Records, 1840-1915,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/5062} : viewed on 16 May 2021), \_up through 1910 > 1895 > image 1922.

\bibitem{Mary4DugganBaptism}
Most Holy Redeemer (East Boston) Baptisms, 1883-1908, p.\ 256, Maria Francesca Duggan; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, AmericanAncestors.org (\url{https://www.americanancestors.org/DB2726/i/55184/256/1424609464} : viewed on 16 May 2021).

\bibitem{Mary4DugganDeath}
Massachusetts Vital Records, Standard Certificate of Death, Middleton, 1959, vol.\ 72, p.\ 459, registered no.\ 28, Mary Frances Johnson (nee Duggan).

\bibitem{JamesJohnsonMarriage}
New York State Department of Health, New York State Marriage Index, 1921, certificate no.\ 941, James F Johnson and Mary F Duggan; accessed at ``New York State, Marriage Index, 1881-1967,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/61632} : viewed on 15 May 2021), 1921 > Marriage > image 719.

City of Poughkeepsie, New York, 1921 marriages, no.\ 3992, James Francis Johnson and Mary Frances Duggan.

\bibitem{JamesJohnsonBirth}
Boston Registrar Department, Return of a Birth to the City Registrar, 1898, p. 29, James Benjamin Johnson; accessed at  ``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, FamilySearch (https://www.familysearch.org/ark:/61903/1:1:F46F-F78 : viewed on 15 May 2021), Suffolk > Boston > Births 1898 > image 29.

St. Mary Star of the Sea (East Boston) Baptisms, 1898-1917, p. 1, James Benjamin Johnson; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, AmericanAncestors.org (https://www.americanancestors.org/DB2726/i/56467/1/73551183 : viewed on 15 May 2020).

\bibitem{JamesJohnsonBaptism}
``St. Mary Star of the Sea (East Boston) Baptisms, 1898-1917,'' p. 1, James Benjamin Johnson.

\bibitem{JamesJohnsonDeath}
James F.\ Johnson obituary, \textit{The Boston Globe}, 30 Mar 1928, p.\ 33; accessed at Newspapers.com (\url{https://www.newspapers.com/clip/77657625/obituary-for-james-f-johnson/?xid=637} : viewed on 15 May 2021).

\bibitem{NewtonMacLeanMarriage}
State of New Hampshire, marriage records, Newton M MacLean and Mary F Johnson, Salem, N.H., certified 1 May 1937; accessed at ``New Hampshire, U.S., Marriage and Divorce Records, 1659-1947,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/5241} : viewed on 16 May 2021), Marriage > 1901-1937 > Makris, A - Miller, G > image 2338.

\bibitem{NewtonMacLeanBirth}
Massachusetts Vital Records, birth records, Lynn, 1894, entry no.\ 532, Newton Matheson McLean; accessed at ``Massachusetts, U.S., Birth Records, 1840-1915,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/5062} : viewed on 16 May 2021), \_up through 1910 > 1894 > image 812.

\bibitem{NewtonMacLeanDeath}
U.S.\ Veterans Administration, Master Index, 1917-1940, claim no.\ 1942511, Newton Matheson MacLean; accessed at ``United States, Veterans Administration Master Index, 1917-1940,'' database with images, FamilySearch (\url{https://familysearch.org/ark:/61903/1:1:71NZ-ZG2M} : viewed on 16 May 2021), Film \# 105256131 > image 4433.

\bibitem{Mary4DugganPhone}
1920 U.S. census, Suffolk County, Massachusetts, population schedule, enumeration district (ED) 11, sheet no.\ 1A, dwelling no.\ 2, family no.\ 3, Mary Duggan in Patrick Duggan household; accessed at ``1920 United States Federal Census,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/6061} : viewed on 19 May 2021), Massachusetts > Suffolk > Boston Ward 1 > District 0011 > image 1.

Massachusetts Vital Records, Standard Certificate of Death, Middleton, 1959, vol.\ 72, p.\ 459, registered no.\ 28, Mary Frances Johnson (nee Duggan).

\bibitem{JamesJohnsonFall}
``WAR VETERAN WAS KILLED IN ACCIDENTAL FALL,'' \textit{Dunkirk Evening Observer}, 31 Mar 1928, p.\ 2; accessed at Newspapers.com (\url{https://www.newspapers.com/clip/77089542/james-f-johnson-death/?xid=637} : viewed on 15 May 2021).

\bibitem{Census1930Mary4Duggan}
1930 U.S.\ census, Suffolk County, Massachusetts, population schedule, Boston, Enumeration District (ED) 13-2, sheet no.\ 4B, dwelling 40, family 65, Mary Johnson in Arthur F.\ Langley household; accessed at ``1930 United States Federal Census,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/6224} : viewed on 16 May 2021), Massachusetts > Suffolk > Boston (Districts 1-250) > District 0002 > image 8.

\bibitem{Mary4Duggan1939}
R. L. Polk \& Co., \textit{The Lynn Directory}, 1939, p.\ 590, Newton McLean at 16 Newhall; accessed at ``U.S., City Directories, 1822-1995,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/2469} : viewed on 16 May 2021), Massachusetts > Lynn > 1939 > Lynn, Massachusetts, City Directory, 1939 > image 550.

\bibitem{Census1940Mary4Duggan}
1940 U.S.\ census, Essex County, Massachusetts, population schedule, Lynn, Enumeration District (ED) 19-72, sheet no.\ 4B, household no.\ 109, Mary Johnson household; accessed at ``1940 United States Federal Census,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/2442} : viewed on 16 May 2021), Massachusetts > Essex > Lynn > 19-72 > image 8.

%% Edward Joseph Duggan

\bibitem{Edward4DugganBirth}
St. Mary Star of the Sea (East Boston) Baptisms, 1898-1917, p. 27, Edward Joseph Duggan; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, AmericanAncestors.org (\url{https://www.americanancestors.org/DB2726/i/56467/27/1425765259} : viewed on 25 Apr 2021).

\bibitem{Edward4DugganDeath}
Massachusetts Vital Records, Death Certificates, 1950, vol.\ 82, p.\ 143, no.\ 15, Edward J.\ Duggan.

\bibitem{Edward4DugganMarriage}
Sacred Heart (East Boston) Marriages, 1906-1920, p.\ 76, Edward J.\ Duggan and Anna M.\ Spracklin; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, AmericanAncestors.org (\url{https://www.americanancestors.org/DB2726/i/60525/76/10000688684} : viewed on 25 Apr 2021).

\bibitem{AnnaSpracklinBirth}
Massachusetts Vital Records, Birth Register, Chelsea, 1900, p.\ 17, entry no.\ 763, Maud Spracklin; accessed at ``Massachusetts, U.S., Birth Records, 1840-1915,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/5062} : viewed on 25 Apr 2021), \_up through 1910 > 1900 > image 2489.

%% Mary Alice Flynn

\bibitem{MaryAlice4FlynnBirth}
Massachusetts Vital Records, Birth Records, 1886, p.\ 74, no.\ 3320, Mary Alice Flynn; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 23 May 2020), \_up through 1910 > 1886 > image 1152.

\bibitem{MaryAlice4FlynnBaptism}
Sacred Heart (East Boston) Baptisms and Confirmations, 1873-1893, p.\ 254, Maria Alicia Flynn baptism; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/58159/254/1426795692} : viewed on 23 May 2020).

\bibitem{MaryAlice4FlynnDeath:1}
Alice (Flynn) Clahane obituary, \textit{The Boston Globe}, 14 Oct 1958, p.\ 59; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/51972536/obituary-for-alice-clahane/?xid=637} : viewed on 23 May 2020).

\bibitem{MaryAlice4FlynnMarriage:1}
Massachusetts Vital Records, Marriage Records, 1908, no.\ 6083, Edward W Clahane and Alice V Flynn; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 23 May 2020), \_up through 1910 > 1908 > image 1912.

\bibitem{EdwardClahaneBirth}
Boston, Massachusetts Vital Records, Birth Records, 1888, no.\ 4862, Edward Clahane; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 23 May 2020), Boston > Births, Marriages and Death > image 45265.

\bibitem{MaryAlice4FlynnMarriage:2}
Massachusetts Vital Records, Marriage Records, 1908, no.\ 6083, Edward W Clahane and Alice V Flynn.

\bibitem{EdwardClahaneDeath}
Edward W.\ Clahane obituary, \textit{The Boston Globe}, 30 May 1962, p.\ 44; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/51988414/obituary-for-ed-ahane/?xid=637} : viewed on 23 May 2020).

\bibitem{MaryAlice4FlynnMarriage:3}
Massachusetts Vital Records, Marriage Records, 1908, no.\ 6083, Edward W Clahane and Alice V Flynn.

\bibitem{Census1940MaryAlice4Flynn:1}
1940 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 15-719, Boston City, sheet no.\ 3A, house no.\ 1137, family no.\ 87, Alive V.\ Clahane household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 23 May 2020), Massachusetts > Suffolk > Boston > 15-719 > image 5; Alice (Flynn) Clahane obituary, \textit{The Boston Globe}, 14 Oct 1958, p.\ 59.

\bibitem{MaryAlice4FlynnDeath:2}
Alice (Flynn) Clahane obituary, \textit{The Boston Globe}, 14 Oct 1958, p.\ 59.

\bibitem{Census1910EdwardClahane}
1910 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 1263, Boston City, sheet no.\ 13A, household no.\ 126, family no.\ 239, Edward W.\ Clahane in Hannah E.\ Flynn household; accessed at ``1920 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6061/} : viewed on 23 May 2020), Massachusetts > Suffolk > Boston Ward 1 > image 25.

\bibitem{Census1920EdwardClahane}
1920 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 240, Boston, sheet no.\ 17A, household no.\ 3, family no.\ 4, Edward Clahane household; accessed at ``1920 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6061/} : viewed on 23 May 2020), Massachusetts > Suffolk > Boston Ward 8 > District 0240 > image 33.

\bibitem{EdwardClahaneWWIIDraft}
United States, Selective Service System, ``World War II Draft Cards (Fourth Registration) for the State of Massachusetts,'' Record Group 147, Series Number M2090, card for Edward William Clahane, serial no.\ 1855, order no.\ [blank]; accessed at ``U.S.\ WWII Draft Cards Young Men, 1940-1947,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 23 May 2020), Massachusetts > Christien, Prudent - Clarke, Robert Irving > Aadland, Gunval - Fernstrom, Ernest Emanuel > image 9222.

\bibitem{Census1940MaryAlice4Flynn:2}
1940 U.S. census, Suffolk Co., Mass., pop.\ sched., Boston, sheet 3A, house 1137, fam.\ 87, Alice V.\ Clahane.

%% Edith Wickens

\bibitem{Edith4WickensBirth}
Massachusetts Vital Records, Birth Records, 1894, no.\ 4885, Edith A.\ Wickens; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 25 May 2020), \_up through 1910 > 1894 > image 1761.

\bibitem{Edith4WickensDeath}
Edith A.\ Giguere obituary, \textit{Detroit Free Press}, 10 Feb 1957, p.\ 35; accessed at \textit{Newspapers.com} (\url{https://www.newspapers.com/clip/55186128/obituary-for-c-icr-f-rk/?xid=637} : viewed on 11 Jul 2020).

\bibitem{Edith4WickensMarriage}
Massachusetts Vital Records, Marriage Records, 1913, p.\ 266 (stamped), no.\ 6103, George H Giguere and Edith Wickens; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 25 May 2020), 1913 > Boston > image 266.

\bibitem{GeorgeGiguereBirth}
Massachusetts Vital Records, Birth Records, 1893, no.\  237, George Hector Giguere; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 25 May 2020), \_up through 1910 > 1893 > image 893.

\bibitem{GeorgeGiguereDeath}
Michigan Vital Records, ``Michigan Death Index,'' entry for George H Giguere, died 19 Jul 1974; accessed at ``Michigan, Death Index, 1971-1996,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3171/} : viewed on 25 May 2020).

\bibitem{Census1930GeorgeGiguere}
1930 U.S. census, Wayne County, Michigan, population schedule, Enumeration District (ED) 82-830, Detroit City, p. 20A, dwelling no.\ 248, family no.\ 1, George H Giguere household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 25 May 2020), Michigan > Wayne > Detroit (Districts 751-879) > District 0830 > image 31.

%% Albert Francis Wickens

\bibitem{Albert4WickensBirth}
Massachusetts Vital Records, Birth Records, 1898, p.\ 79 (written), p.\ 77 (stamped), no.\ 3523, Albert Francis Wickens; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 7 Jun 2020), \_up through 1910 > 1898 > image 1937.

\bibitem{Albert4WickensDeath}
U.S.\ Social Security Administration, \textit{Death Master File}, Albert Wickens, 1977; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 7 Jun 2020).

U.S.\ Department of Veterans Affairs, ``Beneficiary Identification Records Locator Subsystem (BIRLS) Death File,'' Albert Wickens, death date 17 Sep 1977; accessed at ``U.S., Department of Veterans Affairs BIRLS Death File, 1850-2010,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2441/} : viewed on 7 Jun 2020).

\bibitem{Albert4WickensMarriage}
New Jersey Vital Records, ``Index of Marriages in New Jersey,'' Year Range: 1920-1929, Surname Range: P - S, AW and Mary Schaller; accessed at ``New Jersey, Marriage Index, 1901-2016,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/61253/} : viewed on 7 Jun 2020), Bride Index > 1920-1929 > P - S > image 446.

\bibitem{MarySchallerDeath:1}
U.S.\ Social Security Administration, \textit{Death Master File}, Mary Wickens, Apr 1984; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 7 Jun 2020).

1900 U.S. census, Queens County, New York, population schedule, Enumeration District (ED) 672, City of New York, sheet no.\ 5, dwelling no.\ 61, family no.\ 105, Mary Schaller in Frank Schaller household; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 7 Jun 2020), New York > Queens > Queens Ward 04 > District 0672 > image 11.

\bibitem{Census1900MarySchaller:2}
1900 U.S. census, Queens Co., N.Y., pop.\ sch., City of New York, sheet 5, dwell.\ 61, fam.\ 105, Mary Schaller; Michigan Vital Records, Marriage Registers, 1921-1925, Wayne County, no.\ 222296, Aloysius J.\ Schaller and Florence Spurk; accessed at ``Michigan, Marriage Records, 1867-1952,'' \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9093/} : viewed on 7 Jun 2020), Registers, 1887-1925 > 1921-1925 > 1921 Wayne > image 1006.

\bibitem{MarySchallerDeath:2}
U.S.\ Social Security Administration, \textit{Death Master File}, Mary Wickens, Apr 1984; New Jersey Vital Records, ``Index of Deaths for Month -- Annual 1984,'' p.\ 1589, Mary H.\ Wickens; accessed at ``New Jersey, Death Index, 1901-2017,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/61260/} : viewed on 7 Jun 2020), 1984 > image 1593.

\bibitem{Census1930AlbertWickens}
1930 U.S. census, Essex County, New Jersey, population schedule, Enumeration District (ED) 7-188, Newark City, sheet no.\ 2B, dwelling no.\ 36, family no.\ 49, Albert F.\ Wickens household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 7 Jun 2020), New Jersey > Essex > Newark (Districts 1-250) > District 0188 > image 4.

\bibitem{Census1940AlbertWickens}
1930 U.S. census, Essex County, New Jersey, population schedule, Enumeration District (ED) 25-310, Newark, sheet no.\ 1B, dwelling no.\ 57, family no.\ 23, Albert F.\ Wickens household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 7 Jun 2020), New Jersey > Essex > Newark > 25-310 > image 2.

%% Ethel Mary (Wickens) Heuman

\bibitem{Ethel4WickensBirth}
Massachusetts Vital Records, Birth Records, 1902, p.\ 136, no.\ 6102, Ethel Mary Wickens; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 13 Jun 2020), \_up through 1910 > 1902 > image 1720.

\bibitem{Ethel4WickensDeath}
Macomb County, Michigan, Vital Records, Death Index, Ethel Heuman, death date 27 Jul 1967; accessed at ``Web: Macomb County, Michigan, Death Index 1904-2017,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/70854/} : viewed on 13 Jun 2020).

\bibitem{Ethel4WickensMarriage}
Michigan Vital Records, \textit{Record of Marriages}, vol.\ 5, 1923, Kent to Lemawee, no.\ 256168, Harold E.\ Heuman and Ethyle M.\ Wickens; accessed at ``Michigan, Marriage Records, 1867-1952,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9093/} : viewed on 13 Jun 2020),  Registers, 1887-1925 > 1921-1925 > 1923 Kent-Monroe > image 344.

\bibitem{HaroldHeumanDeath:1}
Michigan Vital Records, ``Michigan Death Index,'' Harold E.\ Heuman Sr.\, death date 10 May 1993; accessed at ``Michigan, Death Index, 1971-1996,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3171/} : viewed on 13 Jun 2020).

United States, Selective Service System, ``WWII Draft Registration Cards for Michigan, 10/16/1940-03/31/1947,'' Record Group 147, Box 513, card for Harold Edward Heuman, serial no.\ 2705, order no.\ 12,278; accessed at \textit{U.S.\ WWII Draft Cards Young Men, 1940-1947}, database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 13 Jun 2020), Michigan > Hartman-Holliday > Heuer, Harold-Hiatt, Weldon > image 62.
Birth date shown as 12 May 1903, but this is the only record not showing a birth date of 12 May 1902.

\bibitem{Census1910HaroldHeuman}
1910 U.S. census, Cook County, Illinois, population schedule, Enumeration District (ED) 1409, Chicago City, sheet no.\ 4A, dwelling no.\ 56, family no.\ 62, Harold Heuman in John Heuman household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 13 Jun 2020), Illinois > Cook > Chicago Ward 32 > District 1409 > image 7.

Illinois, Cook County Courthouse, Birth Records, reference/certificate 60940, John G Heuman in entry for Grace Helen Heuman; accessed at ``Illinois, Cook County, Birth Certificates, 1871-1940,'' database, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:Q239-GXYZ} : viewed on 13 Jun 2020). Grace Heuman shown as Harold's sister in 1910 census.

\bibitem{HaroldHeumanDeath:2}
Michigan Vital Records, ``Michigan Death Index,'' Harold E.\ Heuman Sr.\, death date 10 May 1993.

\bibitem{Census1940HaroldHeuman}
1940 U.S. census, Macomb County, Michigan, population schedule, Enumeration District (ED) 50-39, Mount Clemens City, sheet no.\ 16A, house no.\ 159, household no.\ 313, Harold Heuman household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 13 Jun 2020), Michigan > Macomb > Mount Clemens > 50-39 > image 31.

%% Catherine O'Brien

\bibitem{Census1910Edward3OBrien:2}
1910 U.S.\ census, Hartford County, Connecticut, population schedule, Enumeration District (ED) 184, Hartford City, page no.\ 17A, dwelling no.\ 122, family no.\ 277, Edward F.\ O'Brien household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 27 Apr 2020), Connecticut > Hartford > Hartford Ward 7 > District 0179.

1910 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 529, Jamaica Plain, Boston, sheet no.\ 5A, dwelling no.\ 75, family no.\ 99, Edward F.\ O'Brien household; accessed at ``1920 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6061/} : viewed on 27 Apr 2020), Massachusetts > Suffolk > Boston Ward 22 > District 0529 > image 9.

Massachusetts Vital Records, \textit{Index to Marriages}, 1936-1940, Naas - Pottinger, vol.\ 123, Catherine M O'Brien, Boston, 1937, vol.\ 18, p.\ 5; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 15 Jun 2020), 1936-1940 > Naas - Pottinger > image 134.

\bibitem{Catherine4OBrienDeath:1}
Catherine M.\ MacDonald obituary, \textit{The Boston Globe}, 29 Apr 1964, p.\ 32; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/49642054/obituary-for-catherine-m-macdonald/?xid=637} : viewed on 15 Jun 2020).

\bibitem{Catherine4OBrienMarriage:2}
Massachusetts Vital Records, \textit{Index to Marriages}, 1936-1940, Naas - Pottinger, vol.\ 123, Catherine M O'Brien; Massachusetts vital records, certificate of marriage, Fred A MacDonald and Catherine M O'Brien, 1937, vol.\ 18, p.\ 5, no.\ 4635 (stamped).

\bibitem{Catherine4OBrienMarriage2:2}
Massachusetts vital records, certificate of marriage, Fred A MacDonald and Catherine M O'Brien, 1937, vol.\ 18, p.\ 5, no.\ 4635 (stamped); Catherine M.\ MacDonald obituary, \textit{The Boston Globe}, 29 Apr 1964, p.\ 32.

\bibitem{HydePark}
Lewis, Geoff; Avault, John; Vrabel, Jim (November 1999), History of Boston's Economy, Growth and Transition 1970–1998 (PDF), Boston, Massachusetts: Boston Redevelopment Authority, p. 31, archived from the original (PDF) on 2007-06-16 (\url{https://web.archive.org/web/20070616172652/http://www.cityofboston.gov/bra/PDF/ResearchPublications//pdr529.pdf})

\bibitem{FrederickMacDonaldBirth}
Massachusetts Vital Records, Birth Records, 1908, p.\ 11, no.\ 461, Frederick McDonald; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 15 Jun 2020), \_up through 1910 > 1908 > image 1408.

United States, Selective Service System, ``Draft Registration Cards for Massachusetts, 10/16/1940-03/31/1947,'' Record Group 147, Box 587, card for Frederick Augustus MacDonald Jr, serial no.\ 980, order no.\ 3018; accessed at \textit{U.S.\ WWII Draft Cards Young Men, 1940-1947}, database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 15 Jun 2020), Massachusetts > Lawson-Maguire > MacDonald,Anthony-MacDonald,Lawson > image 887.

\bibitem{FrederickMacDonaldDeath:1}
Frederick A.\ MacDonald obituary, \textit{The Boston Globe}, 12 Nov 1983, p.\ 36; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/53523680/obituary-for-frederick-a-macdonald/?xid=637} : viewed on 15 Jun 2020).

\bibitem{Catherine4OBrienMarriage2:3}
Massachusetts vital records, certificate of marriage, Fred A MacDonald and Catherine M O'Brien, 1937, vol.\ 18, p.\ 5, no.\ 4635 (stamped).

\bibitem{FrederickMacDonaldDeath:2}
Frederick A.\ MacDonald obituary, \textit{The Boston Globe}, 12 Nov 1983, p.\ 36.

%% Frances O'Brien

\bibitem{Frances4OBrien2Birth}
Massachusetts Vital Records, Birth Records, 1912, Somerville, no.\ 408, Frances Josephine O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 18 Jun 2020), 1912 > Somerville > image 11.

\bibitem{Frances4OBrien2Death:1}
U.S.\ Social Security Administration, \textit{Death Master File}, Frances J.\ Day, died 8 Jul 1997; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 18 Jun 2020); Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for Frances Day, died 8 Jul 1997.

\bibitem{Frances4OBrien2Death:2}
U.S.\ Social Security Administration, \textit{Death Master File}, Frances J.\ Day, died 8 Jul 1997; Massachusetts Vital Records, \textit{Index to Marriages}, 1941 - 1945, Celle - Degan, vol.\ 129, entry for John R Day, Boston, 1942, vol.\ 15, p.\ 398, and Milton, 1942, vol.\ 80, p.\ 344; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 18 Jun 2020), 1941-1945 > Celle - Degan > image 583.

\bibitem{JohnDaySS:1}
U.S.\ Social Security Administration, ``Social Security Applications and Claims, 1936-2007,'' entry for John R Day; accessed at ``U.S., Social Security Applications and Claims Index, 1936-2007,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/60901/} : viewed on 20 Jun 2020).

\bibitem{JohnDaySS:2}
U.S.\ Social Security Administration, ``Social Security Applications and Claims, 1936-2007,'' entry for John R Day; Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for John R Day, certificate 015631; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 20 Jun 2020).

\bibitem{Census1940Frances4OBrien2}
1940 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 15-663, Boston, sheet no.\ 63A, house no.\ 58, household no.\ 303, Frances O'Brien in Edward O'Brien household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 20 Jun 2020), Massachusetts > Suffolk > Boston > 15-663 > image 33.

\bibitem{JohnDayObit}
Dr.\ John R.\ Day M.D.\ obituary, \textit{The Boston Globe}, 23 Jan 1990, p.\ 18; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/53582210/obituary-for-john-r-md/?xid=637} : viewed on 20 Jun 2020).

R.\ L.\ Polk \& Co., compilers, \textit{Polk's Boston City Directory}, 1948-49 (Boston: R.\ L.\ Polk \& Co., 1949), p.\ 481, John R and Frances Day at 124 Theodore Parker Rd.; accessed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 20 Jun 2020), Massachusetts > Boston > 1948 > Boston, Massachusetts, City Directory, 1948 > image 483.

%% Edward O'Brien

\bibitem{Edward4OBrien3Birth}
Massachusetts Vital Records, Birth Records, City of Boston, 1916, v.\ 2, p.\ 103, no.\ 14109, Edward Francis O'Brien; accessed at ``Massachusetts State Vital Records, 1841-1920,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/3:1:33SQ-GRGB-9Z7} : viewed on 20 Jun 2020), Births > Births 1916 vol 2 no 10001-19857 Boston > image 98.

\bibitem{Edward4OBrien3Death}
Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for Edward F Obrien, certificate 055901; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 20 Jun 2020).

Edward F.\ O'Brien obituary, \textit{The Boston Globe}, 14 Dec 1985, p.\ 16; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/49662479/obituary-for-edward-f-obrien/?xid=637} : viewed on 20 Jun 2020).

\bibitem{Edward4OBrien3Marriage}
Massachusetts Vital Records, \textit{Index to Marriages}, 1946-1950, Naaripa-Pieloscik, vol.\ 150, entry for Edwdard F O'Brien, Milton, 1946, vol.\ 96, p.\ 159; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 20 Jun 2020), 1946-1950 > Naaripa - Pieloscik > image 167.

Massachusetts Vital Records, \textit{Index to Marriages}, 1946-1950, McAnnenny - Mytkowicz, vol.\ 149, entry for Mary A Metivier, Milton, 1946, vol.\ 96, p.\ 159; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 20 Jun 2020), 1946-1950 > McAnneny - Mytkowicz > image 280.

\bibitem{MaryMetivierBirth}
Massachusetts Vital Records, Birth Records, Milton, 1917, p.\ 3 (hand-written), p.\ 61 (stamped), no.\ 126, Mary Metivier; accessed at ``Massachusetts State Vital Records, 1841-1920,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/3:1:33SQ-G1BF-4NS} : viewed on 20 Jun 2020), Births > Births 1917 vol 642 Nantucket-Worcester > image 62.

\bibitem{MaryMetivierDeath}
Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for Mary A Obrien, certificate 044437; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 20 Jun 2020).

\bibitem{Edward4OBrien3Obit:2}
Edward F.\ O'Brien obituary, \textit{The Boston Globe}, 14 Dec 1985, p.\ 16.

%% Beatrice O'Brien

\bibitem{Beatrice4OBrienBirth}
Massachusetts Vital Records, Birth Records, Boston, 1919, Aug 11-Aug 20, vol.\ 30, p.\ 54, certificate no.\ 11115, Beatrice Field O'Brien; accessed at ``Massachusetts State Vital Records, 1841-1920,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:QLGR-5HS6} : viewed on 21 Jun 2020), Births > Births 1919 vol 30 Boston > image 55.

\bibitem{Beatrice4OBrienDeath}
Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for Beatrice Brady, certificate 033686; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 21 Jun 2020).

\bibitem{Beatrice4OBrienMarriage}
Massachusetts Vital Records, \textit{Index to Marriages}, 1941-1945, Bisiniere-Cazavelan, vol.\ 128, entry for John F Brady, Boston, 1941, vol.\ 18, p.\ 446; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 21 Jun 2020), 1941-1945 > Bisiniere - Cazavelan > image 179.

\bibitem{JohnBradyDraft}
United States, Selective Service System, ``Draft Registration Cards for Massachusetts, 10/16/1940-03/31/1947,'' Record Group 147, Box 98, card for John Francis Brady, serial no.\ 1130, order no.\ 2691; accessed at \textit{U.S. WWII Draft Cards Young Men, 1940-1947}, database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 21 Jun 2020), Massachusetts >  Bastardo-Brandon > Bradley, Bernard-Brady, Russell > image 1754.

1920 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 520, City of Boston, sheet no.\ 19B, dwelling no.\ 194, household no.\ 401, John Brady in Patrick Brady household; accessed at ``1920 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6061/} : viewed on 21 Jun 2020), Massachusetts > Suffolk > Boston Ward 21 > District 0520 > image 38.

Boston, Massachusetts Vital Records, Marriage Records, 1909, no.\ 5771, Patrick Brady and Bridget Burke; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511} : viewed on 17 Jul 2020), \_Up Through 1910 > 1909 > image 2044.

Massachusetts Vital Records, \textit{Index to Marriages}, 1941-1945, Nurmi-Ramirez, vol.\ 136, entry for Beatrice O'Brien, Boston, 1941, vol.\ 18, p.\ 446; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 21 Jun 2020), 1941-1945 > Nurmi - Ramirez > image 22.

\bibitem{JohnBradyDeath}
Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for John F Brady, certificate 022707; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 21 Jun 2020).

\bibitem{JohnBrady1951}
R.\ L.\ Polk \& Co., compilers, \textit{Polk's Boston City Directory}, 1951 (Boston: R.\ L.\ Polk \& Co., 1951), p.\ 200, John F and Beatrice F Brady at 72 Addington Rd.; accessed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 21 Jun 2020), Massachusetts > Boston > 1951 > Boston, Massachusetts, City Directory, 1951 > image 414; Massachusetts Bay Transportation Authority, ``The History of the T'' (\url{https://www.mbta.com/history} : viewed on 21 Jun 2020).

\bibitem{JohnBrady1965}
R.\ L.\ Polk \& Co., compilers, \textit{Polk's Boston City Directory}, 1965 (Boston: R.\ L.\ Polk \& Co., 1965), p.\ 168, John F and Beatrice F Brady at 177 Corey; accessed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 21 Jun 2020), Massachusetts > Boston > 1965 > Boston, Massachusetts, City Directory, 1965 > image 446.

\bibitem{Beatrice4OBrienObit}
Beatrice F. (O'Brien) Brady obituary, \textit{The Boston Globe}, 30 Jun 1976, p.\ 37; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/42867888/obituary-for-brady/?xid=637} : viewed on 21 Jun 2020).
	
\end{thebibliography}