\section{Mary Alice (Flynn) Clahane}\label{per:MaryAlice4Flynn}

\MainPerson{Mary Alice\textsuperscript{4} Flynn}\index{Flynn!Mary Alice\textsuperscript{4}|bb}\index{Clahane!Mary Alice\textsuperscript{4} (Flynn)|bb} (aka Alice Veronica Flynn) (\Lineage{3}{Hannah}, \Lineage{2}{Mary}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 10 August 1886.\cite{MaryAlice4FlynnBirth} She was baptized at Sacred Heart (East Boston)\index{Sacred Heart (church)} on 15 August 1886.\cite{MaryAlice4FlynnBaptism} She died in Boston on 13 October 1958.\cite{MaryAlice4FlynnDeath:1} She married, in Boston on 18 November 1908, \MainPerson{Edward William Clahane}.\index{Clahane!Edward William (husband of Hannah/Hanora (Flynn))|b}\cite{MaryAlice4FlynnMarriage:1} He was born in Boston\index{Massachusetts!Boston} on 31 July 1888\cite{EdwardClahaneBirth} to Edward W.\ Clahane\index{Clahane!Edward W.} and Catherine (Nolan) Clahane.\index{Clahane!Catherine (Nolan)}\index{Nolan!Catherine}\cite{MaryAlice4FlynnMarriage:2} He died in Boston\index{Massachusetts!Boston} on 29 May 1962.\cite{EdwardClahaneDeath}

Alice's occupation on her marriage record is listed as ``organist.''\index{organist}\cite{MaryAlice4FlynnMarriage:3} In the 1940 census she was working as a musician for the W.P.A.\ (the federal Works Progress Administration).\index{Works Progress Administration}\cite{Census1940MaryAlice4Flynn:1} She was a member of the Musicians Union,\index{Musicians Union} Local \#9.\cite{MaryAlice4FlynnDeath:2} Edward Clahane's occupations varied from floorwalker\index{floorwalker} at a dry goods store,\index{dry goods store}\cite{Census1910EdwardClahane} insurance claims adjuster,\index{insurance claims adjuster}\cite{Census1920EdwardClahane} and clerk at the Mass.\ Geodetic Survey.\index{Massachusetts Geodetic Survey}\cite{EdwardClahaneWWIIDraft} The family lived at 1137 Commonwealth Ave.\index{Massachusetts!Boston!Commonwealth Ave.}\index{Massachusetts!Boston!Allston} in Boston's Allston neighborhood.\cite{Census1940MaryAlice4Flynn:2}

\begin{KidsIntro}
	Child of Edward W.\ Clahane and Mary Alice\textsuperscript{4} (Flynn) Clahane:
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{Marion Gertrude\textsuperscript{5} Clahane},\index{Clahane!Marion Gertrude\textsuperscript{5}} b.\ Boston 26 Jan.\ 1909;\cite{Marion5ClahaneBirth} d.\ Brookline, Norfolk Co., Mass., 9 April 1971;\cite{Marion5ClahaneDeath} unm.
\end{Kids}