\section{Mary Frances (Duggan) (Johnson) MacLean}\label{per:Mary4Duggan}

\index{Duggan!Mary Frances\textsuperscript{4}|bb}\index{Johnson!Mary Frances\textsuperscript{4}|bb}\index{MacLean!Mary Frances\textsuperscript{4}|bb}
\MainPerson{Mary Frances\textsuperscript{4} Duggan} (\Lineage{3}{Ellen}, \Lineage{2}{Michael}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 15 September 1895.\cite{Mary4DugganBirth} She was baptized at Most Holy Redeemer Church\index{Most Holy Redeemer (church)} in East Boston\index{Massachusetts!Boston!East Boston} on 26 September 1895.\cite{Mary4DugganBaptism} She died at the Essex Sanatorium\index{Essex Sanatorium} in Middleton, Essex County, Massachusetts,\index{Massachusetts!Middleton} on 19 July 1959 and is buried at Holy Cross Cemetery\index{Holy Cross Cemetery} in Malden, Middlesex County, Massachusetts.\index{Massachusetts!Malden}\cite{Mary4DugganDeath} 

Mary married, first, in Poughkeepsie, Dutchess County, New York,\index{New York!Poughkeepsie} on 23 January 1921, \MainPerson{James Francis Johnson}.\footnote{James Francis Johnson appears in his birth and baptismal record as ``James Benjamin Johnson.''}\cite{JamesJohnsonMarriage}\index{Johnson!James Francis|bb} James was born in Boston on 8 January 1898 to James Benjamin Johnson\index{Johnson!James Benjamin} and Rose Quinn.\index{Quinn!Rose}\index{Johnson!Rose (Quinn)}\cite{JamesJohnsonBirth} He was baptized at St. Mary Star of the Sea Church\index{St. Mary Star of the Sea (church)} in East Boston on 20 January 1898.\cite{JamesJohnsonBaptism} He died in Albany, Albany County, New York,\index{New York!Albany} on 29 March 1928.\cite{JamesJohnsonDeath}

Mary married, second, in Salem, Rockingham County, New Hampshire,\index{New Hampshire!Salem} on 23 April 1937, \MainPerson{Newton Matheson MacLean}.\cite{NewtonMacLeanMarriage}\index{MacLean!Newton Matheson|bb} Newton was born in Lynn, Essex County, Massachusetts,\index{Massachusetts!Lynn} on 20 April 1892 to Archibald MacLean\index{MacLean!Archibald} and Mary MacLellan.\index{MacLean!Mary (MacLellan)}\index{MacLellan!Mary}\cite{NewtonMacLeanBirth} He died in Lynn on 8 January 1960.\cite{NewtonMacLeanDeath}

Mary was a long-time worker at the telephone company,\index{telephone company} eventually becoming switchboard supervisor.\cite{Mary4DugganPhone} Her first husband, James F.\ Johnson, was a veteran of World War I. He was gassed during the war and suffered injuries that may have given him epilepsy. It was likely an epileptic attack that caused him to fall down the stairs to his death in Albany.\index{JamesJohnsonFall} Mary and her son Leo then returned to Boston, where they were living with Mary's cousin-in-law at 12 Orient Ave.\ in 1930.\cite{Census1930Mary4Duggan} In 1937 she married Newton M.\ MacLean, a foreman at GE.\cite{Mary4Duggan1939} The couple likely divorced before 1940, when Mary was living alone with Leo in Lynn and had gone back to using the surname ``Johnson.''\cite{Census1940Mary4Duggan}

\begin{KidsIntro}
	Child of James F. Johnson and Mary F.\textsuperscript{4} (Duggan) Johnson:
\end{KidsIntro}

\begin{Kids}
	
	\KidNum{}{i.}\KidName{Leo Francis\textsuperscript{5} Johnson}\index{Johnson!Leo\textsuperscript{5} Francis}, b.\ Boston, 28 Feb.\ 1923;\cite{Leo5JohnsonBirth} d.\ Kaplan Hospice House, Danvers, Essex Co., Mass.;\cite{Leo5JohnsonObit:1} m.\ Swampscott, Essex Co., Mass., 1949, \KidName{Margaret Langford}.\cite{MargaretLangfordMarriage}\index{Langford!Margaret}\index{Johnson!Margaret (Langford)} Leo was a WWII\index{World War II} veteran and retired as a Lt. Col. in the Air Force Reserves.\index{Air Force} He founded Monte Carlo Inc.,\index{Monte Carlo Inc.} which organized charity fundraising events.\cite{Leo5JohnsonObit:2}
	
\end{Kids}