\section{Pauline (O'Brien) Baine}\label{per:Pauline4OBrien}

\MainPerson{Pauline\textsuperscript{4} O'Brien}\index{O'Brien!Pauline M.\textsuperscript{4}|bb}\index{Baine!Pauline M.\textsuperscript{4} (O'Brien)|bb} (\Lineage{2-3}{John}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 9 June 1894.\cite{Pauline4OBrienBirth} She was baptized at St. Peter (Dorchester)\index{St. Peter's (church)} on 17 June 1894.\cite{Pauline4OBrienBaptism}. She died in Malden, Middlesex County, Massachusetts,\index{Massachusetts!Malden} on 2 February 1967.\cite{Pauline4OBrienDeath} She married, at St. Francis of Assisi Church\index{St. Francis of Assisi (church)} in Medford, Middlesex County, Massachusetts,\index{Massachusetts!Medford} on 9 June 1930, \MainPerson{Charles Lucius Baine}.\index{Baine!Charles Lucius}\cite{CharlesBaineMarriage} He was born in Guelph, Wellington County, Ontario, Canada,\index{Canada!Guelph, Ontario} on 27 January 1870\cite{CharlesBainePassport} to William Conrad Baine\index{Baine!William Conrad} and Mary Jane (Reed) Baine.\index{Baine!Mary Jane (Reed)}\index{Reed!Mary Jane}\cite{Census1880CharlesBaine,CharlesBaineBaptism,CharlesBaineMarriage} He died in Brookline, Norfolk County, Massachusetts,\index{Massachusetts!Brookline} on 1 March 1962.\cite{CharlesBaineDeath}

Charles L. Baine\index{Baine!Charles Lucius} served as secretary-treasurer of the Boot and Shoe Workers' International Union\index{Boot and Shoe Workers' International Union} from 1902 to 1931.\cite{Gompers}

Charles L.\ Baine\index{Baine!Charles Lucius} and Pauline (O'Brien) Baine\index{O'Brien!Pauline M.\textsuperscript{4}|bb}\index{Baine!Pauline M.\textsuperscript{4} (O'Brien)|bb} did not have any children together.\cite{Pauline4OBrienDeath2} Charles had three children from a prior marriage.\cite{CharlesBaineDeath}