
\begin{thebibliography}{999}
	\addcontentsline{toc}{chapter}{\bibname}
	\raggedright
	\small

% Appendices

%% Further Research

\bibitem{John3OBrien1916:4}
W. A. Greenough Co., compilers, \textit{1916 Medford Directory} (Boston: W. A. Greenough \& Co., 1916), p.\ 219, entry for John J O'Brien; viewed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 13 Apr 2020), Massachusetts > Medford > 1916 > Medford, Massachusetts, City Directory, 1916 > image 217.\\
``O'Brien John J picture frame mfr 69 Cornhill B 45 Court''\\
John O'Brien appears in the next available Medford city directory for 1918 with no business or profession listed. In the 1920 census his occupation is listed as ``none.''

%% Cemetery Plots

\bibitem{DianaBerberenaLetter1:3}
Diana Berberena, Catholic Cemetery Association of the Archdiocese of Boston, letter to Gavin E.\ O'Brien, dated 27 May 2019. This letter includes burial information for two individuals. William O'Brien, buried 12/30/[1856], age 76 years into O'Brien Family Grave G W124 Range N17 west, owner Edward O'Brien. Mary Ann O'Brien, buried 11/1852, age 1 month, 12 days old.

\bibitem{HolyCrossPlotEdward:2}
The Catholic Cemetery Association of the Archdiocese of Boston, Owner Profile, owner ID C15-61458 (Edward O'Brien) at Holy Cross Cemetery, printed 18 Jul 2019.

\bibitem{HolyCrossPlotMichael}
The Catholic Cemetery Association of the Archdiocese of Boston, Owner Profile, owner ID C15-84952 (Michael O'Brien) at Holy Cross Cemetery, printed 18 Jul 2019.ƒ

\bibitem{HolyCrossPlotFernald}
The Catholic Cemetery Association of the Archdiocese of Boston, Owner Profile, owner ID C15-86405 (Robert Fernald) at Holy Cross Cemetery, printed 22 Jan 2021.

\bibitem{BillMcEvoy:5}
Bill McEvoy, compiler, ``Sand Banks Cemetery Project,'' Excel spreadsheet of plot locations, sourced from burial books and cemetery lot cards of the Catholic Archdiocese of Boston; accessed at \textit{The Historical Society of Watertown} (\url{http://historicalsocietyofwatertownma.org/HSW/} : viewed on 31 Mar 2020), Resources > Sand Banks Cemetery Project > downloadable Excel spreadsheet.

\bibitem{John3OBrienBurial:3}
Mt.\ Calvary Cemetery, Boston, Suffolk County, Massachusetts, printout of Mahoney plot (CL1-1-6D) originally given to Michael O'Brien and verified by Gavin O'Brien at the cemetery office, 28 Dec 2018.

\bibitem{William3OBrienBurial}
Mt.\ Calvary Cemetery, Boston, Suffolk County, Massachusetts, listing for William O'Brien plot (location C7-22-22, owner ID 14237) printed at the cemetery office for Gavin O'Brien on 12 April 2019.

\end{thebibliography}