\textbf{}\begin{thebibliography}{999}
\raggedright
\small

	\bibitem{Edward2OBrienNaturalization}
	Edward O Brien primary declaration of intention (1854), no.\ 487, 
	District of Massachusetts; 
	Record Group 21: Records of the District Courts of the United States; 
	National Archives at Boston, Waltham, Massachusetts;
	viewed at ``Massachusetts, State and Federal Naturalization Records, 1798--1950,''
	database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2361/} : viewed on 23 Mar 2020), image 858.
	
	\bibitem{Edward2OBrienPetition}
	Suffolk County, Massachusetts, Superior Civil Court, Petitions for Naturalization, vol.\ 1, 1864, p.\ 118, entry for Edward O'Brien; accessed at ``Massachusetts, State and Federal Naturalization Records, 1798-1950,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2361/} : viewed on 11 Jul 2020), Superior Court, Suffolk County, Massachusetts > Petitions, V 1, P 6-204, 1864 > image 184.
	
	\bibitem{Michael2OBrienNaturalization}
	Edward O Brien petition for naturalization (1868), 
	Massachusetts Superior Court, Suffolk County; 
	Oct term 1868 (Letters L--Z), Film \# 007795438,
	viewed at ``Primary and final declarations of intention and naturalizations, 1864--1888 and card index 1856--1884,''
	database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-CS9H-83DG-G}) : viewed on 23 Mar 2020), image 1859.
	
	\bibitem{Margaret3DooleyBaptism}
	Watergrasshill \& Glenville Parish (Watergrasshill, Ireland), ``Historical Baptisms from 1836--1901,'' database, ``Margaret Dooly'' baptism, 27 Dec 1840; \textit{Watergrasshill \& Glenville Parish Archives.} \url{http://www.wghparish.ie/index.php/archives/baptisms-1836-1901/easytablerecord/1-baptisms/7008} : viewed on 17 Apr 2019.
	
	\bibitem{TopographicalDictionary}
	Samuel Lewis, \textit{A Topographical History of Ireland}, vol. 2 (London: S.\ Lewis \& Co.\, 1837), 695.
	
	\bibitem{LocalNames}
	Patrick Weston Joyce, \textit{Irish Local Names Explained} (Dublin: The Educational Co.\ of Ireland, Limited, 1922), 93.
	
	\bibitem{Population}
	\textit{Census of Ireland, 1871}, Part 1, Vol. 2 (Dublin: Alexander Thom, 1873), 140; viewed at \textit{Histpop - The Online Historical Population Reports Website} (\url{http://www.histpop.org/}) : viewed on 23 Mar 2020.
	
	\bibitem{2011Census}
	Central Statistics Office (Cork, Ireland) ``Census 2011 -- Population Classified by Area,'' 36; accessed at \textit{Central Statistics Office} (\url{https://www.cso.ie/en/media/csoie/census/documents/census2011vol1andprofile1/Table_5.pdf}) : viewed on 23 Mar 2020.
	
	\bibitem{Grenham1}
	John Grenham, \textit{Tracing your Irish Ancestors} (Dublin: Gill Books, 2019), 1.
	
	\bibitem{Grenham18}
	Ibid., 18.
	
	\bibitem{Jacksons}
	F. Jackson, \textit{The County and City of Cork Post Office General Directory, 1842--43} (Cork: F. Jackson), 125; viewed at \textit{Cork City Libraries} (\url{http://www.corkpastandpresent.ie/places/streetandtradedirectories/1842-3jacksonscountycityofcorkpogeneraldirectory/}) : viewed on 23 Mar 2020.
	
	\bibitem{Peramb1847}
	``Perambulation Book, County of Cork, Barony of Barrymore, Parishes of St.\ Michaels, Templeusque, and Killaspugmullane,'' Parish of Killaspugmullane, Townland of Trantstown, p.\ 22 (hand-written), No.\ 22a, John OBrien, dated 4 Aug 1847; viewed at ``Ireland, Valuation Office Books, 1831--1856,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-L94N-1CR6} : viewed 26 Mar 2020), film \#007246728, image 109.
	
	\bibitem{Peramb1850}
	``Perambulation Book, County of Cork, Barony of Barrymore, Parish of Killaspugmullane,'' Townland of Trantstown, No.\ 7a, John O'Brien, dated 26 Jul 1850; viewed at ``Ireland, Valuation Office Books, 1831--1856,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-L94N-1CR6} : viewed 26 Mar 2020), film \#007246728, image 118.
	
	\bibitem{House1850}
	``1st House Book, County of Cork, Barony of Barrymore, P.\ of Killaspugmullane (Revised),'' Townland of Trantstown, p.\ 5 (hand-written), No.\ 7a, John OBrien, original date Aug 1847, revised date 27 Jul 1850; viewed at ``Ireland, Valuation Office Books, 1831--1856,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-894J-SZCB} : viewed 26 Mar 2020), film \#007246783, image 420.
		
	\bibitem{PaperMill}
	Bina Harte, ``The Old Paper Mill of Trantstown,'' recounted to the author by Jeremiah Harte, The National Folklore Collection, UCD, The Schools' Collection, Volume 0382, p.\ 31; viewed at \textit{d\'{u}chas.ie} (\url{https://www.duchas.ie}), The Schools' Collection > Co.\ Cork > Cnoc na Biolaraighe, image 31.
	
	\bibitem{House1849}
	``House Book, Town of Watergrasshill, County of Cork, Barony of Barrymore, Feby 1849,'' Houses in Town of Watergrasshill, Parish of Ardnageehy, Townland of Tinageragh, No.\ 44 (original), Lot 29 (revised), Wm Brien; viewed at ``Ireland, Valuation Office Books, 1831--1856,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-994N-YC62} : viewed 26 Mar 2020), film \#007246869, image 442.
	
	 \bibitem{HouseIntro}
	``House Book, Town of Watergrasshill, County of Cork, Barony of Barrymore, Feby 1849,'' title page; viewed at ``Ireland, Valuation Office Books, 1831--1856,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-994N-YCXK} : viewed 27 Mar 2020), film \#007246869, image 433.
	
	\bibitem{Bianconi}
	Brian Igoe, ``Charles Bianconi and The Transport Revolution, 1800 -- 1875,'' blog post, published 14 Dec 2012; \textit{The Irish Story} (\url{https://www.theirishstory.com/2012/12/14/charles-bianconi-and-the-transport-revolution-1800-1875/} : viewed 27 Mar 2020).
	
	\bibitem{BoruHistorical}
	O'Brien Clan Foundation, ``Brian Boru: Historical View,'' webpage, \textit{O'Brien Clan Foundation} (\url{https://www.obrienclan.org/historical-view.html} : viewed on 29 Mar 2020).
	
	\bibitem{BoruEarlyHistory}
	O'Brien Clan Foundation, ``Brian Boru: Early History,'' webpage, \textit{O'Brien Clan Foundation} (\url{https://www.obrienclan.org/early-history.html} : viewed on 29 Mar 2020).	
	
	\bibitem{GGI}
	Dennis O'Brien, ``The DNA of Clan O'Brien (Dennis O'Brien)'', recorded presentation and slides, Genetic Genealogy Ireland 2016 conference, posted on \textit{YouTube} 29 Oct 2016 (\url{https://youtu.be/wp-1bfxaXYs} : viewed on 29 Mar 2020).
	
	\bibitem{Bettinger}
	Blaine T. Bettinger and Debbie Parker Wayne, \textit{Genetic Genealogy in Practice} (Arlington: National Genealogical Society, 2016), 23-25.
	
	\bibitem{BarryHistory1}
	E. Barry, \textit{Barrymore : records of the Barrys of County Cork from the earliest to the present time, with pedigrees} (Cork: Guy and Co. Ltd., 1902), 1.
	
	\bibitem{BarryHistory17}
	Ibid., p.\ 17.
	
	\bibitem{ParliamentaryGazetteer}
	\textit{The Parliamentary Gazetteer of Ireland}, Vol. 1 (Dublin, London, and Edinburgh: A. Fullarton and Co., 1846) 227.
	
	\bibitem{JamesBarry1}
	James Barry, email to members of the \textit{Family Tree DNA} ``Barry Project'' on 17 Dec 2019.
	
	\bibitem{BarrymoreDNA}
	James Barry, \textit{Barrymore DNA: The Genetic Records of the Barrys of County Cork and Beyond} (2020) pp.\ 2--4; downloaded from \textit{Academia.edu} (\url{https://www.academia.edu/42454916/Barrymore_DNA_The_Genetic_Records_of_the_Barrys_of_County_Cork_and_Beyond}: viewed on 31 Mar 2020).
	
	\bibitem{BarrymoreDNA2}
	Ibid., p.\ 9.
	
	\bibitem{BarrymoreDNA3}
	Ibid., p.\ 4.
	
	\bibitem{BigY}
	``Big Y -- Results,'' dynamic database of matches, kit \#904650 \textit{Family Tree DNA} (\url{https://www.familytreedna.com/my/big-y#/matches} : viewed 29 Mar 2020). Of the 29 total matches, 25 of them have surnames Barry, Berry, or Bearry. There are no O'Brien surnames or spelling variants in the match list.
	
	\bibitem{TiP}
	``Y-DNA TiP Report,'' comparison of kit \#904650 with kit \#441938 at 111 markers, dynamic database of matches, \textit{Family Tree DNA} (\url{https://www.familytreedna.com/my/y-dna-matches} : viewed 29 Mar 2020).
	
	\bibitem{YFull}
	``SNP matches,'' dynamic database of matches, comparison of YFull member YF63552 with member YF65192, \textit{YFull} (\url{https://www.yfull.com/snp/matches/} : viewed 29 Mar 2020).
	
	\bibitem{Census1855William}
	1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 1, p. 60 (left side), dwelling [blank], family 549, for William O'Brien in Edward O'Brien household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 29 Mar 2020), Suffolk > Boston Ward 01 > image 33.
	
	\bibitem{Census1855Abigail}
	1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 1, p. 60 (left side), dwelling [blank], family 549, for Abby Dooley in Edward O'Brien household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 29 Mar 2020), Suffolk > Boston Ward 01 > image 33.
		
	\bibitem{William1OBrienDeath}
	Massachusetts Town and Vital Records, Death Records, 1856, no. 4206, William O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 29 Mar 2020), Boston > Deaths, 1856 > image 96.
		
	\bibitem{DianaBerberenaLetter1}
	Diana Berberena, Catholic Cemetery Association of the Archdiocese of Boston, letter to Gavin E.\ O'Brien, dated 27 May 2019. This letter includes burial information for two individuals. William O'Brien, buried 12/30/[1856], age 76 years into O'Brien Family Grave G W124 Range N17 west, owner Edward O'Brien. Mary Ann O'Brien, buried 11/1852, age 1 month, 12 days old.
	
	\bibitem{DianaBerberenaLetter2}
	Diana Berberena, Catholic Cemetery Association of the Archdiocese of Boston, letter to Gavin E.\ O'Brien, received 11 Jul.\ 2019.\\
	Michael Dooley: North Cambridge Catholic Cemetery, Range 14 East, Grave 96\\
	Ellen O’Brien: North Cambridge Catholic Cemetery, Range 17 West, Grave 124\\
	Michael O’Brien: Holy Cross Cemetery, 28 North Maple, Grave 27 West
	
	\bibitem{Michael2OBrienDeath}
	Massachusetts Vital Records, Death Records, 1891, no.\ 4862, Michael O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 29 Mar 2020), \_Pre 1903 > 1891 > image 1303.
	
	\bibitem{Abigail2OBrienDeath}
	Massachusetts Vital Records, Death Records, 1897, no.\ 121, Abigail Dooley; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 29 Mar 2020), \_Pre 1903 > 1897 > image 1431.
	
	\bibitem{CarolGordon}
	Carol Gordon, Catholic Cemetery Association of the Archdiocese of Boston, emails to Gavin E.\ O'Brien in Apr.\ 2019.\\
	Holy Cross Cemetery plot locations as follows.\\
	Ann (O’Brien) Dailey: North Monument, Path 17, Grave 34 East\\
	Abigail (O’Brien) Dooley: North Monument, Path 12, Grave 38 East\\
	Mary (O’Brien) Ward: North Monument, Path 12, Grave 38 East
	
	\bibitem{MichaelDooleyBirth}
	Abigail (O'Brien) Dooley and Michael Dooley had two children in County Cork, Ireland, prior to their immigration to the United States. 
	
	\bibitem{Ann2OBrienDeath}
	Massachusetts Vital Records, Death Records, 1898, no.\ 7910, Ann Dailey; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 29 Mar 2020), \_Pre 1903 > 1898 > image 1832.
	
	\bibitem{Mary2OBrienDeath}
	Massachusetts Vital Records, Death Records, 1908, p.\ 576, no.\ 2762, Mary Ward; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 29 Mar 2020), 1908 > Boston > image 2737.
	
	\bibitem{1880CensusAnn}
	1880 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 576, East Boston, p. 24, Havre Street, house no.\ 307, dwelling no.\ 153, family no.\ 267, Ann Dailey in household of Edward O'Brian; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 30 Mar 2020), Massachusetts > Suffolk > Boston > 576 > image 24.

	\bibitem{Census1865Abigail}
	1865 Massachusetts state census, Suffolk County, population schedule, city of Boston, ward 1, dwelling 1570, family 3692, for Abby Duley in William Simonds household; accessed at ``Massachusetts, State Census, 1865,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9203/} : viewed on 29 Mar 2020), Suffolk > Boston Ward 01 > image 203.\\
	Abigail's marital status is listed as ``widowed.''
	
	\bibitem{MichaelDooleyDeath}
	Massachusetts Vital Records, death records, 1857, no.\ 7, Michael Dooley; accessed at ``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/3:1:3QS7-L975-M988} : viewed on 30 Mar 2020), Suffolk > Boston > Deaths 1856-1857 > image 351.\\
	He is listed as ``married'' but wife's name is not included. Age 36. Address is 12 Pearl Pl.
	
	\bibitem{John2OBrienCivilMarriage2}
	City of Boston, Suffolk County, Massachusetts, marriage records, 1853, no.\ 2642, John O'Brien and Mary Mahoney; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Marriages, 1853 > image 157.\\
	John is listed as 33 years old and Mary as 24.
	
	\bibitem{John2OBrienDeath}
	Massachusetts Vital Records, death records, 1863, p.\ 49, no.\ 1270, John O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 31 Mar 2020), \_Pre 1903 > 1863 > image 756.\\
	Cause of death: phthisis.
	
	\bibitem{BillMcEvoy}
	Bill McEvoy, compiler, ``Sand Banks Cemetery Project,'' Excel spreadsheet of plot locations, sourced from burial books and cemetery lot cards of the Catholic Archdiocese of Boston; accessed at \textit{The Historical Society of Watertown} (\url{http://historicalsocietyofwatertownma.org/HSW/} : viewed on 31 Mar 2020), Resources > Sand Banks Cemetery Project > downloadable Excel spreadsheet.
	
	\bibitem{John2OBrienMarriage}
	St. Mary (Boston) Marriages, 1836-1854, p.\ 205, John O'Brien and Mary Mahoney; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/54105/205/1424477986} : viewed on 31 Mar 2020).
	
	\bibitem{John2OBrienCivilMarriage}
	Massachusetts Vital Records, marriage records, 1853, p.\ 156, no.\ 2642, John O'Brien and Mary Mahoney; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 31 Mar 2020), \_Up Through 1910 > 1853 > image 779.
	
	\bibitem{MaryMahoneyBowserMarriage}
	Massachusetts Vital Records, marriage records, 1867, no.\ 267, Thomas Bowser and Mary O'Brien; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 31 Mar 2020), \_Up Through 1910 > 1867 > image 743.
	
	\bibitem{MaryMahoneyDeath}
	Massachusetts Vital Records, death records, 1894, no.\ 755, Mary (Maloney) Bowser, wife of Thomas; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 31 Mar 2020), \_Pre 1903 > 1894 > image 1047.\\
	Parents are listed as John and Ellen Daley; this does not match previous records.
	
	\bibitem{Mary3OBrienBirth}
	Massachusetts Vital Records, birth records, 1856, p.\ 111, no.\ 4896, Mary O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 31 Mar 2020), \_up through 1910 > 1856 > image 818.
	
	\bibitem{Mary3OBrienBaptism}
	St. Stephen (Boston) Baptisms, 1854-1862, p.\ 134, Mary O'Brien, accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/134/1423778090} : viewed on 31 Mar 2020).
	
	\bibitem{Mary3OBrienDeath}
	Massachusetts Vital Records, death records, 1883, p.\ 73, no.\ 1916, Mary F. O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 31 Mar 2020), \_Pre 1903 > 1883 > image 847.
	
	\bibitem{Mary3OBrienDeath2}
	Boston, Massachusetts Vital Records, death records, 1883, no.\ 1916, Mary F. O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Deaths, 1883 > image 67.
	
	\bibitem{James3OBrienBirth}
	Massachusetts Vital Records, birth records, 1858, p.\ 40, no.\ 1761, James Edward O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 31 Mar 2020), \_up through 1910 > 1858 > image 777.
	
	\bibitem{James3OBrienBaptism}
	St. Mary (Boston) Baptisms, 1850-1858, p.\ 491, James Edward O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/54102/491/1424471476} : viewed on 31 Mar 2020).
	
	\bibitem{James3OBrienDeath}
	Boston, Massachusetts Vital Records, death records, 1879, no.\ 2167, James E.\ O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Deaths, 1879 > image 77.
	
	\bibitem{Ellen3OBrienBirth}
	Massachusetts Vital Records, birth records, 1853, p.\ 81, no.\ 3620, Ellen O'Brine; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_up through 1910 > 1853 > image 749.
	
	\bibitem{Ellen3OBrienBaptism}
	St. Stephen (Boston) Baptisms, 1854-1862, p.\ 312, Ellen O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/312/1423781683} : viewed on 31 Mar 2020).
	
	\bibitem{Ellen3OBrienDeath}
	Boston, Massachusetts Vital Records, death records, 1882, no.\ 6860, Ellen F. O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Deaths, 1882 > image 233.
	
	\bibitem{Margaret3OBrienDeath}
	Massachusetts Vital Records, death records, 1863, p.\ 149, no.\ 3752, Margaret O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 31 Mar 2020), \_Pre 1903 > 1863 > image 855.
	
	\bibitem{Anna3OBrienDeath}
	Boston, Massachusetts Vital Records, death records, 1866, no.\ 621, Anna O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Deaths, 1866 > image 19.
	
	\bibitem{Census1860John}
	1860 U.S. census, Suffolk County, Massachusetts, population schedule, Boston, ward 1, p.\ 383, dwelling 1535, family 3004, John O'Brien household; accessed at ``1860 United States Federal Census,'' \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7667/} : viewed on 31 Mar 2020), Massachusetts > Suffolk > Boston Ward 1 > image 384.
	
	\bibitem{TuberculosisHistory}
	I. Berberis, N.L.\ Bragazzi, L.\ Galluzzo, and M. Martini, ``The history of tuberculosis: from the first historical records to the isolation of Koch's bacillus,'' \textit{Journal of Preventive Medicine and Hygiene} 58(1) (March 2017): E9--E12; accessed at \textit{National Center for Biotechnology Information, U.S.\ National Library of Medicine} (\url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5432783/} : viewed on 31 Mar 2020).
	
	\bibitem{John3OBrienBirth}
	Massachusetts Vital Records, birth records, 1861, p.\ 11, no.\ 471, John O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 31 Mar 2020), \_up through 1910 > 1861 > image 909.
	
	\bibitem{Wards}
	City of Boston, Massachusetts, \textit{A Catalogue of the City Councils of Boston, 1822-1890, Roxbury, 1846-1867, Charlestown, 1847-1873 and of the selectmen of Boston, 1634-1822, also of various other town and municipal officers} (City of Boston Printing Department, 1909), 7--40; accessed at \textit{Internet Archive} (\url{https://archive.org/stream/catalogueofcityc00bost#page/6/mode/2up} : viewed on 2 Apr 2020).
	
	\bibitem{1861John3OBrien}
	Adams, Sampson, \& Company, compilers, \textit{The Boston Directory} (Boston: Adams, Sampson, \& Company, 1861), p.\ 355, John O'Brien at 35 Fleet St.; accessed at ``The Boston Directory, 1789 to 1900,'' \textit{Boston Athenaeum Digital Collections} (\url{https://cdm.bostonathenaeum.org/digital/collection/p16057coll32} : viewed on 25 Jul 2020), Home > Boston Directory, 1789 to 1901 > 1861, Boston directory > image 337.
	
	\bibitem{VitalStatistics}
	John S. Billings, M.D., United States Census Office, \textit{Vital statistics of Boston and Philadelphia covering a period of six years ending May 31, 1890} (1895), 30; accessed at \textit{Internet Archive} (\url{https://archive.org/details/vitalstatistics00shungoog/page/n22/mode/2up} : viewed on 2 Apr 2020). 
	
	\bibitem{Edward2OBrienMarriage}
	The author searched the Massachusetts marriage index from 1841--1855 for Edward O'Brien and Bridget Linnehan/Linnihan/Linehan/Linahan/Linnahan. No relevant records found.	
	Massachusetts Vital Records, ``Index to marriages A-Z 1841-1850'' and ``Index to marriages A-Z 1851-1855''; accessed at ``Massachusetts indexes to births and marriages (1841-1920), deaths (1841-1971),'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-C9BG-SSZ9-4} : viewed on 2 Apr 2020).
	
	\bibitem{BridgetLinnehanDeath}
	Boston, Massachusetts Vital Records, death records, 1867, no.\ 1127, Bridget O'Brien, wife of Edward; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 2 Apr 2020), Boston > Births, Marriages and Death > image 32429.
	
	\bibitem{Census1880Edward}
	1880 U.S. census, Suffolk County, Massachusetts, population schedule, East Boston, Enumeration District (ED) 576, p.\ 24, dwelling 153, family 267, Edward O'Brian household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 2 Apr 2020), Massachusetts > Suffolk > Boston > 576 > image 24.
	
	\bibitem{Edward2OBrienProbate}
	Massachusetts Probate Court, Suffolk County, 1881, vol.\ 533, pp.\ 216--217, Edward O'Brien; accessed at ``Suffolk County (Massachusetts) probate records, 1636-1899,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-C9YR-6S4L} : viewed on 2 Apr 2020), ``Probate records v. 533-534 1881,'' Film \#007704174, image 118.
	
	\bibitem{Edward2OBrienDeed}
	Massachusetts, Suffolk County Registry of Deeds, 1874, vol.\ 1224, p. 25, Roome to O'Brien; accessed at ``Massachusetts Land Records, 1620-1986,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QSQ-G9Z3-9BYX} : viewed on 2 Apr 2020), Deeds 1874 vol 1223-1224 > image 369.
	
	\bibitem{HavrePurchase}
	Massachusetts, Suffolk County Registry of Deeds, 1874, vol.\ 1224, p.\ 25, Roome to O’Brien; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QSQ-G9Z3-9BYX} : viewed on 4 Apr 2020), Suffolk > Deeds 1874 vol 1223-1224 > image 369.
	
	\bibitem{HavreMap}
	Massachusetts, Suffolk County Register of Deeds, \textit{Atlas of East Boston,} 1892, vol.\ 9, p.\ 14; accessed at \textit{Suffolk County Register of Deeds} (\url{https://massrods.com/suffolk/suffolk-county-atlas/suffolk-county-atlas-pages/} : viewed on 4 Apr 2020), Research > Suffolk County Atlases > East Boston 1892 > Page 14
	
	\bibitem{EastBostonStreets}
	Massachusetts, Suffolk County Register of Deeds, \textit{Atlas of East Boston,} 1892, vol.\ 9, street index; accessed at \textit{Suffolk County Register of Deeds} (\url{https://massrods.com/suffolk/suffolk-county-atlas/suffolk-county-atlas-pages/} : viewed on 4 Apr 2020), Research > Suffolk County Atlases > East Boston 1892 > Street Index.
	
	\bibitem{MaryAnn3OBrienBirth}
	Massachusetts Vital Records, birth records, 1852, p.\ 47, no.\ 2075, Mary Ann O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_up through 1910 > 1852 > image 675.
	
	\bibitem{MaryAnn3OBrienBaptism}
	Holy Cross (Boston) Baptisms V.9, 1850-1853, p.\ 335, Mary A O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48422/335/1415444935} : viewed on 5 Apr 2020).
	
	\bibitem{MaryAnn3OBrienDeath}
	Massachusetts Vital Records, death records, 1852, no.\ 3333, Mary A.\ O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_Pre 1903 > 1852 > image 501.
	
	\bibitem{Edward3OBrienBirth}
	Boston, Massachusetts Vital Records, birth records, 1861, no.\ 4572, Edward O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 5 Apr 2020), Boston > Births, 1861 > image 13.

	\bibitem{AnnMaria3OBrienDeath}
	Annie M.\ O'Brien obituary, \textit{The Boston Globe}, 25 May 1937, p.\ 14, col.\ 8; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/48037127/obituary-for-annie-m-o-obrien/?xid=637} : viewed on 5 Apr 2020).
	
	\bibitem{AnnMaria3OBrienBirth}
	Boston, Massachusetts Vital Records, birth records, 1855, no.\ 5412, Ann Maria O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_up through 1910 > 1855 > image 798.
	
	\bibitem{AnnMaria3OBrienBaptism}
	St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 102, Ann M.\ O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/102/1423777462} : viewed on 5 Apr 2020).
	
	\bibitem{Margaret3OBrienBaptism}
	St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 312, Margaret O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/312/1423781685} : viewed on 5 Apr 2020).	
	
	\bibitem{Edward3OBrienDeath}
	Massachusetts Vital Records, death records, 1884, p.\ 6, no.\ 162, Edward J.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 5 Apr 2020), \_Pre 1903 > 1884 > image 773.	
	
	\bibitem{Edward2OBrienGrave}
	Holy Cross Cemetery (Malden, Middlesex County, Massachusetts), Edward O'Brien marker, North Monument Ave., Path 17, Grave 34 East; personally read, 14 Apr 2019. \\
	Photos available at \url{https://www.findagrave.com/memorial/201238724/edward-o_brien}.

	\bibitem{LondonStDeed}
	Massachusetts, Suffolk County Registry of Deeds, 1870, vol.\ 1009, p.\ 38, Cutcliffe Jr to O’Brien; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-L9Z3-938P} : viewed on 5 Apr 2020), Suffolk > Deeds 1870 vol 1008-1009 > image 394.\\
	Edward's probate file states he owned ``Lincoln St.\  East Boston,'' however, this was probably a misspelling of ``London St.\'' as there was no Lincoln St.\ located in East Boston.\cite{EastBostonStreets}
	
	\bibitem{LondonStMap}
	Griffith Morgan Hopkins Jr., \textit{Atlas of the county of Suffolk, Massachusetts} (Philadelphia: G.M.\ Hopkins \& Co., 1874), vol.\ 4, plate K, showing 185 London St.; accessed at \textit{Norman B.\ Leventhal Map Center} (\url{https://collections.leventhalmap.org/search/commonwealth:6h446s239} : viewed on 5 Apr 2020).
	
	\bibitem{Bromley1922}
	George Washington Bromley, \textit{Atlas of the city of Boston, Charlestown and East Boston} (Philadelphia: G.W.\ Bromley \& Co., 1874), plate 25, showing 185 London St.; accessed at \textit{Norman B.\ Leventhal Map Center} (\url{https://collections.leventhalmap.org/search/commonwealth:1257c1339} : viewed on 5 Apr 2020).
	
	\bibitem{GlobeRobbery}
	``Take two burglars at revolver point,’’ \textit{The Boston Globe}, 18 Apr 1922, p.\ 7; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/48057899/the-boston-globe/} : viewed on 5 Apr 2020).
	
	\bibitem{Edward2OBrien1876}
	Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1876), 678, Edward O’Brien at 307 Havre, E.B.; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 4 Apr 2020), Massachusetts > Boston > 1876 > Boston, Massachusetts, City Directory, 1876 > image 678.\\
	O’Brien Edward, teamster, house 307 Havre, E.B.
	
	\bibitem{Frances3OBrien1914}
	Sampson \& Murdock Company, compilers, \textit{The Boston Directory} (Boston: Sampson \& Murdoch Company, 1914), p.\ 1973, entry for Frances Wickens; accessed at ``U.S.\ City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 5 Apr 2020), Massachusetts > Boston > 1914 > Boston, Massachusetts, City Directory, 1914 > image 1981.\\
	``Wickens Frances widow John B h 185 London E B''
	
	\bibitem{Teamster}
	``teamster, n.'' \textit{Oxford English Dictionary Online} (\url{https://www-oed-com.ezproxy.bpl.org/view/Entry/198379} : viewed 5 Apr 2020).
	
	\bibitem{Edward2OBrienDeath}
	Massachusetts Vital Records, death records, 1881, no.\ 5857, Edward O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_Pre 1903 > 1881 > image 958.
	
	\bibitem{Mary2OBrienMarriage}
	Massachusetts Vital Records, marriage records, 1850, no.\ 2038 , David Wards to Mary O'Brien; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 5 Apr 2020), \_Up Through 1910 > 1850 > image 643.
	
	\bibitem{DavidWardDeath}
	Massachusetts Vital Records, death records, 1881, no.\ 8782, David Ward; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 5 Apr 2020), \_Pre 1903 > 1881 > image 1056.
	
	\bibitem{DavidWardObit}
	David Ward obituary, \textit{Boston Herald}, 20 Dec 1881, p.\ 6; accessed at \textit{GenealogyBank} (\url{https://twitter.com/ShawnMcCreesh/status/1283567307697119232} : viewed on 16 Jul 2020).
	
	
	\bibitem{DavidWard1876}
	Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1876), 908, Ward David, jr.; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 4 Apr 2020), Massachusetts > Boston > 1876 > Boston, Massachusetts, City Directory, 1876 > image 908.
	
	\bibitem{DavidWard1877}
	Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1876), 918, Ward David, jr.; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 4 Apr 2020), Massachusetts > Boston > 1877 > Boston, Massachusetts, City Directory, 1877 > image 918.
	
	\bibitem{Census1880DavidWard}
	1880 U.S. census, Suffolk County, Massachusetts, population schedule, East Boston, Enumeration District (ED) 576, p.\ 11, dwelling 66, family 121, David Ward household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 5 Apr 2020), Massachusetts > Suffolk > Boston > 576 > image 11.
	
	\bibitem{101Bennington}
	Massachusetts, Suffolk County Registry of Deeds, 1871, vol.\ 1058, p.\ 125, Hargrave to Ward; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-89Z3-MJ6D} : viewed on 5 Apr 2020), Suffolk > Deeds 1871 vol 1057-1058 > image 496.
	
	\bibitem{101BenningtonMap}
	Massachusetts, Suffolk County Register of Deeds, \textit{Atlas of East Boston,} 1892, vol.\ 9, p.\ 14; accessed at \textit{Suffolk County Register of Deeds} (\url{https://massrods.com/suffolk/suffolk-county-atlas/suffolk-county-atlas-pages/} : viewed on 4 Apr 2020), Research > Suffolk County Atlases > East Boston 1892 > Page 14
	
	\bibitem{MaryAnn3WardBaptism}
	Holy Cross (Boston) Baptisms V.9, 1850-1853, p.\ 192, Mary Ward; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48422/192/1415441475} : viewed on 5 Apr 2020).	
	
	\bibitem{MaryAnn3WardDeath}
	Boston, Massachusetts Vital Records, deaths, 1854, no.\ 82, Mary Ann Ward; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 5 Apr 2020), Boston > Births, Marriages and Death > image 30746.
	
	\bibitem{Sarah3WardBirth}
	Boston, Massachusetts Vital Records, births, 1853, no.\ 4476, Sarah Ward; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 5 Apr 2020), Boston > Births, Marriages and Death > image 53540.
	
	\bibitem{Sarah3WardBaptism}
	Holy Cross (Boston) Baptisms V.10, 1853-1858, p.\ 45, Sarah Ward; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48416/45/1415448535} : viewed on 5 Apr 2020).	
	
	\bibitem{Sarah3WardDeath}
	Boston, Massachusetts Vital Records, deaths, 1873, no.\ 2307, Sarah Ward; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 5 Apr 2020), Boston > Deaths, 1873 > image 75.
	
	\bibitem{BridgetColbertMarriage}
	Massachusetts Vital Records, marriage records, 1854, no.\ 165, Michael O'Brien and Bridget Colbert; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 7 Apr 2020), \_Up Through 1910 > 1854 > image 573.
	
	\bibitem{BridgetColbertDeath}
	Massachusetts Vital Records, death records, 1873, no.\ 99, Bridget O'Brien (m.n.) Colbert; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 7 Apr 2020), \_Pre 1903 > 1873 > image 982.
	
	\bibitem{MaryFieldMarriage}
	Boston, Massachusetts Vital Records, marriage records, 1874, no.\ 1240, Michael O'Brien and Mary Feely; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 7 Apr 2020), Boston > Marriages, 1874 > image 74.
	
	\bibitem{MaryFieldDeath}
	Massachusetts Vital Records, death records, 1915, no.\ 195, Mary O'Brien; accessed at ``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-89J2-3ZB6} : viewed on 7 Apr 2020), Suffolk > Boston > Deaths 1915 no 1-1500 > image 208.
	
	\bibitem{EdwardFrancis3OBrienBirth}
	Massachusetts Vital Records, birth records, 1883, p.\ 38, no.\ 1669, Edward Francis O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 7 Apr 2020), \_up through 1910 > 1883 > image 1071.
	
	\bibitem{243BorderPurchase}
	Massachusetts, Suffolk County Registry of Deeds, 1872, vol.\ 1088, p. 159, Appleton, Gdn.\ To O’Brien; accessed at ``Massachusetts Land Records, 1620-1986,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QSQ-G9Z3-MLGY} : viewed on 2 Apr 2020), Deeds 1872 vol 1088-1089 > image 171.
	
	\bibitem{243BorderMap}
	Massachusetts, Suffolk County Register of Deeds, \textit{Atlas of East Boston,} 1892, vol.\ 9, p.\ 11; accessed at \textit{Suffolk County Register of Deeds} (\url{https://massrods.com/suffolk/suffolk-county-atlas/suffolk-county-atlas-pages/} : viewed on 4 Apr 2020), Research > Suffolk County Atlases > East Boston 1892 > Page 11
	
	\bibitem{243BorderFerry}
	Massachusetts, Suffolk County Registry of Deeds, 1886, vol.\ 1753, p. 147, East Boston Co. to O’Brien; accessed at ``Massachusetts Land Records, 1620-1986,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-L9ZD-5QHB} : viewed on 2 Apr 2020), Suffolk > Deeds 1886 vol 1753 > image 77.
	
	\bibitem{Michael2OBrien1886}
	Sampson, Murdock, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Murdock, and Company, 1886), p.\ 888, Michael O'Brien; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 7 Apr 2020), Massachusetts > Boston > 1886 > Boston, Massachusetts, City Directory, 1886 > image 535.\\
	``O'Brien Michael, oyster opener, h. 243 Border''
	
	\bibitem{BridgetColbertChurchMarriage}
	``St. Joseph (Roxbury) Marriages, 1845-1857,'' 1854, p.\ 148, entry for Michael O'Briene and Bridget Colbert; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/rd/56907/148/1426266499} : viewed on 16 Jul 2020).
	
	\bibitem{MaryFieldChurchMarriage}
	``Most Holy Redeemer (East Boston) Marriages, 1851-1900,'' 1874, p.\ 143, entry for Michael O'Brien and Mary Field; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/55186/143/1424614029} : viewed on 16 Jul 2020).
	
	\bibitem{Census1870Ellen3OBrien2}
	1870 U.S. census, Suffolk County, Massachusetts, population schedule, Boston Ward 1 (East Boston), p.\ 292, dwelling 1271, family 2399, Ellen O'Brien in Michael O'Brien household; accessed at ``1870 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7163/} : viewed on 9 Apr 2020), Massachusetts > Suffolk > Boston Ward 01 > image 292.
	
	\bibitem{Census1880Ellen3OBrien2}
	1880 U.S. census, Suffolk County, Massachusetts, population schedule, Boston, Enumeration District (ED) 578, p.\ 2, dwelling 8, family 16, Nellie O'Brien in Michael O'Brien household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 9 Apr 2020), Massachusetts > Suffolk > Boston > 578 > image 2.\\
	House is at 243 Border St.
	
	\bibitem{Ellen3OBrien2Birth}
	Massachusetts Vital Records, birth records, 1857, p.\ 50, no.\ 2233, Ellen O'Brien; accessed at ``Massachusetts Births, 1841-1915,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:S3HT-6QT9-X1N} : viewed on 9 Apr 2020), 004341180 > image 145.
	
	\bibitem{Ellen3OBrien2Baptism}
	St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 193, Ellen O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/193/1423779290} : viewed on 9 Apr 2020).
	
	\bibitem{Michael2OBrienProbate}
	Massachusetts Probate Court, Suffolk County, 1891, vol.\ 648, p.\ 380, petition for administration of Michael O'Brien estate by Mary O'Brien; accessed at ``Suffolk County (Massachusetts) probate records, 1636-1899,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-C9YR-MYW} : viewed on 9 Apr 2020), Probate records v. 648-649 1891 > image 203.
	
	\bibitem{ElizabethAshdownDeath}
	Massachusetts vital records, Norwood death records, 1907, no.\ 272 (stamped), no.\ 78 (hand-written), Elizabeth (Ashdown) Allen; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 16 Jul 2020), 1907 > Norwood > image 80.
	
	\bibitem{Boston1861Map}
	C.\ Pinney, \textit{Plan of the city of Boston} (Boston: L.\ Prang \& Co.), plate 15, showing Ferry St.; accessed at \textit{Norman B.\ Leventhal Map Center} (\url{https://collections.leventhalmap.org/search/commonwealth:6h446v44g} : viewed on 9 Apr 2020).	
	
	\bibitem{MaryAnn3OBrien2Birth}
	Massachusetts Vital Records, birth records, 1859, no.\ 4561, Mary Ann O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 9 Apr 2020), \_up through 1910 > 1859 > image 864.\\
	Address: 38 Fleet St.
	
	\bibitem{MaryAnn3OBrien2Death}
	Boston, Massachusetts Vital Records, death records, 1861, no.\ 1632, Mary A.\ O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 9 Apr 2020), Boston > Deaths, 1861 > image 69.
	
	\bibitem{Mary3OBrien2Birth}
	Massachusetts Vital Records, birth records, 1875, no.\ 852, Mary O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 9 Apr 2020), \_up through 1910 > 1875 > image 932.
	
	\bibitem{Mary3OBrien2Death}
	Massachusetts Vital Records, death records, 1875, no.\ 7956, Mary O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 9 Apr 2020), \_Pre 1903 > 1875 > image 1036.\\
	Cause of death: Bronchitis. Address: 243 Border St.
	
	\bibitem{John3OBrien2Birth}
	Massachusetts Vital Records, birth records, 1876, no.\ 4509, John Joseph O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 9 Apr 2020), \_up through 1910 > 1876 > image 973.
	
	\bibitem{John3OBrien2Death}
	Massachusetts Vital Records, death records, 1881, no.\ 6616, John O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 9 Apr 2020), \_Pre 1903 > 1881 > image 982.\\
	Cause of death: Diphtheria. Address: 243 Border St.
	
	\bibitem{Francis3OBrienBirth}
	Massachusetts Vital Records, birth records, 1883, p.\ 38, no.\ 1669, Edward Francis O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 10 Apr 2020), \_up through 1910 > 1883 > image 1071.\\
	The name in this birth register is likely an error. ``Edward Francis O'Brien'' is the name of his older brother, and he was baptized as ``Francis Joseph O'Brien.''
	
	\bibitem{Francis3OBrienBaptism}
	Most Holy Redeemer (East Boston) Baptisms, 1883-1900, p.\ 2, Franciscus Joseph O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/rd/55184/2/1424603942} : viewed on 10 Apr 2020).	
	Sponsors: Jeremiah Field and Mrs. Ann Daley.
	
	\bibitem{Francis3OBrienDeath}
	Massachusetts Vital Records, death records, 1914, p.\ 377, no.\ 725, Frank J.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 10 Apr 2020), 1914 > New Bedford.
	
	\bibitem{Census1900Francis3OBrien}
	1900 U.S. census, Suffolk County, Massachusetts, population schedule, Boston Ward 1, Enumeration District (ED) 1160, p.\ 12, dwelling 150, family 260, Frank O'Brien in Mary O'Brien household; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 10 Apr 2020), Massachusetts > Suffolk > Boston Ward 01 > District 1160 > image 24.
	
	\bibitem{Francis3OBrien1913}
	W.\ A.\ Greenough \& Co., compilers, \textit{New Bedford and Fairhaven Directory} (Boston: W.\ A.\ Greenough \& Co., 1913), p.\ 772, Frank J O'Brien; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 10 Apr 2020), Massachusetts > New Bedford > 1913 > New Bedford, Massachusetts, City Directory, 1913 > image 774.\\
	``O'Brien Frank J meter tester 125 Middle h 95 S Sixth'' - see also p.\ 1010 (image 1014) of the same directory for the full name of the New Bedford Gas \& Edison Light Co.\ located at 125 Middle St.
	
	\bibitem{Census1855Hannah3Dooley}
	1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 1, p. 60 (left side), dwelling [blank], family 549, for Hannah Dooley in Edward O'Brien household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 29 Mar 2020), Suffolk > Boston Ward 01 > image 33.\\
	Hannah Dooley, age 18, born in Ireland
	
	\bibitem{Hannah3DooleyDeathIndex}
	Massachusetts Vital Records, \textit{Index to Deaths, 1911 - 1915, Cassibo - Enemark}, vol.\ 60, Hannah (Dooley) Cusick, 1911 vol.\ 13 p.\ 631; accessed at ``Massachusetts, Death Index, 1901-1980,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3659/} : viewed on 10 Apr 2020), 1911-1915 > Cassibo - Enemark > image 302.
	
	\bibitem{JeremiahCooneyMarriage}
	Massachusetts Vital Records, marriage records, 1859, no.\ 1734, Jeremiah Cooney and Hannah Doolly; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 10 Apr 2020), \_Up Through 1910 > 1859 > image 666.
	
	\bibitem{MichaelCusickMarriage}
	Massachusetts Vital Records, marriage records, 1884, no.\ 2686, Michael Cusick and Hannah Cooney; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 10 Apr 2020), \_Up Through 1910 > 1884 > image 1030.
	
	\bibitem{Hannah3DooleyDeath}
	Massachusetts Vital Records, death records, 1911, p.\ 631, no.\ 5659, Hannah Cusick; accessed at ``Massachusetts Deaths, 1841-1915,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/3:1:S3HY-DT59-PGR} : viewed on 11 Apr 2020), 2393942 (004283225) > image 2213.
	
	\bibitem{WilliamSimondsDeath}
	Boston, Massachusetts Vital Records, death records, 1873, no.\ 2126, William Simons; accessed at ``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-9975-96WP} : viewed on 11 Apr 2020), Suffolk > Boston > Deaths 1871-1873 > image 533.
	
	\bibitem{WilliamSimondsMarriage}
	In the 1855 Massachusetts state census, William Simonds and Margaret Dooley were living with their respective families. In 1860, William and Margaret's first child was born (Catharine Simonds). No marriage record can be found in Massachusetts. Another possibility is that they were married in Ireland prior to arriving in the U.S., although Margaret would have been only 15 years old or younger.
	
	\bibitem{RobertFernaldMarriage}
	Massachusetts Vital Records, marriage records, 1873, no.\ 2971, Robert Fernald and Margaret Simonds; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 11 Apr 2020), \_Up Through 1910 > 1873 > image 983.\\
	Margaret's parents' names are incorrectly listed as ``John'' and ``Nancy Dooley.''
	
	\bibitem{Census1855WilliamSimonds}
	1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 1, p. 62 (right side), dwelling 187, family 575,for William Simonds in Nicholas Simonds household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 11 Apr 2020), Suffolk > Boston Ward 01 > image 34.
	
	\bibitem{RobertFernaldDeath}
	Robert A.\ Fernald obituary, \textit{The Boston Globe}, 15 Jun 1917, p.\ 15; accessed at \textit{Newspapers.com}, database with images (\url{https://www.newspapers.com/clip/33980133/robert-a-fernald-obituary/} : viewed on 11 Apr 2020).
	
	\bibitem{Census1855RobertFernald}
	1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 8, dwelling 575, family 769,for Robert Ireland in George H.\ Ireland household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 11 Apr 2020), Suffolk > Boston Ward 08 > image 54.
	
	\bibitem{Census1860RobertFernald}
	1860 United States Federal Census, Suffolk County, population schedule, Boston, ward 10, p.\ 186, dwelling 739, family 1432, for Robert Fernald in Joana Fernald household; accessed at ``1860 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7667/} : viewed on 11 Apr 2020), Suffolk > Boston Ward 10 > image 186
	
	\bibitem{Margaret3DooleyDeath}
	Margaret E. Fernald obituary, \textit{The Boston Globe}, 2 Mar 1918, p.\ 12; accessed at \textit{Newspapers.com}, database with images (\url{https://bostonglobe.newspapers.com/clip/48493997/obituary-for-margaret-e-fernald/?xid=637} : viewed on 11 Apr 2020).
	
	\bibitem{Francis4SimondsBirth}
	Massachusetts Vital Records, birth records, 1863, no.\ 4335, Francis Simonds; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 11 Apr 2020), \_Up Through 1910 > 1863 > image 780.
	
	\bibitem{Francis4SimondsDeath}
	Massachusetts Vital Records, death records, 1865, no.\ 2139, Francis Simonds; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 11 Apr 2020), \_Pre 1903 > 1865 > image 768.
	
	\bibitem{Margaret4SimondsBirth}
	Boston, Massachusetts Vital Records, birth records, 1865, no.\ 4421, Margaret Josephine Simons; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 11 Apr 2020), Boston > Births, Marriages and Death > image 55407.
	
	\bibitem{Margaret4SimondsDeath}
	Massachusetts Vital Records, death records, 1866, p.\ 77, no.\ 2292, Margaret J.\ Simonds; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 11 Apr 2020), \_Pre 1903 > 1866 > image 687.
	
	\bibitem{Anna4FernaldBirth}
	Boston, Massachusetts Vital Records, birth records, 1874, no.\ 2243, Anna Fernald; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 11 Apr 2020), Boston > Births, Marriages and Death > image 56910.
	
	\bibitem{Anna4FernaldDeath}
	Massachusetts Vital Records, death records, 1875, no.\ 2910, Anna Fernald; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 11 Apr 2020), \_Pre 1903 > 1875 > image 853.
	
	\bibitem{William3OBrienBirth}
	Massachusetts Vital Records, birth records, no.\ 2848, William O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 11 Apr 2020), \_Up Through 1910 > 1854 > image 735.
	
	\bibitem{William3OBrienBaptism}
	St.\ Mary (Boston) Baptisms, 1850-1858, p.\ 304, William O'Bryen; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/54102/304/1424466134} : viewed on 11 Apr 2020).	
	
	\bibitem{William3OBrienDeath}
	Massachusetts Vital Records, death records, 1889, no.\ 8547, William O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 11 Apr 2020), \_Pre 1903 > 1889 > image 1249.\\
	Cause of death: Consumption; Occupation: Property Man; Address: 96 Tyler St.
	
	\bibitem{JuliaMcCartyDeath}
	Massachusetts Vital Records, death records, 1888, no.\ 9636, Julia T.\ O'Brien m.n.\ McCarthy; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 11 Apr 2020), \_Pre 1903 > 1888 > image 1270.\\
	Cause of death: haemoptysis; address: 16 Somerset St.; parents: Charles and Hannah
	
	\bibitem{CatharineSimondsDeath}
	Massachusetts Vital Records, death records, 1863, p.\ 124, no.\ 3135, Catharine Simonds (m.n.) Keenan; accessed at ``Massachusetts Deaths, 1841-1915,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:S3HY-68YW-S3} : viewed on 12 Apr 2020), 0960183 (004220473) > image 480.
	
	\bibitem{JoannaFernaldDeath}
	Newton, Massachusetts Vital Records, death records, 1895, p.\ 336, no.\ 209, Joanna Fernald; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 12 Apr 2020), \_Pre 1903 > 1895 > image 1044.
	
	\bibitem{JuliaMcCartyBaptism}
	Holy Cross (Boston) Baptisms, vol.\ 10, 1853-1858, p.\ 250, Julia McCarty; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48416/250/1415452885} : viewed on 12 Apr 2020).	
	
	\bibitem{PropertyMan}
	\textit{Collins English Dictionary -- Complete and Unabridged, 12th Edition 2014.} S.v. ``property man''; accessed at \textit{The Free Dictionary} (\url{https://www.thefreedictionary.com/property+man} : viewed on 12 Apr 2020).
	
	\bibitem{WilliamOBrien1880}
	Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1880), p.\ 734, William O'Brien at 82 Hudson St.; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 12 Apr 2020), Massachusetts > Boston > 1880 > Boston, Massachusetts, City Directory, 1880 > image 751.\\
	``O'Brien, William, property man, Globe Theatre, bds.\ 82 Hudson''
	
	\bibitem{WilliamOBrien1883}
	Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1883), p.\ 818, William O'Brien at 82 Hudson St.; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 12 Apr 2020), Massachusetts > Boston > 1883 > Boston, Massachusetts, City Directory, 1883 > image 833.\\
	``O'Brien, William, property man, Howard Athenaeum, house 82 Hudson''
	
	\bibitem{HowardAthenaeum}
	``West End Museum Exhibit `The Old Howard Theatre,''' \textit{North End Waterfront}, 17 Sep 2019;  \url{https://northendwaterfront.com/2019/09/west-end-museum-exhibit-the-old-howard-theatre/} : viewed on 12 Apr 2020.
	
	\bibitem{WilliamOBrienWill}
	Massachusetts Probate Court, Suffolk County, 1889, vol.\ 628, p.\ 13, William O'Brien will; accessed at ``Massachusetts, Wills and Probate Records, 1635-1991,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9069/} : viewed on 12 Apr 2020), Suffolk > Probate Records, Vol 628-629, 1890 > image 12.
	
	\bibitem{Ellen4OBrienBirth}
	Massachusetts Vital Records, birth records, 1885, p.\ 186, no.\ 8330, Ellen Louise O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 12 Apr 2020), \_Up Through 1910 > 1885 > image 1266.\\
	Address: 82 Hudson St.
	
	\bibitem{Ellen4OBrienBaptism}
	St.\ James the Greater (Boston) Baptisms, 1883-1888, p.\ 249, Helenam Louisam O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48713/249/0} : viewed on 12 Apr 2020).
	
	\bibitem{Ellen4OBrienDeath}
	Nellie L. O’Brien obituary, \textit{The Boston Globe}, 16 Jun 1926, p. 10, col. 8; accessed at \textit{Newspapers.com}, database with images (\url{https://bostonglobe.newspapers.com/clip/46645975/the-boston-globe/?xid=637} : viewed on 13 Mar 2020). 
	
	\bibitem{Ellen4OBrienDeath2}
	Massachusetts vital records, standard certificate of death for Nellie L.\ O'Brien, 1926, vol.\ 53, p.\ 72, no.\ 438 (stamped).
	
	\bibitem{Census1900EllenOBrien}
	1900 U.S.\ census, Middlesex County, Massachusetts, population schedule, Enumeration District (ED) 872, Medford, ward 5, sheet 12, dwelling no.\ 226, family no.\ 251, Nellie O'Brien in household of John J.\ O'Brien; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 12 Apr 2020), Massachusetts > Middlesex > Medford Ward 05 > District 0872 > image 24.
	
	\bibitem{Census1910EllenOBrien}
	1910 U.S.\ census, Middlesex County, Massachusetts, population schedule, Enumeration District (ED) 928, Medford, ward 2, sheet 7, dwelling no.\ 117, family no.\ 140, Nellie L.\ O'Brien in household of John J.\ O'Brien; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 12 Apr 2020), Massachusetts > Middlesex > Medford Ward 2 > District 0928 > image 13.
	
	\bibitem{Ellen4OBrien1914}
	W.\ A.\ Greenough \& Co., compilers, \textit{1914 Medford Directory} (Boston: W.\ A.\ Greenough \& Co., 1914), p.\ 199, Nellie O'Brien; accessed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 12 Apr 2020), Massachusetts > Medford > 1914 > Medford, Massachusetts, City Directory, 1914 > image 197.\\
	``O'Brien Nellie removed to Boston''
	
	\bibitem{Ellen4OBrien1919}
	Henry M. Meek Publishing Co., compilers, \textit{The Lowell Suburban Directory} (Salem: Henry M. Meek Publishing Co., 1919), p. 302, entry for Nellie L O'Brien; viewed at ``U.S. City Directories, 1822-1995,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 12 Mar 2020), Massachusetts > Lowell > 1919 > Lowell, Massachusetts, City Directory, 1919 > image 230.\\
	``O'Brien Nellie L, nurse, S I b do'' [State Infirmary, boards ditto - see abbreviations on p.\ 38, image 26]
	
	\bibitem{Ellen4OBrien1924}
	W. A. Greenough Co., compilers, \textit{1924 Medford Directory} (Boston: W. A. Greenough \& Co., 1924), p.\ 231, entry for Nellie L O'Brien; viewed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 12 Mar 2020), Massachusetts > Medford > 1924 > Medford, Massachusetts, City Directory, 1924 > image 231.
	
	\bibitem{Census1920EllenOBrien}
	1920 U.S.\ census, Middlesex County, Massachusetts, population schedule, Tewksbury, enumeration district (ED) 471, sheet 2B, institution: State Infirmary, dwelling [blank], family [blank], Nellie L O'Brien; viewed at "1920 United States Federal Census,” database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/6061/} : viewed on 12 Mar 2020), Massachusetts > Middlesex > Tewksbury > District 0471 > image 4.
	
	\bibitem{RutlandHospital}
	Grant Welker, ``Rutland is hoping for a large-scale development at the former state hospital,'' \textit{Worcester Business Journal}, 7 Jun 2019;  \url{https://www.wbjournal.com/article/rutland-is-hoping-for-a-large-scale-development-at-the-former-state-hospital} : viewed on 12 Apr 2020.
	
	\bibitem{John3OBrienBaptism}
	St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 249, John O'Breine; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/387/1423783173} : viewed on 12 Apr 2020).
	
	\bibitem{John3OBrienDeath}
	John J.\ O'Brien obituary, \textit{The Boston Globe}, 16 May 1938, p.\ 15; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/34912710/obituary_for_john_j_obrien/?xid=637} : viewed on 12 Apr 2020).
	
	\bibitem{John3OBrienBurial}
	Mt.\ Calvary Cemetery, Boston, Suffolk County, Massachusetts, printout of Mahoney plot (CL1-1-6D) originally given to Michael O'Brien and verified by Gavin O'Brien at the cemetery office, 28 Dec 2018.
	
	\bibitem{John3OBrienMarriage}
	Massachusetts Vital Records, marriage records, 1890, p.\ 44, no.\ 775, John J.\ O'Brien and Emma A.\ Mahony; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 12 Apr 2020), \_Up Through 1910 > 1890 > image 1061.
	
	\bibitem{EmmaMahonyBaptism}
	Holy Cross (Boston) Baptisms, v.\ 11, 1858-1868, p.\ 362, Emma Mahony; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48417/362/1415467410} : viewed on 12 Apr 2020).
	
	\bibitem{EmmaMahonyDeath}
	Emma A.\ O'Brien obituary, \textit{Boston Traveler}, 11 July 1950, p.\ 31.
	
	\bibitem{PictureFrameLabel}
	``Ephemera collection,'' \textit{Historic New England} (\url{https://www.historicnewengland.org/explore/collections-access/gusn/265637/}: accessed 13 Apr 2020), digital image, ``Label for John J.\ O'Brien, picture frames, 69 Cornhill, Boston, Mass., undated,'' GUSN-265637, reference code EP001.01.091.01.01.003.
	
	\bibitem{Cornhill}
	Ryan W.\ Owen, ``Cornhill -- Once Boston’s Literary Center, Today Replaced by Government Center,'' \textit{Forgotten New England}, 4 June 2012 (\url{https://forgottennewengland.com/2012/06/04/cornhill-once-bostons-literary-center-today-replaced-by-government-center/} : viewed on 13 Apr 2020).
	
	\bibitem{John3OBrien1880}
	Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1880), p.\ 749, John J.\ O'Brien at 82 Hudson; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 13 Apr 2020), Massachusetts > Boston > 1880 > Boston, Massachusetts, City Directory, 1880 > image 749.\\
	There was no Boston city directory available for 1879 and John does not appear in the 1878 directory. He was probably still living in his parents' household.
	
	\bibitem{John3OBrien1916}
	W. A. Greenough Co., compilers, \textit{1916 Medford Directory} (Boston: W. A. Greenough \& Co., 1916), p.\ 219, entry for John J O'Brien; viewed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 13 Apr 2020), Massachusetts > Medford > 1916 > Medford, Massachusetts, City Directory, 1916 > image 217.\\
	``O'Brien John J picture frame mfr 69 Cornhill B 45 Court''\\
	John O'Brien appears in the next available Medford city directory for 1918 with no business or profession listed. In the 1920 census his occupation is listed as ``none.''
	
	\bibitem{FrameShopFire}
	``BROKE THROUGH ROOF.'' \textit{The Boston Globe}, 6 Jan 1904, p.\ 8, col.\ 1; accessed at \textit{Newspapers.com}, database with images (\url{https://www.newspapers.com/image/430269059} : viewed on 13 Apr 2020).
	
	\bibitem{Mildred4OBrienBirth}
	Massachusetts Vital Records, birth records, 1885, p.\ 242, no.\ 10870, Mildred Loretta O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 13 Apr 2020), \_Up Through 1910 > 1890 > image 1514.
	
	\bibitem{Mildred4OBrienDeath}
	Massachusetts Vital Records, death records, 1891, p.\ 175, no.\ 4054, Mildred L.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 13 Apr 2020), \_Pre 1903 > 1891 > image 1268.\\
	Cause of death: ``Ac.\ Tub.\ Meningitis, 2 days.''
	
	\bibitem{Francis4OBrienMarriage}
	Francis J.\ O'Brien wedding announcement, \textit{The Boston Globe}, 9 Sep 1921, p.\ 6, col.\ 3; accessed at \textit{Newspapers.com}, database with images (\url{https://bostonglobe.newspapers.com/image/430448996} : viewed on 13 Apr 2020).\\
	Wedding to take place 12 Sep 1921 at Immaculate Conception Church in Malden.
	
	\bibitem{Francis4OBrienMarriageCert}
	Massachusetts Vital Records, Copy of Certificate of Marriage, 1921, p.\ 307, no.\ 383, Francis Joseph O'Brien and Helena Catherine Flynn.
	
	\bibitem{Mildred4OBrienMarriage}
	``YOUNG COUPLES WHO SELECTED FEBRUARY AS WEDDING MONTH,'' \textit{The Boston Globe}, 28 Feb 1925, p.\ 9; accessed at \textit{Newspapers.com}, database with images (\url{https://bostonglobe.newspapers.com/clip/48666373/the-boston-globe/?xid=637} : viewed on 13 Apr 2020).\\
	Rectory of St. Francis of Assisi Church in Medford
	
	\bibitem{Edward4OBrienBirth}
	Massachusetts Vital Records, birth records, 1898, no.\ 210, Edward O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 13 Apr 2020), \_Up Through 1910 > 1898 > image 1511.
	
	\bibitem{Edward4OBrienDeath}
	Massachusetts Vital Records, death records, 1898, p.\ 329, no.\ 222, Edward O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 13 Apr 2020), \_Pre 1903 > 1898 > image 1071.\\
	Cause of death: ``Pneumonia''
	
	\bibitem{Almyra4OBrienBirth}
	Massachusetts Vital Records, birth records, 1901, no.\ 246, Almyra Louise O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 13 Apr 2020), \_Up Through 1910 > 1901 > image 1016.
	
	\bibitem{Almyra4OBrienDeath}
	Massachusetts Vital Records, death records, 1902, p.\ 628, no.\ 145, Almira L.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 13 Apr 2020), \_Pre 1903 > 1902 > image 1187.\\
	Cause of death: ``Cerebro-spinal Meningitis''
	
	\bibitem{Hannah3WardBirth}
	Massachusetts Vital Records, birth records, 1860, p.\ 80, no.\ 3574, Hannah Ward; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 14 Apr 2020), \_up through 1910 > 1860 > image 979.\\
	Salutation St.
	
	\bibitem{Hannah3WardDeath}
	Massachusetts Vital Records, Death Records, 1919, p.\ 59, no.\ 559, Hannah Flynn; Massachusetts Archives, Boston.\\
	Cause of death: influenza.
	
	\bibitem{Hannah3WardDeath2}
	Massachusetts Vital Records, \textit{Index to Deaths, 1916 - 1920, Donoghue - Gzmski}, vol. 68, Hannah (Ward) Flynn, 1919, vol.\ 7 p.\ 59; accessed at ``Massachusetts, Death Index, 1901-1980,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3659/} : viewed on 19 Apr 2020), 1916-1920 > Donoghue - Gzmski > image 275.
	
	\bibitem{JohnJHFlynn}
	Massachusetts, Suffolk County Registry of Deeds, vol.\ 3310, p. 501, FLYNN to KRUPP; accessed at \textit{masslandrecords} (\url{https://masslandrecords.com/suffolk/} : viewed on 19 Apr 2020), Search Criteria >  Recorded Land > Unindexed Property Search > Book 3310, Page Number 501.\\
	``I, John H.\ Flynn of Boston in the County of Suffolk and Commonwealth of Massachusetts Known as John Flynn and John J Flynn...''
	
	\bibitem{Hannah3WardMarriage}
	Massachusetts Vital Records, marriage records, 1885, p.\ 165, no.\ 2953, John Flynn and Hannah Ward; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 14 Apr 2020), \_up through 1910 > 1885 > image 1033.
		
	\bibitem{JohnFlynnDeath}
	John J.\ Flynn obituary, \textit{The Boston Globe}, 10 Apr 1920, p.\ 10; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/48110261/obituary-for-john-j-flynn/?xid=637} : viewed on 19 Apr 2020).
	
	\bibitem{Census1900HannahWard}
	1900 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 1163, Boston - City, sheet no.\ 8, dwelling no.\ 67, family no.\ 106, Hannah Flynn in household of Mary Ward; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 14 Apr 2020), Massachusetts > Suffolk > Boston Ward 01 > District 1163 > image 11.	
	
	\bibitem{Census1910HannahWard}
	1910 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 1263, Boston city, sheet no.\ 13, dwelling no.\ 126, family no.\ 239, Hannah E Flynn household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 14 Apr 2020), Massachusetts > Suffolk > Boston Ward 01 > District 1163 > image 11.
	
	\bibitem{MorrisSt}
	Massachusetts, Suffolk County Registry of Deeds, 1889, vol.\ 1866, p.\ 417, Cushing et al to Flynn; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-99ZD-P8F7} : viewed on 19 Apr 2020), Suffolk > Deeds 1889 vol 1866 > image 214.
	
	\bibitem{WesleySt}
	Massachusetts, Suffolk County Registry of Deeds, 1891, vol.\ 2014, p.\ 294, Cronin to Flynn; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-89ZD-2K2X} : viewed on 19 Apr 2020), Suffolk > Deeds 1891 vol 2014 > image 154.
	
	\bibitem{103BenningtonSt}
	Massachusetts, Suffolk County Registry of Deeds, vol.\ 2302, p. 202, Cronan To Flynn; accessed at \textit{masslandrecords} (\url{https://masslandrecords.com/suffolk/} : viewed on 20 Apr 2020), Search Criteria > Recorded Land > Unindexed Property Search > Book 2302, Page Number 202.
	
	\bibitem{HannahWardDirectories}
	A review of Boston city directories between 1892 and 1919 shows Hannah and John J.\ Flynn at different addresses for every directory in which they both appear. Beginning in 1910 Hannah was living at 101 Bennington St.\ and John was living at 236 Lexington St.
	
	\bibitem{236Lexington}
	Massachusetts, Suffolk County Registry of Deeds, vol.\ 3301, p. 454, HARRIGAN Admr.\ to FLYNN.; accessed at \textit{masslandrecords} (\url{https://masslandrecords.com/suffolk/} : viewed on 19 Apr 2020), Search Criteria > Recorded Land > Unindexed Property Search >  Book 3301, Page Number 454.
	
	\bibitem{236Lexington2}
	Massachusetts, Suffolk County Registry of Deeds, vol.\ 4245, p. 352, CLAHANE Admx to EAST BOSTON SAVINGS BANK; accessed at \textit{masslandrecords} (\url{https://masslandrecords.com/suffolk/} : viewed on 18 Apr 2020), Search Criteria > Recorded Land > Unindexed Property Search > Book 4245, Page Number 352.
	
	\bibitem{JohnFlynn1889}
	Sampson, Murdock, \& Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Murdock, \& Company, 1889), p.\ 471, John J.\ Flynn at 61 Brooks; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 20 Apr 2020), Massachusetts > Boston > 1889 > Boston, Massachusetts, City Directory, 1889 > image 471.
	
	\bibitem{BropheyLiquors}
	Thomas Brophey, advertisement, \textit{The Boston Globe}, 20 May 1889, p.\ 6, Licensed Liquor Dealers; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/image/430849704} : viewed on 20 Apr 2020).
	
	\bibitem{Harry4FlynnBirth}
	Boston, Massachusetts Vital Records, birth records, 1889, no.\ 3892, Harry Flynn; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 20 Apr 2020), Boston > Births, Marriages and Death > image 45866.\\
	61 Brooks E.B.; parents John J.\ and Hannah E.\ Flynn; father's occupation: bartender
	
	\bibitem{Harry4FlynnDeath}
	U.S.\ Social Security Administration, \textit{Numerical Identification Files (NUMIDENT), created, 1936 - 2007, documenting the period 1936 - 2007}, File Unit: ``Death Files, 1936 - 2007 (Last Names E through G),'' entry for Harry Flynn, 1967,  SS no.\ 03-114-1019; accessed at \textit{The U.S.\ National Archives and Records Administration} (\url{https://aad.archives.gov/aad/series-description.jsp?s=5057} : viewed on 20 Apr 2020).
	
	\bibitem{Harry4FlynnDraft}
	United States, Selective Service System, \textit{World War I Selective Service System Draft Registration Cards, 1917-1918}, card for Harry Joseph Flynn, serial no.\ 502, order no.\ 4014; accessed at ``U.S., World War I Draft Registration Cards, 1917-1918,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6482/} : viewed on 20 Apr 2020), Massachusetts > East Boston C ity > 2 > Draft Card F > image 327.
	
	\bibitem{Census1930HarryFlynn}
	1930 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 13-388, Boston city (Dorchester), sheet no.\ 9B, dwelling no.\ 81, family no.\ 194, Harry J Flynn in Edward W Clahane household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 20 Apr 2020), Massachusetts > Suffolk > Boston (Districts 251-500) > District 0388 > image 18.
	
	\bibitem{Michael3OBrienBirth}
	Massachusetts Vital Records, birth records, 1864, no.\ 868, Michael O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 20 Apr 2020), \_up through 1910 > 1864 > image 719.\\
	33 Fleet St.
	
	\bibitem{Michael3OBrienDeath}
	Massachusetts Vital Records, death records, 1904, p.\ 355, no.\ 5598, Michael F.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 20 Apr 2020), 1904 > Boston > image 5580.\\
	155 London St.\ Occupation: gas meter maker.
	
	\bibitem{LillianAllenMarriage}
	Massachusetts Vital Records, marriage records, 1883, no.\ 20, Michael O'Brien and Lillian A.\ Allen; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 20 Apr 2020), \_Up Through 1910 > 1883 > image 795.\\
	Michael O'Brien occupation: mill hand. Lillian Allen parents: William and Elizabeth Allen.
	
	\bibitem{LillianAllenDeath}
	Massachusetts Vital Records, death records, 1891, no.\ 33, Lillian A.\ Allen; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 20 Apr 2020), \_Pre 1903 > 1891 > image 998.\\
	Cause of death: congestion of the brain. Residence: Norwood.
	
	\bibitem{MaryMacdougallMarriage}
	Massachusetts Vital Records, marriage records, 1899, p.\ 86, no.\ 1540, Michael F.\ O'Brien and Mary A.\ Macdougall; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 20 Apr 2020), \_Up Through 1910 > 1899 > image 1493.\\
	Michael O'Brien occupation: Moroccodresser. Mary Macdougall occupation: Dressmaker. Mary Macdougall parents: Daniel Macdougall and Mary McLean.
	
	\bibitem{MaryMacdougallDeath}
	Massachusetts Vital Records, \textit{Index to Deaths, 1926-1930, Aabel - Celona}, vol. 81, Mary A (McDougall) Bushen, Boston, 1928, vol.\ 1 p.\ 351; accessed at ``Massachusetts, Death Index, 1901-1980,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3659/} : viewed on 22 Apr 2020), 1926-1930 > Aabel - Celona > image 467.
	
	Mary Macdougall married Wilson Bushen in 1910:
	
	Massachusetts Vital Records, marriage records, 1910, p.\ 31, no.\ 692, Wilson Bushen and Mary A.\ O'Brien mn McDougal; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 22 Apr 2020), \_Up Through 1910 > 1910 > image 1862.
	
	\bibitem{moroccodresser}
	United States Bureau of the Census, \textit{Classified Index to Occupations} (Washington, D.C., 1921), p.\ 111; accessed at \textit{Google Books} (\url{https://www.google.com/books/edition/Classified_Index_to_Occupations/31EbAAAAYAAJ} : viewed on 22 Apr 2020).
	
	\bibitem{Arthur4OBrienBirth}
	Massachusetts Vital Records, birth records, 1883, no.\ 45, Arthur Francis O.\ Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 24 Apr 2020), \_up through 1910 > 1883 > image 957.\\
	Michael's occupation: tanner.
	
	\bibitem{Arthur4OBrienDeath}
	Massachusetts Vital Records, death records, 1904, p.\ 169, no.\ 8111, Arthur O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 24 Apr 2020), 1904 > Boston > image 8063.\\
	Cause of death: ``Pul.\ Tuberculosis 10 mos.''; father's occupation: ``Machine Operator.''
	
	\bibitem{Edward4OBrienBirth}
	Massachusetts Vital Records, birth records, 1884, no.\ 72, Edward William O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 24 Apr 2020), \_up through 1910 > 1884 > image 963.\\
	Father's occupation: tanner.
	
	\bibitem{Edward4OBrienDeath}
	Massachusetts Vital Records, death records, 1887, no.\ 3868, Edward F.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 24 Apr 2020), \_Pre 1903 > 1887 > image 942.\\
	Cause of death: accident; address: 243 Border St.
	
	\bibitem{Edward4OBrienDeath2}
	``Run Over and Killed.'' \textit{The Boston Globe}, 25 Apr 1887, p.\ 5; accessed at \textit{Newspapers.com} (\url{https://www.newspapers.com/clip/33349423/edward-obrien-death/} : viewed on 24 Apr 2020).
	
	\bibitem{Elizabeth4OBrienBirth}
	Massachusetts Vital Records, birth records, 1886, no.\ 44, Elisabeth O.\ Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 24 Apr 2020), \_up through 1910 > 1886 > image 998.\\
	Father's occupation: machinist.
	
	\bibitem{Elizabeth4OBrienDeath}
	Massachusetts Vital Records, death records, 1886, no.\ 39, Elisabeth O.Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 24 Apr 2020), \_Pre 1903 > 1886 > image 704.	
	
	\bibitem{Frances4OBrienBirth}
	Massachusetts Vital Records, birth records, 1901, p.\ 1, no.\ 4, Frances May O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 24 Apr 2020), \_up through 1910 > 1901 > image 1246.
	
	\bibitem{Frances4OBrienDeath}
	Massachusetts Vital Records, death records, 1903, p.\ 493, no.\ 10298, Frances L.O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 24 Apr 2020), 1903 > Boston > image 4188.\\
	Cause of death: pneumonia; address: 182 Marion St.
	
	\bibitem{Frances3OBrienBirth}
	Massachusetts Vital Records, birth records, 1866, no.\ 4054, Frances Elizabeth O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 25 Apr 2020), \_up through 1910 > 1866 > image 847.
	
	\bibitem{Frances3OBrienDeath}
	Massachusetts Vital Records, death records, 1915, p.\ 290, no.\ 1875, Frances Wickens; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 25 Apr 2020), 1915 > Boston > image 148.\\
	Residence: 195 London St.; place of death: E.B.Relief Sta.; cause of death: cholemia.
	
	\bibitem{JohnWickensMarriage}
	Massachusetts Vital Records, marriage records, 1891, no.\ 177, John B.\ Wickens and Fannie E O'Brien; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 25 Apr 2020), \_Up Through 1910 > 1891 > image 1601.\\
	John B.\ Wickens occupation: mariner
	
	\bibitem{JohnWickensNaturalization}
	John B.\ Wickens, petition for naturalization (1895), no.\ 98, District of Massachusetts; Record Group 85: Records of the Immigration and Naturalization Service, 1787-2004; National Archives at Boston, Waltham, Massachusetts; viewed at ``Massachusetts, State and Federal Naturalization Records, 1798-1950,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2361/} : viewed on 25 Apr 2020), District Court, Massachusetts > Petitions, V 203, 1895 > image 211.\\
	Address: 87 Morris Street, East Boston; Occupation: fireman
	
	\bibitem{JohnWickensMarriage2}
	Clark County, Washington, Marriage Records, 1916, no.\ 9304, John B.\ Wickens and Anna M.\ McGunigle; accessed at `` Washington, Clark County, marriage records, 1852-2000, 1867-1947,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-99DT-3G8Y} : viewed on 25 Apr 2020), Marriage certificates, no. 9101-9550, 1916 > image 357.
	
	\bibitem{Nellie4WickensDeath}
	Massachusetts Vital Records, Death Records, 1893, p.\ 295, no.\ 6479, Nellie Wickens; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 26 Apr 2020), \_Pre 1903 > 1893 > image 1582.
	
	\bibitem{Frederick4WickensBirth}
	Massachusetts Vital Records, Birth Records, 1895, no.\ 9274, Frederick John Wickens; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 26 Apr 2020), \_up through 1910 > 1895 > image 1950.
	
	\bibitem{Frederick4WickensDeath}
	Massachusetts Vital Records, Death Records, 1896, p. 272, no.\ 5983, Frederick J.\ Wickens; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 26 Apr 2020), \_Pre 1903 > 1896 > image 1667.
	
	\bibitem{Census1900JohnWickens}
	1900 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 1163,  Boston, sheet no.\ 10, dwelling no.\ 119, family no.\ 212, John Wickens household; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 26 Apr 2020), Massachusetts > Suffolk > Boston Ward 01 > District 1163 > image 20.
	
	\bibitem{Edward3OBrien2Birth}
	Massachusetts Vital Records, Birth Records, 1879, p.\ 63, no.\ 2830, Edward Francis O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 26 Apr 2020), \_up through 1910 > 1879 > image 934.\\
	Address: 243 Border St.; father's occupation: oyster opener.
	
	\bibitem{Edward3OBrien2Death}
	Pennsylvania Vital Records, Death Records, 1929, no.\ 82469, Edward F.\ O'Brien; accessed at ``Pennsylvania, Death Certificates, 1906-1967,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5164/} : viewed on 26 Apr 2020), 1929 > 081001-084000 > image 1591.\\
	Occupation: clerk; cause of death: chronic myocarditis; place of burial: Jamaica Plains Boston, Aug 28 1919.
	
	\bibitem{Edward3OBrien2Marriage}
	Massachusetts Vital Records, Marriage Records, 1909, no.\ 3035 , Edward F O'Brien and Marie F Gill; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 26 Apr 2020), \_Up Through 1910 > 1909 > image 1925.\\
	Edward O'Brien residence: Hartford, Conn.; occupation: gas meter repairer; Marie Gill's parents: John A Gill and Catherine L Howard.
	
	\bibitem{MaryGillBirth}
	Boston, Massachusetts Vital Records, Birth Records, 1884, no.\ 4209, Mary Frances Gill; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 26 Apr 2020), Boston > Births, Marriages and Death > image 43226.	
	
	\bibitem{MaryGillDeath}
	Marie F.\ (Gill) O'Brien obituary, \textit{The Boston Globe}, 16 Jul 1958, p.\ 46; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/49607498/obituary-for-hn-mn-a-fipwn-war/?xid=637} : viewed on 26 Apr 2020).
	
	\bibitem{MaryGillDeath2}
	Massachusetts Vital Records, ``Index to deaths in Massachusetts 1956 - 1960,'' Mary F (Gill) O'Brien; accessed at ``Massachusetts indexes to births and marriages (1841-1920), deaths (1841-1971),'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-CSL5-FSQC-S} : viewed on 26 Apr 2020), Index to deaths Mor-Z 1956-1960 > image 163.
	
	\bibitem{Walter4OBrienBirth}
	Massachusetts Vital Records, Birth Records, 1914, p.\ 398, no.\ 7959, Walter Gill O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 26 Apr 2020), 1914 > Boston > image 199.
	
	\bibitem{Walter4OBrienDeath}
	Lt.\ Walter G.\ O'Brien obituary, \textit{The Boston Globe}, 23 Mar 1949, p.\ 15; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/42657517/obituary/?xid=637} : viewed on 26 Apr 2020).
	
	\bibitem{Walter4OBrienPromotion}
	``Marine From Milton Made 2d Lieutenant,'' \textit{The Boston Globe}, 1 Feb 1943, p.\ 5; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/49659036/the-boston-globe/?xid=637} : viewed on 26 Apr 2020).
	
	\bibitem{Mary4OBrienBirth}
	U.S.\ Social Security Administration, \textit{Death Master File}, entry for Mary L Obrien, 2011; accessed at ``United States Social Security Death Index,'' database, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/1:1:VHC7-JPQ} : viewed on 27 Apr 2020).
	
	\bibitem{Mary4OBrienBirth2}
	Massachusetts Vital Records, \textit{Index to Births, 1921 - 1925, Mikool - Perras}, vol.\ 111, Mary Lucia O'Brien, 1921 vol.\ 1 p.\ 118; accessed at ``Massachusetts, Birth Index, 1860-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3928/} : viewed on 27 Apr 2020), Births > 1921-1925 > Mikool - Perras > image 366.
	
	\bibitem{Mary4OBrienDeath}
	Mary L.\ O'Brien obituary, \textit{The Patriot Ledger}, 5 Sep 2011; \textit{GenealogyBank.com} (\url{https://www.genealogybank.com/doc/obituaries/obit/139995AE102675E0-139995AE102675E0} : viewed on 27 Apr 2020).
	
	\bibitem{Epilogue}
	Emmanuel College, Class of 1942, \textit{The 1942 Epilogue}, p.\ 152, ``Ex-Members''; Emmanuel College Archives, Cardinal Cushing Library (\url{http://library.emmanuel.edu/archive/content/1942-yearbook} : viewed on 27 Apr 2020).
	
	\bibitem{Census1910Edward3OBrien}
	1910 U.S.\ census, Hartford County, Connecticut, population schedule, Enumeration District (ED) 184, Hartford City, page no.\ 17A, dwelling no.\ 122, family no.\ 277, Edward F.\ O'Brien household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 27 Apr 2020), Connecticut > Hartford > Hartford Ward 7 > District 0179.
	
	\bibitem{Census1920Edward3OBrien}
	1910 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 529, Jamaica Plain, Boston, sheet no.\ 5A, dwelling no.\ 75, family no.\ 99, Edward F.\ O'Brien household; accessed at ``1920 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6061/} : viewed on 27 Apr 2020), Massachusetts > Suffolk > Boston Ward 22 > District 0529 > image 9.
	
	\bibitem{Edward3OBrien1920}
	Sampson \& Murdock Company, compilers, \textit{The Boston Directory} (Boston: Sampson \& Murdock Co., 1920), p.\ 1240, Edward F.\ O'Brien at 58 Rockview J P; accessed at ``U.S. City Directories, 1822-1995,'' \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 27 Apr 2020), Massachusetts > Boston > 1920 > Boston, Massachusetts, City Directory, 1920 > image 1248.
	
	\bibitem{Catharine4SimondsBirth}
	Boston, Massachusetts Vital Records, Birth Records, 1860, no.\ 3592, Catharine Simons; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 28 Apr 2020), Boston > Births, Marriages and Death > image 54601.
	
	\bibitem{Catharine4SimondsBaptism}
	St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 380, Catharine Simonds; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/380/1423783048} : viewed on 28 Apr 2020).\\
	Sponsors: Michael O'Brien and Margaret Hughes.
	
	\bibitem{JohnMcCarthyMarriage}
	Massachusetts Vital Records, Marriage Records, 1879, no.\ 560, John McCarthy and Catharine Simons; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 28 Apr 2020), \_Up Through 1910 > 1879 > image 757.\\
	John McCarthy's occupation: painter.
	
	\bibitem{Census1880Catharine4Simonds}
	1880 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 587, Boston, page no.\ 3, dwelling no.\ 15, family no.\ 23, Katie McCarthy in John F.\ McCarthy household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 28 Apr 2020), Massachusetts > Suffolk > Boston > 587 > image 3.\\
	Address: 146 Marginal Street, next door to 148 Marginal Street (Margaret Fernald and Abby Dooley)
	
	\bibitem{Catharine4SimondsDeath}
	Massachusetts Vital Records, Death Records, 1890, no.\ 1930, Catharine McCarthy m.n.\ Simonds; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 28 Apr 2020), \_Pre 1903 > 1890 > image 1087.\\
	Cause of death: ``Alcoholism \& Epiletiform (seizures)''; Address: 252 Paris St.\ and 24 Havre St.; Occupation: housekeeper.
	
	\bibitem{Helen5McCarthyBirth}
	Massachusetts Vital Records, Birth Records, 1879, no.\ 2886, Helen McCarthy; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 29 Apr 2020), \_up through 1910 > 1879 > image 936.
	
	\bibitem{Helen5McCarthyMarriage}
	Massachusetts Vital Records, Marriage Records, 1899, p.\ 191, no.\ 3424, William H.\ Westlake and Helen McCarthy; Accessed at ``Massachusetts Marriages, 1841-1915,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:N44K-5CD} : viewed on 28 Apr 2020), 004332421 > image 205.
	
	\bibitem{Helen5McCarthyDeath}
	Helen Westlake obituary, \textit{The Boston Globe}, 18 Apr 1966, p.\ 50; accessed at \textit{Newsapers.com} (\url{https://bostonglobe.newspapers.com/clip/49813003/obituary-for-helen-westlake/?xid=637} : viewed on 29 Apr 2020).
	
	\bibitem{William5WestlakeBirth}
	Massachusetts Vital Records, Birth Records, 1900, p.\ 148, no.\ 6642, William Atwell Westlake; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 1 May 2020), \_up through 1910 > 1900 > image 2510.	
	
	\bibitem{William5WestlakeDeath}
	``WILLIAM A.\ WESTLAKE WAS A CLERK IN FILENE'S,'' \textit{The Boston Globe}, 2 Jan 1926, p.\ 5; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50033428/the-boston-globe/?xid=637} : viewed on 1 May 2020).

	\bibitem{Abigail4SimondsBirth}
	Massachusetts Vital Records, Birth Records, 1867, no.\ 22, Abby Simonds; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 1 May 2020), \_up through 1910 > 1867 > image 762.\\
	32 Fleet St.
	
	\bibitem{Abigail4SimondsDeath}
	Abigail J. (Simonds) Rogan obituary, \textit{The Boston Globe}, 9 May 1958, p.\ 26; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50035569/the-boston-globe/?xid=637} : viewed on 1 May 2020).
	
	\bibitem{Abigail4SimondsMarriage}
	Boston, Massachusetts Vital Records, Marriage Records, 1890, no.\ 1599, John H.\ Rogan and Abigail J.\ Simonds; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 1 May 2020), Boston > Births, Marriages and Death > image 28139.\\
	John Rogan occupation; printer; Abigail Simonds occupation: operative; John Rogan parents: William and Mary.
	
	\bibitem{Census1880JohnRogan}
	1880 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 790, Chelsea, page no.\ 42, dwelling no.\ 337, family no.\ 472, John Rogan in William Rogan household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 1 May 2020), Massachusetts > Suffolk > Chelsea > 790 > image 42.\\
	John Rogan age 14, born in Mass.
	
	\bibitem{Census1900AbigailSimonds}
	1900 U.S.\ census, Middlesex County, Massachusetts, population schedule, Enumeration District (ED) 947, Somerville, sheet no.\ 3B, dwelling no.\ 51, family no.\ 58, John H.\ Rogan household; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 1 May 2020), Massachusetts > Middlesex > Somerville Ward 05 > District 0947.
	
	\bibitem{Census1910AbigailSimonds}
	1910 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 1269, Boston City, sheet no.\ 13B, dwelling no.\ 104, family no.\ 232, John H.\ Rogan household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 1 May 2020), Massachusetts > Suffolk > Boston Ward 2 > District 1269 > image 26.
	
	\bibitem{Census1930AbigailSimonds}
	1930 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 13-5, sheet no.\ 17A, dwelling no.\ 349, family no.\ 349, Abbigail J.\ Rogan household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 1 May 2020), Massachusetts > Suffolk > Boston (Districts 1-250) > District 0005 > image 33.
	
	\bibitem{Census1930JohnRogan}
	1930 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 13-117, sheet no.\ 17B, dwelling no.\ 216, family no.\ 249, John H.\ Rogan in Mabel F.\ Patton household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 1 May 2020), Massachusetts > Suffolk > Boston (Districts 1-250) > District 0117 > image 34.
	
	\bibitem{William5RoganBirth}
	Massachusetts Vital Records, Birth Records, 1891, p.\ 1, no.\ 43, William H.\ Rogan; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 1 May 2020), \_up through 1910 > 1891 > image 1677.
	
	\bibitem{William5RoganDeath}
	Florida Vital Records, death index, 1877-1998, William H Rogan on Jan 1963; accessed at ``Florida Death Index, 1877-1998,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7338/} : viewed on 2 May 2020).
	
	\bibitem{William5RoganHeadstone}
	``Applications for Headstones for U.S. Military Veterans, 1925-1941,'' application for William H Rogan, Records of the Office of the Quartermaster General, Record Group 92, National Archives at Washington, D.C.; accessed at ``U.S., Headstone Applications for Military Veterans, 1925-1963,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2375/} : viewed on 2 May 2020), 1962-1963 > Robbins, Robert Theodore - Rybicki, George A > image 1546.
	
	\bibitem{William5RoganMarriage}
	New York City Department of Records, ``Index to New York City Marriages, 1866-1937,'' William H Rogan and Irene Hickey, certificate no.\ 22854; accessed at ``New York, New York, Extracted Marriage Index, 1866-1937,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9105/} : viewed on 2 May 2020).
	
	\bibitem{Marguerite5RoganBirth}
	St. Rose of Lima (Chelsea) Baptisms, 1890-1893, p.\ 306, Margarte Rogan; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53438/306/1423647175} : viewed on 2 May 2020).
	
	\bibitem{Census1940Marguerite5Rogan}
	1940 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 15-9, sheet no.\ 8A, dwelling no.\ 58, family no.\ 158, Marguerite Shea in John J Shea household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 2 May 2020), Massachusetts > Suffolk > Boston > 15-9 > image 15.
	
	\bibitem{Abigail5RoganBirth}
	Massachusetts Vital Records, Birth Records, 1898, no.\ 938, Abigail Josephine Rogan; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1898 > image 229.
	
	\bibitem{Abigail5RoganDeath}
	Abbie J.\ Rogan obituary, \textit{The Boston Globe}, 10 Mar 1960, p.\ 14; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50068694/obituary-for-abbie-j-rogan/?xid=637} : viewed on 2 May 2020).
	
	\bibitem{Mary5RoganBirth}
	Massachusetts Vital Records, Birth Records, 1904, p.\ 103, no.\ 4605, Mary Alice Rogan; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1904 > image 1757.
	
	\bibitem{Mary5RoganDeath}
	(Mary) Alice Rogan obituary, \textit{The Boston Globe}, 10 Sep 1971, p.\ 41; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50069142/obituary-for-rogan/?xid=637} : viewed on 2 May 2020).
	
	\bibitem{Anne5RoganBirth}
	Massachusetts Vital Records, Birth Records, 1907, no.\ 17609, Anna Rogan; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1907 > image 2171.
	
	\bibitem{Anne5RoganDeath}
	U.S.\ Social Security Administration, \textit{Death Master File}, Ann I.\ Doran, 2001; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 2 May 2020).
	
	\bibitem{Census1940Anne5Rogan}
	1940 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 13-57, Revere City, sheet no.\ 8B, dwelling no.\ 110, family no.\ 168, Anna Doran in John P.\ Doran household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 2 May 2020), Massachusetts > Suffolk > Revere > 13-57 > image 17.	
	
	\bibitem{Caroline4FernaldBirth}
	Massachusetts Vital Records, Birth Records, 1876, no.\ 4804, Caroline Fernald; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1876 > image 979.
	
	\bibitem{WilliamMcGurinMarriage}
	Boston, Massachusetts Vital Records, Marriage Records, 1873, no.\ 2252, William P McGurin and Harriet F Saunders; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495} : viewed on 16 Jul 2020), Boston > Boston Marriages, 1873 > image 134.
	
	\bibitem{Caroline4FernaldDeath}
	``EAST BOSTON DISTRICT,'' \textit{The Boston Globe}, 31 Aug 1927, p.\ 5; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/24119074/the-boston-globe/?xid=637} : viewed on 2 May 2020).	
	
	\bibitem{Caroline4FernaldMarriage}
	Boston, Massachusetts Vital Records, Marriage Records, 893, no.\ 646, John J.\ McGurin and Caroline E.\ Fernald; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 2 May 2020), Boston > Out of Town Marriages, 1893-1895 > image 39.
	
	\bibitem{JohnMcGurinBirth}
	Massachusetts Vital Records, Birth Records, 1875, no.\ 2301, John McGurin; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1875 > image 965.
	
	\bibitem{JohnMcGurinDeath}
	John J.\ McGurin obituary, \textit{The Boston Globe}, 12 Jan 1968, p.\ 33; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50073830/obituary-for-john-j-mcgurin/?xid=637} : viewed on 2 May 2020).
	
	\bibitem{Robert5McGurinBirth}
	Massachusetts Vital Records, Birth Records, 1894, no.\ 141, Robert McGurin; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1894 > image 1207.	
	
	\bibitem{Robert5McGurinDeath}
	Department of Public Health, Registry of Vital Records and Statistics, ``Index to Deaths in Massachusetts 1951-1955, Krannich - Mysorski,'' vol. 115, Robert A McGurin, Everett, 1955, vol.\ 43, p.\ 286; accessed at ``Massachusetts, Death Index, 1901-1980,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3659/} : viewed on 2 May 2020), 1951-1955 > Krannich - Mysorski > image 405.
	
	\bibitem{Robert5McGurinMarriage}
	Massachusetts Vital Records, Marriage Records, 1913, p.\ 176, no.\ 4026, Robert A McGurin and Alta M Saunders; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 2 May 2020), 1913 > Boston > image 176.
	
	\bibitem{Walter5McGurinBirth}
	Massachusetts Vital Records, Birth Records, 1896, no.\ 4228, Walter Edward McGurn; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1896 > image 1961.
	
	\bibitem{Walter5McGurinDeath}
	Walter E. McGurin obituary, \textit{Boston Herald}, 31 Mar 1974, p.\ 18; accessed at \textit{GenealogyBank} (\url{https://www.genealogybank.com/doc/newspapers/image/v2:1386BF60B4F67060@GB3NEWS-14BA6606AF2D71BD@2442138-14BA6416336E4243@17-14BA6416336E4243} : viewed on 2 May 2020).
	
	\bibitem{Alfred5McGurinBirth}
	Massachusetts Vital Records, Birth Records, 1898, no.\ 2062, Alfred McGurn; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1898 > image 1904.
	
	\bibitem{Alfred5McGurinDeath}
	McGurin obituary, \textit{The Boston Globe}, 21 Oct 1919, p. 10; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/34912236/mcgurin/?xid=637} : viewed on 2 May 2020).	
	
	\bibitem{Alfred5McGurinDeath2}
	``FITTON CLUB HONORS ITS HEROES OF WAR,'' \textit{The Boston Globe}, 30 Apr 1919, p.\ 2; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/34912179/alfred_j_mcgurin/?xid=637} : viewed on 2 May 2020).
	
	\bibitem{Margaret5McGurinBirth}
	Massachusetts Vital Records, Birth Records, 1899, p.\ 262, no.\ 11759, Margaret McGurn; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 2 May 2020), \_up through 1910 > 1899 > image 2307.
	
	\bibitem{Margaret5McGurinDeath}
	Margaret E.\ (McGurin) Phillips obituary, \textit{The Boston Globe}, 19 Nov 1992, p.\ 56; accessed at \textit{Newspapers.com} 
	(\url{https://bostonglobe.newspapers.com/clip/50080606/obituary-for-p-hillips-of-everett/?xid=637} : viewed on 2 May 2020).
	
	\bibitem{Sarah5McGurinBirth}
	Massachusetts Vital Records, Birth Records, 1901, p.\ 182, no.\ 8178, Sarah McGurin; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 4 May 2020), \_up through 1910 > 1901 > image 1766.\\
	Father's occupation: milkman.
	
	\bibitem{Sarah5McGurinDeath}
	Sadie H.\ (McGurin) Murphy obituary; \textit{The Boston Globe}, 10 Jan 1999, p.\ 49; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50255204/obituary-for-mo-rphy-of/?xid=637} : viewed on 4 May 2020).
	
	\bibitem{Edward5McGurinBirth}
	Massachusetts Vital Records, Birth Records, 1902, p.\ 287, no.\ 12907, Edward McGurn; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 4 May 2020), \_up through 1910 > 1902 > image 1871.
	
	\bibitem{Edward5McGurinDeath}
	U.S.\ Social Security Administration, \textit{Death Master File}, Edward McGurin, 1968; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 4 May 2020).
	
	\bibitem{Edward5McGurinMarriage}
	City of Boston Registry Department, Marriage License, Int.\ No.\ 6249, Cert.\ No.\ 5595, Edward J.\ McGurin and Helen Duffy; accessed at ``Massachusetts Marriages, 1841-1915,'' database with images, FamilySearch (https://familysearch.org/ark:/61903/1:1:Q28K-7VML : viewed on 4 May 2020).
	
	\bibitem{Caroline5McGurinBirth}
	Massachusetts Vital Records, Birth Records, 1904, p.\ 136, no.\ 6110, Caroline Josephine McGurin; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 4 May 2020), \_up through 1910 > 1904 > image 1790.	
	
	\bibitem{Caroline5McGurinDeath}
	Caroline McGurin obituary, \textit{The Boston Globe}, 3 Apr 1921, p.\ 40; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50258765/the-boston-globe/?xid=637} : viewed on 4 May 2020).
	
	\bibitem{Catherine5McGurinBirth}
	Massachusetts Vital Records, Birth Records, 1906, no.\ 8657, Catherine McGurin; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 4 May 2020), \_up through 1910 > 1906 > image 1891.	
		
	\bibitem{Catherine5McGurinDeath}
	Catherine (McGurin) Kelleher obituary, \textit{The Boston Globe}, 20 Dec 1999, p.\ 30; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50255152/obituary-for-r-of-kellehe-everett/?xid=637} : viewed at 4 May 2020).
	
	\bibitem{Josephine5McGurinBirth}
	Massachusetts Vital Records, Birth Records, 1908, p.\ 296, no.\ 13289, Josephine McGurin; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 May 2020), \_up through 1910 > 1908 > image 2147.	
	
	\bibitem{Josephine5McGurinDeath}
	Josephine M.\ McGurin obituary; \textit{The Boston Globe}, 20 May 1926, p.\ 28; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50260938/the-boston-globe/?xid=637} : viewed on 5 May 2020).
	
	\bibitem{John5McGurinBirth}
	Massachusetts Vital Records, Birth Records, 1914, p.\ 290, no.\ 5781, John F McGurin; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 May 2020), 1914 > Boston > image 145.	
	
	\bibitem{John5McGurinDeath}
	John F.\ McGurin obituary, \textit{The Boston Globe}, 7 Dec 2005, p.\ 60; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50261436/obituary-for-john-f-mcgurin-aged-91/?xid=637} : viewed on 5 May 2020).
	
	\bibitem{Charles5McGurinBirth}
	United States, Selective Service System, \textit{U.S. WWII Draft Cards Young Men, 1940-1947}, card for Charles Alfred McGurin, serial no.\ 728, order no.\ 218; accessed at ``U.S. WWII Draft Cards Young Men, 1940-1947,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 5 May 2020), Massachusetts > Maguire-McLeod > McGuillan, Roddy-McHugo, Winfred > image 939.
	
	\bibitem{Charles5McGurinDeath}
	Charles A.\ McGurin obituary, \textit{The Boston Globe}, 21 Dec 2004, p.\ 38; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50261840/obituary-for-charles-a-mcgurln-aged/?xid=637} : viewed on 5 May 2020).
	
	\bibitem{Sarah4FernaldBirth}
	Massachusetts Vital Records, Birth Records, 1879, no.\ 2887, Sarah Fernald; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 6 May 2020), \_up through 1910 > 1879 > image 936.
	
	\bibitem{Sarah4FernaldDeath}
	Sarah H.\ Leonard obituary, \textit{The Boston Globe}, 26 Mar 1943, p.\ 21; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50391545/obituary-for-sarah-h-fernald-leonard/?xid=637} : viewed on 6 May 2020).
	
	\bibitem{Sarah4FernaldMarriage}
	Massachusetts Vital Records, Marriage Records, 1902, no.\ 4372, Christopher T Leonard and Sarah H Fernald; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 6 May 2020), \_up through 1910 > 1902 > image 1742.
	
	\bibitem{ChristopherLeonardBirth}
	Boston, Massachusetts Vital Records, Birth Records, 1872, no.\ 6431, Christopher Leonard; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 6 May 2020), Boston > Additions and Corrections to Births, 1870-1881 > image 57.\\
	Aug 24 crossed out and written Jul 29; typed: ``Bapt Rec''
	
	\bibitem{ChristopherLeonardDeath}
	Christopher T. Leonard obituary, \textit{The Boston Globe}, 11 Sep 1945, p.\ 32; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50392156/obituary-for-christopher-t-leonard-in/?xid=637} : viewed on 6 May 2020).
	
	\bibitem{Mary5LeonardBirth}
	Massachusetts Vital Records, Birth Records, 1903, no.\ 13868, Mary Margaret Leonard; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 6 May 2020), \_up through 1910 > 1903 > image 1916.
	
	\bibitem{Mary5LeonardDeath}
	Mary M. (Leonard) Duffy obituary, \textit{The Boston Globe}, 2 Jun 1993, p.\ 28; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50395256/obituary-for-d-uffy-of-holden-aged-89/?xid=637} : viewed on 6 May 2020).\\
	``Retired supervisor for New England Telephone.''
	
	\bibitem{George5LeonardBirth}
	Massachusetts Vital Records, Birth Records, 1905, no.\ 7220, George Thomas Leonard; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 6 May 2020), \_up through 1910 > 1905 > image 1816.
	
	\bibitem{George5LeonardDeath}
	George T.\ Leonard obituary, \textit{The Boston Globe}, 11 Apr 1989, p.\ 24; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50395946/obituary-for-leonard-leonard/?xid=637} : viewed on 6 May 2020).
	
	\bibitem{Robert4FernaldBirth}
	Massachusetts Vital Records, Birth Records, 1882, p.\ 123, no.\ 5520, Robert Atwell Fernald; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 10 May 2020), \_up through 1910 > 1882 > image 1104.
	
	\bibitem{Robert4FernaldDeath}
	Robert A.\ Fernald obituary, \textit{The Boston Globe}, 28 May 1965, p.\ 31; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50690743/obituary-for-robert-a-fernald-aged-82/?xid=637} : viewed on 10 May 2020).
	
	\bibitem{Robert4FernaldMarriage}
	Massachusetts Vital Records, Marriage Records, 1911, p.\ 160, no.\ 3670, Robert A Fernald and Agnes M Leonard; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 10 May 2020), 1911 > Boston > image 160.\\
	Both age 29. Agnes Leonard parents: Matthew Leonard and Mary Harford.
	
	\bibitem{AgnesLeonardBirth}
	Boston, Massachusetts Vital Records, Birth Records, 1881, no.\ 3971, Agnes Leonard; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 10 May 2020), Boston > Births, Marriages and Death > image 58657.
	
	\bibitem{AgnesLeonardDeath}
	U.S.\ Social Security Administration, \textit{Death Master File} database, Agnes Fernald, Oct 1975; accessed at ``United States Social Security Death Index,'' database, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:J1Y2-Q2R} : viewed on 10 May 2020).
	
	\bibitem{Census1915Marion5Fernald}
	1915 New York state census, Monroe County, population schedule, Rochester, block 2, election district 3, ward 13, p.\ 10, 22 Whalin St., Marion E.\ Fernald in Robert A.\ Fernald household; accessed at ``New York, State Census, 1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2703/} : viewed on 10 May 2020), Monroe > Rochester Ward 13 > A.D.\ 03 E.D.\ 03 > image 6.
	
	\bibitem{Marion5FernaldGrave}
	Ancestry, \textit{Find A Grave}, database with images (\url{https://www.findagrave.com/memorial/180138280} : viewed on 10 May 2020), memorial 180138280, Marion Elizabeth Weatherup (1914-2008), gravestone photography by Alex Cost.
	
	\bibitem{Marion5FernaldSS}
	U.S.\ Social Security Administration, \textit{Death Master File} database, Marion Elizabeth Weatherup, 23 Oct 2008; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{FamilySearch} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 10 May 2020).
	
	\bibitem{Francis4OBrienBirth}
	Massachusetts Vital Records, Birth Records, 1892, no.\ 9515, Francis Joseph O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 10 May 2020), \_up through 1910 > 1892 > image 1606.
	
	\bibitem{Francis4OBrienDeath}
	Malden, Middlesex County, Massachusetts, City Vital Records, Standard Certificate of Death for Frank J. O'Brien, 1958, no.\ 72.
	
	\bibitem{MaryFlynnBirth}
	Government of Prince Edward Island, \textit{PARO Collections} database (\url{http://www.gov.pe.ca/parosearch/} : viewed on 10 May 2020), baptismal record of Mary Helena Flynn, citing St. Dunstan's Basilica, record book no.\ 5, p.\ 9.
	
	\bibitem{MaryFlynnDeath}
	Helena C.\ (Flynn) O'Brien obituary, \textit{The Boston Globe}, 21 Apr 1981, p.\ 22; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50697200/obituary-for-helena-c-obrien/?xid=637} : viewed on 10 May 2020).
	
	\bibitem{Francis4OBrienBPOE}
	Deaths, ``MEDFORD LODGE \#915, B.\ P.\ O.\ E.,'' \textit{The Boston Globe}, 6 Feb 1958, p.\ 25; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/50699087/the-boston-globe/?xid=637} : viewed on 10 May 2020).
	
	\bibitem{Francis4OBrienAccounting}
	\textit{Boston and Maine Railroad Employees Magazine}, vol.\ 17, no.\ 5, May 1949, p.\ 30, accounting department photo showing Frank O'Brien; Boston \& Maine Railroad Historical Society, Lowell, Mass.
	
	\bibitem{Francis4OBrienInspector}
	\textit{Boston and Maine Railroad Employees Magazine}, vol.\ 19, no.\ 11, Nov 1951, p.\ 31, photo showing Frank O'Brien; Boston \& Maine Railroad Historical Society, Lowell, Mass.
	
	\bibitem{Francis4OBrienPoet}
	``B.\ of R.\ C.\ Installation,'' \textit{Boston and Maine Railroad Employees Magazine}, vol.\ 4, no.\ 11, Feb 1928, p.\ 28; Boston \& Maine Railroad Historical Society, Lowell, Mass.
	
	\bibitem{Francis5OBrienBirth}
	United States, Selective Service System, ``Draft Registration Cards for Massachusetts, 10/16/1940-03/31/1947,'' Record Group: ``Records of the Selective Service System, 147,'' Box: 722, card for Francis Joseph O'Brien, serial no.\ 140, order no.\ 11626; accessed at ``U.S.\ WWII Draft Cards Young Men, 1940-1947,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 17 May 2020), , Massachusetts > Murphy-Panagacos > O´Brien, Edward L.-O´Brien, John L. > image 290.
	
	\bibitem{Francis5OBrienDeath}
	Francis J. O'Brien obituary, \textit{The Patriot Ledger}, 7 Nov 2015; accessed at \textit{Legacy.com} (\url{https://www.legacy.com/obituaries/southofboston-ledger/obituary.aspx?n=francis-j-obrien\&pid=176378266} : viewed on 17 May 2020).
	
	\bibitem{Francis5OBrienMarriage}
	Town of Andover, Essex County, Massachusetts, ``Copy of Record of Marriage,'' Francis J.\ O'Brien and Marie I.\ Eastwood, married 10 Jun 1950, date of record 13 Jun 1950.
	
	\bibitem{Pauline4OBrienBirth}
	Massachusetts Vital Records, Birth Records, 1894, p.\ 155 (stamped), no.\ 7033, Pauline O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 17 May 2020), \_up through 1910 > 1894 > image 1809.

	\bibitem{Pauline4OBrienBaptism}
	St. Peter (Dorchester) Baptisms, 1887-1895, p.\ 89, Paulina O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/57120/89/1426642661} : viewed on 17 May 2020).
	
	\bibitem{Pauline4OBrienDeath}
	U.S.\ Social Security Administration, \textit{Death Master File}, Pauline Baine, 1967; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 17 May 2020).
	
	\bibitem{Pauline4OBrienDeath2}
	Pauline M.\ Baine obituary, \textit{The Boston Globe}, 3 Feb 1967, p.\ 30; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/46653093/obituary-for-pauline-m-baine/?xid=637} : viewed on 17 May 2020).
	
	\bibitem{CharlesBaineMarriage2}
	Massachusetts Vital Records, ``Index to Marriages in Marrachusetts 1926-1930,'' vol.\ 96, Aaker - Brotherston, entry for Charles Lucius Baine; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 17 May 2020), 1926-1930 > Aaker - Brotherston > image 184.
	
	\bibitem{CharlesBaineMarriage}
	Massachusetts vital records, certificate of marriage, Charles Lucius Baine and Pauline Mary O'Brien, 1930, vol.\ 45, no.\ 323.
	
	\bibitem{CharlesBaineBaptism}
	Chicago, Illinois, Catholic Diocese, ``Old St. Stephen Chicago Baptism 1869-1915 N.I.,'' 1895, p.\ 131, Charles L. Baine on 15 Jul 1895; accessed at ``Illinois, Chicago, Catholic Church Records, 1833-1925,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:QVMJ-3Q37} : viewed on 17 Jul 2020),  St Stephen Parish (Chicago: Old, Ohio St) > Baptisms, marriages 1869-1915 > image 137.
	
	\bibitem{CharlesBaineDeath}
	Charles L.\ Baine obituary, \textit{The Boston Globe}, 2 Mar 1962, p.\ 24; accessed at \textit{Newspapers.com} (\url{https://www.newspapers.com/clip/22565355/charles-l-baine-obituary/?xid=865} : viewed on 17 May 2020).
	
	\bibitem{CharlesBainePassport}
	U.S.\ Department of State, ``Passport Applications, 1914-1925,'' Special Series: New York, vol.\ 4, application numbers 1 to 249, no.\ 51, application for Charles L.\ Baine; aaccessed at ``U.S. Passport Applications, 1795-1925,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/1174/} : viewed on 17 May 2020), Passport Applications: Chicago, New York City, New Orleans, San Francisco and Seattle, 1914-1925 > 1918-1919 > Volume 04: Special Series - New York > image 264.
	
	\bibitem{Census1880CharlesBaine}
	1880 U.S. census, Monroe County, New York, population schedule, Enumeration District (ED) 93, Rochester, p. 11, dwelling no.\ 105, family no.\ 113, William Baine household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 17 May 2020), New York > Monroe > Rochester > 093 > image 11.
	
	\bibitem{Gompers}
	Samuel Gompers, edited by Peter J. Albert and Grace Palladino, \textit{The Samuel Gompers Papers: Progress and Reaction in the Age of Reform, 1909-1913} (Urbana and Chicago: University of Illinois Press, 2000), pp.\ 415--416; accessed at \textit{Google Books} (\url{https://books.google.com/books?id=5IYsQ\_8fSIoC\&lpg=PA416\&ots=oQa308V0UG\&dq=samuel\%20gompers\%20charles\%20baine\&pg=PA416#v=onepage\&q=samuel\%20gompers\%20charles\%20baine\&f=false} : viewed on 17 May 2020).
	
	\bibitem{Mildred4OBrien2Birth}
	Massachusetts Vital Records, Birth Records, 1896, p.\ 169, no.\ 7598, Mildred O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 17 May 2020), \_up through 1910 > 1896 > image 2036.
	
	\bibitem{Mildred4OBrien2Death}
	Boston, Suffolk County, Massachusetts, ``Standard Certificate of Death'' for Mildred French, 1927, no.\ 1911.\\
	Cause of death: pulmonary embolism following caesarian section.
	
	\bibitem{Mildred4OBrien2Marriage}
	``YOUNG COUPLES WHO SELECTED FEBRUARY AS WEDDING MONTH,'' \textit{The Boston Globe}, 28 Feb 1925, p.\ 9; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/48666373/the-boston-globe/?xid=637} : viewed on 17 May 2020).
	
	\bibitem{AlbertFrenchBirth}
	Massachusetts Vital Records, Birth Records, 1900, p.\ 537 (stamped), no.\ 218, Albert Joseph French; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 17 May 2020), \_up through 1910 > 1900 > image 1475.\\
	Born in Medford to Joseph Swan French and Emily Selina Luscombe
	
	\bibitem{AlbertFrenchDeath}
	U.S.\ Social Security Administration, \textit{Death Master File}, Albert French, 1980; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 17 May 2020).
	
	\bibitem{AlbertFrenchDeath2}
	U.S.\ Department of Veterans Affairs, ``Beneficiary Identification Records Locator Subsystem (BIRLS) Death File,'' Albert French, death date 30 Dec 1980; accessed at ``U.S., Department of Veterans Affairs BIRLS Death File, 1850-2010,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2441/} : viewed on 17 May 2020).
	
	\bibitem{Albert5FrenchBirth}
	United States, Selective Service System, ``Draft Registration Cards for Massachusetts, 10/16/1940-03/31/1947,'' Record Group: ``Records of the Selective Service System, 147,'' Box: 344, card for Albert Joseph French Jr., serial no.\ W318C, order no.\ 12,200 C; accessed at ``U.S. WWII Draft Cards Young Men, 1940-1947,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 17 May 2020), Massachusetts > Ellis-Fucca > Freemon, Albert-Frenzo, Salvatore > image 840.
	
	\bibitem{Albert5FrenchDeath}
	Albert J.\ French Jr.\ obituary, \textit{Union Leader}, 1 Apr 2013; accessed at \textit{Legacy.com} (\url{https://www.legacy.com/obituaries/unionleader/obituary.aspx?n=albert-j-french\&pid=163975792}: viewed on 17 May 2020).
	
	\bibitem{InezFrenchDeath}
	Inez Lyons French obituary, \textit{The Boston Globe}, 8 Jan 2012, p.\ B7; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/51542027/the-boston-globe/?xid=637} : viewed on 17 May 2020).
	
	\bibitem{MaryAlice4FlynnBirth}
	Massachusetts Vital Records, Birth Records, 1886, p.\ 74, no.\ 3320, Mary Alice Flynn; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 23 May 2020), \_up through 1910 > 1886 > image 1152.\\
	Born at 101 Bennington St., East Boston.
	
	\bibitem{MaryAlice4FlynnBaptism}
	Sacred Heart (East Boston) Baptisms and Confirmations, 1873-1893, p.\ 254, Maria Alicia Flynn baptism; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/58159/254/1426795692} : viewed on 23 May 2020).
	
	\bibitem{MaryAlice4FlynnDeath}
	Alice (Flynn) Clahane obituary, \textit{The Boston Globe}, 14 Oct 1958, p.\ 59; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/51972536/obituary-for-alice-clahane/?xid=637} : viewed on 23 May 2020).\\
	``Member of Musicians Union, Local \#9.''
	
	\bibitem{MaryAlice4FlynnMarriage}
	Massachusetts Vital Records, Marriage Records, 1908, no.\ 6083, Edward W Clahane and Alice V Flynn; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 23 May 2020), \_up through 1910 > 1908 > image 1912.\\
	Alice V Flynn occupation: organist. Edward W Clahane parents: Edward W Clahane and Catherine Nolan.
	
	\bibitem{EdwardClahaneBirth}
	Boston, Massachusetts Vital Records, Birth Records, 1888, no.\ 4862, Edward Clahane; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 23 May 2020), Boston > Births, Marriages and Death > image 45265.
	
	\bibitem{EdwardClahaneDeath}
	Edward W.\ Clahane obituary, \textit{The Boston Globe}, 30 May 1962, p.\ 44; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/51988414/obituary-for-ed-ahane/?xid=637} : viewed on 23 May 2020).
	
	\bibitem{Census1940MaryAlice4Flynn}
	1940 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 15-719, Boston City, sheet no.\ 3A, house no.\ 1137, family no.\ 87, Alive V.\ Clahane household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 23 May 2020), Massachusetts > Suffolk > Boston > 15-719 > image 5.\\
	1137 Commonwealth Ave.
	
	\bibitem{Census1910EdwardClahane}
	1910 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 1263, Boston City, sheet no.\ 13A, household no.\ 126, family no.\ 239, Edward W.\ Clahane in Hannah E.\ Flynn household; accessed at ``1920 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6061/} : viewed on 23 May 2020), Massachusetts > Suffolk > Boston Ward 1 > image 25.
	
	\bibitem{Census1920EdwardClahane}
	1920 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 240, Boston, sheet no.\ 17A, household no.\ 3, family no.\ 4, Edward Clahane household; accessed at ``1920 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6061/} : viewed on 23 May 2020), Massachusetts > Suffolk > Boston Ward 8 > District 0240 > image 33.
	
	\bibitem{EdwardClahaneWWIIDraft}
	United States, Selective Service System, ``World War II Draft Cards (Fourth Registration) for the State of Massachusetts,'' Record Group 147, Series Number M2090, card for Edward William Clahane, serial no.\ 1855, order no.\ [blank]; accessed at ``U.S.\ WWII Draft Cards Young Men, 1940-1947,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 23 May 2020), Massachusetts > Christien, Prudent - Clarke, Robert Irving > Aadland, Gunval - Fernstrom, Ernest Emanuel > image 9222.
	
	\bibitem{Marion5ClahaneBirth}
	Massachusetts Vital Records, Birth Records, 1909, no.\ 598, Marion Gertrude Clahane; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 23 May 2020), \_up through 1910 > 1909 > image 1802.
	
	\bibitem{Marion5ClahaneDeath}
	Marion Clahane obituary, \textit{The Boston Globe}, 12 Apr 1971, p.\ 33; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/51973045/obituary-for-marion-clahane/?xid=637} : viewed on 23 May 2020).
	
	\bibitem{Edith4WickensBirth}
	Massachusetts Vital Records, Birth Records, 1894, no.\ 4885, Edith A.\ Wickens; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 25 May 2020), \_up through 1910 > 1894 > image 1761.
	
	\bibitem{Edith4WickensMarriage}
	Massachusetts Vital Records, Marriage Records, 1913, p.\ 266 (stamped), no.\ 6103, George H Giguere and Edith Wickens; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 25 May 2020), 1913 > Boston > image 266.\\
	Edith's occupation: bookkeeper. George's occupation: steamfitter. George's parents: John B Giguere and Corinne Le Cours.
	
	\bibitem{GeorgeGiguereBirth}
	Massachusetts Vital Records, Birth Records, 1893, no.\  237, George Hector Giguere; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 25 May 2020), \_up through 1910 > 1893 > image 893.
	
	\bibitem{GeorgeGiguereDeath}
	Michigan Vital Records, ``Michigan Death Index,'' entry for George H Giguere, died 19 Jul 1974; accessed at ``Michigan, Death Index, 1971-1996,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3171/} : viewed on 25 May 2020).
	
	\bibitem{Census1930GeorgeGiguere}
	1930 U.S. census, Wayne County, Michigan, population schedule, Enumeration District (ED) 82-830, Detroit City, p. 20A, dwelling no.\ 248, family no.\ 1, George H Giguere household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 25 May 2020), Michigan > Wayne > Detroit (Districts 751-879) > District 0830 > image 31.
	
	\bibitem{Dorris5GiguereSSDeath}
	U.S.\ Social Security Administration, \textit{Death Master File}, Dorris Leonard, 1981; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 11 Jul 2020).
	
	\bibitem{Dorris5GiguereMichiganDeath}
	Michigan Vital Records, ``Michigan Death Index,'' Dorris Leonard, died 10 Jul 1981; accessed at ``Michigan, Death Index, 1971-1996,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3171/} : viewed on 11 Jul 2020).
	
	\bibitem{RobertMayMarriage} 
	Michigan Vital Records, Marriage Records, ``Michigan, Marriage Records, 1867-1952,'' film 320, film title 82 Wayne 292370-295569, no.\ 614576 (stamped), Marriage License of Robert C.\ May and Dorris M.\ Giguere; accessed at ``Michigan, Marriage Records, 1867-1952,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9093/} : viewed on 11 Jul 2020), Certificates, 1926-1944 > Wayne > Wayne, Part 18 (Miscellanous Years) > image 67911.
	
	\bibitem{JohnMeyersMarriage}
	Steuben, Indiana, United States, Marriage Registration, Indiana Commission on Public Records, Indianapolis, Application for Marriage License, John E Meyers and Dorris M Giguere, 6 Jul 1950; accessed at ``Indiana Marriages, 1811-2007,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:K3LG-899} : viewed on 11 Jul 2020), Indiana Marriages, 1811-2007 > Steuben > 1950-1950 Volume103 > image 622.
	
	\bibitem{Albert4WickensBirth}
	Massachusetts Vital Records, Birth Records, 1898, p.\ 79 (written), p.\ 77 (stamped), no.\ 3523, Albert Francis Wickens; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 7 Jun 2020), \_up through 1910 > 1898 > image 1937.
	
	\bibitem{Albert4WickensDeath}
	U.S.\ Social Security Administration, \textit{Death Master File}, Albert Wickens, 1977; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 7 Jun 2020).
	
	\bibitem{Albert4WickensDeath2}
	U.S.\ Department of Veterans Affairs, ``Beneficiary Identification Records Locator Subsystem (BIRLS) Death File,'' Albert Wickens, death date 17 Sep 1977; accessed at ``U.S., Department of Veterans Affairs BIRLS Death File, 1850-2010,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2441/} : viewed on 7 Jun 2020).
	
	\bibitem{Albert4WickensMarriage}
	New Jersey Vital Records, ``Index of Marriages in New Jersey,'' Year Range: 1920-1929, Surname Range: P - S, AW and Mary Schaller; accessed at ``New Jersey, Marriage Index, 1901-2016,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/61253/} : viewed on 7 Jun 2020), Bride Index > 1920-1929 > P - S > image 446.
	
	\bibitem{Census1930AlbertWickens}
	1930 U.S. census, Essex County, New Jersey, population schedule, Enumeration District (ED) 7-188, Newark City, sheet no.\ 2B, dwelling no.\ 36, family no.\ 49, Albert F.\ Wickens household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 7 Jun 2020), New Jersey > Essex > Newark (Districts 1-250) > District 0188 > image 4.
	
	\bibitem{Census1940AlbertWickens}	
	1930 U.S. census, Essex County, New Jersey, population schedule, Enumeration District (ED) 25-310, Newark, sheet no.\ 1B, dwelling no.\ 57, family no.\ 23, Albert F.\ Wickens household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 7 Jun 2020), New Jersey > Essex > Newark > 25-310 > image 2.
	
	\bibitem{MarySchallerDeath}
	U.S.\ Social Security Administration, \textit{Death Master File}, Mary Wickens, Apr 1984; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 7 Jun 2020).
	
	\bibitem{MarySchallerDeath2}
	New Jersey Vital Records, ``Index of Deaths for Month -- Annual 1984,'' p.\ 1589, Mary H.\ Wickens; accessed at ``New Jersey, Death Index, 1901-2017,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/61260/} : viewed on 7 Jun 2020), 1984 > image 1593.
	
	\bibitem{Census1900MarySchaller}
	1900 U.S. census, Queens County, New York, population schedule, Enumeration District (ED) 672, City of New York, sheet no.\ 5, dwelling no.\ 61, family no.\ 105, Mary Schaller in Frank Schaller household; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 7 Jun 2020), New York > Queens > Queens Ward 04 > District 0672 > image 11.
	
	\bibitem{MarySchallerParents}
	Michigan Vital Records, Marriage Registers, 1921-1925, Wayne County, no.\ 222296, Aloysius J.\ Schaller and Florence Spurk; accessed at ``Michigan, Marriage Records, 1867-1952,'' \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9093/} : viewed on 7 Jun 2020), Registers, 1887-1925 > 1921-1925 > 1921 Wayne > image 1006.
	
	\bibitem{Ethel4WickensBirth}
	Massachusetts Vital Records, Birth Records, 1902, p.\ 136, no.\ 6102, Ethel Mary Wickens; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 13 Jun 2020), \_up through 1910 > 1902 > image 1720.\\
	Father John B Wickens born on Cape Sable Island; occupation: hoseman.
	
	\bibitem{Ethel4WickensDeath}
	Macomb County, Michigan, Vital Records, Death Index, Ethel Heuman, death date 27 Jul 1967; accessed at ``Web: Macomb County, Michigan, Death Index 1904-2017,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/70854/} : viewed on 13 Jun 2020).
	
	\bibitem{Ethel4WickensMarriage}
	Michigan Vital Records, \textit{Record of Marriages}, vol.\ 5, 1923, Kent to Lemawee, no.\ 256168, Harold E.\ Heuman and Ethyle M.\ Wickens; accessed at ``Michigan, Marriage Records, 1867-1952,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9093/} : viewed on 13 Jun 2020),  Registers, 1887-1925 > 1921-1925 > 1923 Kent-Monroe > image 344.
	
	\bibitem{HaroldHeumanDeath}
	Michigan Vital Records, ``Michigan Death Index,'' Harold E.\ Heuman Sr.\, death date 10 May 1993; accessed at ``Michigan, Death Index, 1971-1996,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3171/} : viewed on 13 Jun 2020).
	
	\bibitem{HaroldHeumanDraft}
	United States, Selective Service System, ``WWII Draft Registration Cards for Michigan, 10/16/1940-03/31/1947,'' Record Group 147, Box 513, card for Harold Edward Heuman, serial no.\ 2705, order no.\ 12,278; accessed at \textit{U.S.\ WWII Draft Cards Young Men, 1940-1947}, database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 13 Jun 2020), Michigan > Hartman-Holliday > Heuer, Harold-Hiatt, Weldon > image 62.\\
	Birthplace shown as Chicago, Illinois. Birth date shown as 12 May 1903, but this is the only record not showing a birth date of 12 May 1902.
	
	\bibitem{Census1910HaroldHeuman}
	1910 U.S. census, Cook County, Illinois, population schedule, Enumeration District (ED) 1409, Chicago City, sheet no.\ 4A, dwelling no.\ 56, family no.\ 62, Harold Heuman in John Heuman household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 13 Jun 2020), Illinois > Cook > Chicago Ward 32 > District 1409 > image 7.
	
	\bibitem{GraceHeumanBirth}
	Illinois, Cook County Courthouse, Birth Records, reference/certificate 60940, John G Heuman in entry for Grace Helen Heuman; accessed at ``Illinois, Cook County, Birth Certificates, 1871-1940,'' database, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:Q239-GXYZ} : viewed on 13 Jun 2020).\\
	Parents are John G Heuman and Augusta M Margin. Grace Heuman shown as Harold's sister in 1910 census.
	
	\bibitem{Census1940HaroldHeuman}
	1940 U.S. census, Macomb County, Michigan, population schedule, Enumeration District (ED) 50-39, Mount Clemens City, sheet no.\ 16A, house no.\ 159, household no.\ 313, Harold Heuman household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 13 Jun 2020), Michigan > Macomb > Mount Clemens > 50-39 > image 31.
	
	\bibitem{Catherine4OBrienDeath}
	Catherine M.\ MacDonald obituary, \textit{The Boston Globe}, 29 Apr 1964, p.\ 32; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/49642054/obituary-for-catherine-m-macdonald/?xid=637} : viewed on 15 Jun 2020).
	
	\bibitem{Catherine4OBrienMarriage}
	Massachusetts Vital Records, \textit{Index to Marriages}, 1936-1940, Naas - Pottinger, vol.\ 123, Catherine M O'Brien, Boston, 1937, vol.\ 18, p.\ 5; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 15 Jun 2020), 1936-1940 > Naas - Pottinger > image 134.
	
	\bibitem{Catherine4OBrienMarriage2}
	Massachusetts vital records, certificate of marriage, Fred A MacDonald and Catherine M O'Brien, 1937, vol.\ 18, p.\ 5, no.\ 4635 (stamped).
	
	Massachusetts Vital Records, \textit{Index to Marriages}, 1936-1940, Kreponitsky - Marquis, vol.\ 121, Fred A MacDonald, Boston, 1937, vol.\ 18, p.\ 5; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 15 Jun 2020), 1936-1940 > Kreponitsky - Marquis > image 427.
	
	\bibitem{HydePark}
	Lewis, Geoff; Avault, John; Vrabel, Jim (November 1999), History of Boston's Economy, Growth and Transition 1970–1998 (PDF), Boston, Massachusetts: Boston Redevelopment Authority, p. 31, archived from the original (PDF) on 2007-06-16 (\url{https://web.archive.org/web/20070616172652/http://www.cityofboston.gov/bra/PDF/ResearchPublications//pdr529.pdf})
	
	\bibitem{FrederickMacDonaldBirth}
	Massachusetts Vital Records, Birth Records, 1908, p.\ 11, no.\ 461, Frederick McDonald; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 15 Jun 2020), \_up through 1910 > 1908 > image 1408.
	
	\bibitem{FrederickMacDonaldDraft}
	United States, Selective Service System, ``Draft Registration Cards for Massachusetts, 10/16/1940-03/31/1947,'' Record Group 147, Box 587, card for Frederick Augustus MacDonald Jr, serial no.\ 980, order no.\ 3018; accessed at \textit{U.S.\ WWII Draft Cards Young Men, 1940-1947}, database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 15 Jun 2020), Massachusetts > Lawson-Maguire > MacDonald,Anthony-MacDonald,Lawson > image 887.
	
	\bibitem{FrederickMacDonaldDeath}
	Frederick A.\ MacDonald obituary, \textit{The Boston Globe}, 12 Nov 1983, p.\ 36; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/53523680/obituary-for-frederick-a-macdonald/?xid=637} : viewed on 15 Jun 2020).
	
	\bibitem{Frances4OBrien2Birth}
	Massachusetts Vital Records, Birth Records, 1912, Somerville, no.\ 408, Frances Josephine O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 18 Jun 2020), 1912 > Somerville > image 11.
	
	\bibitem{Frances4OBrien2Death}
	U.S.\ Social Security Administration, \textit{Death Master File}, Frances J.\ Day, died 8 Jul 1997; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 18 Jun 2020).
	
	\bibitem{Frances4OBrien2Death2}
	Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for Frances Day, died 8 Jul 1997; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 18 Jun 2020).
	
	\bibitem{Frances4OBrien2Marriage}
	Massachusetts Vital Records, \textit{Index to Marriages}, 1941 - 1945, Celle - Degan, vol.\ 129, entry for John R Day, Boston, 1942, vol.\ 15, p.\ 398, and Milton, 1942, vol.\ 80, p.\ 344; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 18 Jun 2020), 1941-1945 > Celle - Degan > image 583.
	
	Massachusetts Vital Records, \textit{Index to Marriages}, 1941 - 1945, Nurmi - Ramirez, vol.\ 136, entry for Frances J O'Brien, Boston, 1942, vol.\ 15, p.\ 398, and Milton, 1942, vol.\ 80, p.\ 344;  accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 18 Jun 2020), 1941-1945 > Nurmi - Ramirez > image 26.
	
	\bibitem{JohnDaySS}
	U.S.\ Social Security Administration, ``Social Security Applications and Claims, 1936-2007,'' entry for John R Day, SSN 025420794; accessed at ``U.S., Social Security Applications and Claims Index, 1936-2007,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/60901/} : viewed on 20 Jun 2020).\\
	Parents' names listed as Edward P Day and Jennie C Bowers. Birth place: Dorchester, Massachusetts.
	
	\bibitem{JohnDayDeath}
	Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for John R Day, certificate 015631; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 20 Jun 2020).\\
	Death place: Milton.
	
	\bibitem{Census1940Frances4OBrien2}
	1940 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 15-663, Boston, sheet no.\ 63A, house no.\ 58, household no.\ 303, Frances O'Brien in Edward O'Brien household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 20 Jun 2020), Massachusetts > Suffolk > Boston > 15-663 > image 33.
	
	\bibitem{JohnDayObit}
	Dr.\ John R.\ Day M.D.\ obituary, \textit{The Boston Globe}, 23 Jan 1990, p.\ 18; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/53582210/obituary-for-john-r-md/?xid=637} : viewed on 20 Jun 2020).
	
	\bibitem{JohnDay1948}
	R.\ L.\ Polk \& Co., compilers, \textit{Polk's Boston City Directory}, 1948-49 (Boston: R.\ L.\ Polk \& Co., 1949), p.\ 481, John R and Frances Day at 124 Theodore Parker Rd.; accessed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 20 Jun 2020), Massachusetts > Boston > 1948 > Boston, Massachusetts, City Directory, 1948 > image 483.
	
	\bibitem{Edward4OBrien2Birth}
	Massachusetts Vital Records, Birth Records, City of Boston, 1916, v.\ 2, p.\ 103, no.\ 14109, Edward Francis O'Brien; accessed at ``Massachusetts State Vital Records, 1841-1920,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/3:1:33SQ-GRGB-9Z7} : viewed on 20 Jun 2020), Births > Births 1916 vol 2 no 10001-19857 Boston > image 98.
	
	\bibitem{Edward4OBrien2Death}
	Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for Edward F Obrien, certificate 055901; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 20 Jun 2020).\\
	Death place: Needham.
	
	\bibitem{Edward2OBrien2Obit}
	Edward F.\ O'Brien obituary, \textit{The Boston Globe}, 14 Dec 1985, p.\ 16; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/49662479/obituary-for-edward-f-obrien/?xid=637} : viewed on 20 Jun 2020).
	
	\bibitem{Edward4OBrien2Marriage}
	Massachusetts Vital Records, \textit{Index to Marriages}, 1946-1950, Naaripa-Pieloscik, vol.\ 150, entry for Edwdard F O'Brien, Milton, 1946, vol.\ 96, p.\ 159; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 20 Jun 2020), 1946-1950 > Naaripa - Pieloscik > image 167.
	
	Massachusetts Vital Records, \textit{Index to Marriages}, 1946-1950, McAnnenny - Mytkowicz, vol.\ 149, entry for Mary A Metivier, Milton, 1946, vol.\ 96, p.\ 159; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 20 Jun 2020), 1946-1950 > McAnneny - Mytkowicz > image 280.
	
	\bibitem{MaryMetivierBirth}
	Massachusetts Vital Records, Birth Records, Milton, 1917, p.\ 3 (hand-written), p.\ 61 (stamped), no.\ 126, Mary Metivier; accessed at ``Massachusetts State Vital Records, 1841-1920,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/3:1:33SQ-G1BF-4NS} : viewed on 20 Jun 2020), Births > Births 1917 vol 642 Nantucket-Worcester > image 62.
	
	\bibitem{MaryMetivierDeath}
	Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for Mary A Obrien, certificate 044437; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 20 Jun 2020).\\
	Death place: Needham.
	
	\bibitem{Edward4OBrien2Obit}
	``Edward O'Brien, 69,'' \textit{The Boston Globe}, 14 Dec 1985, p.\ 36; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/49662705/obituary-for-edward-f-obrien-aged-69/?xid=865} : viewed on 20 Jun 2020).
	
	\bibitem{Beatrice4OBrienBirth}
	Massachusetts Vital Records, Birth Records, Boston, 1919, Aug 11-Aug 20, vol.\ 30, p.\ 54, certificate no.\ 11115, Beatrice Field O'Brien; accessed at ``Massachusetts State Vital Records, 1841-1920,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:QLGR-5HS6} : viewed on 21 Jun 2020), Births > Births 1919 vol 30 Boston > image 55.
	
	\bibitem{Beatrice4OBrienDeath}
	Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for Beatrice Brady, certificate 033686; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 21 Jun 2020).\\
	Death place: Needham.
	
	\bibitem{PatrickBradyMarriage}
	Boston, Massachusetts Vital Records, Marriage Records, 1909, no.\ 5771, Patrick Brady and Bridget Burke; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511} : viewed on 17 Jul 2020), \_Up Through 1910 > 1909 > image 2044.
	
	\bibitem{Beatrice4OBrienMarriage}
	Massachusetts Vital Records, \textit{Index to Marriages}, 1941-1945, Bisiniere-Cazavelan, vol.\ 128, entry for John F Brady, Boston, 1941, vol.\ 18, p.\ 446; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 21 Jun 2020), 1941-1945 > Bisiniere - Cazavelan > image 179.
	
	Massachusetts Vital Records, \textit{Index to Marriages}, 1941-1945, Nurmi-Ramirez, vol.\ 136, entry for Beatrice O'Brien, Boston, 1941, vol.\ 18, p.\ 446; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 21 Jun 2020), 1941-1945 > Nurmi - Ramirez > image 22.
	
	\bibitem{Census1920JohnBrady}
	1920 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 520, City of Boston, sheet no.\ 19B, dwelling no.\ 194, household no.\ 401, John Brady in Patrick Brady household; accessed at ``1920 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6061/} : viewed on 21 Jun 2020), Massachusetts > Suffolk > Boston Ward 21 > District 0520 > image 38.
	
	\bibitem{JohnBradyDraft}
	United States, Selective Service System, ``Draft Registration Cards for Massachusetts, 10/16/1940-03/31/1947,'' Record Group 147, Box 98, card for John Francis Brady, serial no.\ 1130, order no.\ 2691; accessed at \textit{U.S. WWII Draft Cards Young Men, 1940-1947}, database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 21 Jun 2020), Massachusetts >  Bastardo-Brandon > Bradley, Bernard-Brady, Russell > image 1754.\\
	Closest contact listed as Mrs. Delia Brady, mother. Address at 24 Montvale St., Roslindale, Mass.
	
	\bibitem{JohnBradyDeath}
	Massachusetts Department of Health Services, ``Massachusetts Death Index, 1970-2003,'' entry for John F Brady, certificate 022707; accessed at ``Massachusetts, Death Index, 1970-2003,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7457/} : viewed on 21 Jun 2020).\\
	Death place: Milton.
	
	\bibitem{JohnBrady1951}
	R.\ L.\ Polk \& Co., compilers, \textit{Polk's Boston City Directory}, 1951 (Boston: R.\ L.\ Polk \& Co., 1951), p.\ 200, John F and Beatrice F Brady at 72 Addington Rd.; accessed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 21 Jun 2020), Massachusetts > Boston > 1951 > Boston, Massachusetts, City Directory, 1951 > image 414.
	
	\bibitem{HistoryoftheT}
	Massachusetts Bay Transportation Authority, ``The History of the T'' (\url{https://www.mbta.com/history} : viewed on 21 Jun 2020).
	
	\bibitem{JohnBrady1965}
	R.\ L.\ Polk \& Co., compilers, \textit{Polk's Boston City Directory}, 1965 (Boston: R.\ L.\ Polk \& Co., 1965), p.\ 168, John F and Beatrice F Brady at 177 Corey; accessed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 21 Jun 2020), Massachusetts > Boston > 1965 > Boston, Massachusetts, City Directory, 1965 > image 446.
	
	\bibitem{Beatrice4OBrienObit}
	Beatrice F. (O'Brien) Brady obituary, \textit{The Boston Globe}, 30 Jun 1976, p.\ 37; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/42867888/obituary-for-brady/?xid=637} : viewed on 21 Jun 2020).
	
	\bibitem{Edith4WickensDeath}
	Edith A.\ Giguere obituary, \textit{Detroit Free Press}, 10 Feb 1957, p.\ 35; accessed at \textit{Newspapers.com} (\url{https://www.newspapers.com/clip/55186128/obituary-for-c-icr-f-rk/?xid=637} : viewed on 11 Jul 2020).
	
	\bibitem{Dorris5GiguereObit}
	Dorris Leonard obituary, \textit{Detroit Free Press}, 12 Jul 1981, p.\ 49; accessed at \textit{Newspapers.com} (\url{https://www.newspapers.com/clip/55184073/obituary-for-leonard-dorris/?xid=637} : viewed on 11 Jul 2020).
	
	\bibitem{Robert5GiguereDeath}
	Robert E.\ Giguere obituary, \textit{The Boston Globe}, 27 Sep 1916, p.\ 14; accessed at \textit{Newspapers.com} (\url{https://www.newspapers.com/clip/55181564/the-boston-globe/?xid=637} : viewed on 11 Jul 2020).

\end{thebibliography}