\begin{thebibliography}{999}
\raggedright
\small

% Uncategorized

\bibitem{Jacksons}
F. Jackson, \textit{The County and City of Cork Post Office General Directory, 1842--43} (Cork: F. Jackson), 125; viewed at \textit{Cork City Libraries} (\url{http://www.corkpastandpresent.ie/places/streetandtradedirectories/1842-3jacksonscountycityofcorkpogeneraldirectory/}) : viewed on 23 Mar 2020.

\bibitem{Peramb1847}
``Perambulation Book, County of Cork, Barony of Barrymore, Parishes of St.\ Michaels, Templeusque, and Killaspugmullane,'' Parish of Killaspugmullane, Townland of Trantstown, p.\ 22 (hand-written), No.\ 22a, John OBrien, dated 4 Aug 1847; viewed at ``Ireland, Valuation Office Books, 1831--1856,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-L94N-1CR6} : viewed 26 Mar 2020), film \#007246728, image 109.

\bibitem{Peramb1850}
``Perambulation Book, County of Cork, Barony of Barrymore, Parish of Killaspugmullane,'' Townland of Trantstown, No.\ 7a, John O'Brien, dated 26 Jul 1850; viewed at ``Ireland, Valuation Office Books, 1831--1856,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-L94N-1CR6} : viewed 26 Mar 2020), film \#007246728, image 118.

\bibitem{House1850}
``1st House Book, County of Cork, Barony of Barrymore, P.\ of Killaspugmullane (Revised),'' Townland of Trantstown, p.\ 5 (hand-written), No.\ 7a, John OBrien, original date Aug 1847, revised date 27 Jul 1850; viewed at ``Ireland, Valuation Office Books, 1831--1856,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-894J-SZCB} : viewed 26 Mar 2020), film \#007246783, image 420.

\bibitem{PaperMill}
Bina Harte, ``The Old Paper Mill of Trantstown,'' recounted to the author by Jeremiah Harte, The National Folklore Collection, UCD, The Schools' Collection, Volume 0382, p.\ 31; viewed at \textit{d\'{u}chas.ie} (\url{https://www.duchas.ie}), The Schools' Collection > Co.\ Cork > Cnoc na Biolaraighe, image 31.


\bibitem{BarryHistory1}
E. Barry, \textit{Barrymore : records of the Barrys of County Cork from the earliest to the present time, with pedigrees} (Cork: Guy and Co. Ltd., 1902), 1.

\bibitem{BarryHistory17}
Ibid., p.\ 17.

\bibitem{ParliamentaryGazetteer}
\textit{The Parliamentary Gazetteer of Ireland}, Vol. 1 (Dublin, London, and Edinburgh: A. Fullarton and Co., 1846) 227.

\bibitem{JamesBarry1}
James Barry, email to members of the \textit{Family Tree DNA} ``Barry Project'' on 17 Dec 2019.

\bibitem{BarrymoreDNA}
James Barry, \textit{Barrymore DNA: The Genetic Records of the Barrys of County Cork and Beyond} (2020) pp.\ 2--4; downloaded from \textit{Academia.edu} (\url{https://www.academia.edu/42454916/Barrymore_DNA_The_Genetic_Records_of_the_Barrys_of_County_Cork_and_Beyond}: viewed on 31 Mar 2020).



\bibitem{MichaelDooleyDeath}
Massachusetts Vital Records, death records, 1857, no.\ 7, Michael Dooley; accessed at ``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/3:1:3QS7-L975-M988} : viewed on 30 Mar 2020), Suffolk > Boston > Deaths 1856-1857 > image 351.\\
He is listed as ``married'' but wife's name is not included. Age 36. Address is 12 Pearl Pl.

\bibitem{John2OBrienCivilMarriage2}
City of Boston, Suffolk County, Massachusetts, marriage records, 1853, no.\ 2642, John O'Brien and Mary Mahoney; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Marriages, 1853 > image 157.\\
John is listed as 33 years old and Mary as 24.

\bibitem{Mary3OBrienDeath2}
Boston, Massachusetts Vital Records, death records, 1883, no.\ 1916, Mary F. O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Deaths, 1883 > image 67.



\bibitem{Edward2OBrienDeed}
Massachusetts, Suffolk County Registry of Deeds, 1874, vol.\ 1224, p. 25, Roome to O'Brien; accessed at ``Massachusetts Land Records, 1620-1986,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QSQ-G9Z3-9BYX} : viewed on 2 Apr 2020), Deeds 1874 vol 1223-1224 > image 369.





\bibitem{Francis3OBrien1913}
W.\ A.\ Greenough \& Co., compilers, \textit{New Bedford and Fairhaven Directory} (Boston: W.\ A.\ Greenough \& Co., 1913), p.\ 772, Frank J O'Brien; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 10 Apr 2020), Massachusetts > New Bedford > 1913 > New Bedford, Massachusetts, City Directory, 1913 > image 774.\\
``O'Brien Frank J meter tester 125 Middle h 95 S Sixth'' - see also p.\ 1010 (image 1014) of the same directory for the full name of the New Bedford Gas \& Edison Light Co.\ located at 125 Middle St.

\bibitem{Hannah3DooleyDeathIndex}
Massachusetts Vital Records, \textit{Index to Deaths, 1911 - 1915, Cassibo - Enemark}, vol.\ 60, Hannah (Dooley) Cusick, 1911 vol.\ 13 p.\ 631; accessed at ``Massachusetts, Death Index, 1901-1980,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3659/} : viewed on 10 Apr 2020), 1911-1915 > Cassibo - Enemark > image 302.








\bibitem{William3OBrienBurial}
Mt.\ Calvary Cemetery, Boston, Suffolk County, Massachusetts, listing for William O'Brien plot (location C7-22-22, owner ID 14237) printed at the cemetery office for Gavin O'Brien on 12 April 2019.









\bibitem{John3OBrien1880}
Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1880), p.\ 749, John J.\ O'Brien at 82 Hudson; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 13 Apr 2020), Massachusetts > Boston > 1880 > Boston, Massachusetts, City Directory, 1880 > image 749.\\
There was no Boston city directory available for 1879 and John does not appear in the 1878 directory. He was probably still living in his parents' household.







\bibitem{Francis4OBrienMarriage}
Francis J.\ O'Brien wedding announcement, \textit{The Boston Globe}, 9 Sep 1921, p.\ 6, col.\ 3; accessed at \textit{Newspapers.com}, database with images (\url{https://bostonglobe.newspapers.com/image/430448996} : viewed on 13 Apr 2020).\\
Wedding to take place 12 Sep 1921 at Immaculate Conception Church in Malden.

\bibitem{Mildred4OBrienMarriage}
``YOUNG COUPLES WHO SELECTED FEBRUARY AS WEDDING MONTH,'' \textit{The Boston Globe}, 28 Feb 1925, p.\ 9; accessed at \textit{Newspapers.com}, database with images (\url{https://bostonglobe.newspapers.com/clip/48666373/the-boston-globe/?xid=637} : viewed on 13 Apr 2020).\\
Rectory of St. Francis of Assisi Church in Medford



\bibitem{Hannah3WardDeath2}
Massachusetts Vital Records, \textit{Index to Deaths, 1916 - 1920, Donoghue - Gzmski}, vol. 68, Hannah (Ward) Flynn, 1919, vol.\ 7 p.\ 59; accessed at ``Massachusetts, Death Index, 1901-1980,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3659/} : viewed on 19 Apr 2020), 1916-1920 > Donoghue - Gzmski > image 275.

\bibitem{JohnJHFlynn}
Massachusetts, Suffolk County Registry of Deeds, vol.\ 3310, p. 501, FLYNN to KRUPP; accessed at \textit{masslandrecords} (\url{https://masslandrecords.com/suffolk/} : viewed on 19 Apr 2020), Search Criteria >  Recorded Land > Unindexed Property Search > Book 3310, Page Number 501.\\
``I, John H.\ Flynn of Boston in the County of Suffolk and Commonwealth of Massachusetts Known as John Flynn and John J Flynn\ldots''



























\bibitem{Michael3OBrienBirth}
Massachusetts Vital Records, birth records, 1864, no.\ 868, Michael O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 20 Apr 2020), \_up through 1910 > 1864 > image 719.\\
33 Fleet St.

\bibitem{Michael3OBrienBaptism}
St.\ Stephen (Boston) Baptisms, 1862-1870, p.\ 89, baptism of Michael O'Brien; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53642/89/1423786289} : viewed on 31 Aug 2020).





\bibitem{Edward4OBrienDeath2}
``Run Over and Killed.'' \textit{The Boston Globe}, 25 Apr 1887, p.\ 5; accessed at \textit{Newspapers.com} (\url{https://www.newspapers.com/clip/33349423/edward-obrien-death/} : viewed on 24 Apr 2020).


\bibitem{JohnWickensMarriage}
Massachusetts Vital Records, marriage records, 1891, no.\ 177, John B.\ Wickens and Fannie E O'Brien; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 25 Apr 2020), \_Up Through 1910 > 1891 > image 1601.\\
John B.\ Wickens occupation: mariner

\bibitem{JohnWickensNaturalization}
John B.\ Wickens, petition for naturalization (1895), no.\ 98, District of Massachusetts; Record Group 85: Records of the Immigration and Naturalization Service, 1787-2004; National Archives at Boston, Waltham, Massachusetts; viewed at ``Massachusetts, State and Federal Naturalization Records, 1798-1950,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2361/} : viewed on 25 Apr 2020), District Court, Massachusetts > Petitions, V 203, 1895 > image 211.\\
Address: 87 Morris Street, East Boston; Occupation: fireman

\bibitem{JohnWickensMarriage2}
Clark County, Washington, Marriage Records, 1916, no.\ 9304, John B.\ Wickens and Anna M.\ McGunigle; accessed at `` Washington, Clark County, marriage records, 1852-2000, 1867-1947,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-99DT-3G8Y} : viewed on 25 Apr 2020), Marriage certificates, no. 9101-9550, 1916 > image 357.

\bibitem{Nellie4WickensDeath}
Massachusetts Vital Records, Death Records, 1893, p.\ 295, no.\ 6479, Nellie Wickens; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 26 Apr 2020), \_Pre 1903 > 1893 > image 1582.

\bibitem{Abigail4SimondsMarriage}
Boston, Massachusetts Vital Records, Marriage Records, 1890, no.\ 1599, John H.\ Rogan and Abigail J.\ Simonds; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 1 May 2020), Boston > Births, Marriages and Death > image 28139.\\
John Rogan occupation; printer; Abigail Simonds occupation: operative; John Rogan parents: William and Mary.

\bibitem{Caroline4FernaldMarriage}
Boston, Massachusetts Vital Records, Marriage Records, 893, no.\ 646, John J.\ McGurin and Caroline E.\ Fernald; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 2 May 2020), Boston > Out of Town Marriages, 1893-1895 > image 39.

\bibitem{Francis5OBrienBirth}
United States, Selective Service System, ``Draft Registration Cards for Massachusetts, 10/16/1940-03/31/1947,'' Record Group: ``Records of the Selective Service System, 147,'' Box: 722, card for Francis Joseph O'Brien, serial no.\ 140, order no.\ 11626; accessed at ``U.S.\ WWII Draft Cards Young Men, 1940-1947,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 17 May 2020), , Massachusetts > Murphy-Panagacos > O´Brien, Edward L.-O´Brien, John L. > image 290.

\bibitem{Francis5OBrienDeath}
Francis J. O'Brien obituary, \textit{The Patriot Ledger}, 7 Nov 2015; accessed at \textit{Legacy.com} (\url{https://www.legacy.com/obituaries/southofboston-ledger/obituary.aspx?n=francis-j-obrien\&pid=176378266} : viewed on 17 May 2020).

\bibitem{Francis5OBrienMarriage}
Town of Andover, Essex County, Massachusetts, ``Copy of Record of Marriage,'' Francis J.\ O'Brien and Marie I.\ Eastwood, married 10 Jun 1950, date of record 13 Jun 1950.

\bibitem{CharlesBaineMarriage2}
Massachusetts Vital Records, ``Index to Marriages in Marrachusetts 1926-1930,'' vol.\ 96, Aaker - Brotherston, entry for Charles Lucius Baine; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 17 May 2020), 1926-1930 > Aaker - Brotherston > image 184.

\bibitem{Dorris5GiguereSSDeath}
U.S.\ Social Security Administration, \textit{Death Master File}, Dorris Leonard, 1981; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 11 Jul 2020).

\bibitem{Albert4WickensBirth}
Massachusetts Vital Records, Birth Records, 1898, p.\ 79 (written), p.\ 77 (stamped), no.\ 3523, Albert Francis Wickens; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 7 Jun 2020), \_up through 1910 > 1898 > image 1937.

\bibitem{Albert4WickensDeath}
U.S.\ Social Security Administration, \textit{Death Master File}, Albert Wickens, 1977; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 7 Jun 2020).

\bibitem{Albert4WickensDeath2}
U.S.\ Department of Veterans Affairs, ``Beneficiary Identification Records Locator Subsystem (BIRLS) Death File,'' Albert Wickens, death date 17 Sep 1977; accessed at ``U.S., Department of Veterans Affairs BIRLS Death File, 1850-2010,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2441/} : viewed on 7 Jun 2020).

\bibitem{Albert4WickensMarriage}
New Jersey Vital Records, ``Index of Marriages in New Jersey,'' Year Range: 1920-1929, Surname Range: P - S, AW and Mary Schaller; accessed at ``New Jersey, Marriage Index, 1901-2016,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/61253/} : viewed on 7 Jun 2020), Bride Index > 1920-1929 > P - S > image 446.

\bibitem{Census1930AlbertWickens}
1930 U.S. census, Essex County, New Jersey, population schedule, Enumeration District (ED) 7-188, Newark City, sheet no.\ 2B, dwelling no.\ 36, family no.\ 49, Albert F.\ Wickens household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 7 Jun 2020), New Jersey > Essex > Newark (Districts 1-250) > District 0188 > image 4.

\bibitem{Census1940AlbertWickens}
1930 U.S. census, Essex County, New Jersey, population schedule, Enumeration District (ED) 25-310, Newark, sheet no.\ 1B, dwelling no.\ 57, family no.\ 23, Albert F.\ Wickens household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 7 Jun 2020), New Jersey > Essex > Newark > 25-310 > image 2.

\bibitem{MarySchallerDeath}
U.S.\ Social Security Administration, \textit{Death Master File}, Mary Wickens, Apr 1984; accessed at ``U.S., Social Security Death Index, 1935-2014,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3693/} : viewed on 7 Jun 2020).

\bibitem{MarySchallerDeath2}
New Jersey Vital Records, ``Index of Deaths for Month -- Annual 1984,'' p.\ 1589, Mary H.\ Wickens; accessed at ``New Jersey, Death Index, 1901-2017,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/61260/} : viewed on 7 Jun 2020), 1984 > image 1593.

\bibitem{Census1900MarySchaller}
1900 U.S. census, Queens County, New York, population schedule, Enumeration District (ED) 672, City of New York, sheet no.\ 5, dwelling no.\ 61, family no.\ 105, Mary Schaller in Frank Schaller household; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 7 Jun 2020), New York > Queens > Queens Ward 04 > District 0672 > image 11.

\bibitem{MarySchallerParents}
Michigan Vital Records, Marriage Registers, 1921-1925, Wayne County, no.\ 222296, Aloysius J.\ Schaller and Florence Spurk; accessed at ``Michigan, Marriage Records, 1867-1952,'' \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9093/} : viewed on 7 Jun 2020), Registers, 1887-1925 > 1921-1925 > 1921 Wayne > image 1006.

\bibitem{Ethel4WickensBirth}
Massachusetts Vital Records, Birth Records, 1902, p.\ 136, no.\ 6102, Ethel Mary Wickens; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 13 Jun 2020), \_up through 1910 > 1902 > image 1720.\\
Father John B Wickens born on Cape Sable Island; occupation: hoseman.

\bibitem{Ethel4WickensDeath}
Macomb County, Michigan, Vital Records, Death Index, Ethel Heuman, death date 27 Jul 1967; accessed at ``Web: Macomb County, Michigan, Death Index 1904-2017,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/70854/} : viewed on 13 Jun 2020).

\bibitem{Ethel4WickensMarriage}
Michigan Vital Records, \textit{Record of Marriages}, vol.\ 5, 1923, Kent to Lemawee, no.\ 256168, Harold E.\ Heuman and Ethyle M.\ Wickens; accessed at ``Michigan, Marriage Records, 1867-1952,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9093/} : viewed on 13 Jun 2020),  Registers, 1887-1925 > 1921-1925 > 1923 Kent-Monroe > image 344.

\bibitem{HaroldHeumanDeath}
Michigan Vital Records, ``Michigan Death Index,'' Harold E.\ Heuman Sr.\, death date 10 May 1993; accessed at ``Michigan, Death Index, 1971-1996,'' database, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3171/} : viewed on 13 Jun 2020).

\bibitem{HaroldHeumanDraft}
United States, Selective Service System, ``WWII Draft Registration Cards for Michigan, 10/16/1940-03/31/1947,'' Record Group 147, Box 513, card for Harold Edward Heuman, serial no.\ 2705, order no.\ 12,278; accessed at \textit{U.S.\ WWII Draft Cards Young Men, 1940-1947}, database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2238/} : viewed on 13 Jun 2020), Michigan > Hartman-Holliday > Heuer, Harold-Hiatt, Weldon > image 62.\\
Birthplace shown as Chicago, Illinois. Birth date shown as 12 May 1903, but this is the only record not showing a birth date of 12 May 1902.

\bibitem{Census1910HaroldHeuman}
1910 U.S. census, Cook County, Illinois, population schedule, Enumeration District (ED) 1409, Chicago City, sheet no.\ 4A, dwelling no.\ 56, family no.\ 62, Harold Heuman in John Heuman household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 13 Jun 2020), Illinois > Cook > Chicago Ward 32 > District 1409 > image 7.

\bibitem{GraceHeumanBirth}
Illinois, Cook County Courthouse, Birth Records, reference/certificate 60940, John G Heuman in entry for Grace Helen Heuman; accessed at ``Illinois, Cook County, Birth Certificates, 1871-1940,'' database, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/1:1:Q239-GXYZ} : viewed on 13 Jun 2020).\\
Parents are John G Heuman and Augusta M Margin. Grace Heuman shown as Harold's sister in 1910 census.

\bibitem{Census1940HaroldHeuman}
1940 U.S. census, Macomb County, Michigan, population schedule, Enumeration District (ED) 50-39, Mount Clemens City, sheet no.\ 16A, house no.\ 159, household no.\ 313, Harold Heuman household; accessed at ``1940 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2442/} : viewed on 13 Jun 2020), Michigan > Macomb > Mount Clemens > 50-39 > image 31.

Massachusetts Vital Records, \textit{Index to Marriages}, 1936-1940, Kreponitsky - Marquis, vol.\ 121, Fred A MacDonald, Boston, 1937, vol.\ 18, p.\ 5; accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 15 Jun 2020), 1936-1940 > Kreponitsky - Marquis > image 427.

Massachusetts Vital Records, \textit{Index to Marriages}, 1941 - 1945, Nurmi - Ramirez, vol.\ 136, entry for Frances J O'Brien, Boston, 1942, vol.\ 15, p.\ 398, and Milton, 1942, vol.\ 80, p.\ 344;  accessed at ``Massachusetts, Marriage Index, 1901-1955 and 1966-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2966/} : viewed on 18 Jun 2020), 1941-1945 > Nurmi - Ramirez > image 26.

\bibitem{Edward4OBrien2Obit}
``Edward O'Brien, 69,'' \textit{The Boston Globe}, 14 Dec 1985, p.\ 36; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/49662705/obituary-for-edward-f-obrien-aged-69/?xid=865} : viewed on 20 Jun 2020).

\bibitem{John2OBrien1860}
Adams, Sampson, \& Company, compilers, \textit{The Boston Directory} (Boston: Adams, Sampson, \& Company, 1860), 324, entry for ``O'Brien John, oysterman, house 32 Fleet,'' accessed at \textit{Boston Athenaeum Digital Collections} (\url{http://catalog.bostonathenaeum.org/vwebv/holdingsInfo?bibId=288020}: viewed on 17 Oct 2020).

\bibitem{MacKenzie:4}
Clyde L.\ MacKenzie Jr.\, ``History of Oystering in the United States and Canada, Featuring the Eight Greatest Oyster Estuaries,'' \textit{Marine Fisheries Review}, 58(4), 1996, 4. 

\bibitem{MacKenzie:29}
Clyde L.\ MacKenzie Jr.\, ``History of Oystering in the United States and Canada, Featuring the Eight Greatest Oyster Estuaries,'' \textit{Marine Fisheries Review}, 58(4), 1996, 29.

\bibitem{HolyCrossPlotMichael}
The Catholic Cemetery Association of the Archdiocese of Boston, Owner Profile, owner ID C15-84952 (Michael O'Brien) at Holy Cross Cemetery, printed 18 Jul 2019.ƒ

\bibitem{HolyCrossPlotFernald}
The Catholic Cemetery Association of the Archdiocese of Boston, Owner Profile, owner ID C15-86405 (Robert Fernald) at Holy Cross Cemetery, printed 22 Jan 2021.


\end{thebibliography}