%% copyrightpage
\begingroup
\footnotesize
\parindent 0pt
\parskip \baselineskip
\textcopyright{} 2007, 2009, 2010 Peter R. Wilson \\
All rights reserved.

This work may be distributed and/or modified under the conditions
of the LaTeX Project Public License, either version~1.3 of this license
or (at your option) any later version. The latest version is in \\
\hspace*{2em} \url{http://www.latex-project.org/lppl.txt} \\
and version~1.3 or later is part of all distributions of LaTeX
version 2005/12/01 or later.

This work has the LPPL maintenance status `maintained'.

The Current Maintainer of this work is Peter Wilson.

The work consists of the file \texttt{titlepages.tex} and the
derived file \texttt{titlepages.pdf}.

\begin{comment}
%%% Until 2009 this work was under the Open Publication License as:
This material may be distributed only subject to the terms and conditions
set forth in the Open Publication License v1.0 or later (the latest
version is presently available at \url{http://www.opencontent.org/openpub/}).
Distribution of substantively modified versions of this document is
prohibited without the explicit permission of the copyright holder.
Distribution of the work or derivative of the work in any standard
(paper) book form is prohibited unless prior permission is obtained
from the copyright holder.


The procedures and applications presented in this work have been
included for their instructional value. They have been tested 
with care but are not guaranteed for any particular purpose.
The publisher does not offer any warranties or representations,
nor does it accept any liabilities with respect to the 
programs or applications.
\end{comment}

The paper used in this publication may meet the minimum 
requirements of the American National Standard for 
Information Sciences --- Permanence of Paper for Printed
Library Materials, ANSI Z39.48--1984.

\begin{center}
	12 11 10 09 08 07\hspace{2em}8 7 6 5 4 3 %2 
\end{center}

\begin{center}
	\begin{tabular}{ll}
		First edition:  & January 2007 \\
		Second impression, with minor extensions & January 2009 \\
		Third impression, with minor extensions & July 2010 
	\end{tabular}
\end{center}

\vfill

Wilson, Peter.\\
\hspace*{2em} Some Examples of Title Pages / Peter Wilson. -- \\
\hspace*{1em} 1st Herries Press ed. \\
\hspace*{2em} p. \hspace*{2em} cm. \\
\hspace*{2em} Includes illustrations, bibliographical references and index. \\
\hspace*{2em} ISBN \\
\hspace*{2em} 1. Book design \hspace*{2em} I. Title


\vfill

Printed in the World

The Herries Press, \\
Normandy Park, WA \\
\texttt{herries dot press (at) earthlink dot net}

%%%%{\LARGE\plogo}
\vspace*{2\baselineskip}


\endgroup
\clearpage
\pagestyle{plain}