
\chapter{Credits}
\raggedright
\nonzeroparskip
\small

\ref{fig:IrelandMap} Map data \copyright 2021 Google, GeoBasis-DE/BKG (\copyright 2009)

\ref{fig:DooleyBaptism} Watergrasshill, County of Cork, Diocese of Cork and Ross, Baptisms, Nov.\ 1840 to Jan.\ 1841, p.\ 27 (\url{http://registers.nli.ie/registers/vtls000635355\#page/27} : viewed on 12 Mar 2021).

\ref{fig:Clipper} Thomas Goldsworthy Dutton, ``Clipper barque Spirit of the Age,'' Royal Museums Greenwich (\url{https://commons.wikimedia.org/wiki/File:Clipper_barque_Spirit_of_the_Age,_PY0633.jpg}).

\ref{fig:ThomasBaker} U.S. National Archives and Records Administration (NARA), ``Passenger lists of vessels arriving at New York, 1820-1897,'' NARA microfilm publication M237, roll 81, July 3-27, 1849, list no.\ 882, entries for Mary O'Brien and Michael O'Brien; accessed at ``New York Passenger Lists, 1820-1891,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/3:1:939V-5P37-F7} : viewed on 19 Sep 2020), 081 - 3 Jul 1849-27 Jul 1849 > image 123.

\ref{fig:Chasca} ``Registers of Passengers Arriving in Massachusetts Ports 1848-1891,'' Massachusetts State Archives, HS 3.02 1990X, record of 27 Jun 1851, vessel \textit{Chascay}, entries for Edmund O'Brien and family; accessed at ``Massachusetts, United States Records,'' images, FamilySearch (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-CSVN-998J-W} : viewed on 11 Nov 2020), image 793.

%\ref{fig:Boston1849} ``Boston, 1849,'' wood engraving, artist unknown, Boston Pictorial Archive, Boston Public Library; accessed at Digital Commonwealth (\url{https://ark.digitalcommonwealth.org/ark:/50959/8623j6654} : viewed on 27 Mar 2021). This work is licensed for use under a Creative Commons Attribution Non-Commercial No Derivatives License (CC BY-NC-ND).

\ref{fig:StMarys} Josiah Johnson Hawes, ``Old St.\ Mary's Church, Endicott ad Cooper Sts.,'' photograph, 1860, Boston Public Library Arts Department (\url{https://ark.digitalcommonwealth.org/ark:/50959/c821h611m}). This work is licensed for use under a Creative Commons Attribution Non-Commercial No Derivatives License (CC BY-NC-ND).

\ref{fig:OysterTongers} Jacob Gayer, ``People tonging oysters near Nanticoke,'' photograph, National Geographic, image ID 1238550, used with permission.

%\ref{fig:EastBoston} Massachusetts, Suffolk County Register of Deeds, Atlas of East Boston, 1892, vol.\ 9, p.\ 14; accessed at Suffolk County Register of Deeds (\url{https://massrods.com/suffolk/suffolk-county-atlas/suffolk-county-atlas-pages/} : viewed on 4 Apr 2020), Research > Suffolk County Atlases > East Boston 1892 > Page 14.

%\ref{fig:BorderSt} G.W.\ Bromley \& Co., \textit{Atlas of the city of Boston} (1884), South \& East Boston, Plate O; accessed at ``Norman B.\ Leventhal Map Center Collection'' (\url{https://collections.leventhalmap.org/search/commonwealth:m900r5907} : viewed on 15 Apr 2021).

\ref{fig:RobertFernald} ``Robert A.\ Fernald, Veteran Tow Boat Captain, Dead,'' \textit{The Boston Globe}, 15 Jun 1917, p.\ 15.

\ref{fig:OliverTwist}
Howard Athen\ae um, season of 1882--3, program for \textit{Oliver Twist!}, week commencing 8 Jan 1883; in collection ``Howard Athen\ae um Programs, 1847-1892,'' vol.\ 2 1851-1892, call number Lg PN2277 .B67 H68, \textit{Boston Athen\ae um}, used with permission.

\ref{fig:PictureFrameLabel} Label for John J.\ O'Brien, picture frames, 69 Cornhill, Boston, Mass., undated. Historic New England, Ephemera Collection, GUSN-265637 (\url{http://gusn.us/265637}), used with permission.

\ref{fig:FrameStore} Detail from ``Crosswalk on Corn Hill opposite Franklin Avenue, looking west, sect. 8 1/2, Boston, Mass.,'' photograph, Boston Transit Commission, 14 Apr 1897, John Booras collection of plate glass negatives, Historic New England, GUSN-318238 (\url{http://gusn.us/318238}), used with permission. 

\ref{fig:WilliamDuggan} U.S.\ Bureau of Marine Inspection and Navigation, Application for Seaman's Certificate of American Citizenship, R.S.\ 4588, no.\ 26601, 31 Oct 1919, William J.\ Duggan; accessed at ``U.S., Applications for Seaman's Protection Certificates, 1916-1940,'' Ancestry.com (\url{https://www.ancestry.com/search/collections/61257/} : viewed on 22 Apr 2021), New York > 242 - New York > image 195.

\ref{fig:FJOB} Scanned image and caption provided by Michael O'Brien.

\ref{fig:HelenaFlynn} Photo courtesy of Helena (O'Brien) Rittershaus.

\ref{fig:MildredOBrien} Scanned image emailed to Gavin O'Brien by Brad French on 20 December 2020.

\ref{fig:Calverts} ``Calvert's Clothing Store,'' photograph, June 1979, Needham Free Public Library, Historical Pictures 145-266R (shelf locator), accessed at \textit{Digital Commonwealth} (\url{https://ark.digitalcommonwealth.org/ark:/50959/js956v51f} : viewed on 21 Mar 2021), used with permission.

\ref{fig:EdwardOBrienGrave} Photo by Gavin O'Brien, 14 April 2019.

\ref{fig:FernaldGrave} Photo by Gavin O'Brien, 14 April 2019.

\ref{fig:MahoneyPlot} Photo by Gavin O'Brien, 19 January 2021.

\ref{fig:WilliamOBrienGrave} Photo by Gavin O'Brien, 19 January 2021.