\section{Corrections}
\emph{Last Updated: 23 August 2021}
\renewcommand{\thefootnote}{[\arabic{footnote}]}

\MainPerson{Michael\textsuperscript{3} O'Brien}

The first edition listed Michael's daughter, Frances May O'Brien, as ``aka'' Frances L.\ O'Brien. These are actually two different individuals with the same first name who both died young. Corrected section follows.

\begin{KidsIntro}
	Children of Michael\textsuperscript{3} O'Brien and Mary A.\ Macdougall:
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{iv.}\KidName{Frances May O'Brien}\index{O'Brien!Frances May\textsuperscript{4}}, b.\ Walpole,\index{Massachusetts!Walpole} Norfolk Co., Mass., 18 Jan.\ 1901;\footnote{Massachusetts Vital Records, birth records, 1901, p.\ 1, no.\ 4, Frances May O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 24 Apr 2020), \_up through 1910 > 1901 > image 1246.} d.\ Walpole, 5 May 1901.\footnote{Walpole, Massachusetts, Vital Records, death records, 1901, p.\ 2, entry no.\ 25, Frances M.\ O'Brien; accessed at ``Massachusetts, U.S., Town and Vital Records, 1620-1988,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/2495} : viewed on 8 Aug 2021), Walpole > Births, Marriages and Death > image 1518.}
	
	\KidNum{}{v.}\KidName{Frances L.\ O'Brien}\index{O'Brien!Frances L.\textsuperscript{4}}, b.\ Walpole, 28 Feb.\ 1902;\footnote{Massachusetts Vital Records, death records, 1903, p.\ 493, no.\ 10298, Frances L.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 24 Apr 2020), 1903 > Boston > image 4188.} 
	d.\ Boston, 20 Dec.\ 1903.\footnote{Massachusetts Vital Records, death records, 1903, p.\ 493, no.\ 10298, Frances L.\ O'Brien.}
\end{Kids}

\MainPerson{Francis Joseph\textsuperscript{4} O'Brien}

The first edition listed Francis's wife's name as Helena Catherine (Flynn) O'Brien. The middle name of ``Catherine'' was taken from their marriage record. However, Helena went by the middle name ``Cecilia.''\footnote{Conversation between the author and Helena Cecilia (Flynn) O'Brien's daughter, Helena Cecilia (O'Brien) Rittershaus, who shares the same middle name.}