\chapter{Further Research}

\begin{itemize}

	\item\MainPerson{William\textsuperscript{1} O'Brien} probably came from the town of Watergrasshill in County Cork, Ireland. What can be found out about his family in Ireland? Can the O'Brien ancestors be traced further back? When and how did a male member of the Barry family acquire the O'Brien surname?

	\item\MainPerson{Mary\textsuperscript{1} Sexton} has unknown parents. She did not accompany her husband William to America, or else had died before his departure from Ireland. 

	\item\MainPerson{Ann\textsuperscript{2} (O'Brien) Dailey} seems to have come to America later than the rest of her family members. What became of her husband Michael Dailey and did she have any children with him in Ireland?

	\item\MainPerson{John\textsuperscript{2} O'Brien} does not have a definitive arrival date in the U.S. It must have been sometime prior to his marriage in Boston on 20 November 1853.

	\item\MainPerson{Ellen\textsuperscript{3} O'Brien}, daughter of Michael\textsuperscript{2} O'Brien and Bridget (Colbert) O'Brien, appears in no records after her father's probate in 1891. She is not buried in her family's cemetery plot in Malden. Perhaps she married and took a different last name.

	\item\MainPerson{John Joseph\textsuperscript{3} O'Brien} owned a frame shop in Boston. What became of the shop after he retired? He last listed his profession as a picture-frame manufacturer in 1916. The 1920 census lists his profession as ``none.''\cite{John3OBrien1916:4}

\end{itemize}