\chapter{List of Persons}
\begin{enumerate}
	\item\label{per:William1OBrien}William\textsuperscript{1} O'Brien
	\item\label{per:Abigail2OBrien}Abigail\textsuperscript{2} (O'Brien) Dooley
	\item\label{per:John2OBrien}John\textsuperscript{2} O'Brien
	\item\label{per:Edward2OBrien}Edward\textsuperscript{2} O'Brien
	\item\label{per:Mary2OBrien}Mary\textsuperscript{2} (O'Brien) Ward
	\item\label{per:Michael2OBrien}Michael\textsuperscript{2} O'Brien
	\item\label{per:Margaret3Dooley}Margaret\textsuperscript{3} (Dooley) (Simonds) Fernald
	\item\label{per:William3OBrien}William\textsuperscript{3} O'Brien
	\item\label{per:John3OBrien}John Joseph\textsuperscript{3} O'Brien
	\item\label{per:Hannah3Ward}Hannah\textsuperscript{3} (Ward) Flynn
	\item\label{per:Michael3OBrien}Michael\textsuperscript{3} O'Brien
	\item\label{per:Frances3OBrien}Frances Elizabeth\textsuperscript{3} (O'Brien) Wickens
	\item\label{per:Edward3OBrien}Edward Francis\textsuperscript{3} O'Brien
	\item\label{per:Catharine4Simonds}Catharine\textsuperscript{4} (Simonds) McCarthy
	\item\label{per:Abigail4Simonds}Abigail J.\textsuperscript{4} (Simonds) Rogan
	\item\label{per:Caroline4Fernald}Caroline Emma\textsuperscript{4} (Fernald) McGurin
	\item\label{per:Sarah4Fernald}Sarah Helen\textsuperscript{4} (Fernald) Leonard
	\item\label{per:Robert4Fernald}Robert Atwell\textsuperscript{4} Fernald
	\item\label{per:Francis4OBrien}Francis Joseph\textsuperscript{4} O'Brien
	\item\label{per:Pauline4OBrien}Pauline\textsuperscript{4} (O'Brien) Baine
	\item\label{per:Mildred4OBrien}Mildred Louise\textsuperscript{4} (O'Brien) French
	\item\label{per:MaryAlice4Flynn}Mary Alice\textsuperscript{4} (Flynn) Clahane
	\item\label{per:Edith4Wickens}Edith A.\textsuperscript{4} (Wickens) Giguere
	\item\label{per:Albert4Wickens}Albert Francis\textsuperscript{4} Wickens
	\item\label{per:Ethel4Wickens}Ethel Mary\textsuperscript{4} Wickens
	\item\label{per:Catherine4OBrien}Catherine\textsuperscript{4} (O'Brien) MacDonald
	\item\label{per:Frances4OBrien}Frances Josephine\textsuperscript{4} (O'Brien) Day
	\item\label{per:Edward4OBrien}Edward Francis\textsuperscript{4} O'Brien Jr.
	\item\label{per:Beatrice4OBrien}Beatrice Field\textsuperscript{4} (O'Brien) Brady
\end{enumerate}

\newpage

\dirtree{%
	.1 William\textsuperscript{1} O'Brien* and Mary\textsuperscript{1} (Sexton) O'Brien*.
	.2 Ann\textsuperscript{2} O'Brien.
	.2 Abigail\textsuperscript{2} ``Abby'' (O'Brien) Dooley*.
		.3 Hannah\textsuperscript{3} (Dooley) (Cooney) Cusick.
		.3 Margaret\textsuperscript{3} (Dooley) (Simonds) Fernald*.
			.4 Catharine\textsuperscript{4} (Simonds) McCarthy*.
				.5 Helen\textsuperscript{5} (McCarthy) Westlake.
					.6 William Atwell\textsuperscript{6} Westlake.
			.4 Francis\textsuperscript{4} Simonds.
			.4 Margaret Josephine\textsuperscript{4} Simonds.
			.4 Abigail J.\textsuperscript{4} Simonds*.
				.5 William H.\textsuperscript{5} Rogan.
				.5 Marguerite E.\textsuperscript{5} (Rogan) Shea.
				.5 Abigail Josephine\textsuperscript{5} ``Abbie'' Rogan.
				.5 Mary Alice\textsuperscript{5} Rogan.
				.5 Anne Irene\textsuperscript{5} (Rogan) Doran.
			.4 Anna\textsuperscript{4} Fernald.
			.4 Caroline Emma\textsuperscript{4} (Fernald) McGurin*.
				.5 Robert Alexander\textsuperscript{5} McGurin.
				.5 Walter Edward\textsuperscript{5} McGurin.
				.5 Alfred John\textsuperscript{5} McGurin.
				.5 Margaret A.\textsuperscript{5} (McGurin) Phillips.
				.5 Sarah H.\textsuperscript{5} ``Sadie'' (McGurin) Murphy.
				.5 Edward Joseph\textsuperscript{5} McGurin.
				.5 Caroline Josephine\textsuperscript{5} McGurin.
				.5 Catherine\textsuperscript{5} (McGurin) Kelleher.
				.5 Josephine\textsuperscript{5} McGurin.
				.5 John Francis\textsuperscript{5} McGurin.
				.5 Charles Alford\textsuperscript{5} McGurin.
			.4 Sarah Helen\textsuperscript{4} (Fernald) Leonard*.
				.5 Mary Margaret\textsuperscript{5} (Leonard) Duffy.
				.5 George Thomas\textsuperscript{5} Leonard.
			.4 Robert Atwell\textsuperscript{4} Fernald*.
				.5 Marion Elizabeth\textsuperscript{5} (Fernald) Weatherup.
	.2 John\textsuperscript{2} O'Brien*.
		.3 William\textsuperscript{3} O'Brien*.
			.4 Ellen Louise\textsuperscript{4} ``Nellie'' O'Brien.
		.3 Mary\textsuperscript{3} O'Brien.
		.3 James Edward\textsuperscript{3} O'Brien.
		.3 Ellen\textsuperscript{3} ``Nellie'' O'Brien.
		.3 John Joseph\textsuperscript{3} O'Brien*.
			.4 Mildred Loretta\textsuperscript{4} O'Brien.
			.4 Francis Joseph\textsuperscript{4} O'Brien*.
				.5 Francis Joseph\textsuperscript{5} ``Frank'' O'Brien Jr.
				.5 Pauline M.\textsuperscript{5} O'Brien.
				.5 Mildred\textsuperscript{5} O'Brien.
				.5 Helena\textsuperscript{5} O'Brien.
				.5 Therese Celine\textsuperscript{5} O'Brien.
			.4 Pauline M.\textsuperscript{4} (O'Brien) Baine*.
			.4 Mildred Louise\textsuperscript{4} (O'Brien) French*.
				.5 Albert Joseph\textsuperscript{5} French Jr.
			.4 Edward\textsuperscript{4} O'Brien.
			.4 Almyra Louise\textsuperscript{4} O'Brien. 
		.3 Margaret\textsuperscript{3} O'Brien.
		.3 Anna\textsuperscript{3} O'Brien.
	.2 Edward\textsuperscript{2} O'Brien*.
		.3 Mary Ann\textsuperscript{3} O'Brien.
		.3 Ellen\textsuperscript{3} O'Brien.
		.3 Ann Maria\textsuperscript{3} ``Annie'' O'Brien.
		.3 Margaret\textsuperscript{3} ``Maggie'' O'Brien.
		.3 Edward J.\textsuperscript{3} O'Brien.
	.2 Mary\textsuperscript{2} (O'Brien) Ward*.
		.3 Mary Ann\textsuperscript{3} Ward.
		.3 Sarah\textsuperscript{3} Ward.
		.3 Hannah\textsuperscript{3} (Ward) Flynn*.
			.4 Mary Alice\textsuperscript{4} (Flynn) Clahane*.
				.5 Marion Gertrude\textsuperscript{5} Clahane.
			.4 Harry Joseph\textsuperscript{4} Flynn.
	.2 Michael\textsuperscript{2} O'Brien*.
		.3 Ellen\textsuperscript{3} ``Nellie'' O'Brien.
		.3 Mary Ann\textsuperscript{3} O'Brien.
		.3 Michael\textsuperscript{3} O'Brien*.
			.4 Arthur Francis\textsuperscript{4} O'Brien.
			.4 Edward William\textsuperscript{4} O'Brien.
			.4 Elizabeth\textsuperscript{4} O'Brien.
			.4 Frances L.\textsuperscript{4} O'Brien.
		.3 Frances Elizabeth\textsuperscript{3} ``Fannie'' (O'Brien) Wickens*.
			.4 Nellie\textsuperscript{4} Wickens.
			.4 Edith A.\textsuperscript{4} (Wickens) Giguere*.
				.5 Robert E.\textsuperscript{5} Giguere.
				.5 Dorris Marjorie\textsuperscript{5} (Giguere) Leonard.
			.4 Frederick John\textsuperscript{4} Wickens.
			.4 Albert Francis\textsuperscript{4} Wickens*.
				.5 Mary E.\textsuperscript{5} Wickens.
				.5 Barbara\textsuperscript{5} Wickens.
				.5 Albert\textsuperscript{5} Wickens.
				.5 Paul\textsuperscript{5} Wickens.
				.5 Jean\textsuperscript{5} Wickens.
				.5 Joseph\textsuperscript{5} Wickens.
				.5 John\textsuperscript{5} Wickens.
				.5 James\textsuperscript{5} Wickens.
			.4 Ethel Mary\textsuperscript{4} (Wickens) Heuman*.
				.5 Virginia\textsuperscript{5} Heuman.
				.5 Edward\textsuperscript{5} Heuman.
				.5 Harold\textsuperscript{5} Heuman Jr.
		.3 Mary\textsuperscript{3} O'Brien.
		.3 John Joseph\textsuperscript{3} O'Brien.
		.3 Edward Francis\textsuperscript{3} O'Brien*.
			.4 Catherine M.\textsuperscript{4} (O'Brien) MacDonald*.
				.5 Jane Marie\textsuperscript{5} MacDonald.
				.5 Frederick A.\textsuperscript{5} MacDonald Jr.
			.4 Frances Josephine\textsuperscript{4} (O'Brien) Day*.
				.5 J.\ Brian\textsuperscript{5} Day.
				.5 Edward\textsuperscript{5} Day.
			.4 Walter Gill\textsuperscript{4} O'Brien.
			.4 Edward Francis\textsuperscript{4} O'Brien Jr*.
				.5 Clare\textsuperscript{5} O'Brien.
				.5 Julie\textsuperscript{5} O'Brien.
				.5 Ted\textsuperscript{5} O'Brien.
				.5 Ellen\textsuperscript{5} O'Brien.
			.4 Beatrice Field\textsuperscript{4} (O'Brien) Brady*.
				.5 Joan\textsuperscript{5} Brady.
				.5 Paul\textsuperscript{5} Brady.
				.5 Water\textsuperscript{5} Brady.
				.5 Beatrice\textsuperscript{5} Brady.
			.4 Mary Lucia\textsuperscript{4} O'Brien.
		.3 Francis Joseph\textsuperscript{3} ``Frank'' O'Brien.
}

% \renewcommand*\DTstyle{\ttfamily\textcolor{red}}
% https://tex.stackexchange.com/a/270761
