\section{Abigail (O'Brien) Dooley}\label{per:Abigail2OBrien}

\MainPerson{Abigail\textsuperscript{2} ``Abby'' O'Brien} (\Lineage{1}{William})\index{O'Brien!Abigail\textsuperscript{2}|bb}\index{Dooley!Abigail\textsuperscript{2} (O'Brien)} was born probably in Watergrasshill, County Cork, Ireland,\index{Ireland!Watergrasshill, County Cork} about 1815\cite{Census1855Abigail} or 1825.\cite{Abigail2OBrienDeath:1} She died in Boston, Suffolk County, Massachusetts\index{Massachusetts!Boston} on 4 January 1897\cite{Abigail2OBrienDeath:2} and is buried in Holy Cross Cemetery, Malden, Middlesex County, Massachusetts.\cite{CarolGordon:2}\index{Holy Cross Cemetery} She married, likely in County Cork,\index{Ireland!County Cork} \MainPerson{Michael Dooley}.\cite{Abigail2OBrienDeath:3}\index{Dooley!Michael} He was born probably in County Cork.\cite{MichaelDooleyBirth}\index{Ireland!County Cork} Michael\index{Dooley!Michael} died sometime before 1 May 1865,\footnote{Abigail's marital status in the 1865 state census is listed as ``widowed.''\cite{Census1865Abigail}} probably in Ireland,\index{Ireland} as he did not accompany Abby\index{O'Brien!Abigail\textsuperscript{2}}\index{Dooley!Abigail\textsuperscript{2} (O'Brien)} to Boston.\cite{Chascay:7}\index{Massachusetts!Boston}

Abigail\index{O'Brien!Abigail\textsuperscript{2}}\index{Dooley!Abigail\textsuperscript{2} (O'Brien)} immigrated to Boston\index{Massachusetts!Boston} on 27 June 1851.\cite{Chascay:8} She was living for a time in the North End\index{Massachusetts!Boston!North End} with her brother Edward\index{O'Brien!Edward/Edmund\textsuperscript{2}} and father William.\index{O'Brien!William\textsuperscript{1}}\cite{Census1855William:4} Later she moved in with her son-in-law's family, the Simonds.\cite{Census1860AbigailOBrien}\index{Simonds!family}

\begin{KidsIntro}
	Children of Michael Dooley\index{Dooley!Michael} and Abigail\textsuperscript{2} (O'Brien) Dooley,\index{O'Brien!Abigail\textsuperscript{2}}\index{Dooley!Abigail\textsuperscript{2} (O'Brien)} both likely born in Watergrasshill:\index{Ireland!Watergrasshill, County Cork}
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{Hannah\textsuperscript{3} Dooley}\index{Dooley!Hannah/Hanora\textsuperscript{3}}\index{Cooney!Hannah/Hanora\textsuperscript{3} (Dooley)}\index{Cusick!Hannah/Hanora\textsuperscript{3} (Dooley) (Cooney)} aka Hanora, b.\ prob.\ Watergrasshill\index{Ireland!Watergrasshill, County Cork} abt.\ 1837;\cite{Census1855Hannah3Dooley} d. Boston\index{Massachusetts!Boston} 14 June 1911;\cite{Hannah3DooleyDeath} m.\ (1) 14 Aug.\ 1859, \KidName{Jeremiah Cooney}\index{Cooney!Jeremiah};\cite{JeremiahCooneyMarriage} m.\ (2) 5 Oct.\ 1884, \KidName{Michael Cusick}.\index{Cusick!Michael}\cite{MichaelCusickMarriage} No known children.
	
	\KidNum{\ref{per:Margaret3Dooley}}{ii.}\KidName{Margaret E. Dooley},\index{Dooley!Margaret\textsuperscript{3}}\index{Fernald!Margaret\textsuperscript{3} (Dooley) (Simonds)}\index{Simonds!Margaret\textsuperscript{3} (Dooley)} b.\ 27 Dec.\ 1840, m.\ (1) \KidName{William Simonds};\index{Simonds!William} m.\ (2) 21 Aug.\ 1873, \KidName{Robert A.\ Fernald}.\index{Fernald!Robert}\index{Ireland (surname)!Robert|see{Fernald, Robert}}
\end{Kids}
