\begin{thebibliography}{999}
	\raggedright
	\small
	
% Chapter 4: Generation 2

%% 1. Abigail O'Brien

\bibitem{Census1855Abigail}
1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 1, p. 60 (left side), dwelling [blank], family 549, for Abby Dooley in Edward O'Brien household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 29 Mar 2020), Suffolk > Boston Ward 01 > image 33.

\bibitem{Abigail2OBrienDeath:1}
Massachusetts Vital Records, Death Records, 1897, no.\ 121, Abigail Dooley; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 29 Mar 2020), \_Pre 1903 > 1897 > image 1431.

\bibitem{Chascay:6}
``Registers of Passengers Arriving in Massachusetts Ports 1848-1891,'' Massachusetts State Archives, HS 3.02 1990X, record of 27 Jun 1851, vessel \textit{Chascay}, entries for Edmund O'Brien and family; accessed at ``Massachusetts, United States Records,'' images, FamilySearch (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-CSVN-998J-W} : viewed on 11 Nov 2020), image 793.\\
On this page the ship name is written as ``Chascay'' but on the previous pages appears as ``Chasca.''

\bibitem{Abigail2OBrienDeath:2}
Massachusetts Vital Records, Death Records, 1897, no.\ 121, Abigail Dooley; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 29 Mar 2020), \_Pre 1903 > 1897 > image 1431.

\bibitem{CarolGordon:2}
Carol Gordon, Catholic Cemetery Association of the Archdiocese of Boston, emails to Gavin E.\ O'Brien in Apr.\ 2019.\\
Holy Cross Cemetery plot locations as follows.\\
Ann (O’Brien) Dailey: North Monument, Path 17, Grave 34 East\\
Abigail (O’Brien) Dooley: North Monument, Path 12, Grave 38 East\\
Mary (O’Brien) Ward: North Monument, Path 12, Grave 38 East

\bibitem{Abigail2OBrienDeath:3}
Massachusetts Vital Records, Death Records, 1897, no.\ 121, Abigail Dooley; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 29 Mar 2020), \_Pre 1903 > 1897 > image 1431.

\bibitem{MichaelDooleyBirth}
Abigail (O'Brien) Dooley and Michael Dooley had two children in County Cork, Ireland, prior to their immigration to the United States. 

\bibitem{Census1865Abigail}
1865 Massachusetts state census, Suffolk County, population schedule, city of Boston, ward 1, dwelling 1570, family 3692, for Abby Duley in William Simonds household; accessed at ``Massachusetts, State Census, 1865,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9203/} : viewed on 29 Mar 2020), Suffolk > Boston Ward 01 > image 203.\\
Abigail's marital status is listed as ``widowed.''

\bibitem{Chascay:7}
``Registers of Passengers Arriving in Massachusetts Ports 1848-1891,'' Massachusetts State Archives, HS 3.02 1990X, record of 27 Jun 1851, vessel \textit{Chascay}, entries for Edmund O'Brien and family; accessed at ``Massachusetts, United States Records,'' images, FamilySearch (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-CSVN-998J-W} : viewed on 11 Nov 2020), image 793.\\
On this page the ship name is written as ``Chascay'' but on the previous pages appears as ``Chasca.''

\bibitem{Chascay:8}
``Registers of Passengers Arriving in Massachusetts Ports 1848-1891,'' Massachusetts State Archives, HS 3.02 1990X, record of 27 Jun 1851, vessel \textit{Chascay}, entries for Edmund O'Brien and family; accessed at ``Massachusetts, United States Records,'' images, FamilySearch (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-CSVN-998J-W} : viewed on 11 Nov 2020), image 793.\\
On this page the ship name is written as ``Chascay'' but on the previous pages appears as ``Chasca.''

\bibitem{Census1855William:3}
1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 1, p. 60 (left side), dwelling [blank], family 549, for William O'Brien in Edward O'Brien household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 29 Mar 2020), Suffolk > Boston Ward 01 > image 33.

\bibitem{Census1860AbigailOBrien}
1860 U.S. census, Suffolk County, Massachusetts, population schedule, City of Boston, Ward 1, p.\ 397, family no.\ 3106, Abby Dooley household; accessed at ``1860 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7667/} : viewed on 12 Nov 2020), Massachusetts > Suffolk > Boston Ward 1 > image 398.

\bibitem{Census1855Hannah3Dooley}
1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 1, p. 60 (left side), dwelling [blank], family 549, for Hannah Dooley in Edward O'Brien household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 29 Mar 2020), Suffolk > Boston Ward 01 > image 33.\\
Hannah Dooley, age 18, born in Ireland

\bibitem{Hannah3DooleyDeath}
Massachusetts Vital Records, death records, 1911, p.\ 631, no.\ 5659, Hannah Cusick; accessed at ``Massachusetts Deaths, 1841-1915,'' database with images, \textit{FamilySearch} (\url{https://familysearch.org/ark:/61903/3:1:S3HY-DT59-PGR} : viewed on 11 Apr 2020), 2393942 (004283225) > image 2213.

\bibitem{JeremiahCooneyMarriage}
Massachusetts Vital Records, marriage records, 1859, no.\ 1734, Jeremiah Cooney and Hannah Doolly; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 10 Apr 2020), \_Up Through 1910 > 1859 > image 666.

\bibitem{MichaelCusickMarriage}
Massachusetts Vital Records, marriage records, 1884, no.\ 2686, Michael Cusick and Hannah Cooney; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 10 Apr 2020), \_Up Through 1910 > 1884 > image 1030.

%% 2. John O'Brien

\bibitem{John2OBrienMarriage:2}
St. Mary (Boston) Marriages, 1836-1854, p.\ 205, John O'Brien and Mary Mahoney; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/54105/205/1424477986} : viewed on 31 Mar 2020).

\bibitem{John2OBrienDeath:2}
Massachusetts Vital Records, death records, 1863, p.\ 49, no.\ 1270, John O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 31 Mar 2020), \_Pre 1903 > 1863 > image 756.\\
Cause of death: phthisis.

\bibitem{BillMcEvoy:1}
Bill McEvoy, compiler, ``Sand Banks Cemetery Project,'' Excel spreadsheet of plot locations, sourced from burial books and cemetery lot cards of the Catholic Archdiocese of Boston; accessed at \textit{The Historical Society of Watertown} (\url{http://historicalsocietyofwatertownma.org/HSW/} : viewed on 31 Mar 2020), Resources > Sand Banks Cemetery Project > downloadable Excel spreadsheet.

\bibitem{John2OBrienMarriage:3}
St. Mary (Boston) Marriages, 1836-1854, p.\ 205, John O'Brien and Mary Mahoney; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/54105/205/1424477986} : viewed on 31 Mar 2020).

\bibitem{John2OBrienCivilMarriage:2}
Massachusetts Vital Records, marriage records, 1853, p.\ 156, no.\ 2642, John O'Brien and Mary Mahoney; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 31 Mar 2020), \_Up Through 1910 > 1853 > image 779.

\bibitem{MaryMahoneyBowserMarriage:1}
Massachusetts Vital Records, marriage records, 1867, no.\ 267, Thomas Bowser and Mary O'Brien; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 31 Mar 2020), \_Up Through 1910 > 1867 > image 743.

\bibitem{MaryMahoneyBowserMarriage:2}
Massachusetts Vital Records, marriage records, 1867, no.\ 267, Thomas Bowser and Mary O'Brien; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 31 Mar 2020), \_Up Through 1910 > 1867 > image 743.

\bibitem{MaryMahoneyDeath}
Massachusetts Vital Records, death records, 1894, no.\ 755, Mary (Maloney) Bowser, wife of Thomas; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 31 Mar 2020), \_Pre 1903 > 1894 > image 1047.\\
Parents are listed as John and Ellen Daley; this does not match previous records.

\bibitem{BillMcEvoy:2}
Bill McEvoy, compiler, ``Sand Banks Cemetery Project,'' Excel spreadsheet of plot locations, sourced from burial books and cemetery lot cards of the Catholic Archdiocese of Boston; accessed at \textit{The Historical Society of Watertown} (\url{http://historicalsocietyofwatertownma.org/HSW/} : viewed on 31 Mar 2020), Resources > Sand Banks Cemetery Project > downloadable Excel spreadsheet.

\bibitem{Census1860John}
1860 U.S. census, Suffolk County, Massachusetts, population schedule, Boston, ward 1, p.\ 383, dwelling 1535, family 3004, John O'Brien household; accessed at ``1860 United States Federal Census,'' \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7667/} : viewed on 31 Mar 2020), Massachusetts > Suffolk > Boston Ward 1 > image 384.

\bibitem{John3OBrienBirth:2}
Massachusetts Vital Records, birth records, 1861, p.\ 11, no.\ 471, John O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 31 Mar 2020), \_up through 1910 > 1861 > image 909.

\bibitem{Wards:2}
City of Boston, Massachusetts, \textit{A Catalogue of the City Councils of Boston, 1822-1890, Roxbury, 1846-1867, Charlestown, 1847-1873 and of the selectmen of Boston, 1634-1822, also of various other town and municipal officers} (City of Boston Printing Department, 1909), 7--40; accessed at \textit{Internet Archive} (\url{https://archive.org/stream/catalogueofcityc00bost} : viewed on 2 Apr 2020).

\bibitem{1861John2OBrien:2}
Adams, Sampson, \& Company, compilers, \textit{The Boston Directory} (Boston: Adams, Sampson, \& Company, 1861), p.\ 355, John O'Brien at 35 Fleet St.; accessed at ``The Boston Directory, 1789 to 1900,'' \textit{Boston Athenaeum Digital Collections} (\url{https://cdm.bostonathenaeum.org/digital/collection/p16057coll32/id/93/rec/11} : viewed on 25 Jul 2020), Home > Boston Directory, 1789 to 1901 > 1861, Boston directory > image 337.\\
``O'Brien John, oysterman, house 35 Fleet''

\bibitem{1861EdwardOBrien}
Adams, Sampson, \& Company, compilers, \textit{Boston City Directory} (Boston: Adams, Sampson, \& Company, 1861), p. 335, Edward O'Brien at 33 Fleet; accessed at \textit{Boston Athenaeum Digital Collections} (\url{https://cdm.bostonathenaeum.org/digital/collection/p16057coll32/id/93/rec/57}: viewed on 19 Nov 2020).

\bibitem{John3OBrienBirth:3}
Massachusetts Vital Records, birth records, 1861, p.\ 11, no.\ 471, John O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 31 Mar 2020), \_up through 1910 > 1861 > image 909.

\bibitem{BillMcEvoy:3}
Bill McEvoy, compiler, ``Sand Banks Cemetery Project,'' Excel spreadsheet of plot locations, sourced from burial books and cemetery lot cards of the Catholic Archdiocese of Boston; accessed at \textit{The Historical Society of Watertown} (\url{http://historicalsocietyofwatertownma.org/HSW/} : viewed on 31 Mar 2020), Resources > Sand Banks Cemetery Project > downloadable Excel spreadsheet.

\bibitem{Mary3OBrienBirth}
Massachusetts Vital Records, birth records, 1856, p.\ 111, no.\ 4896, Mary O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 31 Mar 2020), \_up through 1910 > 1856 > image 818.

\bibitem{Mary3OBrienBaptism}
St. Stephen (Boston) Baptisms, 1854-1862, p.\ 134, Mary O'Brien, accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/134/1423778090} : viewed on 31 Mar 2020).

\bibitem{Mary3OBrienDeath}
Massachusetts Vital Records, death records, 1883, p.\ 73, no.\ 1916, Mary F. O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 31 Mar 2020), \_Pre 1903 > 1883 > image 847.

\bibitem{James3OBrienBirth}
Massachusetts Vital Records, birth records, 1858, p.\ 40, no.\ 1761, James Edward O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 31 Mar 2020), \_up through 1910 > 1858 > image 777.

\bibitem{James3OBrienBaptism}
St. Mary (Boston) Baptisms, 1850-1858, p.\ 491, James Edward O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/54102/491/1424471476} : viewed on 31 Mar 2020).

\bibitem{James3OBrienDeath}
Boston, Massachusetts Vital Records, death records, 1879, no.\ 2167, James E.\ O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Deaths, 1879 > image 77.

\bibitem{Ellen3OBrien2Baptism:1}
St. Stephen (Boston) Baptisms, 1854-1862, p.\ 312, Ellen O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/312/1423781683} : viewed on 31 Mar 2020).

\bibitem{Ellen3OBrien2Baptism:2}
St. Stephen (Boston) Baptisms, 1854-1862, p.\ 312, Ellen O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/312/1423781683} : viewed on 31 Mar 2020).

\bibitem{Ellen3OBrien2Death}
Boston, Massachusetts Vital Records, death records, 1882, no.\ 6860, Ellen F. O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Deaths, 1882 > image 233.

\bibitem{Margaret3OBrienBaptism:1}
St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 312, Margaret O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/312/1423781685} : viewed on 5 Apr 2020).\\
Records of St.\ John the Baptist Church are located in the volume for St.\ Stephen's Church; see note on Mary\textsuperscript{3} O'Brien's baptismal citation.

\bibitem{Margaret3OBrienBaptism:2}
St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 312, Margaret O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/312/1423781685} : viewed on 5 Apr 2020).\\
Records of St.\ John the Baptist Church are located in the volume for St.\ Stephen's Church; see note on Mary\textsuperscript{3} O'Brien's baptismal citation.

\bibitem{Margaret3OBrienDeath}
Massachusetts Vital Records, death records, 1863, p.\ 149, no.\ 3752, Margaret O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 31 Mar 2020), \_Pre 1903 > 1863 > image 855.

\bibitem{Anna3OBrienDeath:1}
Boston, Massachusetts Vital Records, death records, 1866, no.\ 621, Anna O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Deaths, 1866 > image 19.

\bibitem{Anna3OBrienDeath:2}
Boston, Massachusetts Vital Records, death records, 1866, no.\ 621, Anna O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 31 Mar 2020), Boston > Deaths, 1866 > image 19.

%% 3. Edward O'Brien

\bibitem{Edward2OBrienNaturalization:2}
Edward O Brien primary declaration of intention (1854), no.\ 487, 
District of Massachusetts; 
Record Group 21: Records of the District Courts of the United States; 
National Archives at Boston, Waltham, Massachusetts;
viewed at ``Massachusetts, State and Federal Naturalization Records, 1798--1950,''
database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2361/} : viewed on 23 Mar 2020), image 858.

\bibitem{Edward2OBrienDeath}
Massachusetts Vital Records, death records, 1881, no.\ 5857, Edward O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_Pre 1903 > 1881 > image 958.

\bibitem{CarolGordon:3}
Carol Gordon, Catholic Cemetery Association of the Archdiocese of Boston, emails to Gavin E.\ O'Brien in Apr.\ 2019.\\
Holy Cross Cemetery plot locations as follows.\\
Ann (O’Brien) Dailey: North Monument, Path 17, Grave 34 East\\
Abigail (O’Brien) Dooley: North Monument, Path 12, Grave 38 East\\
Mary (O’Brien) Ward: North Monument, Path 12, Grave 38 East

\bibitem{Edward2OBrienMarriage}
The author searched the Massachusetts marriage index from 1841--1855 for Edward O'Brien and Bridget Linnehan/Linnihan/Linehan/Linahan/Linnahan. No relevant records found.	
Massachusetts Vital Records, ``Index to marriages A-Z 1841-1850'' and ``Index to marriages A-Z 1851-1855''; accessed at ``Massachusetts indexes to births and marriages (1841-1920), deaths (1841-1971),'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-C9BG-SSZ9-4} : viewed on 2 Apr 2020).

\bibitem{Edward2OBrienNaturalization:3}
Edward O Brien primary declaration of intention (1854), no.\ 487, 
District of Massachusetts; 
Record Group 21: Records of the District Courts of the United States; 
National Archives at Boston, Waltham, Massachusetts;
viewed at ``Massachusetts, State and Federal Naturalization Records, 1798--1950,''
database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2361/} : viewed on 23 Mar 2020), image 858.

\bibitem{Edward2OBrienPetition}
Suffolk County, Massachusetts, Superior Civil Court, Petitions for Naturalization, vol.\ 1, 1864, p.\ 118, entry for Edward O'Brien; accessed at ``Massachusetts, State and Federal Naturalization Records, 1798-1950,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2361/} : viewed on 11 Jul 2020), Superior Court, Suffolk County, Massachusetts > Petitions, V 1, P 6-204, 1864 > image 184.

\bibitem{BridgetLinnehanDeath:1}
Boston, Massachusetts Vital Records, death records, 1867, no.\ 1127, Bridget O'Brien, wife of Edward; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 2 Apr 2020), Boston > Births, Marriages and Death > image 32429.

\bibitem{MaryGrahamDeath:1}
``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, FamilySearch (\url{https://www.familysearch.org/ark:/61903/1:1:FH6R-Y2N} : viewed on 29 Nov 2020), Mary A Lenehan Graham, 20 Dec 1875; citing Death, Boston, Suffolk, Massachusetts, United States, Massachusetts Secretary of the Commonwealth, Boston; FHL microfilm 004273940.\\
Mary A.\ Graham m.n.\ Linehan, age 40, wife of William, born in Ireland, parents William and Jane, interred at Brookline. [Possible sister of Bridget (Linnehan) O'Brien]

\bibitem{BridgetLinnehanDeath:2}
Boston, Massachusetts Vital Records, death records, 1867, no.\ 1127, Bridget O'Brien, wife of Edward; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 2 Apr 2020), Boston > Births, Marriages and Death > image 32429.

\bibitem{LondonStDeed:1}
Massachusetts, Suffolk County Registry of Deeds, 1870, vol.\ 1009, p.\ 38, Cutcliffe Jr to O’Brien; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-L9Z3-938P} : viewed on 5 Apr 2020), Suffolk > Deeds 1870 vol 1008-1009 > image 394.\\
Edward's probate file states he owned ``Lincoln St.\  East Boston,'' however, this was probably a misspelling of ``London St.\'' as there was no Lincoln St.\ located in East Boston.\cite{EastBostonStreets}

\bibitem{Edward2OBrien1876}
Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1876), 678, Edward O’Brien at 307 Havre, E.B.; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 4 Apr 2020), Massachusetts > Boston > 1876 > Boston, Massachusetts, City Directory, 1876 > image 678.\\
O’Brien Edward, teamster, house 307 Havre, E.B.

\bibitem{Teamster}
``teamster, n.'' \textit{Oxford English Dictionary Online} (\url{https://www-oed-com.ezproxy.bpl.org/view/Entry/198379} : viewed 5 Apr 2020)

\bibitem{MaryAnn3OBrienBirth:1}
Massachusetts Vital Records, birth records, 1852, p.\ 47, no.\ 2075, Mary Ann O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_up through 1910 > 1852 > image 675.

\bibitem{Edward3OBrienBirth:1}
Boston, Massachusetts Vital Records, birth records, 1861, no.\ 4572, Edward O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 5 Apr 2020), Boston > Births, 1861 > image 13.

\bibitem{LondonStDeed:2}
Massachusetts, Suffolk County Registry of Deeds, 1870, vol.\ 1009, p.\ 38, Cutcliffe Jr to O’Brien; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-L9Z3-938P} : viewed on 5 Apr 2020), Suffolk > Deeds 1870 vol 1008-1009 > image 394.\\
Edward's probate file states he owned ``Lincoln St.\  East Boston,'' however, this was probably a misspelling of ``London St.\'' as there was no Lincoln St.\ located in East Boston.\cite{EastBostonStreets}

\bibitem{LondonStMap}
Griffith Morgan Hopkins Jr., \textit{Atlas of the county of Suffolk, Massachusetts} (Philadelphia: G.M.\ Hopkins \& Co., 1874), vol.\ 4, plate K, showing 185 London St.; accessed at \textit{Norman B.\ Leventhal Map Center} (\url{https://collections.leventhalmap.org/search/commonwealth:6h446s239} : viewed on 5 Apr 2020).

\bibitem{EastBostonStreets}
Massachusetts, Suffolk County Register of Deeds, \textit{Atlas of East Boston,} 1892, vol.\ 9, street index; accessed at \textit{Suffolk County Register of Deeds} (\url{https://massrods.com/suffolk/suffolk-county-atlas/suffolk-county-atlas-pages/} : viewed on 4 Apr 2020), Research > Suffolk County Atlases > East Boston 1892 > Street Index.

\bibitem{HavrePurchase}
Massachusetts, Suffolk County Registry of Deeds, 1874, vol.\ 1224, p.\ 25, Roome to O’Brien; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QSQ-G9Z3-9BYX} : viewed on 4 Apr 2020), Suffolk > Deeds 1874 vol 1223-1224 > image 369.

\bibitem{HavreMap}
Massachusetts, Suffolk County Register of Deeds, \textit{Atlas of East Boston,} 1892, vol.\ 9, p.\ 14; accessed at \textit{Suffolk County Register of Deeds} (\url{https://massrods.com/suffolk/suffolk-county-atlas/suffolk-county-atlas-pages/} : viewed on 4 Apr 2020), Research > Suffolk County Atlases > East Boston 1892 > Page 14

\bibitem{Edward2OBrienProbate}
Massachusetts Probate Court, Suffolk County, 1881, vol.\ 533, pp.\ 216--217, Edward O'Brien; accessed at ``Suffolk County (Massachusetts) probate records, 1636-1899,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-C9YR-6S4L} : viewed on 2 Apr 2020), ``Probate records v. 533-534 1881,'' Film \#007704174, image 118.

\bibitem{Bromley1922}
George Washington Bromley, \textit{Atlas of the city of Boston, Charlestown and East Boston} (Philadelphia: G.W.\ Bromley \& Co., 1874), plate 25, showing 185 London St.; accessed at \textit{Norman B.\ Leventhal Map Center} (\url{https://collections.leventhalmap.org/search/commonwealth:1257c1339} : viewed on 5 Apr 2020).

\bibitem{GlobeRobbery}
``Take two burglars at revolver point,’’ \textit{The Boston Globe}, 18 Apr 1922, p.\ 7; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/48057899/the-boston-globe/} : viewed on 5 Apr 2020).

\bibitem{Frances3OBrien1914}
Sampson \& Murdock Company, compilers, \textit{The Boston Directory} (Boston: Sampson \& Murdoch Company, 1914), p.\ 1973, entry for Frances Wickens; accessed at ``U.S.\ City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 5 Apr 2020), Massachusetts > Boston > 1914 > Boston, Massachusetts, City Directory, 1914 > image 1981.\\
``Wickens Frances widow John B h 185 London E B''

\bibitem{AnnMaria3OBrienDeath:1}
Annie M.\ O'Brien obituary, \textit{The Boston Globe}, 25 May 1937, p.\ 14, col.\ 8; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/48037127/obituary-for-annie-m-o-obrien/?xid=637} : viewed on 5 Apr 2020).

\bibitem{Margaret3OBrien2Death:1}
Margaret O'Brien obituary, \textit{Daily Boston Globe} (1928-1960), 7 Mar 1933, p. 17. ProQuest. Web. 28 June 2019. 

\bibitem{Census1880Edward:2}
1880 U.S. census, Suffolk County, Massachusetts, population schedule, East Boston, Enumeration District (ED) 576, p.\ 24, dwelling 153, family 267, Edward O'Brian household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 2 Apr 2020), Massachusetts > Suffolk > Boston > 576 > image 24.

\bibitem{DeliaGrahamBirth}
``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, FamilySearch (\url{https://www.familysearch.org/ark:/61903/1:1:DCY2-NQZM} : viewed on 19 Nov 2020), Delia Jane Graham, 28 Jun 1869; citing Birth, Boston, Suffolk, Massachusetts, United States, Massachusetts Secretary of the Commonwealth, Boston; FHL microfilm 007009365.

\bibitem{MaryGrahamDeath:2}
``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, FamilySearch (\url{https://www.familysearch.org/ark:/61903/1:1:FH6R-Y2N} : viewed on 29 Nov 2020), Mary A Lenehan Graham, 20 Dec 1875; citing Death, Boston, Suffolk, Massachusetts, United States, Massachusetts Secretary of the Commonwealth, Boston; FHL microfilm 004273940.\\
Mary A.\ Graham m.n.\ Linehan, age 40, wife of William, born in Ireland, parents William and Jane, interred at Brookline. [Possible sister of Bridget (Linnehan) O'Brien]

\bibitem{Census1880Edward:3}
1880 U.S. census, Suffolk County, Massachusetts, population schedule, East Boston, Enumeration District (ED) 576, p.\ 24, dwelling 153, family 267, Edward O'Brian household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 2 Apr 2020), Massachusetts > Suffolk > Boston > 576 > image 24.

\bibitem{Edward2OBrienGrave}
Holy Cross Cemetery (Malden, Middlesex County, Massachusetts), Edward O'Brien marker, North Monument Ave., Path 17, Grave 34 East; personally read, 14 Apr 2019. \\
Photos available at \url{https://www.findagrave.com/memorial/201238724/edward-o_brien}.

\bibitem{CarolGordon:4}
Carol Gordon, Catholic Cemetery Association of the Archdiocese of Boston, emails to Gavin E.\ O'Brien in Apr.\ 2019.\\
Holy Cross Cemetery plot locations as follows.\\
Ann (O’Brien) Dailey: North Monument, Path 17, Grave 34 East\\
Abigail (O’Brien) Dooley: North Monument, Path 12, Grave 38 East\\
Mary (O’Brien) Ward: North Monument, Path 12, Grave 38 East

\bibitem{MaryAnn3OBrienBirth:2}
Massachusetts Vital Records, birth records, 1852, p.\ 47, no.\ 2075, Mary Ann O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_up through 1910 > 1852 > image 675.

\bibitem{MaryAnn3OBrienBaptism}
Holy Cross (Boston) Baptisms V.9, 1850-1853, p.\ 335, Mary A O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48422/335/1415444935} : viewed on 5 Apr 2020).

\bibitem{MaryAnn3OBrienDeath}
Massachusetts Vital Records, death records, 1852, no.\ 3333, Mary A.\ O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_Pre 1903 > 1852 > image 501.

\bibitem{DianaBerberenaLetter1:2}
Diana Berberena, Catholic Cemetery Association of the Archdiocese of Boston, letter to Gavin E.\ O'Brien, dated 27 May 2019. This letter includes burial information for two individuals. William O'Brien, buried 12/30/[1856], age 76 years into O'Brien Family Grave G W124 Range N17 west, owner Edward O'Brien. Mary Ann O'Brien, buried 11/1852, age 1 month, 12 days old.

\bibitem{Ellen3OBrienBirth}
Massachusetts Vital Records, birth records, 1853, p.\ 81, no.\ 3620, Ellen O'Brine; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_up through 1910 > 1853 > image 749.

\bibitem{Ellen3OBrienBaptism}
Holy Cross (Boston) Baptisms, v.\ 10, 1853-1858, p.\ 39, Ellen O'Brian; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' AmericanAncestors.org (\url{https://www.americanancestors.org/DB2726/i/48416/39/1415448399} : viewed on 20 Feb 2021).

\bibitem{Ellen3OBrienDeath}
Boston, Massachusetts vital records, 1857 deaths, entry 1164, Ellen O'Brien; accessed at ``Massachusetts, U.S., Town and Vital Records, 1620-1988,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/2495} : viewed on 8 Feb 2021), Boston > Births, Marriages and Death > image 31052.\\
Dropsy in head.

\bibitem{DianaBerberenaLetter2:1}
Diana Berberena, Catholic Cemetery Association of the Archdiocese of Boston, letter to Gavin E.\ O'Brien, received 11 Jul.\ 2019.\\
Michael Dooley: North Cambridge Catholic Cemetery, Range 14 East, Grave 96\\
Ellen O’Brien: North Cambridge Catholic Cemetery, Range 17 West, Grave 124\\
Michael O’Brien: Holy Cross Cemetery, 28 North Maple, Grave 27 West

\bibitem{AnnMaria3OBrienBirth}
Boston, Massachusetts Vital Records, birth records, 1855, no.\ 5412, Ann Maria O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 5 Apr 2020), \_up through 1910 > 1855 > image 798.

\bibitem{AnnMaria3OBrienBaptism}
St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 102, Ann M.\ O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/102/1423777462} : viewed on 5 Apr 2020).\\
Records in the St.\ Stephen's volume prior to the church's establishment on 26 Sep 1862. See title page of this volume and the history of St. Stephen's in James S.\ Sullivan, \textit{One Hundred Years of Progress; A Graphic, Historical and Pictorial Account of the Catholic Church of New England: Archdiocese of Boston} (Illustrated Publishing Company: Boston and Portland, 1895), p.\ 128.

\bibitem{AnnMaria3OBrienDeath:2}
Annie M.\ O'Brien obituary, \textit{The Boston Globe}, 25 May 1937, p.\ 14, col.\ 8; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/48037127/obituary-for-annie-m-o-obrien/?xid=637} : viewed on 5 Apr 2020).

\bibitem{CarolGordon:5}
Carol Gordon, Catholic Cemetery Association of the Archdiocese of Boston, emails to Gavin E.\ O'Brien in Apr.\ 2019.\\
Holy Cross Cemetery plot locations as follows.\\
Ann (O’Brien) Dailey: North Monument, Path 17, Grave 34 East\\
Abigail (O’Brien) Dooley: North Monument, Path 12, Grave 38 East\\
Mary (O’Brien) Ward: North Monument, Path 12, Grave 38 East

\bibitem{Margaret3OBrien2Baptism:1}
St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 312, Margaret O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/312/1423781685} : viewed on 8 Feb 2021).

\bibitem{Margaret3OBrien2Baptism:2}
St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 312, Margaret O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/312/1423781685} : viewed on 8 Feb 2021).

\bibitem{CarolGordon:6}
Carol Gordon, Catholic Cemetery Association of the Archdiocese of Boston, emails to Gavin E.\ O'Brien in Apr.\ 2019.\\
Holy Cross Cemetery plot locations as follows.\\
Ann (O’Brien) Dailey: North Monument, Path 17, Grave 34 East\\
Abigail (O’Brien) Dooley: North Monument, Path 12, Grave 38 East\\
Mary (O’Brien) Ward: North Monument, Path 12, Grave 38 East

\bibitem{Margaret3OBrien2Death:2}
Margaret O'Brien obituary, \textit{Daily Boston Globe} (1928-1960), 7 Mar 1933, p. 17. ProQuest. Web. 28 June 2019. 

\bibitem{Edward3OBrienBirth:2}
Boston, Massachusetts Vital Records, birth records, 1861, no.\ 4572, Edward O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 5 Apr 2020), Boston > Births, 1861 > image 13.

\bibitem{Edward3OBrienDeath}
Massachusetts Vital Records, death records, 1884, p.\ 6, no.\ 162, Edward J.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 5 Apr 2020), \_Pre 1903 > 1884 > image 773.	

\bibitem{CarolGordon:7}
Carol Gordon, Catholic Cemetery Association of the Archdiocese of Boston, emails to Gavin E.\ O'Brien in Apr.\ 2019.\\
Holy Cross Cemetery plot locations as follows.\\
Ann (O’Brien) Dailey: North Monument, Path 17, Grave 34 East\\
Abigail (O’Brien) Dooley: North Monument, Path 12, Grave 38 East\\
Mary (O’Brien) Ward: North Monument, Path 12, Grave 38 East

% 4. Mary O'Brien

\bibitem{Mary2OBrienMarriage:1}
Massachusetts Vital Records, marriage records, 1850, no.\ 2038 , David Wards to Mary O'Brien; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 5 Apr 2020), \_Up Through 1910 > 1850 > image 643.

\bibitem{Mary2OBrienDeath:2}
Massachusetts Vital Records, Death Records, 1908, p.\ 576, no.\ 2762, Mary Ward; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 29 Mar 2020), 1908 > Boston > image 2737.

\bibitem{CarolGordon:8}
Carol Gordon, Catholic Cemetery Association of the Archdiocese of Boston, emails to Gavin E.\ O'Brien in Apr.\ 2019.\\
Holy Cross Cemetery plot locations as follows.\\
Ann (O’Brien) Dailey: North Monument, Path 17, Grave 34 East\\
Abigail (O’Brien) Dooley: North Monument, Path 12, Grave 38 East\\
Mary (O’Brien) Ward: North Monument, Path 12, Grave 38 East

\bibitem{Mary2OBrienMarriage:2}
Massachusetts Vital Records, marriage records, 1850, no.\ 2038 , David Wards to Mary O'Brien; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 5 Apr 2020), \_Up Through 1910 > 1850 > image 643.

\bibitem{Mary2OBrienMarriage2:1}
Holy Cross (Boston) Marriages, vol.\ 8, 1844-1856, p.\ 175, entry for David Ward and Mary O'Brien; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48428/175/1415482355} : viewed on 22 Aug 2020).

\bibitem{DavidWardObit}
David Ward obituary, \textit{Boston Herald}, 20 Dec 1881, p.\ 6; accessed at \textit{GenealogyBank} (\url{https://twitter.com/ShawnMcCreesh/status/1283567307697119232} : viewed on 16 Jul 2020).

\bibitem{DavidWardDeath:1}
Massachusetts Vital Records, death records, 1881, no.\ 8782, David Ward; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 5 Apr 2020), \_Pre 1903 > 1881 > image 1056.

\bibitem{DavidWardDeath:2}
Massachusetts Vital Records, death records, 1881, no.\ 8782, David Ward; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 5 Apr 2020), \_Pre 1903 > 1881 > image 1056.\\

\bibitem{Mary2OBrienMarriage2:2}
Holy Cross (Boston) Marriages, vol.\ 8, 1844-1856, p.\ 175, entry for David Ward and Mary O'Brien; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48428/175/1415482355} : viewed on 22 Aug 2020). \\
``I, the undersigned, about to marry Mary OBrien, promise never to disturb her in the exercise of her religion, \& if God grant us children, to have them brought up in the faith \& practices of the Catholic Church.''

\bibitem{DavidWard1876}
Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1876), 908, Ward David, jr.; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 4 Apr 2020), Massachusetts > Boston > 1876 > Boston, Massachusetts, City Directory, 1876 > image 908.

\bibitem{DavidWard1877}
Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1876), 918, Ward David, jr.; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 4 Apr 2020), Massachusetts > Boston > 1877 > Boston, Massachusetts, City Directory, 1877 > image 918.

\bibitem{Census1880DavidWard:1}
1880 U.S. census, Suffolk County, Massachusetts, population schedule, East Boston, Enumeration District (ED) 576, p.\ 11, dwelling 66, family 121, David Ward household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 5 Apr 2020), Massachusetts > Suffolk > Boston > 576 > image 11.

\bibitem{101Bennington:1}
Massachusetts, Suffolk County Registry of Deeds, 1871, vol.\ 1058, p.\ 125, Hargrave to Ward; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-89Z3-MJ6D} : viewed on 5 Apr 2020), Suffolk > Deeds 1871 vol 1057-1058 > image 496.

\bibitem{101BenningtonMap}
Massachusetts, Suffolk County Register of Deeds, \textit{Atlas of East Boston,} 1892, vol.\ 9, p.\ 14; accessed at \textit{Suffolk County Register of Deeds} (\url{https://massrods.com/suffolk/suffolk-county-atlas/suffolk-county-atlas-pages/} : viewed on 4 Apr 2020), Research > Suffolk County Atlases > East Boston 1892 > Page 14

\bibitem{MaryAnn3WardBaptism:1}
Holy Cross (Boston) Baptisms V.9, 1850-1853, p.\ 192, Mary Ward; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48422/192/1415441475} : viewed on 5 Apr 2020).	

\bibitem{MaryAnn3WardBaptism:2}
Holy Cross (Boston) Baptisms V.9, 1850-1853, p.\ 192, Mary Ward; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48422/192/1415441475} : viewed on 5 Apr 2020).	

\bibitem{MaryAnn3WardDeath}
Boston, Massachusetts Vital Records, deaths, 1854, no.\ 82, Mary Ann Ward; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 5 Apr 2020), Boston > Births, Marriages and Death > image 30746.

\bibitem{Sarah3WardBirth}
Boston, Massachusetts Vital Records, births, 1853, no.\ 4476, Sarah Ward; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 5 Apr 2020), Boston > Births, Marriages and Death > image 53540.

\bibitem{Sarah3WardBaptism}
Holy Cross (Boston) Baptisms V.10, 1853-1858, p.\ 45, Sarah Ward; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48416/45/1415448535} : viewed on 5 Apr 2020).	

\bibitem{Sarah3WardDeath}
Boston, Massachusetts Vital Records, deaths, 1873, no.\ 2307, Sarah Ward; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 5 Apr 2020), Boston > Deaths, 1873 > image 75.

%% 5. Michael O'Brien

\bibitem{Michael2OBrienNaturalization:2}
Michael OBrien petition for naturalization (1868), 
Massachusetts Superior Court, Suffolk County; 
Oct term 1868 (Letters L--Z), Film \# 007795438,
viewed at ``Primary and final declarations of intention and naturalizations, 1864--1888 and card index 1856--1884,''
database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-CS9H-83DG-G}) : viewed on 23 Mar 2020), image 1859.

\bibitem{Michael2OBrienDeath:2}
Massachusetts Vital Records, Death Records, 1891, no.\ 4862, Michael O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 29 Mar 2020), \_Pre 1903 > 1891 > image 1303.

\bibitem{DianaBerberenaLetter2:2}
Diana Berberena, Catholic Cemetery Association of the Archdiocese of Boston, letter to Gavin E.\ O'Brien, received 11 Jul.\ 2019.\\
Michael Dooley: North Cambridge Catholic Cemetery, Range 14 East, Grave 96\\
Ellen O’Brien: North Cambridge Catholic Cemetery, Range 17 West, Grave 124\\
Michael O’Brien: Holy Cross Cemetery, 28 North Maple, Grave 27 West

\bibitem{BridgetColbertMarriage:1}
Massachusetts Vital Records, marriage records, 1854, no.\ 165, Michael O'Brien and Bridget Colbert; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 7 Apr 2020), \_Up Through 1910 > 1854 > image 573.

\bibitem{BridgetColbertChurchMarriage}
``St. Joseph (Roxbury) Marriages, 1845-1857,'' 1854, p.\ 148, entry for Michael O'Briene and Bridget Colbert; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/rd/56907/148/1426266499} : viewed on 16 Jul 2020).

\bibitem{BridgetColbertMarriage:2}
Massachusetts Vital Records, marriage records, 1854, no.\ 165, Michael O'Brien and Bridget Colbert; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 7 Apr 2020), \_Up Through 1910 > 1854 > image 573.

\bibitem{BridgetColbertDeath}
Massachusetts Vital Records, death records, 1873, no.\ 99, Bridget O'Brien (m.n.) Colbert; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 7 Apr 2020), \_Pre 1903 > 1873 > image 982.

\bibitem{BillMcEvoy:4}
Bill McEvoy, compiler, ``Sand Banks Cemetery Project,'' Excel spreadsheet of plot locations, sourced from burial books and cemetery lot cards of the Catholic Archdiocese of Boston; accessed at \textit{The Historical Society of Watertown} (\url{http://historicalsocietyofwatertownma.org/HSW/} : viewed on 31 Mar 2020), Resources > Sand Banks Cemetery Project > downloadable Excel spreadsheet.

\bibitem{MaryFieldMarriage:1}
Boston, Massachusetts Vital Records, marriage records, 1874, no.\ 1240, Michael O'Brien and Mary Feely; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 7 Apr 2020), Boston > Marriages, 1874 > image 74.

\bibitem{MaryFieldChurchMarriage}
``Most Holy Redeemer (East Boston) Marriages, 1851-1900,'' 1874, p.\ 143, entry for Michael O'Brien and Mary Field; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/55186/143/1424614029} : viewed on 16 Jul 2020).

\bibitem{MaryFieldMarriage:2}
Boston, Massachusetts Vital Records, marriage records, 1874, no.\ 1240, Michael O'Brien and Mary Feely; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 7 Apr 2020), Boston > Marriages, 1874 > image 74.

\bibitem{MaryFieldDeath:1}
Massachusetts Vital Records, death records, 1915, no.\ 195, Mary O'Brien; accessed at ``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-89J2-3ZB6} : viewed on 7 Apr 2020), Suffolk > Boston > Deaths 1915 no 1-1500 > image 208.

\bibitem{MaryFieldDeath:2}
Massachusetts Vital Records, death records, 1915, no.\ 195, Mary O'Brien; accessed at ``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-89J2-3ZB6} : viewed on 7 Apr 2020), Suffolk > Boston > Deaths 1915 no 1-1500 > image 208.

\bibitem{EdwardFrancis3OBrienBirth:2}
Massachusetts Vital Records, birth records, 1883, p.\ 38, no.\ 1669, Edward Francis O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 7 Apr 2020), \_up through 1910 > 1883 > image 1071.

\bibitem{Michael2OBrien1886:2}
Sampson, Murdock, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Murdock, and Company, 1886), p.\ 888, Michael O'Brien; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 7 Apr 2020), Massachusetts > Boston > 1886 > Boston, Massachusetts, City Directory, 1886 > image 535.\\
``O'Brien Michael, oyster opener, h. 243 Border''

\bibitem{243BorderPurchase}
Massachusetts, Suffolk County Registry of Deeds, 1872, vol.\ 1088, p. 159, Appleton, Gdn.\ To O’Brien; accessed at ``Massachusetts Land Records, 1620-1986,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QSQ-G9Z3-MLGY} : viewed on 2 Apr 2020), Deeds 1872 vol 1088-1089 > image 171.

\bibitem{243BorderMap}
Massachusetts, Suffolk County Register of Deeds, \textit{Atlas of East Boston,} 1892, vol.\ 9, p.\ 11; accessed at \textit{Suffolk County Register of Deeds} (\url{https://massrods.com/suffolk/suffolk-county-atlas/suffolk-county-atlas-pages/} : viewed on 4 Apr 2020), Research > Suffolk County Atlases > East Boston 1892 > Page 11

\bibitem{243BorderFerry}
Massachusetts, Suffolk County Registry of Deeds, 1886, vol.\ 1753, p. 147, East Boston Co. to O’Brien; accessed at ``Massachusetts Land Records, 1620-1986,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-L9ZD-5QHB} : viewed on 2 Apr 2020), Suffolk > Deeds 1886 vol 1753 > image 77.

\bibitem{Census1870Ellen3OBrien3}
1870 U.S. census, Suffolk County, Massachusetts, population schedule, Boston Ward 1 (East Boston), p.\ 292, dwelling 1271, family 2399, Ellen O'Brien in Michael O'Brien household; accessed at ``1870 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7163/} : viewed on 9 Apr 2020), Massachusetts > Suffolk > Boston Ward 01 > image 292.

\bibitem{Census1880Ellen3OBrien3}
1880 U.S. census, Suffolk County, Massachusetts, population schedule, Boston, Enumeration District (ED) 578, p.\ 2, dwelling 8, family 16, Nellie O'Brien in Michael O'Brien household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 9 Apr 2020), Massachusetts > Suffolk > Boston > 578 > image 2.\\
House is at 243 Border St.

\bibitem{Ellen3OBrien3Birth}
Massachusetts Vital Records, birth records, 1857, p.\ 50, no.\ 2233, Ellen O'Brien; accessed at ``Massachusetts Births, 1841-1915,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:S3HT-6QT9-X1N} : viewed on 9 Apr 2020), 004341180 > image 145.

\bibitem{Ellen3OBrien3Baptism}
St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 193, Ellen O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/193/1423779290} : viewed on 9 Apr 2020).\\
Records of St.\ John the Baptist Church are located in the volume for St.\ Stephen's Church; see note on Mary\textsuperscript{3} O'Brien's baptismal citation.

\bibitem{Boston1861Map}
C.\ Pinney, \textit{Plan of the city of Boston} (Boston: L.\ Prang \& Co.), plate 15, showing Ferry St.; accessed at \textit{Norman B.\ Leventhal Map Center} (\url{https://collections.leventhalmap.org/search/commonwealth:6h446v44g} : viewed on 9 Apr 2020).	

\bibitem{Michael2OBrienProbate}
Massachusetts Probate Court, Suffolk County, 1891, vol.\ 648, p.\ 380, petition for administration of Michael O'Brien estate by Mary O'Brien; accessed at ``Suffolk County (Massachusetts) probate records, 1636-1899,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-C9YR-MYW} : viewed on 9 Apr 2020), Probate records v. 648-649 1891 > image 203.

\bibitem{MaryAnn3OBrien2Birth}
Massachusetts Vital Records, birth records, 1859, no.\ 4561, Mary Ann O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 9 Apr 2020), \_up through 1910 > 1859 > image 864.\\
Address: 38 Fleet St.

\bibitem{MaryAnn3OBrien2Death}
Boston, Massachusetts Vital Records, death records, 1861, no.\ 1632, Mary A.\ O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 9 Apr 2020), Boston > Deaths, 1861 > image 69.

\bibitem{Mary3OBrien2Birth}
Massachusetts Vital Records, birth records, 1875, no.\ 852, Mary O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 9 Apr 2020), \_up through 1910 > 1875 > image 932.

\bibitem{Mary3OBrien2Death}
Massachusetts Vital Records, death records, 1875, no.\ 7956, Mary O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 9 Apr 2020), \_Pre 1903 > 1875 > image 1036.\\
Cause of death: Bronchitis. Address: 243 Border St.

\bibitem{John3OBrien2Birth}
Massachusetts Vital Records, birth records, 1876, no.\ 4509, John Joseph O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 9 Apr 2020), \_up through 1910 > 1876 > image 973.

\bibitem{John3OBrien2Death}
Massachusetts Vital Records, death records, 1881, no.\ 6616, John O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 9 Apr 2020), \_Pre 1903 > 1881 > image 982.\\
Cause of death: Diphtheria. Address: 243 Border St.

\bibitem{Francis3OBrienBirth}
Massachusetts Vital Records, birth records, 1883, p.\ 38, no.\ 1669, Edward Francis O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 10 Apr 2020), \_up through 1910 > 1883 > image 1071.\\
The name in this birth register is likely an error. ``Edward Francis O'Brien'' is the name of his older brother, and he was baptized as ``Francis Joseph O'Brien.''

\bibitem{Francis3OBrienBaptism}
Most Holy Redeemer (East Boston) Baptisms, 1883-1900, p.\ 2, Franciscus Joseph O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/rd/55184/2/1424603942} : viewed on 10 Apr 2020).	
Sponsors: Jeremiah Field and Mrs. Ann Daley.

\bibitem{Francis3OBrienDeath:1}
Massachusetts Vital Records, death records, 1914, p.\ 377, no.\ 725, Frank J.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 10 Apr 2020), 1914 > New Bedford.

\bibitem{Census1900Francis3OBrien}
1900 U.S. census, Suffolk County, Massachusetts, population schedule, Boston Ward 1, Enumeration District (ED) 1160, p.\ 12, dwelling 150, family 260, Frank O'Brien in Mary O'Brien household; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 10 Apr 2020), Massachusetts > Suffolk > Boston Ward 01 > District 1160 > image 24.

\bibitem{Francis3OBrienDeath:2}
Massachusetts Vital Records, death records, 1914, p.\ 377, no.\ 725, Frank J.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 10 Apr 2020), 1914 > New Bedford.

\bibitem{Francis3OBrien1913:1}
W.\ A.\ Greenough \& Co., compilers, \textit{New Bedford and Fairhaven Directory} (Boston: W.\ A.\ Greenough \& Co., 1913), p.\ 772, Frank J O'Brien; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 10 Apr 2020), Massachusetts > New Bedford > 1913 > New Bedford, Massachusetts, City Directory, 1913 > image 774.\\
``O'Brien Frank J meter tester 125 Middle h 95 S Sixth'' - see also p.\ 1010 (image 1014) of the same directory for the full name of the New Bedford Gas \& Edison Light Co.\ located at 125 Middle St.

\bibitem{Francis3OBrien1913:2}
W.\ A.\ Greenough \& Co., compilers, \textit{New Bedford and Fairhaven Directory} (Boston: W.\ A.\ Greenough \& Co., 1913), p.\ 772, Frank J O'Brien; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 10 Apr 2020), Massachusetts > New Bedford > 1913 > New Bedford, Massachusetts, City Directory, 1913 > image 774.\\
``O'Brien Frank J meter tester 125 Middle h 95 S Sixth'' - see also p.\ 1010 (image 1014) of the same directory for the full name of the New Bedford Gas \& Edison Light Co.\ located at 125 Middle St.

\bibitem{Francis3OBrienDeath:3}
Massachusetts Vital Records, death records, 1914, p.\ 377, no.\ 725, Frank J.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 10 Apr 2020), 1914 > New Bedford.
	
\end{thebibliography}