\section{John O'Brien}\label{per:John2OBrien}

\MainPerson{John\textsuperscript{2} O'Brien}\index{O'Brien!John\textsuperscript{2}|bb} (\Lineage{1}{William}) was born probably in Watergrasshill, County Cork, Ireland,\index{Ireland!Watergrasshill, County Cork} about 1820.\cite{John2OBrienMarriage:1} He died in Boston, Suffolk County, Massachusetts\index{Massachusetts!Boston} on 22 April 1863 of ``phthisis'' \cite{John2OBrienDeath:2}\index{tuberculosis} and is buried in Catholic Mt. Auburn Cemetery, Watertown, Massachusetts.\cite{BillMcEvoy:1}\index{Catholic Mt.\ Auburn Cemetery}\index{Massachusetts!Watertown} He married \MainPerson{Mary Mahoney}\index{Mahoney/Mahony!Mary}\index{O'Brien!Mary (Mahoney)}\index{Bowser!Mary (Mahoney) (O'Brien)} on 20 November 1853 at St.\ Mary's Church,\index{St. Mary's of the Sacred Heart (church)} Boston.\cite{John2OBrienMarriage:3}\index{Massachusetts!Boston} She was born in Ireland\index{Ireland} about 1829--1832 to James or Patrick Mahoney\index{Mahoney/Mahony!James}\index{Mahoney/Mahony!Patrick} and Mary (\_\_\_\_\_) Mahoney.\index{Mahoney/Mahony!Mary (\_\_\_\_\_)}\index{_@Unknown surnames!Mary (mother of Mary Mahoney)}\cite{John2OBrienCivilMarriage:1,MaryMahoneyBowserMarriage:1} After John's death, Mary married Thomas Bowser\index{Bowser!Thomas} in 1867.\cite{MaryMahoneyBowserMarriage:2} Mary died in Somerville, Middlesex County, Massachusetts,\index{Massachusetts!Somerville} on 18 November 1894 of ``apoplexy.''\cite{MaryMahoneyDeath}\index{apoplexy} Mary and Thomas Bowser\index{Bowser!Thomas} are buried with John O'Brien in Catholic Mt. Auburn Cemetery.\cite{BillMcEvoy:2}\index{Catholic Mt.\ Auburn Cemetery}

John\index{O'Brien!John\textsuperscript{2}|bb} arrived in the U.S.\ sometime prior to his marriage to Mary Mahoney\index{Mahoney/Mahony!Mary}\index{O'Brien!Mary (Mahoney)}\index{Bowser!Mary (Mahoney) (O'Brien)} in November 1853. He appears in the 1860 federal census in Boston's North End neighborhood,\index{Massachusetts!Boston!North End} living with wife Mary and four children. Also living with the family was Amelia Rease,\index{Rease!Amelia} age 19, born in Pico W.\ P.\ \cite{Census1860John} (this is probably Pico Island in the Portuguese Azores).\index{Azores} 

John\index{O'Brien!John\textsuperscript{2}|bb} was living at 35 Fleet Street in the North End\index{Massachusetts!Boston!North End}\index{Massachusetts!Boston!Fleet St.} when his son John Joseph\index{O'Brien!John Joseph\textsuperscript{3} (1861--1938)} was born in 1861. His occupation was listed as ``grocer''\cite{John3OBrienBirth:1,Wards:1}\index{grocer} and ``oysterman.''\cite{1861John2OBrien:1}\index{oyster harvesting} John's brother Edward\index{O'Brien!Edward/Edmund\textsuperscript{2}} probably lived next door at 33 Fleet St.,\cite{1861EdwardOBrien}\index{Massachusetts!Boston!Fleet St.} and his son Edward\index{O'Brien!Edward\textsuperscript{3} (1861--1884)} was born at John's address just nine weeks after John's son John Joseph\index{O'Brien!John Joseph\textsuperscript{3} (1861--1938)} was born there.\cite{John3OBrienBirth:3}

\begin{KidsIntro}
	Children of John\textsuperscript{2} O'Brien\index{O'Brien!John\textsuperscript{2}|bb} and Mary (Mahoney) O'Brien,\index{Mahoney/Mahony!Mary}\index{O'Brien!Mary (Mahoney)}\index{Bowser!Mary (Mahoney) (O'Brien)} all born in Boston\index{Massachusetts!Boston} and all except for John Joseph O'Brien\index{O'Brien!John Joseph\textsuperscript{3} (1861--1938)} buried at Catholic Mt.\ Auburn Cemetery,\index{Catholic Mt.\ Auburn Cemetery}\index{Massachusetts!Watertown} Watertown, Middlesex County, Massachusetts:\cite{BillMcEvoy:3}
\end{KidsIntro}

\begin{Kids}
	\KidNum{\ref{per:William3OBrien}}{i.}\KidName{William\textsuperscript{3} O'Brien},\index{O'Brien!William\textsuperscript{3}} b.\ 9 Nov.\ 1854; m.\ 27 Sept.\ 1881, \KidName{Julia T.\ McCarty}.\index{McCarty!Julia T.}\index{O'Brien!Julia T.\ (McCarty)}
	
	\KidNum{}{ii.}\KidName{Mary O'Brien},\index{O'Brien!Mary\textsuperscript{3} (1856--1883)} b.\ 11 Jun.\ 1856;\cite{Mary3OBrienBirth} bap.\ St.\ Stephen (Boston)\index{St. Stephen's (church)}\index{Massachusetts!Boston} 13 June 1856;\cite{Mary3OBrienBaptism} d.\ 18 March 1883.\cite{Mary3OBrienDeath}
	
	\KidNum{}{iii.}\KidName{James Edward O'Brien},\index{O'Brien!James Edward\textsuperscript{3}} b.\ 1 Feb.\ 1858;\cite{James3OBrienBirth} bap.\ St.\ Mary (Boston)\index{St.\ Mary's of the Sacred Heart (church)} 3 Feb.\ 1858;\cite{James3OBrienBaptism} d.\ 11 April 1879. Occupation frame polisher,\index{frame polisher}\index{picture frame manufacturing}\cite{James3OBrienDeath} perhaps working at brother John Joseph's\index{O'Brien!John Joseph\textsuperscript{3} (1861--1938)} frame shop.\index{picture frame manufacturing}
	
	\KidNum{}{iv.}\KidName{Ellen ``Nellie'' O'Brien},\index{O'Brien!Ellen/Nellie\textsuperscript{3} (1859--1882)} b.\ 27 Aug. 1859;\cite{Ellen3OBrien2Baptism:1} bap.\ St.\ Stephen\index{St. Stephen's (church)} 28 Aug. 1859;\cite{Ellen3OBrien2Baptism:2} d.\ 1 Oct.\ 1882.\cite{Ellen3OBrien2Death}
	
	\KidNum{\ref{per:John3OBrien}}{v.}\KidName{John Joseph O'Brien},\index{O'Brien!John Joseph\textsuperscript{3} (1861--1938)} b.\ 29 Jan.\ 1861, m.\ 6 Feb.\ 1890, \KidName{Emma A.\ Mahony}.\index{Mahoney/Mahony!Emma}\index{O'Brien!Emma (Mahony)}
	
	\KidNum{}{vi.}\KidName{Margaret O'Brien},\index{O'Brien!Margaret\textsuperscript{3} (1862--1863)} b.\ 18 May 1862;\cite{Margaret3OBrienBaptism:1} bap.\ St.\ John the Baptist\index{St.\ John the Baptist (church)} 19 May 1862;\cite{Margaret3OBrienBaptism:2} d.\ 23 Oct.\ 1863.\cite{Margaret3OBrienDeath}
	
	\KidNum{}{vii.}\KidName{Anna O'Brien},\index{O'Brien!Anna\textsuperscript{3}} b.\ bet.\ 19 Aug.--18 Sept.\ 1863;\cite{Anna3OBrienDeath:1} d.\ 28 Feb.\ 1866.\cite{Anna3OBrienDeath:2}
	
\end{Kids}