\section{Mary (O'Brien) Ward}\label{per:Mary2OBrien}

\MainPerson{Mary\textsuperscript{2} (O'Brien) Ward}\index{O'Brien!Mary\textsuperscript{2}|bb}\index{Ward!Mary\textsuperscript{2} (O'Brien)} (\Lineage{1}{William}) was born probably in Water\-grass\-hill, Coun\-ty Cork, Ireland,\index{Ireland!Watergrasshill, County Cork} about 1828.{\cite{Mary2OBrienMarriage:1} She died in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 23 March 1908\cite{Mary2OBrienDeath:2} and is buried at Holy Cross Cemetery\index{Holy Cross Cemetery}\index{Massachusetts!Malden} in Malden, Middlesex County, Massachusetts.\cite{CarolGordon:8} She married \MainPerson{David Ward}\index{Ward!David (husband of Mary (O'Brien))} at Holy Cross Church \index{Holy Cross (church)}in Boston\index{Massachusetts!Boston} on 31 October 1850.\cite{Mary2OBrienMarriage:2,Mary2OBrienMarriage2:1} David was born in Mayfield, Fulton County, New York,\index{New York!Mayfield} in 1823\cite{DavidWardObit} to David Ward\index{Ward!David} and Mary A.\ (\_\_\_\_\_) Ward.\index{Ward!Mary (\_\_\_\_\_)}\index{_@Unknown surnames!Mary (mother of David Ward)}\cite{DavidWardDeath:1} He died of cancer\index{cancer} in Boston\index{Massachusetts!Boston} on 19 December 1881.\cite{DavidWardDeath:2}
	
David Ward was not Catholic,\index{Catholicism} but promised to raise his children with Mary\index{O'Brien!Mary\textsuperscript{2}}\index{Ward!Mary\textsuperscript{2} (O'Brien)} as Catholic so that the couple could be married in the Catholic\index{Catholicism}\index{Catholic Church} Church.\cite{Mary2OBrienMarriage2:2} David\index{Ward!David (husband of Mary (O'Brien))} was a cook\index{cook} by trade. He was working at Quincy House\index{Quincy House} in 1876,\cite{DavidWard1876} Maverick House\index{Maverick House} in 1877,\cite{DavidWard1877} and at a saloon\index{saloon} in 1880.\cite{Census1880DavidWard:1} David and Mary purchased the property at 101 Bennington St.\index{Massachusetts!Boston!Bennington St.} in East Boston\index{Massachusetts!Boston!East Boston} for \$2,200 in 1871.\cite{101Bennington:1,101BenningtonMap}

\begin{KidsIntro}
	Children of David Ward\index{Ward!David (husband of Mary (O'Brien))} and Mary\textsuperscript{2} (O'Brien) Ward,\index{O'Brien!Mary\textsuperscript{2}}\index{Ward!Mary\textsuperscript{2} (O'Brien)} all born in Boston:\index{Massachusetts!Boston}
\end{KidsIntro}

\begin{Kids}
	
	\KidNum{}{i.}\KidName{Mary Ann\textsuperscript{3} Ward},\index{Ward!Mary Ann\textsuperscript{3}} b.\ 24 July 1851;\cite{MaryAnn3WardBaptism:1} bap.\ Holy Cross (Boston)\index{Holy Cross (church)} 27 July 1851;\cite{MaryAnn3WardBaptism:2} d.\ 6 Jan.\ 1854.\cite{MaryAnn3WardDeath}
	
	\KidNum{}{ii.}\KidName{Sarah Ward},\index{Ward!Sara\textsuperscript{3}} b.\ 9 Dec.\ 1853;\cite{Sarah3WardBirth} bap.\ Holy Cross\index{Holy Cross (church)} 17 Dec.\ 1853;\cite{Sarah3WardBaptism} d.\ 10 April 1873.\cite{Sarah3WardDeath}
	
	\KidNum{\ref{per:Hannah3Ward}}{iii.}\KidName{Hannah Ward},\index{Ward!Hannah/Hanora\textsuperscript{3}}\index{Flynn!Hannah/Hanora\textsuperscript{3} (Ward)} b.\ 13 Sept.\ 1860; m.\ 23 Sept.\ 1885, \KidName{John J.\ Flynn}.\index{Flynn!John J.}
	
\end{Kids}