\section{Michael O'Brien}

\MainPerson{Michael\textsuperscript{2} O'Brien}\index{O'Brien!Michael\textsuperscript{2}|bb} (\Lineage{1}{William}) was born in Watergrasshill, County Cork, Ireland,\index{Ireland!Watergrasshill, County Cork} on 15 December 1832.\cite{Michael2OBrienNaturalization} He died in Boston, Suffolk County, Massachusetts, on 25 June 1891\cite{Michael2OBrienDeath} and is buried at Holy Cross Cemetery,\index{Holy Cross Cemetery}\index{Massachusetts!Malden} Malden, Middlesex County, Massachusetts.\cite{DianaBerberenaLetter2} 

Michael married, first, \MainPerson{Bridget Colbert}\index{Colbert!Bridget}\index{O'Brien!Bridget (Colbert)} at St. Joseph Church \index{St. Joseph (church)} in Roxbury, Norfolk County, Massachusetts\index{Massachusetts!Roxbury}\index{Massachusetts!Boston!Roxbury} (now part of Boston) on 10 July 1854.\cite{BridgetColbertMarriage,BridgetColbertChurchMarriage} Bridget was born in Ireland\index{Ireland} about 1832 to Patrick\index{Colbert!Patrick} and Ellen (\_\_\_\_\_) Colbert.\index{Colbert!Ellen (\_\_\_\_\_)}\index{_@Unknown surnames!Ellen (mother of Bridget Colbert)}\cite{BridgetColbertMarriage} She died in Boston\index{Massachusetts!Boston} on 21 October 1873\cite{BridgetColbertDeath} and is buried with the family of Michael's brother, John J.\ O'Brien,\index{O'Brien!John Joseph\textsuperscript{3} (1861--1938)} at Catholic Mt.\ Auburn Cemetery,\index{Catholic Mt.\ Auburn Cemetery}\index{Massachusetts!Watertown} Watertown, Middlesex County, Massachusetts.\cite{BillMcEvoy}

Michael married, second, \MainPerson{Mary Field} (aka Mary Feely)\index{Field!Mary}\index{O'Brien!Mary (Field)} at Most Holy Redeemer Church\index{Most Holy Redeemer (church)}\index{Massachusetts!Boston!East Boston} in East Boston on 19 April 1874.\cite{MaryFieldMarriage,MaryFieldChurchMarriage} Mary was born in Ireland\index{Ireland} about 1845\cite{MaryFieldMarriage} to Patrick Field\index{Field!Patrick} and Mary Sheehan.\index{Sheehan!Mary}\index{Field!Mary (Sheehan)}\cite{MaryFieldDeath} She died in Boston\index{Massachusetts!Boston} on 6 January 1915 and was buried at Holy Cross Cemetery.\index{Most Holy Cross Cemetery}\cite{MaryFieldDeath}

Michael\index{O'Brien!Michael\textsuperscript{2}|bb} worked as an oysterman\index{oyster harvesting} and oyster opener.\cite{EdwardFrancis3OBrienBirth,Michael2OBrien1886} In 1871 he purchased the property at 243 Border St.\ in East Boston\index{Massachusetts!Boston!Border St.}\index{Massachusetts!Boston!East Boston} for \$3,600.\cite{243BorderPurchase,243BorderMap} He may have been operating a ferry\index{ferry} service from this waterfront location.\cite{243BorderFerry}

\begin{KidsIntro}
	Children of Michael\textsuperscript{2} O'Brien\index{O'Brien!Michael\textsuperscript{2}|bb} and Bridget (Colbert) O'Brien:\index{Colbert!Bridget}\index{O'Brien!Bridget (Colbert)}
\end{KidsIntro}

\begin{Kids}
	
	\KidNum{}{i.}\KidName{Ellen\textsuperscript{3} ``Nellie'' O'Brien},\index{O'Brien!Ellen/Nellie\textsuperscript{3} (1858--1891)} b.\ bet.\ 2 Jun 1857--1 Jun 1858;\cite{Census1870Ellen3OBrien2,Census1880Ellen3OBrien2} d.\ unk.
	
	\begin{KidsMoreText}
		Very few records are available for Ellen. Her most likely date of birth was 16 July 1857, parents listed as Michael and Bridget, address at 30 Ferry St.\ in Boston.\index{Massachusetts!Boston!Ferry St.}\cite{Ellen3OBrien2Birth} This corresponds with a baptismal record at St.\ John the Baptist Church\index{St. John the Baptist (church)} in Boston on 18 July 1857, parents Michael O'Brien and Bridget Colman.\index{Colman!Bridget|see{Colbert, Bridget}}\cite{Ellen3OBrien2Baptism} ``Colman'' could be a misspelling of ``Colbert.'' Ferry St.\ and St.\ John the Baptist Church place the family near Michael's other siblings in Boston's North End\index{Massachusetts!Boston!East Boston} neighborhood.\cite{Boston1861Map}
		
		No plausible marriage or death records for Ellen have been found. She was alive as of 1891 as she appears on the list of father Michael's heirs in his probate\index{probate} file.\cite{Michael2OBrienProbate}
	\end{KidsMoreText}
	
	\KidNum{}{ii.}\KidName{Mary Ann O'Brien},\index{O'Brien!Mary Ann\textsuperscript{3} (1859--1861)} b.\ 18 Aug.\ 1859;\cite{MaryAnn3OBrien2Birth} d. 10 June 1861.\cite{MaryAnn3OBrien2Death}
	
	\KidNum{\ref{per:Michael3OBrien}}{iii.}\KidName{Michael O'Brien},\index{O'Brien!Michael\textsuperscript{3}} b.\ 24 March 1864; m.\ (1) 4 July 1883, \KidName{Lillian A.\ Allen};\index{Allen!Lillian A.}\index{O'Brien!Lillian A.\ (Allen)} m.\ (2) 13 April 1899, \KidName{Mary A.\ Macdougall}.\index{Macdougall!Mary A.}\index{O'Brien!Mary A.\ (Macdougall)}
	
	\KidNum{\ref{per:Frances3OBrien}}{iv.}\KidName{Frances Elizabeth ``Fannie'' O'Brien},\index{O'Brien!Frances Elizabeth\textsuperscript{3}}\index{Wickens!Frances Elizabeth\textsuperscript{3} (O'Brien)} b.\ 16 Dec.\ 1866; m.\ 1 Jan.\ 1891, \KidName{John B.\ Wickens}.\index{Wickens!John B.}
	
\end{Kids}

\begin{KidsIntro}
	Children of Michael\textsuperscript{2} O'Brien\index{O'Brien!Michael\textsuperscript{2}|bb} and Mary (Field) O'Brien:\index{Field!Mary}\index{O'Brien!Mary (Field)}
\end{KidsIntro}

\begin{Kids}
	
	\KidNum{}{v.}\KidName{Mary\textsuperscript{3} O'Brien},\index{O'Brien!Mary\textsuperscript{3} (1875--1875)} b.\ 10 Nov.\ 1875;\cite{Mary3OBrien2Birth} d.\ 20 Nov.\ 1875.\cite{Mary3OBrien2Death}
	
	\KidNum{}{vi.}\KidName{John Joseph O'Brien},\index{O'Brien!John Joseph\textsuperscript{3} (1876--1881)} b.\ 30 Oct.\ 1876;\cite{John3OBrien2Birth} d.\ 21 Sept.\ 1881.\cite{John3OBrien2Death}
	
	\KidNum{\ref{per:Edward3OBrien}}{vii.}\KidName{Edward Francis O'Brien},\index{O'Brien!Edward Francis\textsuperscript{3} (1879--1929)} b.\ 30 Oct.\ 1879; m.\ 23 June 1909, \KidName{Mary Frances Gill}.\index{Gill!Mary/Marie Frances}\index{O'Brien!Mary/Marie Frances (Gill)}
	
	\KidNum{}{viii.}\KidName{Francis Joseph ``Frank'' O'Brien},\index{O'Brien!Francis Joseph\textsuperscript{3}} b.\ 17 Mar 1883;\cite{Francis3OBrienBirth} bap.\ Most Holy Redeemer (East Boston),\index{Most Holy Redeemer (church)} 18 March 1883;\cite{Francis3OBrienBaptism} d.\ 1 May 1914.\cite{Francis3OBrienDeath}
	
	\begin{KidsMoreText}
		Frank worked first as a gas fitter\cite{Census1900Francis3OBrien}\index{gas fitter} and then was a meter tester\index{meter tester} for the New Bedford Gas \& Edison Light Co.\cite{Francis3OBrienDeath,Francis3OBrien1913}\index{New Bedford Gas \& Edison Light Co.\} He was living at 95 S.\ Sixth St.\ in New Bedford, Bristol County, Massachusetts,\index{Massachusetts!New Bedford} when he died.\cite{Francis3OBrien1913} He never married.\cite{Francis3OBrienDeath}
	\end{KidsMoreText}
	
	\KidNum{}
	
	
\end{Kids}