\begin{thebibliography}{999}
	\addcontentsline{toc}{section}{\bibname}

% Chapter 4: Generation 1

\bibitem{Census1855William:1}
1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 1, p.\ 60 (left side), dwelling [blank], family 549, for William O'Brien in Edward O'Brien household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 29 Mar 2020), Suffolk > Boston Ward 01 > image 33.

\bibitem{William1OBrienDeath:1}
Massachusetts Town and Vital Records, Death Records, 1856, no.\ 4206, William O'Brien; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 29 Mar 2020), Boston > Deaths, 1856 > image 96.

\bibitem{DianaBerberenaLetter1:1}
Diana Berberena, Catholic Cemetery Association of the Archdiocese of Boston, letter to Gavin E.\ O'Brien, dated 27 May 2019. This letter includes burial information for two individuals. William O'Brien, buried 12/30/[1856], age 76 years into O'Brien Family Grave G W124 Range N17 west, owner Edward O'Brien. Mary Ann O'Brien, buried 11/1852, age 1 month, 12 days old.

\bibitem{MarySexton}
Mary Sexton named as mother in death records of her children Michael, Abigail, Ann, and Mary.

\bibitem{WilliamOBrienSearch:1}
``Report on the O'Brien Family,'' Timeline Research Ireland, 28 Jan 2021, report provided to Gavin O'Brien.\\
This research included a search of Tithe Applotment Books for records of a William O'Brien in the parishes of Ardnageehy, Dunbulloge, Killaspugmullane, Kilquane (Barrymore) and Kilshanahan; a search of Valuation Office Books for a person named William O'Brien in the civil parishes of Ardnageehy, Dunbulloge, Killaspugmullane, Kilquane (Barrymore) and Kilshanahan; a search of Griffith's Valuation for the townland of Tinageeragh/Tinageragh for any Brien/O'Brien names; and a search of Griffith's Valuation in Watergrasshill and the Parish of Ardnageehy for John O'Brien.

\bibitem{TenureBook1847:1}
Tenure Book, Parish of Ardnageehy, Townland of Tinageragh, 8 Nov 1847, Lot 50, William Brien.

\bibitem{HouseBook1849}
House Book, Parish of Ardnageehy, Houses in the Town of Watergrasshill, Townland of Tinageragh, 12 Feb 1849, Lot 44, Wm. Brien.

\bibitem{TenureBook1847:2}
Tenure Book, Parish of Ardnageehy, Townland of Tinageragh, 8 Nov 1847, Lot 50, William Brien.

\bibitem{HouseBook1850}
House Book, Parish of Ardnageehy, Townland of Tinageeragh, 9 Sep 1850, Lot 49, William Brien.

\bibitem{WilliamOBrienSearch:2}
``Report on the O'Brien Family,'' Timeline Research Ireland, 28 Jan 2021, report provided to Gavin O'Brien.

\bibitem{Chascay2:2}
Advertisement for the ship Chasca, \textit{Gore's Liverpool General Advertiser}, 1 May 1851, p.\ 2; accessed at the British newspaper collection, database with images, Findmypast (\url{https://search.findmypast.com/search/british-newspapers} : viewed on 11 Nov 2020).\\
The ship \textit{Chasca} departed Liverpool, England, on 11 May 1851 bound for Boston. 
\begin{quote}
	\textit{Will sail on the 11th instant.}\\
	For BOSTON,\\
	The first-class American Ship CHASCA,\\
	G. D. WISE, Commander ;\\
	Burthen per register 658 tons. Boston built, now in her second year, coppered and copper fastened, is a remarkably fast sailer, and will be found a most desirable conveyance.---For freight apply to\\
	PILKINGTON and WILSON.
\end{quote}

\bibitem{Chascay:5}
``Registers of Passengers Arriving in Massachusetts Ports 1848-1891,'' Massachusetts State Archives, HS 3.02 1990X, record of 27 Jun 1851, vessel \textit{Chascay}, entries for Edmund O'Brien and family; accessed at ``Massachusetts, United States Records,'' images, FamilySearch (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-CSVN-998J-W} : viewed on 11 Nov 2020), image 793.\\
On this page the ship name is written as ``Chascay'' but on the previous pages appears as ``Chasca.''

\bibitem{Census1855William:2}
1855 Massachusetts state census, Suffolk Co., pop.\ sch., Boston, p.\ 60 (left side), dwell.\ [blank], fam.\ 549,  William O'Brien.

\bibitem{Wards:1}
City of Boston, Massachusetts, \textit{A Catalogue of the City Councils of Boston, 1822-1890, Roxbury, 1846-1867, Charlestown, 1847-1873 and of the selectmen of Boston, 1634-1822, also of various other town and municipal officers} (City of Boston Printing Department, 1909), 7--40; accessed at \textit{Internet Archive} (\url{https://archive.org/stream/catalogueofcityc00bost} : viewed on 2 Apr 2020).

\bibitem{William1OBrienDeath:2}
Massachusetts Vital Records, Death Records, 1856, no.\ 4206, William O'Brien.

\bibitem{1880CensusAnn}
1880 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 576, East Boston, p. 24, Havre Street, house no.\ 307, dwelling no.\ 153, family no.\ 267, Ann Dailey in household of Edward O'Brian; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 30 Mar 2020), Massachusetts > Suffolk > Boston > 576 > image 24.

\bibitem{Ann2OBrienDeath:1}
Massachusetts Vital Records, Death Records, 1898, no.\ 7910, Ann Dailey; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 29 Mar 2020), \_Pre 1903 > 1898 > image 1832.

\bibitem{Ann2OBrienDeath:2}
Massachusetts Vital Records, Death Records, 1898, no.\ 7910, Ann Dailey.

\end{thebibliography}