\section{William O'Brien and Mary Sexton}\label{per:William1OBrien}

\MainPerson{William\textsuperscript{1} O'Brien}\index{O'Brien!William\textsuperscript{1}|bb} was born probably in County Cork, Ireland,\index{Ireland!County Cork} about 1791.\cite{Census1855William:2} He died in Boston, Massachusetts,\index{Massachusetts!Boston} 28 December 1856,\cite{William1OBrienDeath:1} and was buried at North Cambridge Catholic Cemetery,\index{North Cambridge Catholic Cemetery} Cambridge, Massachusetts.\index{Massachusetts!Cambridge}\cite{DianaBerberenaLetter1:1} He married, likely in County Cork,\index{Ireland!County Cork} \MainPerson{Mary Sexton}.\index{Sexton!Mary\textsuperscript{1}}\index{O'Brien!Mary\textsuperscript{1} (Sexton)}\cite{MarySexton} No further information about Mary\index{Sexton!Mary\textsuperscript{1}}\index{O'Brien!Mary\textsuperscript{1} (Sexton)} is known.

A search of available records in the areas near Watergrasshill shows only one William O'Brien who could potentially be the one in question. This William O'Brien was leasing a house and garden in the townland of Tinageragh (part of the Town of Watergrasshill is located in this townland). He was paying 21 pence per year ground rent to Mary Barry.\cite{TenureBook1847:1} His house measured 29 feet in length, 17 feet in width, and 7 feet in height.\cite{HouseBook1849} The quality designation of ``2B'' indicates that it was a thatched house built with stone or brick and lime mortar, of medium age (between 25--50 years old), slightly decayed, but in good repair. It does not appear that William leased any farmland, so he was likely a tradesman or laborer.\cite{WilliamOBrienSearch:1} 

William appears in Valuation Office records occupying the same property between 1847\cite{TenureBook1847:2} and 1850.\cite{HouseBook1850} He must have departed his property prior to 2 April 1853, when Griffith's Valuation was published, as he is not included in the final valuation.\cite{WilliamOBrienSearch:2} These dates correspond with William O'Brien's known arrival with his family in Boston in 1851.

William\index{O'Brien!William\textsuperscript{1}} left Ireland\index{Ireland} at age 60 with his son Edward,\index{O'Brien!Edward/Edmund\textsuperscript{2}} daughter-in-law Bridget,\index{Linehan/Linnehan!Bridget}\index{O'Brien!Bridget (Linnehan)} daughter Abby,\index{O'Brien!Abigail\textsuperscript{2}}\index{Dooley!Abigail\textsuperscript{2} (O'Brien)} and granddaughters Margaret\index{Dooley!Margaret\textsuperscript{3}}\index{Fernald!Margaret\textsuperscript{3} (Dooley) (Simonds)}\index{Simonds!Margaret\textsuperscript{3} (Dooley)} and Hannah.\index{Dooley!Hannah/Hanora\textsuperscript{3}}\index{Cooney!Hannah/Hanora\textsuperscript{3} (Dooley)} They sailed on the ship \textit{Chasca}\cite{Chascay2:2}\index{Chasca (ship)} from Liverpool, England,\index{England!Liverpool} arriving in Boston\index{Massachusetts!Boston} on 27 June 1851 after a 47-day voyage.\cite{Chascay:5}

In 1855, William\index{O'Brien!William\textsuperscript{1}} was living in Boston's North End\index{Massachusetts!Boston!North End} neighborhood with Edward\index{O'Brien!Edward/Edmund\textsuperscript{2}} and Abby.\index{O'Brien!Abigail\textsuperscript{2}}\index{Dooley!Abigail\textsuperscript{2} (O'Brien)}\cite{Census1855William:3,Wards:1} William's\index{O'Brien!William\textsuperscript{1}} wife Mary\index{Sexton!Mary\textsuperscript{1}}\index{O'Brien!Mary\textsuperscript{1} (Sexton)} does not appear in any census records from this time. She may have died in Ireland\index{Ireland} before 1851.

William\index{O'Brien!William\textsuperscript{1}} lived in Boston\index{Massachusetts!Boston} for five years before dying of ``pleurisy.''\index{pleurisy} He was living at 207 North Street\index{Massachusetts!Boston!North St.} in the North End\index{Massachusetts!Boston!North End} at the time.\cite{William1OBrienDeath:2}

\begin{KidsIntro}
	Children of William\textsuperscript{1} O'Brien\index{O'Brien!William\textsuperscript{1}} and Mary (Sexton) O'Brien,\index{Sexton!Mary\textsuperscript{1}}\index{O'Brien!Mary\textsuperscript{1} (Sexton)} all likely born in Watergrasshill:\index{Ireland!Watergrasshill, County Cork}
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{Ann\textsuperscript{2} O'Brien},\index{O'Brien!Ann\textsuperscript{2}}\index{Dailey!Ann\textsuperscript{2} (O'Brien)} b.\ abt.\ 1813;\cite{1880CensusAnn} d.\ 23 Sept.\ 1898;\cite{Ann2OBrienDeath:1} m.\ \KidName{Michael Dailey}.\index{Dailey!Michael}\cite{Ann2OBrienDeath:2} Unknown if she had any children. She does not appear until the 1880 census, when she was living with her brother Edward.\index{O'Brien!Edward/Edmund\textsuperscript{2}} She may have arrived in the U.S. sometime between 1870--1880. No record of husband Michael Dailey\index{Dailey!Michael} being in the U.S.
	
	\KidNum{\ref{per:Abigail2OBrien}}{ii.}\KidName{Abigail ``Abby'' O'Brien},\index{O'Brien!Abigail\textsuperscript{2}}\index{Dooley!Abigail\textsuperscript{2} (O'Brien)} b.\ abt.\ 1815 or 1825; m.\ \KidName{Michael Dooley}.\index{Dooley!Michael}
	
	\KidNum{\ref{per:John2OBrien}}{iii.}\KidName{John O'Brien},\index{O'Brien!John\textsuperscript{2}} b.\ abt.\ 1820; m.\ 20 Nov.\ 1853, \KidName{Mary Mahoney}.\index{Mahoney/Mahony!Mary}\index{O'Brien!Mary (Mahoney)}
	
	\KidNum{\ref{per:Edward2OBrien}}{iv.}\KidName{Edward O'Brien},\index{O'Brien!Edward/Edmund\textsuperscript{2}} b.\ 10 Oct.\ 1822; m.\ \KidName{Bridget Linnehan}.\index{Linehan/Linnehan!Bridget}\index{O'Brien!Bridget (Linnehan)}
		
	\KidNum{\ref{per:Mary2OBrien}}{v.}\KidName{Mary O'Brien},\index{O'Brien!Mary\textsuperscript{2}}\index{Ward!Mary\textsuperscript{2} (O'Brien)} b.\ abt.\ 1828; m.\ 31 Oct.\ 1850, \KidName{David Ward}.\index{Ward!David (husband of Mary (O'Brien))}
	
	\KidNum{\ref{per:Michael2OBrien}}{vi.}\KidName{Michael O'Brien},\index{O'Brien!Michael\textsuperscript{2}} b.\ 15 Dec.\ 1832; m.\ (1) 10 July 1854, \KidName{Bridget Colbert};\index{Colbert!Bridget}\index{O'Brien!Bridget (Colbert)} m.\ (2) 19 April 1874, \KidName{Mary Field}.\index{Field!Mary}\index{O'Brien!Mary (Field)}\index{Feely, Mary!see {Field, Mary}}
			
\end{Kids}
