\section{Edward Francis O'Brien}

\MainPerson{Edward Francis\textsuperscript{3} O'Brien}\index{O'Brien!Edward Francis\textsuperscript{3} (1879--1929)|textbf} (\Lineage{2}{Michael}, \Lineage{1}{William}) was born in Boston,\index{Massachusetts!Boston} Suffolk County, Massachusetts, on 30 October 1879.\cite{Edward3OBrien2Birth} He died in Concord,\index{Pennsylvania!Concord} Delaware County, Pennsylvania, on 26 August 1929.\cite{Edward3OBrien2Death} He married, in Boston on 23 June 1909, \MainPerson{Mary Frances Gill}\index{Gill!Mary/Marie Frances}\index{O'Brien!Mary/Marie Frances (Gill)} (aka Marie Frances Gill).\cite{Edward3OBrien2Marriage} She was born in Boston on 3 March 1884 to John A.\ Gill\index{Gill!John A.} and Catherine L.\ Howard.\index{Howard!Catherine L.}\index{Gill!Catherine L. (Howard)}\cite{MaryGillBirth,Edward3OBrien2Marriage} She died in Boston on 15 July 1958.\cite{MaryGillDeath,MaryGillDeath2}

In 1910, Edward\index{O'Brien!Edward Francis\textsuperscript{3} (1879--1929)} was living in Hartford,\index{Connecticut!Hartford} Hartford County, Connecticut, and his occupation is listed as foreman\index{foreman}\index{gas company} at a gas company.\cite{Census1910Edward3OBrien} In 1920 he was living in the Jamaica Plain\index{Massachusetts!Boston!Jamaica Plain} neighborhood of Boston, Massachusetts (58 Rockview St.),\index{Massachusetts!Boston!Rockview St.} along with his wife, five children, his sister-in-law Beatrice C.\ Gill,\index{Gill!Beatrice C.} a maid, and a lodger. At the time Edward was working as a water meter reader\index{water meter reader} for the Boston Public Works Department,\index{Boston Public Works Department} a job he began in January 1917.\cite{Edward3OBrienCityEmployee} He was also working as a clerk\index{post office}\index{Massachusetts!Boston!Back Bay} at the Back Bay (Boston) post office.\cite{Edward3OBrien1920}

\begin{KidsIntro}
	Children of Edward Francis\textsuperscript{3} O'Brien\index{O'Brien!Edward Francis\textsuperscript{3} (1879--1929)} and Mary Frances Gill:\index{Gill!Mary/Marie Frances}\index{O'Brien!Mary/Marie Frances (Gill)}
\end{KidsIntro}

\begin{Kids}
	\KidNum{\ref{per:Catherine4OBrien}}{i.}\KidName{Catherine M.\textsuperscript{4} O'Brien},\index{O'Brien!Catherine M.\textsuperscript{4}}\index{MacDonald!Catherine M.\textsuperscript{4} (O'Brien)} b.\ Connecticut,\index{Connecticut} abt.\ 1910; m.\ 1937, \KidName{Frederick A.\ MacDonald}.\index{MacDonald!Frederick A.}
	
	\KidNum{\ref{per:Frances4OBrien}}{ii.}\KidName{Frances Josephine O'Brien},\index{O'Brien!Frances Josephine\textsuperscript{4}}\index{Day!Frances Josephine\textsuperscript{4}} b.\ Somerville,\index{Massachusetts!Somerville} Middlesex Co., Mass., 26 March 1912; m.\ 1942, \KidName{John R.\ Day}.\index{Day!John R.}
	
	\KidNum{}{iii.}\KidName{Walter Gill O'Brien},\index{O'Brien!Walter Gill\textsuperscript{4}} b.\ Boston, 2 June 1914;\cite{Walter4OBrienBirth} d.\ Okinawa,\index{Japan!Okinawa} Japan, 21 June 1945.\cite{Walter4OBrienDeath}
	
	\begin{KidsMoreText}
		Lt.\ Walter Gill O'Brien served in the 6th Marine Division\index{Marines}\index{World War II} and was killed in action at Okinawa.\cite{Walter4OBrienDeath} Before enlisting in the Marine Corps, he graduated from Boston College Law School\index{Boston College Law School} and worked for the Suffolk County Superior Court.\index{Suffolk County Superior Court}\cite{Walter4OBrienPromotion}
	\end{KidsMoreText}
	
	\KidNum{\ref{per:Edward4OBrien}}{iv.}\KidName{Edward Francis O'Brien Jr.},\index{O'Brien!Edward Francis\textsuperscript{4} Jr. (1916--1985)} b.\ Mass., 17 Sept.\ 1916; m.\ Milton,\index{Massachusetts!Milton} Norfolk Co., Mass., 1946, \KidName{Mary A.\ Metivier}.\index{Metivier, Mary A.}\index{O'Brien!Mary A. (Metivier)}
	
	\KidNum{\ref{per:Beatrice4OBrien}}{v.}\KidName{Beatrice Field O'Brien},\index{O'Brien!Beatrice Field\textsuperscript{4}}\index{Brady!Beatrice Field\textsuperscript{4} (O'Brien)} b.\ Boston,\index{Massachusetts!Boston} 11 August 1919; m.\ Boston, 1941, \KidName{John Francis Brady}.\index{Brady!John Francis}
	
	\KidNum{}{vi.}\KidName{Mary Lucia O'Brien},\index{O'Brien!Mary Lucia} b.\ Boston, 14 March 1921;\cite{Mary4OBrienBirth,Mary4OBrienBirth2} d.\ 1 Sept.\ 2011.\cite{Mary4OBrienBirth,Mary4OBrienDeath}
	
	\begin{KidsMoreText}
		From Mary's obituary: ``She was raised in Boston,\index{Massachusetts!Boston} graduated from Notre Dame Academy\index{Notre Dame Academy (Boston)} in Roxbury\index{Massachusetts!Boston!Roxbury} in 1938, Emmanuel College\index{Emmanuel College} in Boston Class of 1942 and received her Master's in education from Boston College\index{Boston College} in 1957. Miss O'Brien worked as a school teacher\index{teacher} 45 years. Mary taught school for the Archdiocese of Boston\index{Archdiocese of Boston}\index{Catholic Church} from 1942-1973 and then in Boston Public Schools\index{Boston Public Schools} and St. Mary's School\index{St.\ Mary's School} in Lynn\index{Massachusetts!Lynn} from 1973 to 1987.''\cite{Mary4OBrienDeath} For a time (probably coinciding with her teaching for the Archdiocese), Mary was known as ``Sr.\ Beatrice Marie, S.N.D.,''\index{Beatrice Marie, Sister|see {O'Brien!Mary Lucia}} being a Sister of Notre Dame de Namur.\index{Sisters of Notre Dame de Namur} \cite{Epilogue,MaryGillDeath} Mary's obituary requested contributions to the Sisters in Everett, Mass.\cite{Mary4OBrienDeath}\index{Massachusetts!Everett}
	\end{KidsMoreText}
	
\end{Kids}