\section{Frances Elizabeth (O'Brien) Wickens}

\MainPerson{Frances Elizabeth\textsuperscript{3} ``Fannie'' O'Brien}\index{O'Brien!Frances Elizabeth\textsuperscript{3}|bb}\index{Wickens!Frances Elizabeth\textsuperscript{3} (O'Brien)|bb} (\Lineage{2}{Michael}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 16 December 1866.\cite{Frances3OBrienBirth} She was baptized at St. Mary Star of the Sea Church\index{St.\ Mary Star of the Sea (church)}\index{Massachusetts!Boston!East Boston} in East Boston.\cite{Frances3OBrienBaptism} She died in Boston on 22 February 1915.\cite{Frances3OBrienDeath} She married, in Boston on 1 January 1891, \MainPerson{John B.\ Wickens}.\index{Wickens!John B.}\cite{JohnWickensMarriage} He was born in Cape Sable Island,\index{Canada!Cape Sable Island, Nova Scotia} Shelburne County, Nova Scotia, Canada, on 12 March 1873\cite{JohnWickensNaturalization} to Charles Wickens\index{Wickens!Charles} and Jane (Smith) Wickens.\index{Wickens!Jane (Smith)}\index{Smith!Jane}\cite{JohnWickensMarriage,JohnWickensMarriage2} He died sometime after 1 November 1916.\cite{JohnWickensMarriage2}

John Wickens's profession is listed as ``mariner,''\index{mariner}\cite{JohnWickensMarriage} ``fireman,''\index{fireman}\cite{JohnWickensNaturalization} and ``marine engineer.''\index{marine engineer}\cite{Census1900JohnWickens} After his wife Frances died, he moved to Washington\index{Washington (state)} state and married Anna M.\ McGunigle.\index{McGunigle!Anna M.}\index{Wickens!Anna M.\ (McGunigle)}\cite{JohnWickensMarriage2} It is unknown where or when he died.

\begin{KidsIntro}
	Children of John B.\ Wickens\index{Wickens!John B.} and Frances E.\ (O'Brien) Wickens:\index{O'Brien!Frances Elizabeth\textsuperscript{3}|bb}\index{Wickens!Frances Elizabeth\textsuperscript{3} (O'Brien)|bb}
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{i.}\KidName{Nellie\textsuperscript{4} Wickens},\index{Wickens!Nellie\textsuperscript{4}} b.\ Boston, 22 July 1893;\cite{Nellie4WickensDeath} d.\ Boston,\index{Massachusetts!Boston} 23 July 1893.\cite{Nellie4WickensDeath}
	
	\KidNum{\ref{per:Edith4Wickens}}{ii.}\KidName{Edith A.\ Wickens},\index{Wickens!Edith A.\textsuperscript{4}}\index{Giguere!Edith A.\textsuperscript{4} (Wickens)} b.\ Boston, 22 July 1894; m.\ Boston, 12 Oct.\ 1913, \KidName{George H.\ Giguere}.\index{Giguere!George Hector}
	
	\KidNum{}{iii.}\KidName{Frederick John Wickens},\index{Wickens!Frederick John\textsuperscript{3}} b.\ Boston,\index{Massachusetts!Boston} 3 Nov.\ 1895;\cite{Frederick4WickensBirth} d.\ Boston, 9 July 1896.\cite{Frederick4WickensDeath}
	
	\KidNum{\ref{per:Albert4Wickens}}{iv.}\KidName{Albert Francis Wickens},\index{Wickens!Albert Francis\textsuperscript{4}} b.\ Boston, 7 May 1898; m.\ New Jersey,\index{New Jersey} 13 June 1922, \KidName{Mary H.\ Schaller}.\index{Schaller!Mary Helen}\index{Wickens!Mary Helen (Schaller)}
	
	\KidNum{\ref{per:Ethel4Wickens}}{v.}\KidName{Ethel Mary Wickens},\index{Wickens!Ethel Mary\textsuperscript{4}}\index{Heuman!Ethel Mary\textsuperscript{4} (Wickens)} b.\ Boston, 17 June 1902; m.\ Wayne Co., Michigan, 20 Sept.\ 1923, \KidName{Harold Edward Heuman}.\index{Heuman!Harold Edward}
	
\end{Kids}