\begin{thebibliography}{999}
	\addcontentsline{toc}{section}{\bibname}
	
% Generation 3

%% Margaret Dooley

\bibitem{Margaret3DooleyBaptism:2}
Watergrasshill \& Glenville Parish (Watergrasshill, Ireland), ``Historical Baptisms from 1836--1901,'' database, ``Margaret Dooly'' baptism, 27 Dec 1840; \textit{Watergrasshill \& Glenville Parish Archives.} \url{http://www.wghparish.ie/index.php/archives/baptisms-1836-1901/easytablerecord/1-baptisms/7008} : viewed on 17 Apr 2019.

\bibitem{Margaret3DooleyDeath}
Margaret E. Fernald obituary, \textit{The Boston Globe}, 2 Mar 1918, p.\ 12; accessed at \textit{Newspapers.com}, database with images (\url{https://bostonglobe.newspapers.com/clip/48493997/obituary-for-margaret-e-fernald/?xid=637} : viewed on 11 Apr 2020).

\bibitem{WilliamSimondsMarriage}
In the 1855 Massachusetts state census, William Simonds and Margaret Dooley were living with their respective families. In 1860, William and Margaret's first child was born (Catharine Simonds). No marriage record can be found in Massachusetts. Another possibility is that they were married in Ireland prior to arriving in the U.S., although Margaret would have been only 15 years old or younger.

\bibitem{RobertFernaldMarriage:2}
Massachusetts Vital Records, marriage records, 1873, no.\ 2971, Robert Fernald and Margaret Simonds; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 11 Apr 2020), \_Up Through 1910 > 1873 > image 983.\\
Margaret's parents' names are incorrectly listed as ``John'' and ``Nancy Dooley.''

\bibitem{Census1855RobertFernald:1}
1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 8, dwelling 575, family 769,for Robert Ireland in George H.\ Ireland household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 11 Apr 2020), Suffolk > Boston Ward 08 > image 54.

\bibitem{Census1855WilliamSimonds}
1855 Massachusetts state census, Suffolk County, population schedule, Boston, ward 1, p. 62 (right side), dwelling 187, family 575,for William Simonds in Nicholas Simonds household; accessed at ``Massachusetts, State Census, 1855,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/4472/} : viewed on 11 Apr 2020), Suffolk > Boston Ward 01 > image 34.

\bibitem{WilliamSimondsDeath}
Boston, Massachusetts Vital Records, death records, 1873, no.\ 2126, William Simons; accessed at ``Massachusetts, Town Clerk, Vital and Town Records, 1626-2001,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-9975-96WP} : viewed on 11 Apr 2020), Suffolk > Boston > Deaths 1871-1873 > image 533.

\bibitem{CatharineSimondsDeath}
Massachusetts Vital Records, death records, 1863, p.\ 124, no.\ 3135, Catharine Simonds (m.n.) Keenan; accessed at ``Massachusetts Deaths, 1841-1915,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:S3HY-68YW-S3} : viewed on 12 Apr 2020), 0960183 (004220473) > image 480.

\bibitem{RobertFernaldMarriage:3}
Massachusetts Vital Records, marriage records, 1873, no.\ 2971, Robert Fernald and Margaret Simonds.

\bibitem{JoannaFernaldDeath}
Newton, Massachusetts Vital Records, death records, 1895, p.\ 336, no.\ 209, Joanna Fernald; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 12 Apr 2020), \_Pre 1903 > 1895 > image 1044.

\bibitem{RobertFernaldDeath:1}
Robert A.\ Fernald obituary, \textit{The Boston Globe}, 15 Jun 1917, p.\ 15; accessed at \textit{Newspapers.com}, database with images (\url{https://www.newspapers.com/clip/33980133/robert-a-fernald-obituary/} : viewed on 11 Apr 2020).

\bibitem{Chascay:9}
``Registers of Passengers Arriving in Massachusetts Ports 1848-1891,'' Massachusetts State Archives, HS 3.02 1990X, record of 27 Jun 1851, vessel \textit{Chascay}, entries for Edmund O'Brien and family; accessed at ``Massachusetts, United States Records,'' images, FamilySearch (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-CSVN-998J-W} : viewed on 11 Nov 2020), image 793.\\
On this page the ship name is written as ``Chascay'' but on the previous pages appears as ``Chasca.''

\bibitem{RobertFernaldDeath:2}
Robert A.\ Fernald obituary, \textit{The Boston Globe}, 15 Jun 1917, p.\ 15.

\bibitem{Census1855RobertFernald:2}
1855 Massachusetts state census, Suffolk Co., pop.\ sch., Boston, dwell.\ 575, fam.\ 769, Robert Ireland.

\bibitem{Census1860RobertFernald}
1860 United States Federal Census, Suffolk County, population schedule, Boston, ward 10, p.\ 186, dwelling 739, family 1432, for Robert Fernald in Joana Fernald household; accessed at ``1860 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7667/} : viewed on 11 Apr 2020), Suffolk > Boston Ward 10 > image 186

\bibitem{Francis4SimondsBirth}
Massachusetts Vital Records, birth records, 1863, no.\ 4335, Francis Simonds; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 11 Apr 2020), \_Up Through 1910 > 1863 > image 780.

\bibitem{Francis4SimondsDeath}
Massachusetts Vital Records, death records, 1865, no.\ 2139, Francis Simonds; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 11 Apr 2020), \_Pre 1903 > 1865 > image 768.

\bibitem{Margaret4SimondsBirth}
Boston, Massachusetts Vital Records, birth records, 1865, no.\ 4421, Margaret Josephine Simons; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 11 Apr 2020), Boston > Births, Marriages and Death > image 55407.

\bibitem{Margaret4SimondsDeath}
Massachusetts Vital Records, death records, 1866, p.\ 77, no.\ 2292, Margaret J.\ Simonds; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 11 Apr 2020), \_Pre 1903 > 1866 > image 687.

\bibitem{Anna4FernaldBirth}
Boston, Massachusetts Vital Records, birth records, 1874, no.\ 2243, Anna Fernald; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 11 Apr 2020), Boston > Births, Marriages and Death > image 56910.

\bibitem{Anna4FernaldDeath}
Massachusetts Vital Records, death records, 1875, no.\ 2910, Anna Fernald; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 11 Apr 2020), \_Pre 1903 > 1875 > image 853.

\bibitem{Leonards}
Matthew Leonard's marriage record states his parents' names as Christopher Leonard and Mary Harford. Agnes (Leonard) Fernald's marriage record states her parents' names also as Christopher Leonard and Mary Harford.

%% William O'Brien

\bibitem{William3OBrienBirth}
Massachusetts Vital Records, birth records, no.\ 2848, William O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 11 Apr 2020), \_Up Through 1910 > 1854 > image 735.

\bibitem{William3OBrienBaptism}
St.\ Mary (Boston) Baptisms, 1850-1858, p.\ 304, William O'Bryen; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/54102/304/1424466134} : viewed on 11 Apr 2020).

\bibitem{William3OBrienDeath:1}
Massachusetts Vital Records, death records, 1889, no.\ 8547, William O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 11 Apr 2020), \_Pre 1903 > 1889 > image 1249.\\
Cause of death: Consumption; Occupation: Property Man; Address: 96 Tyler St.

\bibitem{William3OBrienMarriage}
St. James the Greater (Boston) Marriages, 1874-1884, p. 370, O'Brien and McCarthy marriage; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48717/370/1417008328} : viewed on 22 Aug 2020).

\bibitem{JuliaMcCartyBaptism}
Holy Cross (Boston) Baptisms, vol.\ 10, 1853-1858, p.\ 250, Julia McCarty; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48416/250/1415452885} : viewed on 12 Apr 2020).

\bibitem{JuliaMcCartyDeath:1}
Massachusetts Vital Records, death records, 1888, no.\ 9636, Julia T.\ O'Brien m.n.\ McCarthy; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 11 Apr 2020), \_Pre 1903 > 1888 > image 1270.\\
Cause of death: haemoptysis; address: 16 Somerset St.; parents: Charles and Hannah

\bibitem{PropertyMan}
\textit{Collins English Dictionary -- Complete and Unabridged, 12th Edition 2014.} S.v. ``property man''; accessed at \textit{The Free Dictionary} (\url{https://www.thefreedictionary.com/property+man} : viewed on 12 Apr 2020).

\bibitem{WilliamOBrien1880}
Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1880), p.\ 734, William O'Brien at 82 Hudson St.; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 12 Apr 2020), Massachusetts > Boston > 1880 > Boston, Massachusetts, City Directory, 1880 > image 751.\\
``O'Brien, William, property man, Globe Theatre, bds.\ 82 Hudson''

\bibitem{WilliamOBrien1883}
Sampson, Davenport, and Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, and Company, 1883), p.\ 818, William O'Brien at 82 Hudson St.; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 12 Apr 2020), Massachusetts > Boston > 1883 > Boston, Massachusetts, City Directory, 1883 > image 833.\\
``O'Brien, William, property man, Howard Athenaeum, house 82 Hudson''

\bibitem{William3OBrienProgram}
Howard Athen\ae um, season of 1882--3, program for \textit{Oliver Twist!}, week commencing 8 Jan 1883; in collection ``Howard Athen\ae um Programs, 1847-1892,'' vol.\ 2 1851-1892, call number Lg PN2277 .B67 H68, \textit{Boston Athen\ae um}, viewed by Gavin O'Brien on 22 Sep 2020.

\bibitem{HowardAthenaeum}
``West End Museum Exhibit `The Old Howard Theatre,''' \textit{North End Waterfront}, 17 Sep 2019;  \url{https://northendwaterfront.com/2019/09/west-end-museum-exhibit-the-old-howard-theatre/} : viewed on 12 Apr 2020.

\bibitem{JuliaMcCartyDeath:2}
Massachusetts Vital Records, death records, 1888, no.\ 9636, Julia T.\ O'Brien m.n.\ McCarthy.

\bibitem{William3OBrienDeath:2}
Massachusetts Vital Records, death records, 1889, no.\ 8547, William O'Brien.

\bibitem{WilliamOBrienWill}
Massachusetts Probate Court, Suffolk County, 1889, vol.\ 628, p.\ 13, William O'Brien will; accessed at ``Massachusetts, Wills and Probate Records, 1635-1991,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/9069/} : viewed on 12 Apr 2020), Suffolk > Probate Records, Vol 628-629, 1890 > image 12.

\bibitem{Ellen4OBrienBirth}
Massachusetts Vital Records, birth records, 1885, p.\ 186, no.\ 8330, Ellen Louise O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 12 Apr 2020), \_Up Through 1910 > 1885 > image 1266.\\
Address: 82 Hudson St.

\bibitem{Ellen4OBrienBaptism}
St.\ James the Greater (Boston) Baptisms, 1883-1888, p.\ 249, Helenam Louisam O'Brien; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48713/249/0} : viewed on 12 Apr 2020).

\bibitem{Ellen4OBrienDeath:1}
Nellie L.\ O’Brien obituary, \textit{The Boston Globe}, 16 Jun 1926, p. 10, col. 8; accessed at \textit{Newspapers.com}, database with images (\url{https://bostonglobe.newspapers.com/clip/46645975/the-boston-globe/?xid=637} : viewed on 13 Mar 2020). 

\bibitem{Census1900EllenOBrien}
1900 U.S.\ census, Middlesex County, Massachusetts, population schedule, Enumeration District (ED) 872, Medford, ward 5, sheet 12, dwelling no.\ 226, family no.\ 251, Nellie O'Brien in household of John J.\ O'Brien; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 12 Apr 2020), Massachusetts > Middlesex > Medford Ward 05 > District 0872 > image 24.

\bibitem{Census1910EllenOBrien}
1910 U.S.\ census, Middlesex County, Massachusetts, population schedule, Enumeration District (ED) 928, Medford, ward 2, sheet 7, dwelling no.\ 117, family no.\ 140, Nellie L.\ O'Brien in household of John J.\ O'Brien; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 12 Apr 2020), Massachusetts > Middlesex > Medford Ward 2 > District 0928 > image 13.

\bibitem{Ellen4OBrien1914}
W.\ A.\ Greenough \& Co., compilers, \textit{1914 Medford Directory} (Boston: W.\ A.\ Greenough \& Co., 1914), p.\ 199, Nellie O'Brien; accessed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 12 Apr 2020), Massachusetts > Medford > 1914 > Medford, Massachusetts, City Directory, 1914 > image 197.\\
``O'Brien Nellie removed to Boston''

\bibitem{Ellen4OBrien1919}
Henry M. Meek Publishing Co., compilers, \textit{The Lowell Suburban Directory} (Salem: Henry M. Meek Publishing Co., 1919), p. 302, entry for Nellie L O'Brien; viewed at ``U.S. City Directories, 1822-1995,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 12 Mar 2020), Massachusetts > Lowell > 1919 > Lowell, Massachusetts, City Directory, 1919 > image 230.\\
``O'Brien Nellie L, nurse, S I b do'' [State Infirmary, boards ditto - see abbreviations on p.\ 38, image 26]

\bibitem{Census1920EllenOBrien}
1920 U.S.\ census, Middlesex County, Massachusetts, population schedule, Tewksbury, enumeration district (ED) 471, sheet 2B, institution: State Infirmary, dwelling [blank], family [blank], Nellie L O'Brien; viewed at ``1920 United States Federal Census,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/6061/} : viewed on 12 Mar 2020), Massachusetts > Middlesex > Tewksbury > District 0471 > image 4.

\bibitem{Ellen4OBrien1924}
W. A. Greenough Co., compilers, \textit{1924 Medford Directory} (Boston: W. A. Greenough \& Co., 1924), p.\ 231, entry for Nellie L O'Brien; viewed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 12 Mar 2020), Massachusetts > Medford > 1924 > Medford, Massachusetts, City Directory, 1924 > image 231.

\bibitem{Ellen4OBrienDeath:2}
Nellie L.\ O’Brien obituary, \textit{The Boston Globe}, 16 Jun 1926, p. 10, col. 8.

\bibitem{RutlandHospital}
Grant Welker, ``Rutland is hoping for a large-scale development at the former state hospital,'' \textit{Worcester Business Journal}, 7 Jun 2019;  \url{https://www.wbjournal.com/article/rutland-is-hoping-for-a-large-scale-development-at-the-former-state-hospital} : viewed on 12 Apr 2020.

\bibitem{Ellen4OBrienDeath2:1}
Massachusetts vital records, standard certificate of death for Nellie L.\ O'Brien, 1926, vol.\ 53, p.\ 72, no.\ 438 (stamped).

\bibitem{Ellen4OBrienDeath2:2}
Massachusetts vital records, standard certificate of death for Nellie L.\ O'Brien, 1926, vol.\ 53, p.\ 72, no.\ 438 (stamped).

%% John O'Brien

\bibitem{John3OBrienBirth:4}
Massachusetts Vital Records, birth records, 1861, p.\ 11, no.\ 471, John O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 31 Mar 2020), \_up through 1910 > 1861 > image 909.

\bibitem{John3OBrienBaptism}
St.\ Stephen (Boston) Baptisms, 1854-1862, p.\ 249, John O'Breine; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53641/387/1423783173} : viewed on 12 Apr 2020).\\
Records of St.\ John the Baptist Church are located in the volume for St.\ Stephen's Church; see note on Mary\textsuperscript{3} O'Brien's baptismal citation.

\bibitem{John3OBrienDeath}
John J.\ O'Brien obituary, \textit{The Boston Globe}, 16 May 1938, p.\ 15; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/34912710/obituary_for_john_j_obrien/?xid=637} : viewed on 12 Apr 2020).

\bibitem{John3OBrienBurial:1}
Mt.\ Calvary Cemetery, Boston, Suffolk County, Massachusetts, printout of Mahoney plot (CL1-1-6D) originally given to Michael O'Brien and verified by Gavin O'Brien at the cemetery office, 28 Dec 2018.

\bibitem{John3OBrienMarriage}
Massachusetts Vital Records, marriage records, 1890, p.\ 44, no.\ 775, John J.\ O'Brien and Emma A.\ Mahony; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 12 Apr 2020), \_Up Through 1910 > 1890 > image 1061.

\bibitem{John3OBrienMarriage2}
St. Augustine (South Boston) Marriages, 1868-1899, p.\ 103a, marriage of Jno.\ J.\ OBrien and Emma A.\ Mahoney; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53689/103a/1423874818} : viewed on 22 Aug 2020).

\bibitem{EmmaMahonyBaptism}
Holy Cross (Boston) Baptisms, v.\ 11, 1858-1868, p.\ 362, Emma Mahony; accessed at ``Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/48417/362/1415467410} : viewed on 12 Apr 2020).

\bibitem{EmmaMahonyDeath}
Emma A.\ O'Brien obituary, \textit{Boston Traveler}, 11 July 1950, p.\ 31.

\bibitem{John2OBrienDeath:3}
Massachusetts Vital Records, death records, 1863, p.\ 49, no.\ 1270, John O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 31 Mar 2020), \_Pre 1903 > 1863 > image 756.\\
Cause of death: phthisis.

\bibitem{MaryMahoneyBowserMarriage:3}
Massachusetts Vital Records, marriage records, 1867, no.\ 267, Thomas Bowser and Mary O'Brien; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 31 Mar 2020), \_Up Through 1910 > 1867 > image 743.

\bibitem{ThomasBowser1870}
Sampson, Davenport, \& Co., compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, \& Co., 1870), p.\ 103; accessed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 13 Sep 2020), Massachusetts > Boston > 1870 > Boston, Massachusetts, City Directory, 1870 > image 112.\\
``Bowser Thomas, mariner, house 450 Hanover''

\bibitem{ThomasBowser1876}
Sampson, Davenport, \& Co., compilers, \textit{The Boston Directory} (Boston: Sampson, Davenport, \& Co., 1876), p.\ 121; accessed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 13 Sep 2020), Massachusetts > Boston > 1876 > Boston, Massachusetts, City Directory, 1876 > image 121.\\
``Bowser Thomas, laborer, house 23 Hudson''

\bibitem{Census1910John3OBrien}
1910 U.S. census, Suffolk County, Massachusetts, population schedule, Middlesex County, Medford, Enumeration District (ED) no.\ 928, sheet 7A, dwelling no.\ 117, family no.\ 140, John J O'Brien household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884} : viewed on 29 Nov 2020), Massachusetts > Middlesex > Medford Ward 2 > District 0928 > image 13.

\bibitem{Census1930John3OBrien}
1930 U.S. census, Suffolk County, Massachusetts, population schedule, Middlesex County, Medford, Enumeration District (ED) no.\ 9-313, sheet 12A, dwelling no.\ 191, family no.\ 259, John J O'Brien household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224} : viewed on 29 Nov 2020), Massachusetts > Middlesex > Medford > District 0313 > image 23.

\bibitem{PictureFrameLabel}
``Ephemera collection,'' \textit{Historic New England} (\url{https://www.historicnewengland.org/explore/collections-access/gusn/265637/}: accessed 13 Apr 2020), digital image, ``Label for John J.\ O'Brien, picture frames, 69 Cornhill, Boston, Mass., undated,'' GUSN-265637, reference code EP001.01.091.01.01.003.

\bibitem{Sargent}
Boston tax assessment records for 1881 (ward 7, pt.\ 2, p.\ 280) show a ``Sargent'' who lives at 4 Bolton Pl.\ occupying the property at 69 Cornhill. The tax assessment records for 1883 (ward 7, p.\ 292) show that the same property is now occupied by ``O'Brien'' who lives at 199 Hampden (crossed out) and 59 Hudson (written in pencil). The Boston city directory for 1881 lists a B.\ Ferdinand Sargent, ``picture-frame manuf. 69 Cornhill, house 4 Bolton place, Chsn.'' The 1882 directory lists ''Sargent B.\ Ferdinand, removed to Minnesota.'' 

\bibitem{John3OBrien1916:1}
W. A. Greenough Co., compilers, \textit{1916 Medford Directory} (Boston: W. A. Greenough \& Co., 1916), p.\ 219, entry for John J O'Brien; viewed at ``U.S. City Directories, 1822-1995,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 13 Apr 2020), Massachusetts > Medford > 1916 > Medford, Massachusetts, City Directory, 1916 > image 217.\\
``O'Brien John J picture frame mfr 69 Cornhill B 45 Court''\\
John O'Brien appears in the next available Medford city directory for 1918 with no business or profession listed. In the 1920 census his occupation is listed as ``none.''

\bibitem{John3OBrien1916:2}
W. A. Greenough Co., compilers, \textit{1916 Medford Directory}, p.\ 219, entry for John J O'Brien.

\bibitem{FrameShopFire:1}
``BROKE THROUGH ROOF.'' \textit{The Boston Globe}, 6 Jan 1904, p.\ 8, col.\ 1; accessed at \textit{Newspapers.com}, database with images (\url{https://www.newspapers.com/image/430269059} : viewed on 13 Apr 2020).

\bibitem{Cornhill:1}
Ryan W.\ Owen, ``Cornhill -- Once Boston’s Literary Center, Today Replaced by Government Center,'' \textit{Forgotten New England}, 4 June 2012 (\url{https://forgottennewengland.com/2012/06/04/cornhill-once-bostons-literary-center-today-replaced-by-government-center/} : viewed on 13 Apr 2020).

\bibitem{Cornhill:2}
Owen, ``Cornhill -- Once Boston’s Literary Center, Today Replaced by Government Center,'' \textit{Forgotten New England}.

\bibitem{FrameShopFire:2}
``BROKE THROUGH ROOF.'' \textit{The Boston Globe}, 6 Jan 1904, p.\ 8, col.\ 1.

\bibitem{John3OBrien1916:3}
W. A. Greenough Co., compilers, \textit{1916 Medford Directory}, p.\ 219, entry for John J O'Brien.

\bibitem{John3OBrienBurial:2}
Mt.\ Calvary Cemetery, Boston, Suffolk County, Massachusetts, printout of Mahoney plot (CL1-1-6D).

\bibitem{Mildred4OBrienBirth}
Massachusetts Vital Records, birth records, 1885, p.\ 242, no.\ 10870, Mildred Loretta O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 13 Apr 2020), \_Up Through 1910 > 1890 > image 1514.

\bibitem{Mildred4OBrienDeath}
Massachusetts Vital Records, death records, 1891, p.\ 175, no.\ 4054, Mildred L.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 13 Apr 2020), \_Pre 1903 > 1891 > image 1268.\\
Cause of death: ``Ac.\ Tub.\ Meningitis, 2 days.''

\bibitem{Edward4OBrienBirth}
Massachusetts Vital Records, birth records, 1898, no.\ 210, Edward O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 13 Apr 2020), \_Up Through 1910 > 1898 > image 1511.

\bibitem{Edward4OBrienDeath}
Massachusetts Vital Records, death records, 1898, p.\ 329, no.\ 222, Edward O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 13 Apr 2020), \_Pre 1903 > 1898 > image 1071.\\
Cause of death: ``Pneumonia''

\bibitem{Almyra4OBrienBirth}
Massachusetts Vital Records, birth records, 1901, no.\ 246, Almyra Louise O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 13 Apr 2020), \_Up Through 1910 > 1901 > image 1016.

\bibitem{Almyra4OBrienDeath}
Massachusetts Vital Records, death records, 1902, p.\ 628, no.\ 145, Almira L.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 13 Apr 2020), \_Pre 1903 > 1902 > image 1187.\\
Cause of death: ``Cerebro-spinal Meningitis''

%% Hannah Ward

\bibitem{Hannah3WardBirth}
Massachusetts Vital Records, birth records, 1860, p.\ 80, no.\ 3574, Hannah Ward; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 14 Apr 2020), \_up through 1910 > 1860 > image 979.\\
Salutation St.

\bibitem{Hannah3WardDeath}
Massachusetts Vital Records, Death Records, 1919, p.\ 59, no.\ 559, Hannah Flynn; Massachusetts Archives, Boston.\\
Cause of death: influenza.

\bibitem{Hannah3WardMarriage:1}
Massachusetts Vital Records, marriage records, 1885, p.\ 165, no.\ 2953, John Flynn and Hannah Ward; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 14 Apr 2020), \_up through 1910 > 1885 > image 1033.

\bibitem{Hannah3WardMarriage:2}
Massachusetts Vital Records, marriage records, 1885, p.\ 165, no.\ 2953, John Flynn and Hannah Ward.

\bibitem{JohnJHFlynn}
Massachusetts, Suffolk County Registry of Deeds, vol.\ 3310, p. 501, FLYNN to KRUPP; accessed at \textit{masslandrecords} (\url{https://masslandrecords.com/suffolk/} : viewed on 19 Apr 2020), Search Criteria >  Recorded Land > Unindexed Property Search > Book 3310, Page Number 501.\\
``I, John H.\ Flynn of Boston in the County of Suffolk and Commonwealth of Massachusetts Known as John Flynn and John J Flynn\ldots''

\bibitem{JohnFlynnDeath:1}
John J.\ Flynn obituary, \textit{The Boston Globe}, 10 Apr 1920, p.\ 10; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/48110261/obituary-for-john-j-flynn/?xid=637} : viewed on 19 Apr 2020).

\bibitem{Chascay:10}
``Registers of Passengers Arriving in Massachusetts Ports 1848-1891,'' Massachusetts State Archives, HS 3.02 1990X, record of 27 Jun 1851, vessel \textit{Chascay}, entries for Edmund O'Brien and family.

\bibitem{101Bennington:2}
Massachusetts, Suffolk County Registry of Deeds, 1871, vol.\ 1058, p.\ 125, Hargrave to Ward; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-89Z3-MJ6D} : viewed on 5 Apr 2020), Suffolk > Deeds 1871 vol 1057-1058 > image 496.

\bibitem{Census1880DavidWard:2}
1880 U.S. census, Suffolk County, Massachusetts, population schedule, East Boston, Enumeration District (ED) 576, p.\ 11, dwelling 66, family 121, David Ward household; accessed at ``1880 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6742/} : viewed on 5 Apr 2020), Massachusetts > Suffolk > Boston > 576 > image 11.

\bibitem{Census1910HannahWard:1}
1910 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 1263, Boston city, sheet no.\ 13, dwelling no.\ 126, family no.\ 239, Hannah E Flynn household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 14 Apr 2020), Massachusetts > Suffolk > Boston Ward 01 > District 1163 > image 11.

\bibitem{103BenningtonSt}
Massachusetts, Suffolk County Registry of Deeds, vol.\ 2302, p. 202, Cronan To Flynn; accessed at \textit{masslandrecords} (\url{https://masslandrecords.com/suffolk/} : viewed on 20 Apr 2020), Search Criteria > Recorded Land > Unindexed Property Search > Book 2302, Page Number 202.

\bibitem{MorrisSt}
Massachusetts, Suffolk County Registry of Deeds, 1889, vol.\ 1866, p.\ 417, Cushing et al to Flynn; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-99ZD-P8F7} : viewed on 19 Apr 2020), Suffolk > Deeds 1889 vol 1866 > image 214.

\bibitem{WesleySt}
Massachusetts, Suffolk County Registry of Deeds, 1891, vol.\ 2014, p.\ 294, Cronin to Flynn; accessed at ``Massachusetts Land Records, 1620-1986,’’ database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-89ZD-2K2X} : viewed on 19 Apr 2020), Suffolk > Deeds 1891 vol 2014 > image 154.

\bibitem{HannahWardDirectories}
A review of Boston city directories between 1892 and 1919 shows Hannah and John J.\ Flynn at different addresses for every directory in which they both appear. Beginning in 1910 Hannah was living at 101 Bennington St.\ and John was living at 236 Lexington St.

\bibitem{Census1900HannahWard}
1900 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 1163, Boston - City, sheet no.\ 8, dwelling no.\ 67, family no.\ 106, Hannah Flynn in household of Mary Ward; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 14 Apr 2020), Massachusetts > Suffolk > Boston Ward 01 > District 1163 > image 11.

\bibitem{Census1910HannahWard:2}
1910 U.S. census, Suffolk Co., Mass., pop.\ sch., Boston, sheet 13, dwell.\ 126, fam.\ 239, Hannah E Flynn.

\bibitem{236Lexington}
Massachusetts, Suffolk County Registry of Deeds, vol.\ 3301, p. 454, HARRIGAN Admr.\ to FLYNN.; accessed at \textit{masslandrecords} (\url{https://masslandrecords.com/suffolk/} : viewed on 19 Apr 2020), Search Criteria > Recorded Land > Unindexed Property Search >  Book 3301, Page Number 454.

\bibitem{JohnFlynnDeath:2}
John J.\ Flynn obituary, \textit{The Boston Globe}, 10 Apr 1920, p.\ 10.

\bibitem{236Lexington2}
Massachusetts, Suffolk County Registry of Deeds, vol.\ 4245, p. 352, CLAHANE Admx to EAST BOSTON SAVINGS BANK; accessed at \textit{masslandrecords} (\url{https://masslandrecords.com/suffolk/} : viewed on 18 Apr 2020), Search Criteria > Recorded Land > Unindexed Property Search > Book 4245, Page Number 352.

\bibitem{Hannah3WardMarriage:3}
Massachusetts Vital Records, marriage records, 1885, p.\ 165, no.\ 2953, John Flynn and Hannah Ward.

\bibitem{Harry4FlynnBirth:1}
Boston, Massachusetts Vital Records, birth records, 1889, no.\ 3892, Harry Flynn; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 20 Apr 2020), Boston > Births, Marriages and Death > image 45866.\\
61 Brooks E.B.; parents John J.\ and Hannah E.\ Flynn; father's occupation: bartender

\bibitem{JohnFlynn1889}
Sampson, Murdock, \& Company, compilers, \textit{The Boston Directory} (Boston: Sampson, Murdock, \& Company, 1889), p.\ 471, John J.\ Flynn at 61 Brooks; accessed at ``U.S.\ City Directories, 1822-1995,’’ \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 20 Apr 2020), Massachusetts > Boston > 1889 > Boston, Massachusetts, City Directory, 1889 > image 471.

\bibitem{BropheyLiquors}
Thomas Brophey, advertisement, \textit{The Boston Globe}, 20 May 1889, p.\ 6, Licensed Liquor Dealers; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/image/430849704} : viewed on 20 Apr 2020).

\bibitem{Harry4FlynnBirth:2}
Boston, Massachusetts Vital Records, birth records, 1889, no.\ 3892, Harry Flynn.

\bibitem{Harry4FlynnDeath}
U.S.\ Social Security Administration, \textit{Numerical Identification Files (NUMIDENT), created, 1936 - 2007, documenting the period 1936 - 2007}, File Unit: ``Death Files, 1936 - 2007 (Last Names E through G),'' entry for Harry Flynn, 1967,  SS no.\ 03-114-1019; accessed at \textit{The U.S.\ National Archives and Records Administration} (\url{https://aad.archives.gov/aad/series-description.jsp?s=5057} : viewed on 20 Apr 2020).

\bibitem{Harry4FlynnDraft}
United States, Selective Service System, \textit{World War I Selective Service System Draft Registration Cards, 1917-1918}, card for Harry Joseph Flynn, serial no.\ 502, order no.\ 4014; accessed at ``U.S., World War I Draft Registration Cards, 1917-1918,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6482/} : viewed on 20 Apr 2020), Massachusetts > East Boston C ity > 2 > Draft Card F > image 327.

\bibitem{Census1930HarryFlynn}
1930 U.S. census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 13-388, Boston city (Dorchester), sheet no.\ 9B, dwelling no.\ 81, family no.\ 194, Harry J Flynn in Edward W Clahane household; accessed at ``1930 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/6224/} : viewed on 20 Apr 2020), Massachusetts > Suffolk > Boston (Districts 251-500) > District 0388 > image 18.

%% Michael O'Brien

\bibitem{Michael3OBrienBirth:1}
Massachusetts Vital Records, birth records, 1864, no.\ 868, Michael O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 20 Apr 2020), \_up through 1910 > 1864 > image 719.\\
33 Fleet St.

\bibitem{Michael3OBrienBaptism}
St.\ Stephen (Boston) Baptisms, 1862-1870, p.\ 89, baptism of Michael O'Brien; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/53642/89/1423786289} : viewed on 31 Aug 2020).

\bibitem{Michael3OBrienBirth:2}
Massachusetts Vital Records, birth records, 1864, no.\ 868, Michael O'Brien.

\bibitem{LillianAllenMarriage:1}
Massachusetts Vital Records, marriage records, 1883, no.\ 20, Michael O'Brien and Lillian A.\ Allen; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 20 Apr 2020), \_Up Through 1910 > 1883 > image 795.\\
Michael O'Brien occupation: mill hand. Lillian Allen parents: William and Elizabeth Allen.

\bibitem{LillianAllenMarriage:2}
Massachusetts Vital Records, marriage records, 1883, no.\ 20, Michael O'Brien and Lillian A.\ Allen.

\bibitem{ElizabethAshdownDeath}
Massachusetts vital records, Norwood death records, 1907, no.\ 272 (stamped), no.\ 78 (hand-written), Elizabeth (Ashdown) Allen; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 16 Jul 2020), 1907 > Norwood > image 80.

\bibitem{LillianAllenDeath}
Massachusetts Vital Records, death records, 1891, no.\ 33, Lillian A.\ Allen; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 20 Apr 2020), \_Pre 1903 > 1891 > image 998.\\
Cause of death: congestion of the brain. Residence: Norwood.

\bibitem{MaryMacdougallMarriage:1}
Massachusetts Vital Records, marriage records, 1899, p.\ 86, no.\ 1540, Michael F.\ O'Brien and Mary A.\ Macdougall; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 20 Apr 2020), \_Up Through 1910 > 1899 > image 1493.\\
Michael O'Brien occupation: Moroccodresser. Mary Macdougall occupation: Dressmaker. Mary Macdougall parents: Daniel Macdougall and Mary McLean.

\bibitem{MaryMacdougallMarriage:2}
Massachusetts Vital Records, marriage records, 1899, p.\ 86, no.\ 1540, Michael F.\ O'Brien and Mary A.\ Macdougall.

\bibitem{MaryMacdougallDeath}
Massachusetts Vital Records, \textit{Index to Deaths, 1926-1930, Aabel - Celona}, vol. 81, Mary A (McDougall) Bushen, Boston, 1928, vol.\ 1 p.\ 351; accessed at ``Massachusetts, Death Index, 1901-1980,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3659/} : viewed on 22 Apr 2020), 1926-1930 > Aabel - Celona > image 467.

Mary Macdougall married Wilson Bushen in 1910:\\

Massachusetts Vital Records, marriage records, 1910, p.\ 31, no.\ 692, Wilson Bushen and Mary A.\ O'Brien mn McDougal; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 22 Apr 2020), \_Up Through 1910 > 1910 > image 1862.

\bibitem{MaryMacdougallMarriage:3}
Massachusetts Vital Records, marriage records, 1899, p.\ 86, no.\ 1540, Michael F.\ O'Brien and Mary A.\ Macdougall.

\bibitem{moroccodresser}
United States Bureau of the Census, \textit{Classified Index to Occupations} (Washington, D.C., 1921), p.\ 111; accessed at \textit{Google Books} (\url{https://www.google.com/books/edition/Classified_Index_to_Occupations/31EbAAAAYAAJ} : viewed on 22 Apr 2020).

\bibitem{Michael3OBrienDeath}
Massachusetts Vital Records, death records, 1904, p.\ 355, no.\ 5598, Michael F.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 20 Apr 2020), 1904 > Boston > image 5580.\\
155 London St.\ Occupation: gas meter maker.

\bibitem{LillianAllenMarriage}
Massachusetts Vital Records, marriage records, 1883, no.\ 20, Michael O'Brien and Lillian A.\ Allen; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 20 Apr 2020), \_Up Through 1910 > 1883 > image 795.\\
Michael O'Brien occupation: mill hand. Lillian Allen parents: William and Elizabeth Allen.

\bibitem{Arthur4OBrienBirth}
Massachusetts Vital Records, birth records, 1883, no.\ 45, Arthur Francis O.\ Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 24 Apr 2020), \_up through 1910 > 1883 > image 957.\\
Michael's occupation: tanner.

\bibitem{Arthur4OBrienDeath}
Massachusetts Vital Records, death records, 1904, p.\ 169, no.\ 8111, Arthur O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 24 Apr 2020), 1904 > Boston > image 8063.\\
Cause of death: ``Pul.\ Tuberculosis 10 mos.''; father's occupation: ``Machine Operator.''

\bibitem{Edward4OBrien2Birth}
Massachusetts Vital Records, birth records, 1884, entry 72, Edward William O'Brien; accessed at ``Massachusetts, U.S., Birth Records, 1840-1915,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/5062} : viewed on 11 Feb 2021), \_up through 1910 > 1884 > image 963.

\bibitem{Edward4OBrien2Death}
Massachusetts Vital Records, death records, 1887, entry 3068, Edward F.\ O'Brien; accessed at ``Massachusetts, U.S., Death Records, 1841-1915,'' database with images, Ancestry.com (\url{https://www.ancestry.com/search/collections/2101} : viewed on 11 Feb 2021), \_Pre 1903 > 1887 > image 942.

\bibitem{Edward4OBrien2Death2}
``Run Over and Killed.'' \textit{The Boston Globe}, 25 Apr 1887, p.\ 5; accessed at Newspapers.com (\url{https://www.newspapers.com/clip/33349423/edward-obrien-death/?xid=637} : viewed on 11 Feb 2021).

\bibitem{Elizabeth4OBrienBirth}
Massachusetts Vital Records, birth records, 1886, no.\ 44, Elisabeth O.\ Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 24 Apr 2020), \_up through 1910 > 1886 > image 998.\\
Father's occupation: machinist.

\bibitem{Elizabeth4OBrienDeath}
Massachusetts Vital Records, death records, 1886, no.\ 39, Elisabeth O.Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 24 Apr 2020), \_Pre 1903 > 1886 > image 704.

\bibitem{Frances4OBrienBirth}
Massachusetts Vital Records, birth records, 1901, p.\ 1, no.\ 4, Frances May O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 24 Apr 2020), \_up through 1910 > 1901 > image 1246.

\bibitem{Frances4OBrienDeath}
Massachusetts Vital Records, death records, 1903, p.\ 493, no.\ 10298, Frances L.\ O'Brien; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 24 Apr 2020), 1903 > Boston > image 4188.\\
Cause of death: pneumonia; address: 182 Marion St.

%% Frances O'Brien

\bibitem{Frances3OBrienBirth}
Massachusetts Vital Records, birth records, 1866, no.\ 4054, Frances Elizabeth O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 25 Apr 2020), \_up through 1910 > 1866 > image 847.

\bibitem{Frances3OBrienBaptism}
St. Mary Star of the Sea (East Boston) Baptisms, 1866-1897, p.\ 3, baptism of Frances E.\ O'Brien; accessed at ``Massachusetts: Roman Catholic Archdiocese of Boston Records, 1789-1920,'' database with images, \textit{AmericanAncestors.org} (\url{https://www.americanancestors.org/DB2726/i/56466/3/1425760040} : viewed on 31 Aug 2020).

\bibitem{Frances3OBrienDeath}
Massachusetts Vital Records, death records, 1915, p.\ 290, no.\ 1875, Frances Wickens; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 25 Apr 2020), 1915 > Boston > image 148.\\
Residence: 195 London St.; place of death: E.B.Relief Sta.; cause of death: cholemia.

\bibitem{JohnWickensMarriage:1}
Massachusetts Vital Records, marriage records, 1891, no.\ 177, John B.\ Wickens and Fannie E O'Brien; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 25 Apr 2020), \_Up Through 1910 > 1891 > image 1601.\\
John B.\ Wickens occupation: mariner

\bibitem{JohnWickensNaturalization:1}
John B.\ Wickens, petition for naturalization (1895), no.\ 98, District of Massachusetts; Record Group 85: Records of the Immigration and Naturalization Service, 1787-2004; National Archives at Boston, Waltham, Massachusetts; viewed at ``Massachusetts, State and Federal Naturalization Records, 1798-1950,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2361/} : viewed on 25 Apr 2020), District Court, Massachusetts > Petitions, V 203, 1895 > image 211.\\
Address: 87 Morris Street, East Boston; Occupation: fireman

\bibitem{JohnWickensMarriage:2}
Massachusetts Vital Records, marriage records, 1891, no.\ 177, John B.\ Wickens and Fannie E O'Brien.

\bibitem{JohnWickensMarriage2:1}
Clark County, Washington, Marriage Records, 1916, no.\ 9304, John B.\ Wickens and Anna M.\ McGunigle; accessed at `` Washington, Clark County, marriage records, 1852-2000, 1867-1947,'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3QS7-99DT-3G8Y} : viewed on 25 Apr 2020), Marriage certificates, no. 9101-9550, 1916 > image 357.

\bibitem{JohnWickensMarriage2:2}
Clark County, Washington, Marriage Records, 1916, no.\ 9304, John B.\ Wickens and Anna M.\ McGunigle.

\bibitem{JohnWickensMarriage:3}
Massachusetts Vital Records, marriage records, 1891, no.\ 177, John B.\ Wickens and Fannie E O'Brien.

\bibitem{JohnWickensNaturalization:2}
John B.\ Wickens, petition for naturalization (1895), no.\ 98, District of Massachusetts.

\bibitem{Census1900JohnWickens}
1900 U.S.\ census, Suffolk County, Massachusetts, population schedule, Enumeration District (ED) 1163,  Boston, sheet no.\ 10, dwelling no.\ 119, family no.\ 212, John Wickens household; accessed at ``1900 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7602/} : viewed on 26 Apr 2020), Massachusetts > Suffolk > Boston Ward 01 > District 1163 > image 20.

\bibitem{JohnWickensMarriage2:3}
Clark County, Washington, Marriage Records, 1916, no.\ 9304, John B.\ Wickens and Anna M.\ McGunigle.

\bibitem{Nellie4WickensDeath:1}
Massachusetts Vital Records, Death Records, 1893, p.\ 295, no.\ 6479, Nellie Wickens; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 26 Apr 2020), \_Pre 1903 > 1893 > image 1582.

\bibitem{Nellie4WickensDeath:2}
Massachusetts Vital Records, Death Records, 1893, p.\ 295, no.\ 6479, Nellie Wickens.

\bibitem{Frederick4WickensBirth}
Massachusetts Vital Records, Birth Records, 1895, no.\ 9274, Frederick John Wickens; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 26 Apr 2020), \_up through 1910 > 1895 > image 1950.

\bibitem{Frederick4WickensDeath}
Massachusetts Vital Records, Death Records, 1896, p. 272, no.\ 5983, Frederick J.\ Wickens; accessed at ``Massachusetts, Death Records, 1841-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2101/} : viewed on 26 Apr 2020), \_Pre 1903 > 1896 > image 1667.

%% Edward O'Brien

\bibitem{Edward3OBrien2Birth}
Massachusetts Vital Records, Birth Records, 1879, p.\ 63, no.\ 2830, Edward Francis O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 26 Apr 2020), \_up through 1910 > 1879 > image 934.\\
Address: 243 Border St.; father's occupation: oyster opener.

\bibitem{Edward3OBrien2Death}
Pennsylvania Vital Records, Death Records, 1929, no.\ 82469, Edward F.\ O'Brien; accessed at ``Pennsylvania, Death Certificates, 1906-1967,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5164/} : viewed on 26 Apr 2020), 1929 > 081001-084000 > image 1591.\\
Occupation: clerk; cause of death: chronic myocarditis; place of burial: Jamaica Plains Boston, Aug 28 1919.

\bibitem{Edward3OBrien2Marriage:1}
Massachusetts Vital Records, Marriage Records, 1909, no.\ 3035 , Edward F O'Brien and Marie F Gill; accessed at ``Massachusetts, Marriage Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2511/} : viewed on 26 Apr 2020), \_Up Through 1910 > 1909 > image 1925.\\
Edward O'Brien residence: Hartford, Conn.; occupation: gas meter repairer; Marie Gill's parents: John A Gill and Catherine L Howard.

\bibitem{MaryGillBirth}
Boston, Massachusetts Vital Records, Birth Records, 1884, no.\ 4209, Mary Frances Gill; accessed at ``Massachusetts, Town and Vital Records, 1620-1988,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2495/} : viewed on 26 Apr 2020), Boston > Births, Marriages and Death > image 43226.

\bibitem{Edward3OBrien2Marriage:2}
Massachusetts Vital Records, Marriage Records, 1909, no.\ 3035 , Edward F O'Brien and Marie F Gill.

\bibitem{MaryGillDeath:1}
Marie F.\ (Gill) O'Brien obituary, \textit{The Boston Globe}, 16 Jul 1958, p.\ 46; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/49607498/obituary-for-hn-mn-a-fipwn-war/?xid=637} : viewed on 26 Apr 2020).

\bibitem{MaryGillDeath2}
Massachusetts Vital Records, ``Index to deaths in Massachusetts 1956 - 1960,'' Mary F (Gill) O'Brien; accessed at ``Massachusetts indexes to births and marriages (1841-1920), deaths (1841-1971),'' database with images, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/3:1:3Q9M-CSL5-FSQC-S} : viewed on 26 Apr 2020), Index to deaths Mor-Z 1956-1960 > image 163.

\bibitem{Census1910Edward3OBrien:1}
1910 U.S.\ census, Hartford County, Connecticut, population schedule, Enumeration District (ED) 184, Hartford City, page no.\ 17A, dwelling no.\ 122, family no.\ 277, Edward F.\ O'Brien household; accessed at ``1910 United States Federal Census,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/7884/} : viewed on 27 Apr 2020), Connecticut > Hartford > Hartford Ward 7 > District 0179.

\bibitem{Edward3OBrienCityEmployee}
City of Boston, \textit{Officals and Employees of the City of Boston} (Boston: City of Boston Printing Department, 1920), City Document No.\ 73, p.\ 233, 
entry for Edward F.\ O'Brien; held by Boston City Archives, ``Lists of Officials and Employees'' collection, identifier 2200.009 (\url{https://archives.cityofboston.gov/repositories/2/resources/272} : scanned copy sent by email from Martha Crilly to Gavin O'Brien, 18 Nov 2020).

\bibitem{Edward3OBrien1920}
Sampson \& Murdock Company, compilers, \textit{The Boston Directory} (Boston: Sampson \& Murdock Co., 1920), p.\ 1240, Edward F.\ O'Brien at 58 Rockview J P; accessed at ``U.S. City Directories, 1822-1995,'' \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/2469/} : viewed on 27 Apr 2020), Massachusetts > Boston > 1920 > Boston, Massachusetts, City Directory, 1920 > image 1248.

\bibitem{Walter4OBrienBirth}
Massachusetts Vital Records, Birth Records, 1914, p.\ 398, no.\ 7959, Walter Gill O'Brien; accessed at ``Massachusetts, Birth Records, 1840-1915,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/5062/} : viewed on 26 Apr 2020), 1914 > Boston > image 199.

\bibitem{Walter4OBrienDeath:1}
Lt.\ Walter G.\ O'Brien obituary, \textit{The Boston Globe}, 23 Mar 1949, p.\ 15; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/42657517/obituary/?xid=637} : viewed on 26 Apr 2020).

\bibitem{Walter4OBrienDeath:2}
Lt.\ Walter G.\ O'Brien obituary, \textit{The Boston Globe}, 23 Mar 1949, p.\ 15.

\bibitem{Walter4OBrienPromotion}
``Marine From Milton Made 2d Lieutenant,'' \textit{The Boston Globe}, 1 Feb 1943, p.\ 5; accessed at \textit{Newspapers.com} (\url{https://bostonglobe.newspapers.com/clip/49659036/the-boston-globe/?xid=637} : viewed on 26 Apr 2020).

\bibitem{Mary4OBrienBirth:1}
U.S.\ Social Security Administration, \textit{Death Master File}, entry for Mary L Obrien, 2011; accessed at ``United States Social Security Death Index,'' database, \textit{FamilySearch} (\url{https://www.familysearch.org/ark:/61903/1:1:VHC7-JPQ} : viewed on 27 Apr 2020).

\bibitem{Mary4OBrienBirth2}
Massachusetts Vital Records, \textit{Index to Births, 1921 - 1925, Mikool - Perras}, vol.\ 111, Mary Lucia O'Brien, 1921 vol.\ 1 p.\ 118; accessed at ``Massachusetts, Birth Index, 1860-1970,'' database with images, \textit{Ancestry.com} (\url{https://www.ancestry.com/search/collections/3928/} : viewed on 27 Apr 2020), Births > 1921-1925 > Mikool - Perras > image 366.

\bibitem{Mary4OBrienBirth:2}
U.S.\ Social Security Administration, \textit{Death Master File}, entry for Mary L Obrien, 2011.

\bibitem{Mary4OBrienDeath:1}
Mary L.\ O'Brien obituary, \textit{The Patriot Ledger}, 5 Sep 2011; \textit{GenealogyBank.com} (\url{https://www.genealogybank.com/doc/obituaries/obit/139995AE102675E0-139995AE102675E0} : viewed on 27 Apr 2020).

\bibitem{Mary4OBrienDeath:2}
Mary L.\ O'Brien obituary, \textit{The Patriot Ledger}, 5 Sep 2011.

\bibitem{Epilogue}
Emmanuel College, Class of 1942, \textit{The 1942 Epilogue}, p.\ 152, ``Ex-Members''; Emmanuel College Archives, Cardinal Cushing Library (\url{http://library.emmanuel.edu/archive/content/1942-yearbook} : viewed on 27 Apr 2020).

\bibitem{MaryGillDeath:2}
Marie F.\ (Gill) O'Brien obituary, \textit{The Boston Globe}, 16 Jul 1958, p.\ 46.

\bibitem{Mary4OBrienDeath:3}
Mary L.\ O'Brien obituary, \textit{The Patriot Ledger}, 5 Sep 2011.
	
\end{thebibliography}