\section{Hannah (Ward) Flynn}\label{per:Hannah3Ward}

\MainPerson{Hannah\textsuperscript{3} Ward}\index{Ward!Hannah/Hanora\textsuperscript{3}|bb}\index{Flynn!Hannah/Hanora\textsuperscript{3} (Ward)|bb} (\Lineage{2}{Mary}, \Lineage{1}{William}) was born in Boston,\index{Massachusetts!Boston} Suffolk County, Massachusetts, on 13 September 1860.\cite{Hannah3WardBirth} She died in Boston on 10 January 1919.\cite{Hannah3WardDeath} She married, in Boston on 23 September 1885, \MainPerson{John J.\ Flynn}\index{Flynn!John J.|bb}\cite{Hannah3WardMarriage:1} (aka John H.\ Flynn\cite{JohnJHFlynn}). He was born in Boston about 1861 to James Flynn\index{Flynn!James} and Anna (\_\_\_\_\_) Flynn.\index{Flynn!Anna (\_\_\_\_\_)}\index{_@Unknown surnames!Anna}\cite{Hannah3WardMarriage:2} He died in Boston on 8 April 1920.\cite{JohnFlynnDeath:1}

Hannah arrived in Boston\index{Massachusetts!Boston} on 27 June 1851, traveling with her mother, sister, and other relatives.\cite{Chascay:10}

Hannah spent most of her life at the house originally owned by her parents at 101 Bennington St.\index{Massachusetts!Boston!Bennington St.}\index{Massachusetts!Boston!East Boston} in East Boston.\cite{101Bennington:2} She purchased the adjacent property at 103 Bennington St.\cite{103BenningtonSt} and other East Boston properties on Morris St.\cite{MorrisSt}\index{Massachusetts!Boston!Morris St.} and Wesley St.\cite{WesleySt}\index{Massachusetts!Boston!Wesley St.}

Although they remained married, it does not appear that Hannah and her husband lived together after the birth of their two children.\footnote{A review of Boston city directories between 1892 and 1919 shows Hannah and John J.\ Flynn at different addresses for every directory in which they both appear. Beginning in 1910 Hannah was living at 101 Bennington St.\ and John was living at 236 Lexington St.} In the 1900 census, Hannah is living at 101 Bennington St.\index{Massachusetts!Boston!Bennington St.} with her children and her mother Mary.\index{Ward!Mary\textsuperscript{2} (O'Brien)}\index{O'Brien!Mary\textsuperscript{2}}\cite{Census1900HannahWard} In the 1910 census, she is at the same address, now living with her son Harry,\index{Flynn!Harry Joseph\textsuperscript{4}} her daughter Alice,\index{Flynn!Mary Alice\textsuperscript{4}}\index{Clahane!Mary Alice\textsuperscript{4} (Flynn)} Alice's husband Edward Clahane,\index{Clahane!Edward William (husband of Hannah/Hanora (Flynn))} and her granddaughter, Marion.\index{Clahane!Marion Gertrude\textsuperscript{5}}\cite{Census1910HannahWard:2} Hannah's husband John purchased the property at 236 Lexington St.\index{Massachusetts!Boston!Lexington St.}\index{Massachusetts!Boston!East Boston} in East Boston in 1908 and resided there for the remainder of his life.\cite{236Lexington} After his death, the property passed to Hannah and John's daughter, Mary Alice.\index{Flynn!Mary Alice\textsuperscript{4}}\index{Clahane!Mary Alice\textsuperscript{4} (Flynn)}}\cite{236Lexington2}

John J.\ Flynn was a trader,\index{trader}\cite{Hannah3WardMarriage:3} a bartender,\index{bartender}\cite{Harry4FlynnBirth:1} and a clerk at a liquor dealer.\index{liquor dealer}\cite{JohnFlynn1889}

\begin{KidsIntro}
	Children of John J.\ Flynn and Hannah\textsuperscript{3} (Ward) Flynn:
\end{KidsIntro}

\begin{Kids}
	\KidNum{\ref{per:MaryAlice4Flynn}}{i.}\KidName{Mary Alice\textsuperscript{4} Flynn},\index{Flynn!Mary Alice\textsuperscript{4}}\index{Clahane!Mary Alice\textsuperscript{4} (Flynn)}\index{Flynn!Alice Veronica\textsuperscript{4}|see{Flynn, Mary Alice\textsuperscript{4}}}\index{Clahane!Alice Veronica\textsuperscript{4}|see{Clahane, Mary Alice\textsuperscript{4} (Flynn)}} aka Alice V.\ Flynn, b.\ Boston\index{Massachusetts!Boston} 10 Aug.\ 1886; m. Boston 18 Nov.\ 1908, \KidName{Edward William Clahane}.\index{Clahane!Edward William (husband of Hannah/Hanora (Flynn))}
	
	\KidNum{}{ii.}\KidName{Harry Joseph Flynn},\index{Flynn!Harry Joseph\textsuperscript{4}} b.\ Boston\index{Massachusetts!Boston} 6 June 1889;\cite{Harry4FlynnBirth:2} d.\ Boston 15 Jan.\ 1967;\cite{Harry4FlynnDeath} unm.
	
	\begin{KidsMoreText}
		His WWI\index{World War I} draft card lists his occupation as ``Collector''\index{collector} and employer as ``R.\ H.\ Hinkley \& Co.''\index{R.\ H.\ Hinkley \& Co.} He claimed a draft exemption due to being the main support for both his parents.\cite{Harry4FlynnDraft} In the 1930 census, he was living with his sister and brother-in-law and working as a salesman\index{salesman}\index{advertising} in advertising.\cite{Census1930HarryFlynn}
	\end{KidsMoreText}
	
\end{Kids}