\section{Michael O'Brien}\label{per:Michael3OBrien}

\MainPerson{Michael\textsuperscript{3} O'Brien}\index{O'Brien!Michael\textsuperscript{3}|bb} (\Lineage{2}{Michael}, \Lineage{1}{William}) was born in Boston, Suffolk County, Massachusetts,\index{Massachusetts!Boston} on 24 March 1864.\cite{Michael3OBrienBirth:1} He was baptized at St. Ste\-phen's Church\index{St.\ Stephen's (church)} in Boston.\cite{Michael3OBrienBaptism} He died in Boston on 3 July 1904.\cite{Michael3OBrienBirth:2} 

Michael married, first, in Franklin,\index{Massachusetts!Franklin} Norfolk County, Massachusetts, on 4 July 1883, \MainPerson{Lillian A.\ Allen}.\index{Allen!Lillian A.}\index{O'Brien!Lillian A.\ (Allen)}\cite{LillianAllenMarriage:1} Lillian was born in Sevenoaks,\index{England!Sevenoaks, Kent County} Kent County, England, about 1866 to William Allen\index{Allen!William} and Elizabeth (Ashdown) Allen.\index{Allen!Elizabeth (Ashdown)}\index{Ashdown!Elizabeth}\cite{LillianAllenMarriage:2} She died in Norwood,\index{Massachusetts!Norwood} Norfolk County, Massachusetts, on 2 October 1891.\cite{LillianAllenDeath} 

Michael married, second, in Boston,\index{Massachusetts!Boston} on 13 April 1899, \MainPerson{Mary A.\ Macdougall}.\index{Macdougall!Mary A.}\index{O'Brien!Mary A.\ (Macdougall)}\cite{MaryMacdougallMarriage:1} Mary Macdougall was born in Ingonish,\index{Canada!Ingonish, Nova Scotia} Victoria County, Nova Scotia, Canada, about 1871 to Daniel Macdougall\index{Macdougall!Daniel} and Mary McLean.\index{McLean!Mary}\index{Macdougall!Mary (McLean)}\cite{MaryMacdougallMarriage:2} She died in Boston\index{Massachusetts!Boston} in 1928.\cite{MaryMacdougallDeath}

Michael's\index{O'Brien!Michael\textsuperscript{3}} occupation in 1899 was ``moroccodresser,''\index{moroccodresser}\cite{MaryMacdougallMarriage:3} a job that involves dressing leather in a tannery.\index{leather tanning}\cite{moroccodresser} Michael's death record states his occupation as ``Gas Meter maker.''\cite{Michael3OBrienDeath}\index{gas meter maker} 

\begin{KidsIntro}
	Children of Michael\textsuperscript{3} O'Brien\index{O'Brien!Michael\textsuperscript{3}} and Lillian (Allen) O'Brien:\index{Allen!Lillian A.}\index{O'Brien!Lillian A.\ (Allen)}\cite{LillianAllenMarriage}
\end{KidsIntro}

\begin{Kids}
	
	\KidNum{}{i.}\KidName{Arthur Francis\textsuperscript{4} O'Brien},\index{O'Brien!Arthur Francis\textsuperscript{4}} b.\ Norwood,\index{Massachusetts!Norwood} Norfolk Co., Mass., 2 Oct.\ 1883;\cite{Arthur4OBrienBirth} d.\ Boston, 28 Sept.\ 1904.\cite{Arthur4OBrienDeath}
	
	\KidNum{}{ii.}\KidName{Edward William O'Brien} aka Edward F.\ O'Brien,\index{O'Brien!Edward William\textsuperscript{4} (1884--1887)} b.\ Norwood, 18 Dec.\ 1884;\cite{Edward4OBrien2Birth} d.\ Boston,\index{Massachusetts!Boston} 25 April 1887.\cite{Edward4OBrien2Death}
	
	\begin{KidsMoreText}
		A mention of Edward's death from the \textit{The Boston Globe}: ``Edward O'Brien, aged 2 years, living with his grandfather at 243 Border street,\index{Massachusetts!Boston!East Boston}\index{Massachusetts!Boston!Border St.} East Boston, was run over by Sturtevant's lumber team\index{Sturtevant's lumber} in front of his residence this afternoon, and instantly killed.''\cite{Edward4OBrien2Death2}
	\end{KidsMoreText}
	
	\KidNum{}{iii.}\KidName{Elizabeth O'Brien},\index{O'Brien!Elizabeth} b.\ Norwood,\index{Massachusetts!Norwood} 29 July 1886;\cite{Elizabeth4OBrienBirth} d.\ Norwood, 5 Oct.\ 1886.\cite{Elizabeth4OBrienDeath}
	
\end{Kids}

\begin{KidsIntro}
	Children of Michael\textsuperscript{3} O'Brien\index{O'Brien!Michael\textsuperscript{3}} and Mary A.\ Macdougall:\index{Macdougall!Mary A.}\index{O'Brien!Mary A.\ (Macdougall)}
\end{KidsIntro}

\begin{Kids}
	\KidNum{}{iv.}\KidName{Frances L.\ O'Brien}\index{O'Brien!Frances L.\textsuperscript{4}} aka Frances May O'Brien, b.\ Walpole,\index{Massachusetts!Walpole} Norfolk Co., Mass., 18 Jan.\ 1901;\cite{Frances4OBrienBirth} d.\ Boston, 20 Dec.\ 1903.\cite{Frances4OBrienDeath}
\end{Kids}